### 2022-06-04 src/tex/ms.tex
[showyourwork] first commit

% Define document class
\documentclass[twocolumn]{aastex631}
\usepackage{showyourwork}

% Begin!
\begin{document}

% Title
\title{An open source scientific article}

% Author list
\author{@LiekeVanSon}

% Abstract with filler text
\begin{abstract}
    Lorem ipsum dolor sit amet, consectetuer adipiscing elit. 
    Ut purus elit, vestibulum ut, placerat ac, adipiscing vitae, felis. 
    Curabitur dictum gravida mauris, consectetuer id, vulputate a, magna. 
    Donec vehicula augue eu neque, morbi tristique senectus et netus et. 
    Mauris ut leo, cras viverra metus rhoncus sem, nulla et lectus vestibulum. 
    Phasellus eu tellus sit amet tortor gravida placerat. 
    Integer sapien est, iaculis in, pretium quis, viverra ac, nunc. 
    Praesent eget sem vel leo ultrices bibendum. 
    Aenean faucibus, morbi dolor nulla, malesuada eu, pulvinar at, mollis ac. 
    Curabitur auctor semper nulla donec varius orci eget risus. 
    Duis nibh mi, congue eu, accumsan eleifend, sagittis quis, diam. 
    Duis eget orci sit amet orci dignissim rutrum.
\end{abstract}

% Main body with filler text
\section{Introduction}
\label{sec:intro}

Lorem ipsum dolor sit amet, consectetuer adipiscing elit. 
Ut purus elit, vestibulum ut, placerat ac, adipiscing vitae, felis. 
Curabitur dictum gravida mauris, consectetuer id, vulputate a, magna. 
Donec vehicula augue eu neque, morbi tristique senectus et netus et. 
Mauris ut leo, cras viverra metus rhoncus sem, nulla et lectus vestibulum. 
Phasellus eu tellus sit amet tortor gravida placerat. 
Integer sapien est, iaculis in, pretium quis, viverra ac, nunc. 
Praesent eget sem vel leo ultrices bibendum. 
Aenean faucibus, morbi dolor nulla, malesuada eu, pulvinar at, mollis ac. 
Curabitur auctor semper nulla donec varius orci eget risus. 
Duis nibh mi, congue eu, accumsan eleifend, sagittis quis, diam. 
Duis eget orci sit amet orci dignissim rutrum.

Nam dui ligula, fringilla a, euismod sodales, sollici- tudin vel, wisi. 
Morbi auctor lorem non justo, nam lacus libero, pretium at, lobortis vitae. 
Donec aliquet, tortor sed accumsan bibendum, erat ligula aliquet magna. 
Morbi ac orci et nisl hendrerit mollis, suspendisse ut massa, cras nec ante. 
Pellentesque a nulla cum sociis natoque penatibus et magnis dis parturient. 
Aliquam tincidunt urna, nulla ullamcorper vestibulum turpis. 
Pellentesque cursus luctus mauris \citep{Luger2021}.

\bibliography{bib}

\end{document}

### 2022-06-04 src/tex/ms.tex
working on initial setup

@@
 \usepackage{showyourwork}
+
+\newcommand\aastex{AAS\TeX}
+\newcommand\latex{La\TeX}
+
+\newcommand{\kms}{\ensuremath{\,\rm{km}\,\rm{s}^{-1}}\xspace}
+\newcommand{\Rsun}{\ensuremath{\,\rm{R_\odot}}}
+\newcommand{\Msun}{\ensuremath{\rm{M}_{\odot}}\xspace}
+\newcommand{\Zsun}{\ensuremath{\,\rm{Z}_{\rm \odot}}\xspace}
+\newcommand{\Lsun}{\ensuremath{\,\rm{L}_{\rm \odot}}\xspace}
+\newcommand{\kpc}{\ensuremath{\,\rm{kpc}}\xspace}
+\newcommand{\yr}{\ensuremath{\,\rm{yr}}\xspace}
+\newcommand{\Myr}{\ensuremath{\,\rm{Myr}}\xspace}
+\newcommand{\Gyr}{\ensuremath{\,\rm{Gyr}}\xspace}
+\newcommand{\Mpc}{\ensuremath{\,\rm{Gpc}}\xspace}
+\newcommand{\Gpc}{\ensuremath{\,\rm{Gpc}}\xspace}
+\newcommand{\cGpc}{\ensuremath{\,\rm{cGpc}}\xspace}
+
+% Mass descriptions
+\newcommand{\Mbh}{\ensuremath{\,M_{\rm BH}}\xspace}
+\newcommand{\Mbheen}{\ensuremath{\,M_{\rm BH, 1}}\xspace}
+\newcommand{\Mbhtwee}{\ensuremath{\,M_{\rm BH, 2}}\xspace}
+\newcommand{\MZAMSI}{\ensuremath{M_{\rm ZAMS, 1}}\xspace}
+\newcommand{\MZAMSII}{\ensuremath{M_{\rm ZAMS, 2}}\xspace}
+
+\newcommand{\Mcore}{\ensuremath{M_{\rm core}}\xspace}
+\newcommand{\dMsnI}{\ensuremath{dM_{\rm SN, 1}}\xspace}
+\newcommand{\dMsnII}{\ensuremath{dM_{\rm SN, 2}}\xspace}
+
+\newcommand{\Mco}{\ensuremath{\,M_{\rm CO}}\xspace}
+\newcommand{\Mchirp}{\ensuremath{\,M_{\rm chirp}}\xspace}
+
+% mass ratios
+\newcommand{\qzams}{\ensuremath{q_{\mathrm{ZAMS}} }\xspace}
+\newcommand{\qfinal}{\ensuremath{q_{\mathrm{final}} }\xspace}
+\newcommand{\qBBH}{\ensuremath{q_{\mathrm{BBH}} }\xspace}
+
+\newcommand{\fcore}{\ensuremath{f_{\mathrm{core}} }\xspace}
+
+% SFRD prescriptions and rates
+\newcommand{\tdelay}{\ensuremath{\,t_{\rm delay}}\xspace}
+
+\newcommand{\SFRDzZ}{\ensuremath{\mathcal{S}(Z,z)}\xspace} 
+\newcommand{\SFRDz}{\ensuremath{\mathrm{SFRD}(z)}\xspace} 
+\newcommand{\dPdZ}{\ensuremath{\mathrm{\frac{dP}{dZ}}(Z,z)}\xspace}
+\newcommand{\dpdZ}{\ensuremath{\mathrm{dP/dZ}(Z,z)}\xspace}
+
+\newcommand{\RBBH}{\ensuremath{R_{\mathrm{BBH}}(z)}\xspace}
+
+% Codes etc
+\newcommand{\COMPAS}{{\tt COMPAS}\xspace}
+\newcommand{\python}{{\tt python}\xspace}
+
+\newcommand{\todo}[1]{{\color{purple}\bf{#1}}}
+\newcommand{\SdM}[1]{{\color{pink}\bf{#1}}}
+
+\usepackage{xspace}
+\usepackage{cancel}
+\usepackage{amsmath}
 
@@
 % Title
-\title{An open source scientific article}
+\title{ A convenient, flexible and intuitive analytic expression for the metallicity-dependent cosmic star formation rate  }
 
 % Author list
-\author{@LiekeVanSon}
+
+\correspondingauthor{L.~van Son}
+\email{lieke.van.son@cfa.harvard.edu}
+
+\author[0000-0001-5484-4987]{L.~A.~C.~van~Son}
+\affiliation{Center for Astrophysics $|$ Harvard $\&$ Smithsonian,
+60 Garden St., Cambridge, MA 02138, USA}
+\affiliation{Anton Pannekoek Institute of Astronomy and GRAPPA, Science Park 904, University of Amsterdam, 1098XH Amsterdam, The Netherlands}
+\affiliation{Max Planck Institute for Astrophysics, Karl-Schwarzschild-Str. 1, 85748 Garching, Germany}
+
+ \author[0000-0001-9336-2825]{S. E. de Mink}
+ \affiliation{Max Planck Institute for Astrophysics, Karl-Schwarzschild-Str. 1, 85748 Garching, Germany}
+\affiliation{Anton Pannekoek Institute of Astronomy and GRAPPA, Science Park 904, University of Amsterdam, 1098XH Amsterdam, The Netherlands}
+\affiliation{Center for Astrophysics $|$ Harvard $\&$ Smithsonian, 60 Garden St., Cambridge, MA 02138, USA}
+% %%%%%
+
+ \author[0000-0003-3308-2420]{R. Pakmor}
+ \affiliation{Max Planck Institute for Astrophysics, Karl-Schwarzschild-Str. 1, 85748 Garching, Germany}
+
+\author{et al?}
 
@@
 \begin{abstract}
-    Lorem ipsum dolor sit amet, consectetuer adipiscing elit. 
-    Ut purus elit, vestibulum ut, placerat ac, adipiscing vitae, felis. 
-    Curabitur dictum gravida mauris, consectetuer id, vulputate a, magna. 
-    Donec vehicula augue eu neque, morbi tristique senectus et netus et. 
-    Mauris ut leo, cras viverra metus rhoncus sem, nulla et lectus vestibulum. 
-    Phasellus eu tellus sit amet tortor gravida placerat. 
-    Integer sapien est, iaculis in, pretium quis, viverra ac, nunc. 
-    Praesent eget sem vel leo ultrices bibendum. 
-    Aenean faucibus, morbi dolor nulla, malesuada eu, pulvinar at, mollis ac. 
-    Curabitur auctor semper nulla donec varius orci eget risus. 
-    Duis nibh mi, congue eu, accumsan eleifend, sagittis quis, diam. 
-    Duis eget orci sit amet orci dignissim rutrum.
+New observational facilities are probing star formation and stellar transients and gravitational wave sources at ever increasing redshifts.
+Comparing these observations with predictions from model for stellar populations or the channels for the formation of gravitational wave sources require assumptions for the cosmic starformation rate density and, in particular, how this depends on metallicity.
+Various approaches exist ranging from fully empirical prescriptions to prescriptions that are based on cosmological simulations.
+Both these approaches come with advantages and disadvantages and inherent uncertainties.
+
+To make it easier to produce model predictions we propose a simple analytical prescription that captures the main behavior of the advanced simulations.
+At the same time, the prescription comes with parameters that allow for variations in the overall shape and which can be easily interpreted.
+Our hope is that this expression provides a useful starting point for making predictions and comparison with observations.
 \end{abstract}
@@
 % Main body with filler text
-\section{Introduction}
-\label{sec:intro}
+\section{Introduction \label{sec: intro}}
 
-Lorem ipsum dolor sit amet, consectetuer adipiscing elit. 
-Ut purus elit, vestibulum ut, placerat ac, adipiscing vitae, felis. 
-Curabitur dictum gravida mauris, consectetuer id, vulputate a, magna. 
-Donec vehicula augue eu neque, morbi tristique senectus et netus et. 
-Mauris ut leo, cras viverra metus rhoncus sem, nulla et lectus vestibulum. 
-Phasellus eu tellus sit amet tortor gravida placerat. 
-Integer sapien est, iaculis in, pretium quis, viverra ac, nunc. 
-Praesent eget sem vel leo ultrices bibendum. 
-Aenean faucibus, morbi dolor nulla, malesuada eu, pulvinar at, mollis ac. 
-Curabitur auctor semper nulla donec varius orci eget risus. 
-Duis nibh mi, congue eu, accumsan eleifend, sagittis quis, diam. 
-Duis eget orci sit amet orci dignissim rutrum.
+%opening from Chruslinska & Nelemans. Crucially needed are simple prescriptions
+% 2 ways in which we can tackle this: observationally or theoretically
+% 3 problemen met waarnemingen: 1) high redshift cant see, 2) metallicity measurements 3) xx?
+% Theoretical: issues with illustris 1, here we provide a simple  fit to 
+% give zenodo + data
+% dan een beetje science 
+LIGO/Virgo are revealing double compact object mergers throughout the Universe. These systems originate from largely
+% Er zijn allemaal BBH detecties, super leuk
+% Om de rate te bedenken moeten we niet alleen numbe of meging BBH maar ook SFRD
+% In dit paper geven we een nieuwe SFRD fit
 
-Nam dui ligula, fringilla a, euismod sodales, sollici- tudin vel, wisi. 
-Morbi auctor lorem non justo, nam lacus libero, pretium at, lobortis vitae. 
-Donec aliquet, tortor sed accumsan bibendum, erat ligula aliquet magna. 
-Morbi ac orci et nisl hendrerit mollis, suspendisse ut massa, cras nec ante. 
-Pellentesque a nulla cum sociis natoque penatibus et magnis dis parturient. 
-Aliquam tincidunt urna, nulla ullamcorper vestibulum turpis. 
-Pellentesque cursus luctus mauris \citep{Luger2021}.
+% Er zijn vechillende manieren om een SFRD meer te geven
 
-\bibliography{bib}
+% make 2D grid in z, Z, at each point: 
+% What is delta  = |dModel-dTNG|?
+% plot in 2d the delta
+
+Since the delay time of BBHs can range from Myrs to multiple Gyrs, the birth environment of BBHs varies significantly and we cannot ignore the cosmological (metallicity) evolution of the Universe. 
+The rate of Binary Black Hole (BBH) mergers at different redshifts depends both on the delay time distribution as well as the metallicity dependent star-formation rate density (\SFRDzZ).
+The assumed cosmic star formation rate density (SFRD) will therefore greatly influence the observed rate of double compact object mergers \citep{Neijssel+2019, Chruslinska2019, Boco2020,Broekgaarden+2021a}.
+Moreover, it is the nuclear reactions in massive stars are responsible for the metal enrichment of the Universe at high redshift.
+The birth of massive stars, and their death as BHs are thus inseparable from the evolution of the metallicity distribution of the Universe.
+
+%%  metallicity density distribution %%
+Merging BBHs are found to form more efficiently at low metallicities e.g.
+\citep[e.g.][]{BelczynskiVink2010, Stevenson+2017,Mapelli2017,Chruslinska2019_effectCO}.
+Therefore the assumed metallicity specific star formation rate will in particular have a large impact on the inferred merger rate \citep[e.g.][]{Chruslinska2019,Chruslinska2019_effectCO, Neijssel2019, Broekgaarden+2021a}.
+
+It is difficult to observationally constrain the shape of the metallicity density distribution over redshift (see \cite{Chruslinska2019} for an extensive overview and discussion of relevant observational caveats).
+Traditionally the metallicity density distribution is estimated by combining a mass-metallicity relation (MZ-relation) and a galaxy stellar mass function (GSMF) \citep[see also][]{Chruslinska+2018, Chruslinska2019_effectCO, Broekgaarden+2021a}.
+Another way is to extract the metallicity density fraction from cosmological simulations \citep[e.g.]{Mapelli2017, Schneider+2017}
+Alternatively, one can combine an observed star formation rate, SFR(z), like from \cite{MadauDickinson2014} or \cite{Madau+2017}, and convolve this with some belief about the shape of the metallicity density distribution, such as was was done in \cite{Neijssel+2019}.
+A third option is extract this information from cosmological simulations \citep[e.g.][]{Mapelli+2017,Schneider+2017}.
+In this work we provide a new fit to the \SFRDzZ based on the TNG 100 simulation \citep{Pillepich2018, Weinberger2017}.
+
+Large uncertainties exist in the shape and redshift evolution of both \SFRDz, and  \dpdZ (see e.g.
+\citealt{Chruslinska2019}, \citealt{Boco2021} and \citealt{Chruslinska+2021} for an extended discussion on the metallicity dependent star formation rate density, in light of empirical data).
+
+To construct \SFRDzZ from empirical data, one can estimate \dpdZ by combining observed mass-metallicity relations with galaxy stellar mass functions \citep[see e.g.][]{Chruslinska+2018, Chruslinska2019, Broekgaarden+2021b}.
+Alternatively, one could extract \SFRDzZ directly from cosmological simulations \citep[e.g.][]{Mapelli2017, Briel+2021}.
+
+In this work, we take an approach similar to \citet{Mapelli2017} and \cite{Briel+2021}  but instead of directly extracting the \SFRDzZ from a cosmological simulation we fit analytical representations of \SFRDz and \dpdZ to simulation data.
+
+By adopting an analytical, parametrized form for \SFRDzZ, the large uncertainties in \SFRDzZ can be systematically explored through smoothly varying the parameters that control its shape (cf.~\citealt{Briel+2021}).
+
+Different cosmological simulations produce varying \SFRDzZ which lead to different redshift evolution of the BBH merger rate with redshift.
+\cite{Briel+2021} find that the EAGLE and TNG simulation provide the best \SFRDzZ based on the predicted cosmic rates for electromagnetic and gravitational-wave transients.
+Although we only consider our fit to describe the IllustrisTNG100 simulation and the phenomenological fit from \cite{Neijssel+2019}, our prescription can be easily be updated to fit other observational or simulated data of the metallicity dependent star formation rate density.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Illustris-TNG Cosmological simulations}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+The IllustrisTNG-project considers galaxy formation and evolution through large-scale cosmological hydrodynamical simulations.
+
+\SdM{Insert a description of enrichment and gas recycling. }
+
+They have been shown to reproduce many of the global properties of galaxies and their scaling relations for a representative portion of the Universe \citep[e.g.][]{FirstResTNG_Naiman2018,Torrey+2021,Genel+2018,Hemler+2021}.These simulations are publicly available\footnote{ \url{https://www.tng-project.org/}} \citep{FirstResTNG_Springel2018,FirstResTNG_Marinacci2018, FirstResTNG_Nelson2018,FirstResTNG_Pillepich2018, FirstResTNG_Naiman2018}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{A convenient analytic expression for the metallicity-dependent star formation rate density}
+\label{sec: SFRD}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\label{s: fitting SFRD}
+We assume that the metallicity dependent star formation rate density can be separated into two independent functions \citep[e.g.\ ][]{Langer2006},
+
+\begin{equation}
+\label{eq: SFRD1}
+    \SFRDzZ = \SFRDz \times \dPdZ.
+\end{equation}
+The first term is the star formation rate density, \SFRDz, that is the amount of mass formed in stars per unit time and per unit comoving volume at each redshift.
+The second term, \dpdZ, is a probability density function that expresses what fraction of star formation occurs at which metallicity, at each redshift.
+
+%% SFR(z) %%
+
+% $a=0.02$, $b=1.48$, $c=4.45$ and $d=5.9$ as best fitting parameters,
+\subsection{The metallicity probability density function}
+For the probability distribution of metallicities we draw inspiration from the approach by \citep[e.g.\ ][]{Neijssel+2019} who used a log-normal distribution.
+Unfortunately, this expression does not capture the asymmetry well that we see in the results of the cosmological simulations, which show an extended tail towards low metallicity combined with a very limited tail towards higher metallicity, when plotted as a function of $\log_10 Z$.
+To capture this behavior we adopt a skewed-log-normal distribution instead.
+This is an extension of the normal distribution that introduces an additional shape parameter, $\alpha$, that regulates the skewness \citep{Ohagan+1976}.
+This allows us to more accurately capture the asymmetry in the metallicity distribution at each redshift.
+
+The skewed-log-normal distribution of metallicities is defined as:
+
+\begin{equation}
+\begin{aligned}
+\label{eq: pure log skew}
+\mathrm{\frac{dP}{dZ}}(Z) &= \frac{1}{Z} \times \frac{\rm dP}{{\rm d}\ln Z}  \\
+&= \frac{2}{Z} \times
+    \underbrace { \phi \left(\frac{\ln Z - \xi}{\omega}\right)
+                 }_{(1)}
+    \underbrace {
+                \Phi\left(\alpha \frac{\ln Z - \xi}{\omega} \right)
+                }_{(2)},
+\end{aligned}
+\end{equation}
+
+\noindent where (1) is the standard log-normal distribution, $\phi$,
+%
+\begin{equation}
+\label{eq: log normal and CDF}
+ \phi \left(\frac{\ln Z - \xi}{\omega}\right) \equiv 
+% \underbrace{
+    \frac{1}{\omega \sqrt{2 \pi}} 
+    \exp{
+         \left\{
+            -\frac{1}{2} \left(\frac{\ln Z - \xi}{\omega}\right)^2
+        \right\}
+        }
+  %  }_{(1)} 
+    \end{equation}
+and (2) is the new term that allows for asymmetry, which is equal to the cumulative of the log-normal distribution, $\Phi$,
+    \begin{equation}
+    \begin{array}{cc}
+ \Phi\left(\alpha \frac{\ln Z - \xi}{\omega} \right) &\equiv 
+% \underbrace {
+    \frac{1}{2} 
+    \left( 
+        1 + {\rm erf}
+            \left\{
+%                \frac{ \left(\alpha \frac{\ln(Z) - \xi}{\omega} \right)  }{\sqrt{2}} 
+                \alpha \frac{\ln Z - \xi}{\omega \sqrt{2}}
+            \right\} 
+    \right) \\
+    %}_{(2)}.
+  &=    \frac{1}{2} 
+       \int_{\infty}^{\alpha\left( \frac{\ln Z -\xi}{\omega}\right)}
+       \frac{1}{\sqrt{2\pi}}e^{-t^2/2}dt
+    \end{array}
+\end{equation}
+
+%
+\noindent This introduces three parameters, $\alpha, \omega$ and $\xi$ each of which may depend on redshift.
+The first parameter, $\alpha$, is known as the ``shape''.
+It affects the skewness of the distribution and thus allows for asymmetries between metallicities that are higher and lower than the mean.
+The symmetric log-normal distribution is recovered for $\alpha=0$.
+The second parameter, $\omega$  is known as the ``scale''.
+It provides a measure of the spread in metallicities at each redshift.
+Finally, $\xi$, is known as the ``location'', because this parameter plays a role in setting the mean of the distribution at each redshift.
+
+\paragraph{The location and the mean of the metallicity distribution}
+To obtain a useful expression for the redshift dependence of the ``location'' $\xi(z)$ we first express the expectation value or mean metallicity at a given redshift
+
+\begin{equation}
+ \langle  Z \rangle 
+ = 2 \exp
+        \left( \frac{\xi\,\omega^2}{2} \right)
+         \Phi\left(\beta\, \omega\right)
+ \label{eqn:Zmean}
+\end{equation}
+where $\beta$ is 
+\begin{equation}
+\label{eq: beta}
+\beta = \frac{\alpha}{\sqrt{1 + \alpha^2} }.
+\end{equation}
+
+\noindent For the evolution of the mean metallicity with redshift we follow \cite{Neijssel+2019} and \cite{Langer2006} in assuming that the mean of the probability density function of metallicities evolves with redshift as:
+\begin{equation}
+\label{eq: mean Z}
+    \langle Z \rangle \equiv \mu(z) = \mu_0 \cdot 10^{\mu_z \cdot z},
+\end{equation}
+where $\mu_0
+%= 0.025 
+$ is the mean metallicity at redshift 0, and $\mu_z
+%= -0.048
+$ determines redshift evolution of the location. Equating this to Equation~\ref{eqn:Zmean}, we get an expression for $\xi(z)$,
+
+\begin{equation}
+\label{eq mu z}
+    \xi(z) = -\frac{\omega^2}{2}\, \ln\left(\frac{  \mu_0 \cdot 10^{\mu_z \cdot z} }{2\, \Phi(\beta\, \omega)}  \right).
+\end{equation}
+
+\paragraph{The scale (and variance) of the metallicity distribution}
+
+We will also allow the ``scale'' $w$ also evolves with redshift in a similar manner, 
+\begin{equation}
+\label{eq: sigma z}
+    \omega(z) = \omega_0 \cdot 10^{\omega_z \cdot z}.
+\end{equation}
+where $\omega_0$ is
+%$\omega_0 = 1.125$, 
+the width of the metallicity distribution at $z=0$, and $\omega_z$
+%$\omega_z = 0.048$, 
+the redshift evolution of the scale.
+
+Note that the width, $w(z)$ is not the same as the variance. The variance, $\sigma(z)^2$, can be expressed as
+
+\begin{equation}
+    \sigma(z)^2 = \omega(z)^2 \left( 1 - \frac{2\beta^2}{\pi} \right)
+\end{equation}
+
+\paragraph{Assymetry of the metallicity distribution: $\alpha$}
+We have considered variations where the ``skewness'' $\alpha$ varies with redshift but we did not find very significant improvements compared to the simpler assumption where $\alpha$ is kept constant.
+
+%We allow the mean metallicity and the spread of metallicities to evolve with redshift by allowing the ``location'' $\xi(z)$ and ``scale'' $\omega(z)$ to vary as functions of redshift.
+We have also considered to allow the ``skewness'' to vary with redshift, but we did not find a very significant improvement and we opted to keep this constant.
+
+In summary, Equation~\ref{eq: pure log skew} becomes:
+\begin{equation}
+\label{eq: z log skew}
+\mathrm{\frac{dP}{dZ}}(Z,z) = \frac{2}{Z} \times \phi \left(\frac{\ln Z - \xi(z)}{\omega(z)}\right) \Phi\left(\alpha \frac{\ln Z - \xi(z)}{\omega(z)} \right),
+\end{equation}
+
+\noindent where $\xi(z)$ and $\omega(z)$ are defined in Equations~\ref{eq mu z} and \ref{eq: sigma z} respectively and we have assumed $\alpha$ to be constant.
+
+%, and our fit value for $\alpha = -1.77$. Our set of parameters for \dpdZ is thus:  $\mu_0 = 0.025, \mu_z = -0.048, \sigma_0 = 1.125, \sigma_z = 0.048$ and $\alpha = -1.77$.
+
+\subsection{The overall cosmic star formation rate density}
+For the star formation rate density, we assume the analytical form proposed by \cite{MadauDickinson2014},
+\begin{eqnarray}
+\label{eq: sfr1}
+    \SFRDz  = 
+    \frac{d^2 M_{\rm SFR}}{dt dV_c} (z)= 
+    a \frac{\left(1 + z\right)^b}{1 + \left[ (1 + z)/c \right]^d} \,
+\end{eqnarray}
+in units of $\left[ \Msun \,yr^{-1} \,cMpc^{-3} \right]$.
+This introduces four parameters, $a$ which sets the overal normalisation and which has the same units as \SFRDz and $b,c$ and $d$ which are unitless and which govern the shape of the overal cosmic starformation rate density with redshift.
+
+\subsection{Combined function}
+We combine equations \ref{eq: z log skew} and \ref{eq: sfr1} to form a full metallicity specific starformation rate density (\SFRDzZ).
+We fit for the following nine free parameters $\alpha, \mu_0, \mu_z, \omega_0, \omega_z$, which govern the metallicity dependence and $a,b, c$ and $d$, which set the overall starformation rate.
+
+\section{Analytical fit against Cosmological simulation}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\begin{figure*}
+%\includegraphics[width=\textwidth]{figures/SFRD_FIT_evaluation_compare.pdf}
+%\caption{Fit for SFRD shown against TNG and Neijssel.  \label{fig: fit SFRD}}
+%\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%
+The task we have at hand here is not a standard textbook fitting problem given the specific aims and requirements that we have that are driven by the astrophysical applications we have in mind.
+Qualitatively, our aims are the following.
+Our main aim is to find solution for the free parameters, for which the expression reproduces the overall behavior that is observed in the cosmological simulations.
+For the purposes we have in mind, it will be more important to prioritize fitting the large scale trends, while we are not so interested in smaller scale fluctuations.
+We further prioritize getting the bulk of the cosmic star formation right and are less interested in capturing the behavior in metallicity and redshift bins where the cosmic starformation rate is very low and thus insignificant for the overall picture.
+Finally, we are especially interested in capturing the asymmetry of the metallicity distribution.
+
+There is not one unique procedure that will full fill these criteria.
+After experimenting with different criteria we have adopted the procedure below, which we believe works well for the aims we have in mind.
+
+\subsection{Choices and binning of the data}
+
+We fit our function to the metallicity distribution of the starforming gas in the TNG100 simulation.
+For this we use a binned version of the TNG data $\SFRDzZ_{\rm sim}$.
+We consider metallicities between $Z= -5$ to $\log_{10} Z= 0$ in 30 bins, where we use $Z_i$ to refer to the logarithmic centers of the bins.
+We ignore star formation in metallicities $\log_{10} Z \le -5$ as this only accounts for less than 1\% of the total cosmic starformation rate in these simulations.
+
+We consider bins in redshifts between $z=0$ and $z=10$, with a step size of $dz=0.05$, where $z_j$ refers to the centers of the bins.
+
+\subsection{Optimization function}
+
+To find a solution we use a method based on the sum of the quadratic differences between the simulations and our fit function.
+Using a vanilla $\chi$-squared approach does not serve our purposes very well as it does a poor job in fitting regions where the starformation is very low.
+Using a $\chi$-squared approach on the logarithm of the function instead places far too much weight on trying to fit the starformation rate in regions where the rate is very low or not even significant.
+After experimenting, we find that the following approach gives us satisfactory results.
+
+We first consider a given redshift $z_j$.  For this redshift we compute the sum of the squared residuals between the cosmological simulation and our fit.  
+%
+\begin{equation}
+\label{eq: chisquare}
+    \chi^2 (z_j) \equiv \sum_{Z_i} \left( 
+        \mathcal{S}(Z_i,z_j)_{\rm sim} - 
+        \mathcal{S}(Z_i,z_j)_{\rm fit}\right)^2
+    %chi_square = ((obs - model )**2)/np.sum(model) 
+\end{equation}
+%
+Here, the variable $Z_i$ runs over all redshift bins, but excludes bins where the starformation rate density is lower $10^{-10} \Msun \yr \Mpc^{-3}$ per bin.
+
+Subsequently we sum the $\chi^2 (z_j)$ for all redshift bins $z_j$.
+To ensure that our fit procedure gives sufficient weight to the behavior at all redshifts, we find that we need to introduce a penalization factor to somewhat reduce the contribution of redshifts where the peak of cosmic starformation occurs, while increasing the weight where at redshifts where the overal cosmic starformation rate is lower.
+To achive this we divide $\chi^2 (z_j)$ by the starformation $\sum_{Z_i} \mathcal{S}(Z_i,z_j)$ per redshift bin before adding the contribution of all redshifts.
+Our final expression for the cost function reads
+
+\begin{equation}
+\label{eq: chisquare}
+    \chi  = \sum_{z_j} \frac{ \chi^2 (z_j) } 
+        {\sum_{Z_i} \mathcal{S}(Z_i,z_j)}
+    %chi_square = ((obs - model )**2)/np.sum(model) 
+\end{equation}
+
+We use the \texttt{scipy.optimize.minimize} 
+from SciPy v1.6.3 implementation of the optimized quasi-Newton method of Broyden, Fletcher, Goldfarb, and Shanno (BFGS) \url{http://www.apmath.spbu.ru/cnsa/pdf/monograf/Numerical_Optimization2006.pdf}
+
+With the fit parameters as mentioned above, we find a maximum residual between the model and the TNG100 data of $2.3\cdot 10^{-3} \Msun \yr^{-1} \Mpc^{-3}$ at any given redshift.
+
+Our best fitting parameters are listed in Table \ref{tab: fit params}. With these fit parameters, $\chi^2(z_j)$ is smaller than $2\cdot 10^{-4}$ at any given redshift.
+
+\begin{deluxetable}{cccc}
+\label{tab: fit params}
+\tablecaption{Best fitting parameters for our \SFRDzZ fit to TNG100 data.}
+\tablehead{\colhead{dP/dZ param.} & \colhead{best fit} & \colhead{SFRD(z) param.} & \colhead{best fit} } 
+%% All data must appear between the \startdata and \enddata commands
+\startdata
+$\mu_0$ &  0.025 &  $a$ &  0.02 \\
+$\mu_z$ &  -0.048 &  $b$ &  1.48 \\
+$\alpha_0$ &  -1.767 &  $c$ &  4.45 \\
+$\sigma_0$  & 1.125       &  $d$ &  5.90 \\
+$\sigma_z$ &  0.048 &   \\
+\enddata
+%sf_a_best, sf_b_best, sf_c_best,  sf_d_best = 0.02, 1.48, 4.45, 5.90
+% sf_a =0.01687063881834458, sf_b =1.4834054063851878, sf_c =4.448574027958166, sf_d =5.903964702985274
+
+%muz =-0.048, mu0 =0.025, sigma_0 =1.125, sigma_z =0.048, alpha=-1.767
+% muz =-0.048244647721407255, mu0 =0.024667742078400792, sigma_0 =1.1253850972905333, sigma_z =0.048072863682492945, alpha=-1.7671626767422142
+\end{deluxetable}
+
+\bibliography{my_bib,main_bib}
 

### 2022-06-04 src/scripts/FitComparison_3panelPlot.py
messy but working version of fig 1 added

@@ -1,0 +1,421 @@
+
+import h5py as h5
+import numpy as np
+import pandas as pd
+import matplotlib.pyplot as plt
+import seaborn as sns
+import astropy.units as u
+from astropy import constants as const
+from matplotlib.colors import ListedColormap, LinearSegmentedColormap
+
+from scipy import interpolate
+from scipy.optimize import minimize
+from scipy.optimize import curve_fit
+
+from astropy.cosmology import WMAP9, z_at_value
+from astropy.cosmology import Planck18  as cosmo# Planck 2018
+from astropy.cosmology import z_at_value
+
+from astropy.table import Table, Column
+import os
+
+import paths
+
+import matplotlib
+from pylab import *
+from matplotlib import ticker, cm
+import matplotlib.gridspec as gridspec
+
+def Mchirp(m1, m2):
+    chirp_mass = np.divide(np.power(np.multiply(m1, m2), 3./5.), np.power(np.add(m1, m2), 1./5.))
+    return chirp_mass    
+   
+base_dir    = '/Users/lieke/surfdrive/Documents/RateMassRedshiftEvolution/'
+save_loc    =  base_dir+'/plots/'
+TNGlocation = '/Users/lieke/surfdrive/Documents/CompareCOMPAS/'
+
+############################
+# Custom scripts
+import get_ZdepSFRD as Z_SFRD
+
+
+
+############################
+##PLOT setttings
+from matplotlib import rc
+import matplotlib
+matplotlib.rcParams['mathtext.fontset'] = 'stix'
+matplotlib.rcParams['font.family'] = 'STIXGeneral'
+rc('font',**{'family':'sans-serif','sans-serif':['Helvetica']})
+plt.rc('font', family='serif')
+rc('text', usetex=True)
+fsize, SMALL_SIZE, MEDIUM_SIZE, BIGGER_SIZE = 30,20,20,30
+for obj in ['axes','xtick','ytick']:
+    plt.rc(obj, labelsize=MEDIUM_SIZE)          # controls default text sizes
+for obj in ['figure','axes']:
+    plt.rc(obj, titlesize=BIGGER_SIZE)    # fontsize of the tick labels
+plt.rc('font', size=MEDIUM_SIZE)          # controls default text sizes
+plt.rc('legend', fontsize=SMALL_SIZE)    # legend fontsize
+
+
+
+def Residuals_Zz_plane(obs_lookback = [], obs_metal = [], obs_SFRD = [],
[…]

### 2022-06-04 src/scripts/get_ZdepSFRD.py

@@ -1,0 +1,252 @@
+import h5py as h5
+import numpy as np
+import pandas as pd
+import matplotlib.pyplot as plt
+import seaborn as sns
+import astropy.units as u
+from astropy import constants as const
+from matplotlib.colors import ListedColormap, LinearSegmentedColormap
+
+from scipy import interpolate
+from scipy.optimize import minimize
+from scipy.optimize import curve_fit
+
+from astropy.cosmology import WMAP9, z_at_value
+from astropy.cosmology import Planck18  as cosmo# Planck 2018
+from astropy.cosmology import z_at_value
+
+from astropy.table import Table, Column
+import os
+
+import paths
+
+import matplotlib
+from pylab import *
+from matplotlib import ticker, cm
+import matplotlib.gridspec as gridspec
+
+def Mchirp(m1, m2):
+    chirp_mass = np.divide(np.power(np.multiply(m1, m2), 3./5.), np.power(np.add(m1, m2), 1./5.))
+    return chirp_mass    
+   
+base_dir    = '/Users/lieke/surfdrive/Documents/RateMassRedshiftEvolution/'
+save_loc    =  base_dir+'/plots/'
+TNGlocation = '/Users/lieke/surfdrive/Documents/CompareCOMPAS/'
+
+############################
+# Custom scripts
+import get_ZdepSFRD as Z_SFRD
+
+
+
+# SFR(z) Madau & Dickinson 2014 shape
+
+
+########################################################
+##
+########################################################
+def Madau_Dickinson2014(z, a=0.015, b=2.77, c=2.9, d=5.6):
+    """
+    Args:
+        z             --> [list of floats] List of redshifts at which to calculate things
+        a,b,c,d       --> [floats] values to determine the shape of our SFR
+    
+    Calculates the star-formation rate density as a function of redshift
+    Based on the functional form from Madau & Dickinson 2014
+    default 'Neijssel et al 2019': a=0.01, b=2.77, c=2.9,  d=4.7
+    Madau & Dickinson 2014: a=0.015, b=2.7, c=2.9,  d=5.6
+    Madau & Fragos 2017: a=0.01, b=2.6, c=3.2,  d=6.2
+
+    Returns:
+        SFR(z) in Msun/yr/Mpc^3
+    """
[…]

### 2022-06-07 src/tex/ms.tex
messy but working version of fig 1 added
fixed dependencies so build now works

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure*}
-%\includegraphics[width=\textwidth]{figures/SFRD_FIT_evaluation_compare.pdf}
-%\caption{Fit for SFRD shown against TNG and Neijssel.  \label{fig: fit SFRD}}
-%\end{figure*}
+\begin{figure*}
+\script{FitComparison_3panelPlot.py}
+\includegraphics[width=\textwidth]{figures/SFRD_FIT_evaluation_compare.pdf}
+\caption{Fit for SFRD shown against TNG and Neijssel.  \label{fig: fit SFRD}}
+\end{figure*}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 Qualitatively, our aims are the following.
-Our main aim is to find solution for the free parameters, for which the expression reproduces the overall behavior that is observed in the cosmological simulations.
-For the purposes we have in mind, it will be more important to prioritize fitting the large scale trends, while we are not so interested in smaller scale fluctuations.
-We further prioritize getting the bulk of the cosmic star formation right and are less interested in capturing the behavior in metallicity and redshift bins where the cosmic starformation rate is very low and thus insignificant for the overall picture.
+Our main aim is to find solution for the free parameters, for which the expression reproduces the overall behaviour that is observed in the cosmological simulations.
+For the purposes we have in mind, it will be more important to prioritise fitting the large scale trends, while we are not so interested in smaller scale fluctuations.
+We further prioritise getting the bulk of the cosmic star formation right and are less interested in capturing the behaviour in metallicity and redshift bins where the cosmic starformation rate is very low and thus insignificant for the overall picture.
 Finally, we are especially interested in capturing the asymmetry of the metallicity distribution.
@@
 
-\subsection{Optimization function}
+\subsection{Optimisation function}
 
@@
 Subsequently we sum the $\chi^2 (z_j)$ for all redshift bins $z_j$.
-To ensure that our fit procedure gives sufficient weight to the behavior at all redshifts, we find that we need to introduce a penalization factor to somewhat reduce the contribution of redshifts where the peak of cosmic starformation occurs, while increasing the weight where at redshifts where the overal cosmic starformation rate is lower.
-To achive this we divide $\chi^2 (z_j)$ by the starformation $\sum_{Z_i} \mathcal{S}(Z_i,z_j)$ per redshift bin before adding the contribution of all redshifts.
+To ensure that our fit procedure gives sufficient weight to the behaviour at all redshifts, we find that we need to introduce a penalisation factor to somewhat reduce the contribution of redshifts where the peak of cosmic starformation occurs, while increasing the weight where at redshifts where the overal cosmic starformation rate is lower.
+To achieve this we divide $\chi^2 (z_j)$ by the starformation $\sum_{Z_i} \mathcal{S}(Z_i,z_j)$ per redshift bin before adding the contribution of all redshifts.
 Our final expression for the cost function reads
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Effect on the local mass distribution of BBH mergers}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}
+\script{Plot_Mass_distributions.py}
+\includegraphics[width=\textwidth]{figures/SFRD_variations_combined.pdf}
+\caption{The effects of several variations in the SFRD  \label{fig: mass dists}}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \bibliography{my_bib,main_bib}

### 2022-06-07 src/scripts/FitComparison_3panelPlot.py

@@ -1,7 +1,6 @@
 
 import h5py as h5
 import numpy as np
-import pandas as pd
 import matplotlib.pyplot as plt
 import seaborn as sns
 import astropy.units as u
@@ -16,7 +15,7 @@ from astropy.cosmology import WMAP9, z_at_value
 from astropy.cosmology import Planck18  as cosmo# Planck 2018
 from astropy.cosmology import z_at_value
 
-from astropy.table import Table, Column
+# from astropy.table import Table, Column
 import os
 
 import paths

### 2022-06-07 src/scripts/MassDistHelperFunctions.py

@@ -4,7 +4,7 @@ import numpy as np
 import h5py as h5
 import os
 
-from astropy.table import vstack, Table, Column
+from astropy.table import Table
 import astropy.units as u
 from astropy import constants as const
 

### 2022-06-07 src/scripts/Plot_Mass_distributions.py

@@ -1,0 +1,380 @@
+"""
+
+# Plotting the BH mass distribution for several SFRD Z-distribution variations
+
+
+
+"""
+
+
+import sys
+import numpy as np
+import matplotlib.pyplot as plt
+
+import seaborn as sns
+from scipy import stats
+
+import h5py
+from astropy.table import Table
+import astropy.units as u
+from astropy import constants as const
+
+# Chosen cosmology 
+from astropy.cosmology import WMAP9 as cosmo
+from astropy.cosmology import z_at_value
+
+import json
+import argparse
+
+# My own helper funcitons:
+import importlib
+import MassDistHelperFunctions as mfunc
+importlib.reload(mfunc)
+
+import gc
+
+
+######################################
+## locations
+save_loc    =  '/Users/lieke/surfdrive/Documents'+'/SFRD_fit/src/tex/figures/' #/n/home04/lvanson/
+data_dir    = '/Volumes/StorageSpac'+'/CompasOutput/v02.19.04/SFRD_fit_data/fWR1.0coolWind1.0/output/' # '/n/holystore01/LABS/hernquist_lab/Users/lvanson/'
+
+
+######################################
+## PLOT setttings
+plt.rc('font', family='serif')
+from matplotlib import rc
+import matplotlib
+matplotlib.rcParams['mathtext.fontset'] = 'stix'
+matplotlib.rcParams['font.family'] = 'STIXGeneral'
+rc('font',**{'family':'sans-serif','sans-serif':['Helvetica']})
+rc('text', usetex=True)
+fsize, SMALL_SIZE, MEDIUM_SIZE, BIGGER_SIZE = 30,25,25,30
+for obj in ['axes','xtick','ytick']:
+    plt.rc(obj, labelsize=MEDIUM_SIZE)          # controls default text sizes
+for obj in ['figure','axes']:
+    plt.rc(obj, titlesize=BIGGER_SIZE)    # fontsize of the tick labels
+plt.rc('font', size=MEDIUM_SIZE)          # controls default text sizes
+plt.rc('legend', fontsize=SMALL_SIZE)    # legend fontsize
+
+
+
+
+######################################
+# Distribution plot function
+######################################
+def plot_mass_distribution(sim_dir = '', x_key = 'M_moreMassive', rate_keys = ['Rates_mu00.025_muz-0.05_alpha-1.77_sigma0%s_sigmaz0.05_zBinned'%(x) for x in [0.8, 1.125, 1.4]],
[…]

### 2022-06-07 src/scripts/get_ZdepSFRD.py

@@ -15,7 +15,7 @@ from astropy.cosmology import WMAP9, z_at_value
 from astropy.cosmology import Planck18  as cosmo# Planck 2018
 from astropy.cosmology import z_at_value
 
-from astropy.table import Table, Column
+# from astropy.table import Table, Column
 import os
 
 import paths

### 2022-06-08 src/scripts/FitComparison_3panelPlot.py
integrating overleaf

@@ -111,8 +111,8 @@ def three_panel_SFRD_plot(obs_SFRD = [], mu0=0.025, muz=-0.49,alpha = -1.77, sig
     fit_values_string = r'$\mathrm{log-skew-normal}$'+'\n'+\
                     r'$\mu_0=%s,$'%(np.round(mu0_best,3)) +'\n'+\
                     r'$\mu_z=%s,$'%(np.round(muz_best,3)) +'\n'+\
-                    r'$\sigma_0=%s,$'%(np.round(sigma0_best,3)) +'\n'\
-                    r'$\sigma_z=%s,$'%(np.round(sigmaz_best,3)) +'\n'\
+                    r'$\omega_0=%s,$'%(np.round(sigma0_best,3)) +'\n'\
+                    r'$\omega_z=%s,$'%(np.round(sigmaz_best,3)) +'\n'\
                     r'$a_0=%s$'%(np.round(alpha0_best,3))
 
     SFR_fit_string = r'$\mathrm{Star \ formation \ rate}$'+'\n'+\
@@ -321,7 +321,6 @@ def three_panel_SFRD_plot(obs_SFRD = [], mu0=0.025, muz=-0.49,alpha = -1.77, sig
     ##################################################################################
     print('!!!! Obs_redshifts', np.round(Obs_redshifts,2) )
     redshifts_to_plot = [0,0.2, 0.5, 1, 2.01, 3.52, 5.3, 8.68]
-    # redsfift_indces = [0,5,10,20, 40, 60,120,160]#[0,8,15,32, 50, 100, 150, 170]#
     redshift_indces   = [np.where(np.round(Obs_redshifts,2) == x)[0][0] for x in redshifts_to_plot]
     print('redshift_indces', redshift_indces)
 
@@ -343,7 +342,7 @@ def three_panel_SFRD_plot(obs_SFRD = [], mu0=0.025, muz=-0.49,alpha = -1.77, sig
         ######################################
         # Model: new SFRD
         l = ax_metals.plot(np.log10(low_res_metallicities), low_res_model_SFRD[:,redshift_i] + shift_step,
-                       lw = 4, ls = '--', c = colors[i], label = "$z=%s$"%(np.round(Obs_redshifts[redshift_i], 3)) )    
+                       lw = 4, ls = '--', c = colors[i], label = "$z=%s$"%(np.round(Obs_redshifts[redshift_i], 1)) )    
         plot_lines.append([l])
         
         ######################################

### 2022-06-08 src/scripts/Plot_Mass_distributions.py

@@ -133,13 +133,15 @@ def plot_mass_distribution(sim_dir = '', x_key = 'M_moreMassive', rate_keys = ['
 
 		legend1 = plt.legend(**leg1_args)
 
-		nplot = 0
+	nplot = 0
 	    
-		################################################
-		# My Simulations
-		################################################
-		DCO = mfunc.read_data(loc = sim_dir +'/COMPAS_Output_wWeights.h5')
+	################################################
+	# My Simulations
+	################################################
+	DCO = mfunc.read_data(loc = sim_dir +'/COMPAS_Output_wWeights.h5')
 
+	# We'll show the change in rate between SFRD at several reference masses
+	m10, m25, m40 = [], [], []
 
 	print('nplot', nplot, '\n')
 	####################################################
@@ -189,6 +191,10 @@ def plot_mass_distribution(sim_dir = '', x_key = 'M_moreMassive', rate_keys = ['
 		kernel = stats.gaussian_kde(x_vals, bw_method=kde_width, weights=Weights)
 		binwidth = np.diff(bin_edge)
 
+		m10.append(kernel(10)*sum(hist)) # append value at reference mass 
+		m25.append(kernel(25)*sum(hist)) # append value at reference mass 
+		m40.append(kernel(40)*sum(hist)) # append value at reference mass 
+
 		########################
 		# Plot the Hist 
 		if show_hist:
@@ -227,6 +233,18 @@ def plot_mass_distribution(sim_dir = '', x_key = 'M_moreMassive', rate_keys = ['
 		#         ax.fill_between(x_KDE, percentiles[0],percentiles[1], alpha=0.4, color=Color, zorder = 11) # 1-sigma
 
 		nplot += 1
+
+
+	#########################################
+	# Show the variation in SFR at 3 different masses
+	reference_masses = [10, 25, 40]
+	for m, mpoint in enumerate([m10, m25, m40]):
+		print('m', np.median(mpoint), max(mpoint), min(mpoint))
+		print()
+		ax.vlines(x=reference_masses[m], ymin=min(mpoint), ymax=max(mpoint), colors='k', lw=3, zorder = 20)
+		ax.hlines(y=[min(mpoint), max(mpoint)], xmin=reference_masses[m]-0.5, xmax=reference_masses[m]+0.5, linewidth=3, color='k', zorder = 20)
[…]

### 2022-06-08 src/tex/ms.tex
[showyourwork]
[showyourwork] overleaf sync

@@
 \citep[e.g.][]{BelczynskiVink2010, Stevenson+2017,Mapelli2017,Chruslinska2019_effectCO}.
-Therefore the assumed metallicity specific star formation rate will in particular have a large impact on the inferred merger rate \citep[e.g.][]{Chruslinska2019,Chruslinska2019_effectCO, Neijssel2019, Broekgaarden+2021a}.
+Therefore the assumed metallicity specific star formation rate will in particular have a large impact on the inferred merger rate \citep[e.g.][]{Chruslinska2019_obs,Chruslinska2019_effectCO, Neijssel2019, Broekgaarden+2021a}.
 
-It is difficult to observationally constrain the shape of the metallicity density distribution over redshift (see \cite{Chruslinska2019} for an extensive overview and discussion of relevant observational caveats).
+It is difficult to observationally constrain the shape of the metallicity density distribution over redshift (see \cite{Chruslinska2019_obs} for an extensive overview and discussion of relevant observational caveats).
 Traditionally the metallicity density distribution is estimated by combining a mass-metallicity relation (MZ-relation) and a galaxy stellar mass function (GSMF) \citep[see also][]{Chruslinska+2018, Chruslinska2019_effectCO, Broekgaarden+2021a}.
@@
 Large uncertainties exist in the shape and redshift evolution of both \SFRDz, and  \dpdZ (see e.g.
-\citealt{Chruslinska2019}, \citealt{Boco2021} and \citealt{Chruslinska+2021} for an extended discussion on the metallicity dependent star formation rate density, in light of empirical data).
+\citealt{Chruslinska2019_obs}, \citealt{Boco2021} and \citealt{Chruslinska+2021} for an extended discussion on the metallicity dependent star formation rate density, in light of empirical data).
 
@@
 $\alpha_0$ &  -1.767 &  $c$ &  4.45 \\
-$\sigma_0$  & 1.125       &  $d$ &  5.90 \\
-$\sigma_z$ &  0.048 &   \\
+$\omega_0$  & 1.125       &  $d$ &  5.90 \\
+$\omega_z$ &  0.048 &   \\
 \enddata
@@
 \section{Effect on the local mass distribution of BBH mergers}
+
+Testing if this works: I now changed something in the overleaf!
 

### 2022-06-08 src/scripts/FitComparison_3panelPlot.py
less sign numbers in z

@@ -364,7 +364,7 @@ def three_panel_SFRD_plot(obs_SFRD = [], mu0=0.025, muz=-0.49,alpha = -1.77, sig
                      bbox_to_anchor=(0.4, 1.0), loc='lower left')
     ax_metals.add_artist(legend2)
     
-    legend3 = ax_metals.legend(lines[1::3], ["$%s$"%(np.round(Obs_redshifts[redshift_i], 3)) for redshift_i in redshift_indces],
+    legend3 = ax_metals.legend(lines[1::3], ["$%s$"%(np.round(Obs_redshifts[redshift_i], 1)) for redshift_i in redshift_indces],
                      ncol=1, bbox_to_anchor=(1.02, 1), loc='upper left', title=r'$\mathrm{redshift}$')
     
     ax_metals.set_xlabel(r'$\log_{10}(Z)$', size =25)

### 2022-06-08 src/scripts/Plot_Mass_distributions.py
changed to omega

@@ -317,9 +317,9 @@ subplot2 = fig.add_subplot(322)
 ax2 = plot_mass_distribution(sim_dir = data_dir, x_key = 'M_moreMassive',  rate_keys = ['Rates_mu00.025_muz-0.05_alpha-1.77_sigma01.125_sigmaz%s_zBinned'%(x) for x in [0.025, 0.05, 0.1]],
                        show_hist = False, show_KDE = True, kde_width = 0.07, plot_LIGO = True, Color = '#00a6a0', 
                        bootstrap = False, bootstraps = 50, save_name = 'SFRD_zevol_width_variations.pdf',  titletext = 'z-evol  of  metallicity  width',
-                       labels = [r'$\mathrm{Flat \ width: \ } \phantom{i} (\sigma_z = 0.025) \ \mathcal{R}_{0} = \ $',
-                                 r'$\mathrm{Fiducial: \ } \phantom{xxi} (\sigma_z = 0.050) \ \mathcal{R}_{0}= \ $', 
-                                 r'$\mathrm{Steep \ width: \ } (\sigma_z = 0.100) \mathcal{R}_{0} = \ $'],
+                       labels = [r'$\mathrm{Flat \ width: \ } \phantom{i} (\omega_z = 0.025) \ \mathcal{R}_{0} = \ $',
+                                 r'$\mathrm{Fiducial: \ } \phantom{xxi} (\omega_z = 0.050) \ \mathcal{R}_{0}= \ $', 
+                                 r'$\mathrm{Steep \ width: \ } (\omega_z = 0.100) \mathcal{R}_{0} = \ $'],
                         multipanel = True, subplot = subplot2)
 
 

### 2022-06-08 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 Although we only consider our fit to describe the IllustrisTNG100 simulation and the phenomenological fit from \cite{Neijssel+2019}, our prescription can be easily be updated to fit other observational or simulated data of the metallicity dependent star formation rate density.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Illustris-TNG Cosmological simulations}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-The IllustrisTNG-project considers galaxy formation and evolution through large-scale cosmological hydrodynamical simulations.
-
-\SdM{Insert a description of enrichment and gas recycling. }
-
-They have been shown to reproduce many of the global properties of galaxies and their scaling relations for a representative portion of the Universe \citep[e.g.][]{FirstResTNG_Naiman2018,Torrey+2021,Genel+2018,Hemler+2021}.These simulations are publicly available\footnote{ \url{https://www.tng-project.org/}} \citep{FirstResTNG_Springel2018,FirstResTNG_Marinacci2018, FirstResTNG_Nelson2018,FirstResTNG_Pillepich2018, FirstResTNG_Naiman2018}.
 
@@
 
-\section{Analytical fit against Cosmological simulation}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Result: Analytical fit against Cosmological simulation}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Illustris-TNG Cosmological simulations}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+The IllustrisTNG-project considers galaxy formation and evolution through large-scale cosmological hydrodynamical simulations.
+
+\SdM{Insert a description of enrichment and gas recycling. }
+
+They have been shown to reproduce many of the global properties of galaxies and their scaling relations for a representative portion of the Universe \citep[e.g.][]{FirstResTNG_Naiman2018,Torrey+2021,Genel+2018,Hemler+2021}.These simulations are publicly available\footnote{ \url{https://www.tng-project.org/}} \citep{FirstResTNG_Springel2018,FirstResTNG_Marinacci2018, FirstResTNG_Nelson2018,FirstResTNG_Pillepich2018, FirstResTNG_Naiman2018}.
 
@@
 \begin{equation}
-\label{eq: chisquare}
+\label{eq: cost function}
     \chi  = \sum_{z_j} \frac{ \chi^2 (z_j) } 
@@
 
-Testing if this works: I now changed something in the overleaf!
+We investigate the effect of the shape of the cosmic metallicity distribution on the local mass distribution of BBH mergers by systemically varying each of the variables that make up \dpdZ (first column of Table \ref{tab: fit params} and eq.
+\ref{eq: z log skew}).
 

### 2022-06-08 src/scripts/FitComparison_3panelPlot.py
description text

@@ -108,7 +108,7 @@ def three_panel_SFRD_plot(obs_SFRD = [], mu0=0.025, muz=-0.49,alpha = -1.77, sig
 
     ######################################
     
-    fit_values_string = r'$\mathrm{log-skew-normal}$'+'\n'+\
+    fit_values_string = r'$\mathrm{Cosmic \ metallicity \ dist.}$'+'\n'+\
                     r'$\mu_0=%s,$'%(np.round(mu0_best,3)) +'\n'+\
                     r'$\mu_z=%s,$'%(np.round(muz_best,3)) +'\n'+\
                     r'$\omega_0=%s,$'%(np.round(sigma0_best,3)) +'\n'\

### 2022-06-08 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 \label{eq: z log skew}
-\mathrm{\frac{dP}{dZ}}(Z,z) = \frac{2}{Z} \times \phi \left(\frac{\ln Z - \xi(z)}{\omega(z)}\right) \Phi\left(\alpha \frac{\ln Z - \xi(z)}{\omega(z)} \right),
+\boxed{
+    \dPdZ = \frac{2}{Z} \times \phi \left(\frac{\ln Z - \xi(z)}{\omega(z)}\right) \Phi\left(\alpha \frac{\ln Z - \xi(z)}{\omega(z)} \right)
+    } \ , 
 \end{equation}
@@
 \label{eq: sfr1}
+\boxed{
     \SFRDz  = 
     \frac{d^2 M_{\rm SFR}}{dt dV_c} (z)= 
-    a \frac{\left(1 + z\right)^b}{1 + \left[ (1 + z)/c \right]^d} \,
+    a \frac{\left(1 + z\right)^b}{1 + \left[ (1 + z)/c \right]^d} 
+    }\,
 \end{eqnarray}
@@
 \subsection{Combined function}
-We combine equations \ref{eq: z log skew} and \ref{eq: sfr1} to form a full metallicity specific starformation rate density (\SFRDzZ).
-We fit for the following nine free parameters $\alpha, \mu_0, \mu_z, \omega_0, \omega_z$, which govern the metallicity dependence and $a,b, c$ and $d$, which set the overall starformation rate.
+We combine equations \ref{eq: z log skew} and \ref{eq: sfr1} to form a full metallicity specific starformation rate density 
+\begin{equation}
+\label{eq: total sfrd}
+\boxed{
+    \SFRDzZ = \dPdZ \times \SFRDz
+    } \ , 
+\end{equation}
+
+\noindent We fit for the following nine free parameters $\alpha, \mu_0, \mu_z, \omega_0, \omega_z$, which govern the metallicity dependence and $a,b, c$ and $d$, which set the overall starformation rate.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Result: Analytical fit against Cosmological simulation}
+\section{Analytical fit against Cosmological simulation}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}
+\script{FitComparison_3panelPlot.py}
+\includegraphics[width=\textwidth]{figures/SFRD_FIT_evaluation_compare.pdf}
+\caption{Fit for SFRD shown against TNG and Neijssel.  \label{fig: fit SFRD}}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+We fit our newly defined functional form of \SFRDzZ as defined in the previous section to the Illustris-TNG cosmological simulations.
+Below we briefly summarise relevant physics behind the Illustris-TNG simulations, and we elaborate on our choices made during the fitting procedure.
+
+% %
+% The task we have at hand here is not a standard textbook fitting problem given the specific aims and requirements that we have that are driven by the astrophysical applications we have in mind.
+Qualitatively, our aims are the following.
+Our main aim is to find solution for the free parameters, for which the expression reproduces the overall behaviour that is observed in the cosmological simulations.
+For the purposes we have in mind, it will be more important to prioritise fitting the large scale trends, while we are not so interested in smaller scale fluctuations.
+We further prioritise getting the bulk of the cosmic star formation right and are less interested in capturing the behaviour in metallicity and redshift bins where the cosmic starformation rate is very low and thus insignificant for the overall picture.
+Finally, we are especially interested in capturing the asymmetry of the metallicity distribution.
+% There is not one unique procedure that will full fill these criteria.
+After experimenting with different criteria we have adopted the procedure below, which we believe works well for the aims we have in mind.
 
@@
 \SdM{Insert a description of enrichment and gas recycling. }
-
 They have been shown to reproduce many of the global properties of galaxies and their scaling relations for a representative portion of the Universe \citep[e.g.][]{FirstResTNG_Naiman2018,Torrey+2021,Genel+2018,Hemler+2021}.These simulations are publicly available\footnote{ \url{https://www.tng-project.org/}} \citep{FirstResTNG_Springel2018,FirstResTNG_Marinacci2018, FirstResTNG_Nelson2018,FirstResTNG_Pillepich2018, FirstResTNG_Naiman2018}.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}
-\script{FitComparison_3panelPlot.py}
-\includegraphics[width=\textwidth]{figures/SFRD_FIT_evaluation_compare.pdf}
-\caption{Fit for SFRD shown against TNG and Neijssel.  \label{fig: fit SFRD}}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%
-The task we have at hand here is not a standard textbook fitting problem given the specific aims and requirements that we have that are driven by the astrophysical applications we have in mind.
-Qualitatively, our aims are the following.
-Our main aim is to find solution for the free parameters, for which the expression reproduces the overall behaviour that is observed in the cosmological simulations.
-For the purposes we have in mind, it will be more important to prioritise fitting the large scale trends, while we are not so interested in smaller scale fluctuations.
-We further prioritise getting the bulk of the cosmic star formation right and are less interested in capturing the behaviour in metallicity and redshift bins where the cosmic starformation rate is very low and thus insignificant for the overall picture.
-Finally, we are especially interested in capturing the asymmetry of the metallicity distribution.
-
-There is not one unique procedure that will full fill these criteria.
-After experimenting with different criteria we have adopted the procedure below, which we believe works well for the aims we have in mind.
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Choices and binning of the data}
-
-We fit our function to the metallicity distribution of the starforming gas in the TNG100 simulation.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+We fit equation \ref{eq: total sfrd} to the metallicity-dependent starformation rate of the starforming gas in the TNG100 simulation.
 For this we use a binned version of the TNG data $\SFRDzZ_{\rm sim}$.
 We consider metallicities between $Z= -5$ to $\log_{10} Z= 0$ in 30 bins, where we use $Z_i$ to refer to the logarithmic centers of the bins.
-We ignore star formation in metallicities $\log_{10} Z \le -5$ as this only accounts for less than 1\% of the total cosmic starformation rate in these simulations.
+We ignore star formation in metallicities $\log_{10} Z \le -5$ as this accounts for less than 1\% of the total cosmic starformation rate in these simulations.
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Optimisation function}
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 To find a solution we use a method based on the sum of the quadratic differences between the simulations and our fit function.
@@
 We use the \texttt{scipy.optimize.minimize} 
-from SciPy v1.6.3 implementation of the optimized quasi-Newton method of Broyden, Fletcher, Goldfarb, and Shanno (BFGS) \url{http://www.apmath.spbu.ru/cnsa/pdf/monograf/Numerical_Optimization2006.pdf}
+from SciPy v1.6.3 implementation of the optimized quasi-Newton method of Broyden, Fletcher, Goldfarb, and Shanno (BFGS).
+\footnote{\url{http://www.apmath.spbu.ru/cnsa/pdf/monograf/Numerical_Optimization2006.pdf}}
 
-With the fit parameters as mentioned above, we find a maximum residual between the model and the TNG100 data of $2.3\cdot 10^{-3} \Msun \yr^{-1} \Mpc^{-3}$ at any given redshift.
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Resulting \SFRDzZ}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 Our best fitting parameters are listed in Table \ref{tab: fit params}. With these fit parameters, $\chi^2(z_j)$ is smaller than $2\cdot 10^{-4}$ at any given redshift.
+% With the fit parameters as mentioned above, we find a maximum residual between the model and the TNG100 data of $2.3\cdot 10^{-3} \Msun \yr^{-1} \Mpc^{-3}$ at any given redshift.
 
@@
 % sf_a =0.01687063881834458, sf_b =1.4834054063851878, sf_c =4.448574027958166, sf_d =5.903964702985274
-
 %muz =-0.048, mu0 =0.025, sigma_0 =1.125, sigma_z =0.048, alpha=-1.767
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+In Figure \ref{fig: fit SFRD} we show the shape of this \SFRDzZ in the plane of the
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Effect on the local mass distribution of BBH mergers}
-
-We investigate the effect of the shape of the cosmic metallicity distribution on the local mass distribution of BBH mergers by systemically varying each of the variables that make up \dpdZ (first column of Table \ref{tab: fit params} and eq.
-\ref{eq: z log skew}).
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
+We investigate the effect of the shape of the cosmic metallicity distribution on the local mass distribution of BBH mergers by systemically varying each of the variables that make up \dpdZ (first column of Table \ref{tab: fit params} and eq.
+\ref{eq: z log skew}).
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Summary and conclusions}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+We present a flexible analytic expression for the metallicity-dependent starformation rate.
+Such an analytical expression allows 
+we find the low mass end of the mass distribution is least affected the change in the \SFRDzZ.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{acknowledgments}
+% Grant Acknowledgements
+The authors acknowledge partial financial support from the  National Science Foundation under Grant No. (NSF grant number 2009131  and PHY-1748958).”
+, the Netherlands Organisation for Scientific Research (NWO) as part of the Vidi research program BinWaves with project number 639.042.728 and the European Union’s Horizon 2020 research and innovation program from the European Research Council (ERC, Grant agreement No.
+715063).
+\end{acknowledgments}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \bibliography{my_bib,main_bib}

### 2022-06-08 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 The rate of Binary Black Hole (BBH) mergers at different redshifts depends both on the delay time distribution as well as the metallicity dependent star-formation rate density (\SFRDzZ).
-The assumed cosmic star formation rate density (SFRD) will therefore greatly influence the observed rate of double compact object mergers \citep{Neijssel+2019, Chruslinska2019, Boco2020,Broekgaarden+2021a}.
+The assumed cosmic star formation rate density (SFRD) will therefore greatly influence the observed rate of double compact object mergers \citep{Neijssel+2019, Chruslinska2019_obs, Boco2020,Broekgaarden+2021a}.
 Moreover, it is the nuclear reactions in massive stars are responsible for the metal enrichment of the Universe at high redshift.
@@
 
-To construct \SFRDzZ from empirical data, one can estimate \dpdZ by combining observed mass-metallicity relations with galaxy stellar mass functions \citep[see e.g.][]{Chruslinska+2018, Chruslinska2019, Broekgaarden+2021b}.
+To construct \SFRDzZ from empirical data, one can estimate \dpdZ by combining observed mass-metallicity relations with galaxy stellar mass functions \citep[see e.g.][]{Chruslinska+2018, Chruslinska2019_obs, Broekgaarden+2021b}.
 Alternatively, one could extract \SFRDzZ directly from cosmological simulations \citep[e.g.][]{Mapelli2017, Briel+2021}.
@@
 
-In Figure \ref{fig: fit SFRD} we show the shape of this \SFRDzZ in the plane of the
+In Figure \ref{fig: fit SFRD} we show the shape of this \SFRDzZ for different redshifts and metallicities. 
+In the top panel we
 

### 2022-06-08 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Our best fitting parameters are listed in Table \ref{tab: fit params}. With these fit parameters, $\chi^2(z_j)$ is smaller than $2\cdot 10^{-4}$ at any given redshift.
+Our best fitting parameters are listed in Table \ref{tab: fit params}.
+With these fit parameters, $\chi^2(z_j)$ is smaller than $2\cdot 10^{-4}$ at any given redshift.
+From now on, we will refer to the \SFRDzZ with the parameters listed in Table \ref{tab: fit params} as our fiducial \SFRDzZ model.
 % With the fit parameters as mentioned above, we find a maximum residual between the model and the TNG100 data of $2.3\cdot 10^{-3} \Msun \yr^{-1} \Mpc^{-3}$ at any given redshift.
@@
 
-In Figure \ref{fig: fit SFRD} we show the shape of this \SFRDzZ for different redshifts and metallicities. 
-In the top panel we
+In Figure \ref{fig: fit SFRD} we show our fiducial \SFRDzZ model at different redshifts and metallicities. 
+In the top panel we show the general trend of the \SFRDzZ linear in lookback time.
+
+Main results:
+
+1) We did a pretty good job at fitting the data. 
+In general, the skewed-log normal metallicity distribution does a good job at capturing the metallicity dependent star formation in TNG. 
+We did miss some features like the almoast dubble peak at redshift 2,
+
+Adopting a skewed-lognormal distribution furthermore allows for a tail of low metallicity star formation
+
+0) the starformation rate peaks at metallicities above $10^{-2}$ for all redshifts out to at least $z=6$
+most star formation happens at metallicities above $Z \gtr 10^{-2}$
+
+% Things to say about this plot: 
+We recognise some of the features discussed in \cite{Pakmor+2022}
+We make a comparison to Neijssel fiducial: their model is extremely narrow, while the metallicity in the TNG is more broad
 

### 2022-06-08 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 \includegraphics[width=\textwidth]{figures/SFRD_FIT_evaluation_compare.pdf}
-\caption{Fit for SFRD shown against TNG and Neijssel.  \label{fig: fit SFRD}}
+\caption{Our fiducial \SFRDzZ model, adopting the best fitting parameters (listed on the top right) to fit the TNG100 simulation. 
+The contours in the top panel range from $10^{-7} - 10^{-2} \Msun \yr^{-1}\Mpc^{-3}$. 
+Fit for SFRD shown against TNG and Neijssel.  \label{fig: fit SFRD}}
 \end{figure*}
@@
 
-Adopting a skewed-lognormal distribution furthermore allows for a tail of low metallicity star formation
+Adopting a skewed-lognormal distribution furthermore allows for a tail of low metallicity star formation. To clarify, we compare to the phenomenological model from \cite{Neijssel+2019} in dotted grey.
 
 0) the starformation rate peaks at metallicities above $10^{-2}$ for all redshifts out to at least $z=6$
-most star formation happens at metallicities above $Z \gtr 10^{-2}$
+most star formation happens at metallicities above $Z \geq 10^{-2}$
 

### 2022-06-09 src/tex/ms.tex
[showyourwork] overleaf sync

--- 2022-06-08 src/tex/ms.tex
@@
 % Author list
-
 \correspondingauthor{L.~van Son}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 % Abstract with filler text
@@
 \end{abstract}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-% Main body with filler text
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Introduction \label{sec: intro}}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \section{A convenient analytic expression for the metallicity-dependent star formation rate density}
-\label{sec: SFRD}
+\label{sec: model for sfrd(zZ)}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\label{s: fitting SFRD}
 We assume that the metallicity dependent star formation rate density can be separated into two independent functions \citep[e.g.\ ][]{Langer2006},
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Analytical fit against Cosmological simulation}
+\section{Analytical fit against Cosmological simulation \label{sec: fit against tng}}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \includegraphics[width=\textwidth]{figures/SFRD_FIT_evaluation_compare.pdf}
-\caption{Fit for SFRD shown against TNG and Neijssel.  \label{fig: fit SFRD}}
+\caption{Our fiducial \SFRDzZ model, adopting the best fitting parameters (listed on the top right) to fit the TNG100 simulations.
+The top panel shows the full two dimensional \SFRDzZ linear in time.
+The bottom left (right) panel shows slices of the distribution in redshift (metallicity).
+Each slice is displaced by 0.01$\Msun \yr^{-1}\Mpc^{-3}$.
+We show the TNG100 simulation data with thick gray lines.
+For comparison, we also show the phenomenological model from \protect\cite{Neijssel+2019} in each panel with grey dotted lines.
+For the latter, the contours in the top panel range from $10^{-7} - 10^{-2} \Msun \yr^{-1}\Mpc^{-3}$.
+ \label{fig: fit SFRD}}
 \end{figure*}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Our best fitting parameters are listed in Table \ref{tab: fit params}. With these fit parameters, $\chi^2(z_j)$ is smaller than $2\cdot 10^{-4}$ at any given redshift.
+Our best fitting parameters are listed in Table \ref{tab: fit params}.
+With these fit parameters, $\chi^2(z_j)$ is smaller than $2\cdot 10^{-4}$ at any given redshift.
+We will refer to the \SFRDzZ with the parameters listed in Table \ref{tab: fit params} as our fiducial \SFRDzZ model.
 % With the fit parameters as mentioned above, we find a maximum residual between the model and the TNG100 data of $2.3\cdot 10^{-3} \Msun \yr^{-1} \Mpc^{-3}$ at any given redshift.
@@
 \tablehead{\colhead{dP/dZ param.} & \colhead{best fit} & \colhead{SFRD(z) param.} & \colhead{best fit} } 
-%% All data must appear between the \startdata and \enddata commands
 \startdata
@@
 \enddata
-%sf_a_best, sf_b_best, sf_c_best,  sf_d_best = 0.02, 1.48, 4.45, 5.90
-% sf_a =0.01687063881834458, sf_b =1.4834054063851878, sf_c =4.448574027958166, sf_d =5.903964702985274
-%muz =-0.048, mu0 =0.025, sigma_0 =1.125, sigma_z =0.048, alpha=-1.767
-% muz =-0.048244647721407255, mu0 =0.024667742078400792, sigma_0 =1.1253850972905333, sigma_z =0.048072863682492945, alpha=-1.7671626767422142
 \end{deluxetable}
 
-In Figure \ref{fig: fit SFRD} we show the shape of this \SFRDzZ for different redshifts and metallicities. 
-In the top panel we
+In Figure \ref{fig: fit SFRD} we show our fiducial \SFRDzZ model at different redshifts and metallicities.
+In general, our analytical model captures the metallicity dependent star formation in the TNG100 simulations well (bottom panels). 
+The skewed-log normal metallicity distribution is able to reproduce the overall behaviour that is observed in TNG100 \citep[bottom left panel, but cf.
+][for an in-depth discussion of low metallicity star formation in the TNG50 simulation]{Pakmor+2022}
+Only minor features like the additional bump just above $\log_{10}(Z) = -2$ at redshift 2 are missed. 
+However, for our purposes, it is more important to prioritise fitting the large scale trends, while we are not so interested in smaller scale fluctuations.
+
+Adopting a skewed-lognormal metallicity distribution allows for a tail of low metallicity star formation out to low redshifts.
+To emphasise the difference between a skewed-lognormal and a symmetric lognormal distribution, we show the phenomenological model from \cite{Neijssel+2019} in dotted grey.
+Their model falls within the family of functions that is encompassed by our model described in Section \ref{sec: model for sfrd(zZ)}.
+\footnote{The phenomenological model from \cite{Neijssel+2019} is recovered by adopting $\mu_0= 0.035$, $\mu_z=-0.23$, $\omega_0=0.39 $, $\omega_z = 0$, $\alpha = 0$, $a=0.01$, $b=2.77$, $c=2.9$ and $d=4.7$.
+}
+The \SFRDzZ from \cite{Neijssel+2019} was optimised to match the local rate of double compact object mergers as presented in the second gravitational-wave catalogue.
+However, the resulting symmetric distribution cuts-off virtually all low-metallicity ($Z\leq 10^{-2.5}$) star formation which is inconsistent with \todo{other observations}.
+% For both \SFRDzZ distributions, most star formation happens at metallicities above $Z \geq 10^{-2}$ (top panel).
 

### 2022-06-09 src/scripts/FitComparison_3panelPlot.py
minor changes to plots

@@ -5,6 +5,8 @@ import matplotlib.pyplot as plt
 import seaborn as sns
 import astropy.units as u
 from astropy import constants as const
+
+from matplotlib import cm
 from matplotlib.colors import ListedColormap, LinearSegmentedColormap
 
 from scipy import interpolate
@@ -244,13 +246,16 @@ def three_panel_SFRD_plot(obs_SFRD = [], mu0=0.025, muz=-0.49,alpha = -1.77, sig
         # Get the SFR Neijssel et al 2019:
         neijssel_sfr = Z_SFRD.Madau_Dickinson2014(neijssel_redshifts, a=0.01, b=2.77, c=2.9, d=4.7) # Msun year-1 Mpc-3 
         Neijssel_SFRDzZ = (neijssel_sfr*neijssel_dPdlogZ.T).value
-        
+
+        greys = cm.get_cmap('Greys')
+        greys = greys(np.linspace(0.2,1,10)) # Don't start the cmap in white
         cs_N = ax.contour(high_res_t, high_res_metals, Neijssel_SFRDzZ, levels, linewidths=4,linestyles =':', alpha = 0.95, zorder=0,
-                          cmap=sns.color_palette('Greys', as_cmap=True),locator=ticker.LogLocator())
+                          cmap=ListedColormap(greys),locator=ticker.LogLocator())
         
     ##############################################################################
     # Plotvalues for top panel
     ######################################
+    ax.text(0.05, 0.05, r"$ \mathcal{S}(Z,z) \ \mathrm{[M_{\odot} yr^{-1} Mpc^{-3}]}$", transform=ax.transAxes)
     ax.xaxis.grid(5) # vertical lines
     ax.set_yscale('log')
     ax.set_xlabel('$\mathrm{Lookback \ time \ [Gyr]}$', fontsize = 25)
@@ -368,7 +373,7 @@ def three_panel_SFRD_plot(obs_SFRD = [], mu0=0.025, muz=-0.49,alpha = -1.77, sig
                      ncol=1, bbox_to_anchor=(1.02, 1), loc='upper left', title=r'$\mathrm{redshift}$')
     
     ax_metals.set_xlabel(r'$\log_{10}(Z)$', size =25)
[…]

### 2022-06-09 src/scripts/Plot_Mass_distributions.py

@@ -244,7 +244,7 @@ def plot_mass_distribution(sim_dir = '', x_key = 'M_moreMassive', rate_keys = ['
 		ax.vlines(x=reference_masses[m], ymin=min(mpoint), ymax=max(mpoint), colors='k', lw=3, zorder = 20)
 		ax.hlines(y=[min(mpoint), max(mpoint)], xmin=reference_masses[m]-0.5, xmax=reference_masses[m]+0.5, linewidth=3, color='k', zorder = 20)
 		ax.text(reference_masses[m] - 0.7, (max(mpoint)+min(mpoint))/2 , r'%s $\times $'%(np.round( (max(mpoint)/min(mpoint))[0] , 1)) ,
-			bbox=dict(facecolor='white', edgecolor='none', boxstyle='round,pad=1', alpha = 0.5), ha = 'right', size = 25, zorder = 20)
+			bbox=dict(facecolor='white', edgecolor='none', boxstyle='round,pad=0.1', alpha = 0.5), ha = 'right', size = 25, zorder = 20)
 
 	#########################################
 	# plot values
@@ -301,7 +301,6 @@ subplot1 = fig.add_subplot(321)
 ax1 = plot_mass_distribution(sim_dir = data_dir, x_key = 'M_moreMassive',  rate_keys = ['Rates_mu00.025_muz-0.05_alpha-1.77_sigma0%s_sigmaz0.05_zBinned'%(x) for x in [0.8, 1.125, 1.4]],
                        show_hist = False, show_KDE = True, kde_width = 0.07, plot_LIGO = True, Color =  'navy', 
                        bootstrap = False, bootstraps = 50, save_name = 'SFRD_width_variations.pdf', titletext = 'Width of metallicity  dist.',
-                       xlabel = r'$M_{\mathrm{BH, mm}} \ \rm [M_{\odot}]$', 
                        labels = [r'$\mathrm{Narrow: \ } \phantom{xxx} (\omega_0 = 0.800) \  \mathcal{R}_{0} = \ $',
                                  r'$\mathrm{Fiducial: \ } \phantom{xxi} (\omega_0 = 1.125) \ \mathcal{R}_{0}= \ $', 
                                  r'$\mathrm{Wide \ SFRD: \ }  (\omega_0 = 1.400) \  \mathcal{R}_{0} = \ $'],
@@ -319,7 +318,7 @@ ax2 = plot_mass_distribution(sim_dir = data_dir, x_key = 'M_moreMassive',  rate_
[…]

### 2022-06-09 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 \begin{figure*}
+\centering
 \script{FitComparison_3panelPlot.py}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Effect on the local mass distribution of BBH mergers}
+\section{Application: systematic variations of \SFRDzZ and the effect on the mass distribution of merging BBHs}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-We investigate the effect of the shape of the cosmic metallicity distribution on the local mass distribution of BBH mergers by systemically varying each of the variables that make up \dpdZ (first column of Table \ref{tab: fit params} and eq.
+We will now demonstrate the flexibility of our analytical model by systematically varying each of the parameters in our fiducial \SFRDzZ model, and investigate their effect on the local mass distribution of BBH mergers.
+To this end we use the publicly available simulations as presented in \cite{vanson+2022}
+We use the framework described in detail in \cite{vanson+2022} that is part of the \COMPAS suite to compute local merger rates of BBH systems originating from
+
+% We investigate the effect of the shape of the cosmic metallicity distribution on the local mass distribution of BBH mergers by systemically varying each of the variables that make up \dpdZ (first column of Table \ref{tab: fit params} and eq.
 \ref{eq: z log skew}).
+
+% We study merging binary black holes formed from the
+% evolution of isolated massive binary stars (the ‘isolated
+% binary evolution’ channel) using the publicly available
+% simulations presented in Broekgaarden et al. (2021);
+% Broekgaarden et al. (2022). These simulations were per-
+% formed using the rapid binary population synthesis suite
+% COMPAS4 (Stevenson et al. 2017; Vigna-G ́omez et al.
+% 2018; Broekgaarden et al. 2019; Team COMPAS: Riley
+% et al. 2022), which employs simple parameterized models
+% of single (Hurley et al. 2000) and binary stellar evolu-
+% tion (Hurley et al. 2002) in order to rapidly evolve large
+% populations of binaries.
 

### 2022-06-09 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 We will now demonstrate the flexibility of our analytical model by systematically varying each of the parameters in our fiducial \SFRDzZ model, and investigate their effect on the local mass distribution of BBH mergers.
-To this end we use the publicly available simulations as presented in \cite{vanson+2022}
-We use the framework described in detail in \cite{vanson+2022} that is part of the \COMPAS suite to compute local merger rates of BBH systems originating from
+To this end we use the publicly available simulations as presented in \cite{vanson+2022}, consisting of rapid binary population synthesis using v02.19.04 of the \COMPAS suite \citep{COMPAS_method} \footnote{\url{https://compas.science/}}.
+We use the framework described in \cite{vanson+2022} to compute local merger rates of BBH systems originating from isolated binaries.
 
+% that is part of the \COMPAS suite 
 % We investigate the effect of the shape of the cosmic metallicity distribution on the local mass distribution of BBH mergers by systemically varying each of the variables that make up \dpdZ (first column of Table \ref{tab: fit params} and eq.

### 2022-06-09 src/scripts/Plot_Mass_distributions.py
changed reference redshift

@@ -61,7 +61,7 @@ plt.rc('legend', fontsize=SMALL_SIZE)    # legend fontsize
 # Distribution plot function
 ######################################
 def plot_mass_distribution(sim_dir = '', x_key = 'M_moreMassive', rate_keys = ['Rates_mu00.025_muz-0.05_alpha-1.77_sigma0%s_sigmaz0.05_zBinned'%(x) for x in [0.8, 1.125, 1.4]],
-                   bins = np.arange(0.,55,2.5), z_bin_edges = [0,0.5], 
+                   bins = np.arange(0.,55,2.5), z_bin_edges = [0,0.25], 
                    plot_LIGO = False, show_hist = False, show_KDE = True, kde_width = 0.1,  
                    bootstrap = False, bootstraps = 10, x_lim=(0.,50),  y_lim = (1e-2,50), 
                    Color = '#e388b0', linestyles = ['--','-', ':'], titletext = '',
@@ -173,11 +173,12 @@ def plot_mass_distribution(sim_dir = '', x_key = 'M_moreMassive', rate_keys = ['
 
 		# # # # # # # # # # # # # # # # # # 
 		## Calculate average rate density per z-bin
-		crude_rate_density  = mfunc.get_crude_rate_density(Red_intr_rate_dens[:,:], redshifts, z_bin_edges)
+		# crude_rate_density  = mfunc.get_crude_rate_density(Red_intr_rate_dens[:,:], redshifts, z_bin_edges)
 		#########################################
 		# X value and weight
 		x_vals              = merging_BBH[x_key]
-		Weights             = crude_rate_density[:,0]
+		i_redshift = np.where(redshifts == 4)[0]
+		Weights             = Red_intr_rate_dens[:, i_redshift]#crude_rate_density[:,0]
 
 		print(labels[i], ' len(table)=', len(merging_BBH) , ' Rate = ', np.sum(Weights), ' Gpc-3 yr-1')
 
@@ -300,7 +301,7 @@ subplot1 = fig.add_subplot(321)
 
 ax1 = plot_mass_distribution(sim_dir = data_dir, x_key = 'M_moreMassive',  rate_keys = ['Rates_mu00.025_muz-0.05_alpha-1.77_sigma0%s_sigmaz0.05_zBinned'%(x) for x in [0.8, 1.125, 1.4]],
[…]

### 2022-06-09 src/tex/ms.tex
[showyourwork] overleaf sync

--- 2022-06-09 src/tex/ms.tex
@@
 
-We investigate the effect of the shape of the cosmic metallicity distribution on the local mass distribution of BBH mergers by systemically varying each of the variables that make up \dpdZ (first column of Table \ref{tab: fit params} and eq.
+We will now demonstrate the flexibility of our analytical model by systematically varying each of the parameters in our fiducial \SFRDzZ model, and investigate their effect on the local mass distribution of BBH mergers originating from isolated binaries.
+To this end we use the publicly available rapid binary population synthesis simulations as presented in \cite{vanson+2022}.
+These simulations were run using version v02.19.04 of the open source \COMPAS suite \citep{COMPAS_method} \footnote{\url{https://github.com/TeamCOMPAS/COMPAS}}.
+\COMPAS is based on algorithms  model the evolution of massive stars in binary systems following \citet{Hurley+2000, Hurley+2002}, based on detailed evolutionary models by \citet{Pols+1998}.
+We use the framework described in \cite{vanson+2022} to compute local merger rates of BBH systems.
+
+% that is part of the \COMPAS suite 
+% We investigate the effect of the shape of the cosmic metallicity distribution on the local mass distribution of BBH mergers by systemically varying each of the variables that make up \dpdZ (first column of Table \ref{tab: fit params} and eq.
 \ref{eq: z log skew}).

### 2022-06-09 src/scripts/Plot_Mass_distributions.py
changed fiducial z

@@ -177,9 +177,10 @@ def plot_mass_distribution(sim_dir = '', x_key = 'M_moreMassive', rate_keys = ['
 		#########################################
 		# X value and weight
 		x_vals              = merging_BBH[x_key]
-		i_redshift = np.where(redshifts == 4)[0]
+		i_redshift = np.where(redshifts == 0.2)[0][0]
+		print('i_redshift', i_redshift)
 		Weights             = Red_intr_rate_dens[:, i_redshift]#crude_rate_density[:,0]
-
+		print('!X!X!X!', np.shape(Weights), np.shape(x_vals) )
 		print(labels[i], ' len(table)=', len(merging_BBH) , ' Rate = ', np.sum(Weights), ' Gpc-3 yr-1')
 
 		########################

### 2022-06-09 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 These simulations were run using version v02.19.04 of the open source \COMPAS suite \citep{COMPAS_method} \footnote{\url{https://github.com/TeamCOMPAS/COMPAS}}.
-\COMPAS is based on algorithms  model the evolution of massive stars in binary systems following \citet{Hurley+2000, Hurley+2002}, based on detailed evolutionary models by \citet{Pols+1998}.
+\COMPAS is based on algorithms that model the evolution of massive binary stars following \citet{Hurley+2000, Hurley+2002}, based on detailed evolutionary models by \citet{Pols+1998}.
 We use the framework described in \cite{vanson+2022} to compute local merger rates of BBH systems.

### 2022-06-09 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 For the latter, the contours in the top panel range from $10^{-7} - 10^{-2} \Msun \yr^{-1}\Mpc^{-3}$.
+This shows that our analytical model adequately captures the \SFRDzZ of the TNG100 simulations.
  \label{fig: fit SFRD}}
@@
 $\mu_z$ &  -0.048 &  $b$ &  1.48 \\
-$\alpha_0$ &  -1.767 &  $c$ &  4.45 \\
+$\alpha$ &  -1.767 &  $c$ &  4.45 \\
 $\omega_0$  & 1.125       &  $d$ &  5.90 \\
@@
 \begin{figure*}
+\centering
 \script{Plot_Mass_distributions.py}
-\includegraphics[width=\textwidth]{figures/SFRD_variations_combined.pdf}
-\caption{The effects of several variations in the SFRD  \label{fig: mass dists}}
+\includegraphics[width=0.95\textwidth]{figures/SFRD_variations_combined.pdf}
+\caption{The primary mass distribution of merging BBH systems from isolated binary evolution for several variations in \SFRDzZ. 
+The first five panels show variations of the cosmic metallicity distribution  \dpdZ (eq.
+\ref{eq: z log skew}, parameters listed in the first two columns of Table \ref{tab: fit params}).
+The bottom right panel shows variations in the magnitude of the star formation rate with redshift, i.e.
+\SFRDz.
+For the latter we vary the four fiducial parameters of \SFRDz simultaneously (last two columns of Table \ref{tab: fit params}).
+All panels are shown at a reference redshift of $z=0.2$, with the corresponding predicted BBH merger rate annotated in the legend.
+We show the power-law + peak model from \protect\cite{GWTC3_popPaper2021} in grey.
+Lastly we annotate the relative change in the rate at three reference masses: $10\Msun$, $25\Msun$ and $40\Msun$.
+Variations in \SFRDzZ have the largest impact on the high mass end of the distribution, while around $\Mbheen=10$, variations are smaller than a factor of 3.
+  \label{fig: mass dists}}
 \end{figure*}
@@
 
-We will now demonstrate the flexibility of our analytical model by systematically varying each of the parameters in our fiducial \SFRDzZ model, and investigate their effect on the local mass distribution of BBH mergers originating from isolated binaries.
+We will now demonstrate the flexibility of our analytical model by systematically varying the parameters in our fiducial \SFRDzZ model, and investigate their effect on the local mass distribution of BBH mergers originating from isolated binaries.
+%
 To this end we use the publicly available rapid binary population synthesis simulations as presented in \cite{vanson+2022}.
@@
 \COMPAS is based on algorithms that model the evolution of massive binary stars following \citet{Hurley+2000, Hurley+2002}, based on detailed evolutionary models by \citet{Pols+1998}.
-We use the framework described in \cite{vanson+2022} to compute local merger rates of BBH systems.
+The framework used to compute local merger rates of BBH systems is described in \cite{vanson+2022}.
+We refer the reader to their methods section for a detailed description of our adopted physics parameters and assumptions.
 
-% that is part of the \COMPAS suite 
-% We investigate the effect of the shape of the cosmic metallicity distribution on the local mass distribution of BBH mergers by systemically varying each of the variables that make up \dpdZ (first column of Table \ref{tab: fit params} and eq.
-\ref{eq: z log skew}).
+In Figure \ref{fig: mass dists} we show the mass distribution of the more massive BH from BBH mergers. We will refer to the more (less) massive component as the primary (secondary) from hereon. 
+In general we note that the main features in the primary mass distribution remain distinguishable throughout all \SFRDzZ variations. 
+We annotate the relative change between models at three reference masses: $10\Msun$, $25\Msun$ and $40\Msun$. 
+This shows that changes in \SFRDzZ have the largest impact on the high mass end of the primary mass distribution, while at $\Mbheen=10\Msun$, we find at most a factor 3 between the differen \SFRDzZ models.
+
+We find that parameter variations that affect shape of \SFRDzZ at low redshift primarily change the normalisation of the mass distribution.
+These include the width of the cosmic metallicity distribution at $z=0$, $\omega_0$, the mean metallicity of the cosmic metallicity distribution at $z=0$, $\mu_0$, and the skewness of the cosmic metallicity distribution, $\alpha$ (left column of Figure \ref{fig: mass dists}).
+Model variations that increase the amount of star formation at low metallicity (i.e.
+for a low mean metallicity $\mu_0=0.015$ and a wide metallicity distribution $\omega_0 = 1.4$ ) increase the predicted BBH merger rate.
+ This is consistent with other work \todo{copy ref from wind paper.}
+
+On the other hand, parameters that change the evolution of the metallicity distribution \dpdZ with redshift, such as $\omega_z$ and $\mu_z$ (top right and centre right panel), primarily affect the slope of the high mass end of the BBH mass distribution.
+Changing the \SFRDz has a surprisingly small effect. 
+\todo{describe difference between 3 papers}.
 

### 2022-06-09 src/scripts/Plot_Mass_distributions.py
changing size

@@ -63,7 +63,7 @@ plt.rc('legend', fontsize=SMALL_SIZE)    # legend fontsize
 def plot_mass_distribution(sim_dir = '', x_key = 'M_moreMassive', rate_keys = ['Rates_mu00.025_muz-0.05_alpha-1.77_sigma0%s_sigmaz0.05_zBinned'%(x) for x in [0.8, 1.125, 1.4]],
                    bins = np.arange(0.,55,2.5), z_bin_edges = [0,0.25], 
                    plot_LIGO = False, show_hist = False, show_KDE = True, kde_width = 0.1,  
-                   bootstrap = False, bootstraps = 10, x_lim=(0.,50),  y_lim = (1e-2,50), 
+                   bootstrap = False, bootstraps = 10, x_lim=(0.,50),  y_lim = (1e-2,30), 
                    Color = '#e388b0', linestyles = ['--','-', ':'], titletext = '',
                    labels = [r'$\mathrm{CE \ channel = \ }$', r'$\mathrm{stable \ RLOF \ channel = \ }$', r'$\mathrm{All = \ }$'],
                    xlabel = r'$M_{\mathrm{BH, 1}} \ \rm [M_{\odot}]$', ylabel = r'$\frac{d\mathcal{R}}{dM_{\mathrm{BH, 1} }} \ \mathrm{[Gpc^{-3}yr^{-1}M^{-1}_{\odot}]}$',
@@ -291,7 +291,7 @@ def plot_mass_distribution(sim_dir = '', x_key = 'M_moreMassive', rate_keys = ['
 #																								#
 #################################################################################################
 
-fig = plt.figure( figsize = (24, 30))
+fig = plt.figure( figsize = (24, 28))
 
 
 ####################################################
@@ -303,9 +303,9 @@ subplot1 = fig.add_subplot(321)
 ax1 = plot_mass_distribution(sim_dir = data_dir, x_key = 'M_moreMassive',  rate_keys = ['Rates_mu00.025_muz-0.05_alpha-1.77_sigma0%s_sigmaz0.05_zBinned'%(x) for x in [0.8, 1.125, 1.4]],
                        show_hist = False, show_KDE = True, kde_width = 0.07, plot_LIGO = True, Color =  'navy', 
[…]

### 2022-06-27 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 
-To make it easier to produce model predictions we propose a simple analytical prescription that captures the main behavior of the advanced simulations.
+To make it easier to produce model predictions we propose a simple analytical prescription that captures the main behaviour of the advanced simulations.
 At the same time, the prescription comes with parameters that allow for variations in the overall shape and which can be easily interpreted.
@@
 \end{abstract}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Introduction \label{sec: intro}}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 %opening from Chruslinska & Nelemans. Crucially needed are simple prescriptions
@@
 % dan een beetje science 
-LIGO/Virgo are revealing double compact object mergers throughout the Universe. These systems originate from largely
 % Er zijn allemaal BBH detecties, super leuk
@@
 
-% make 2D grid in z, Z, at each point: 
-% What is delta  = |dModel-dTNG|?
-% plot in 2d the delta
-
-Since the delay time of BBHs can range from Myrs to multiple Gyrs, the birth environment of BBHs varies significantly and we cannot ignore the cosmological (metallicity) evolution of the Universe. 
-The rate of Binary Black Hole (BBH) mergers at different redshifts depends both on the delay time distribution as well as the metallicity dependent star-formation rate density (\SFRDzZ).
-The assumed cosmic star formation rate density (SFRD) will therefore greatly influence the observed rate of double compact object mergers \citep{Neijssel+2019, Chruslinska2019_obs, Boco2020,Broekgaarden+2021a}.
-Moreover, it is the nuclear reactions in massive stars are responsible for the metal enrichment of the Universe at high redshift.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Introduction \label{sec: intro}}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Since the delay time of binary black holes (BBHs) can range from Myrs to multiple Gyrs, the birth environment of BBHs varies significantly and we cannot ignore the cosmological (metallicity) evolution of the Universe.
+% The rate of Binary Black Hole (BBH) mergers at different redshifts depends both on the delay time distribution as well as the metallicity dependent star-formation rate density (\SFRDzZ).
+% The assumed cosmic star formation rate density (SFRD) will therefore greatly influence the observed rate of double compact object mergers \citep{Neijssel+2019, Chruslinska2019_obs, Boco2020,Broekgaarden+2021a}.
+% Moreover, it is the nuclear reactions in massive stars are responsible for the metal enrichment of the Universe at high redshift.
 The birth of massive stars, and their death as BHs are thus inseparable from the evolution of the metallicity distribution of the Universe.
 
-%%  metallicity density distribution %%
-Merging BBHs are found to form more efficiently at low metallicities e.g.
+% %%  metallicity density distribution %%
+% Merging BBHs are found to form more efficiently at low metallicities e.g.
 \citep[e.g.][]{BelczynskiVink2010, Stevenson+2017,Mapelli2017,Chruslinska2019_effectCO}.
@@
 
-It is difficult to observationally constrain the shape of the metallicity density distribution over redshift (see \cite{Chruslinska2019_obs} for an extensive overview and discussion of relevant observational caveats).
+A myriad of astrophysical phenomena depend critically on the rate of star formation throughout the cosmic history of the Universe. 
+Transient phenomena, including core collapse supernovae, (pulsational) pair-instability supernovae, long gamma-ray bursts and gravitational wave (GW) events are particularly sensitive to the metallicity at which star formation occurs at different epochs throughout the Universe.
+The field of transient astronomy has seen explosive growth in the past few decades due to increased observational capabilities.
+But in order to correctly model and interpret these observations, it is fundamental to know rate of star formation at different metallicities throughout cosmic history (i.e.
+the metallicity-dependent star formation rate density, \SFRDzZ).
+
+It is difficult to observationally constrain the shape of \SFRDzZ (see \cite{Chruslinska2019_obs} for an extensive overview and discussion of relevant observational caveats).
+Even at low redshifts, the low metallicity part of the distribution is poorly constrained \citep{Chruslinska+2021}.
 Traditionally the metallicity density distribution is estimated by combining a mass-metallicity relation (MZ-relation) and a galaxy stellar mass function (GSMF) \citep[see also][]{Chruslinska+2018, Chruslinska2019_effectCO, Broekgaarden+2021a}.
 Another way is to extract the metallicity density fraction from cosmological simulations \citep[e.g.]{Mapelli2017, Schneider+2017}
-Alternatively, one can combine an observed star formation rate, SFR(z), like from \cite{MadauDickinson2014} or \cite{Madau+2017}, and convolve this with some belief about the shape of the metallicity density distribution, such as was was done in \cite{Neijssel+2019}.
+Alternatively, one can combine an observed star formation rate, \SFRDz, like from \cite{MadauDickinson2014} or \cite{Madau+2017}, and convolve this with some belief about the shape of the metallicity density distribution, such as was was done in \cite{Neijssel+2019}.
 A third option is extract this information from cosmological simulations \citep[e.g.][]{Mapelli+2017,Schneider+2017}.
-In this work we provide a new fit to the \SFRDzZ based on the TNG 100 simulation \citep{Pillepich2018, Weinberger2017}.
+In this work we provide an analytical model which we fit to the \SFRDzZ based on the TNG 100 simulation \citep{Pillepich2018, Weinberger2017}.
 
-Large uncertainties exist in the shape and redshift evolution of both \SFRDz, and  \dpdZ (see e.g.
+% Large uncertainties exist in the shape and redshift evolution of both \SFRDz, and the cosmic distribution of metallicities \dpdZ (see e.g.
 \citealt{Chruslinska2019_obs}, \citealt{Boco2021} and \citealt{Chruslinska+2021} for an extended discussion on the metallicity dependent star formation rate density, in light of empirical data).
 
-To construct \SFRDzZ from empirical data, one can estimate \dpdZ by combining observed mass-metallicity relations with galaxy stellar mass functions \citep[see e.g.][]{Chruslinska+2018, Chruslinska2019_obs, Broekgaarden+2021b}.
+% To construct \SFRDzZ from empirical data, one can estimate \dpdZ by combining observed mass-metallicity relations with galaxy stellar mass functions \citep[see e.g.][]{Chruslinska+2018, Chruslinska2019_obs, Broekgaarden+2021b}.
 Alternatively, one could extract \SFRDzZ directly from cosmological simulations \citep[e.g.][]{Mapelli2017, Briel+2021}.
 
-In this work, we take an approach similar to \citet{Mapelli2017} and \cite{Briel+2021}  but instead of directly extracting the \SFRDzZ from a cosmological simulation we fit analytical representations of \SFRDz and \dpdZ to simulation data.
+% \citet{Mapelli2017} and \cite{Briel+2021}  but instead of directly extracting the \SFRDzZ from a cosmological simulation
 
-By adopting an analytical, parametrized form for \SFRDzZ, the large uncertainties in \SFRDzZ can be systematically explored through smoothly varying the parameters that control its shape (cf.~\citealt{Briel+2021}).
+% we take an approach similar to \cite{LangerNorman}, but instead of following the observed mean metallicity with redshift, we fit our combined analytical representations of \SFRDz and \dpdZ to simulation data.
 
-Different cosmological simulations produce varying \SFRDzZ which lead to different redshift evolution of the BBH merger rate with redshift.
-\cite{Briel+2021} find that the EAGLE and TNG simulation provide the best \SFRDzZ based on the predicted cosmic rates for electromagnetic and gravitational-wave transients.
-Although we only consider our fit to describe the IllustrisTNG100 simulation and the phenomenological fit from \cite{Neijssel+2019}, our prescription can be easily be updated to fit other observational or simulated data of the metallicity dependent star formation rate density.
+In this work, we present a convenient flexible model for the \SFRDzZ that can be fit to both simulation and observational data.
+By adopting an analytical, parametrized form for \SFRDzZ, the large uncertainties in \SFRDzZ can be systematically explored through smoothly varying the parameters that control its shape.
+
+We describe our model for \SFRDzZ in Section \ref{sec: model for sfrd(zZ)}.
+We fit our model to to the starforming gas in the illustris TNG simulation in Section \ref{sec: fit against tng}.
+In Section \ref{sec: mass dists} we demonstrate an example application of our model by systematically varying the parameters that determine the shape of \SFRDzZ and investigate their impact on the local distribution of merging BBH masses.
+We summarise in Section \ref{sec: summary}.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{A convenient analytic expression for the metallicity-dependent star formation rate density}
-\label{sec: model for sfrd(zZ)}
+\section{A convenient analytic expression for the metallicity-dependent star formation rate density \label{sec: model for sfrd(zZ)} }
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\paragraph{Assymetry of the metallicity distribution: $\alpha$}
+\paragraph{Asymmetry of the metallicity distribution: $\alpha$}
 We have considered variations where the ``skewness'' $\alpha$ varies with redshift but we did not find very significant improvements compared to the simpler assumption where $\alpha$ is kept constant.
@@
 They have been shown to reproduce many of the global properties of galaxies and their scaling relations for a representative portion of the Universe \citep[e.g.][]{FirstResTNG_Naiman2018,Torrey+2021,Genel+2018,Hemler+2021}.These simulations are publicly available\footnote{ \url{https://www.tng-project.org/}} \citep{FirstResTNG_Springel2018,FirstResTNG_Marinacci2018, FirstResTNG_Nelson2018,FirstResTNG_Pillepich2018, FirstResTNG_Naiman2018}.
+
+Different cosmological simulations produce varying \SFRDzZ which lead to different redshift evolution of the BBH merger rate with redshift.
+\cite{Briel+2021} find that the EAGLE and TNG simulation provide the best \SFRDzZ based on the predicted cosmic rates for electromagnetic and gravitational-wave transients.
+Although we only consider our model to describe the IllustrisTNG100 simulation and the phenomenological fit from \cite{Neijssel+2019}, our prescription can be easily be used to fit other observational or simulated data of the metallicity dependent star formation rate density.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Application: systematic variations of \SFRDzZ and the effect on the mass distribution of merging BBHs}
+\section{Application: systematic variations of \SFRDzZ and the effect on the mass distribution of merging BBHs \label{sec: mass dists}}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \script{Plot_Mass_distributions.py}
-\includegraphics[width=0.95\textwidth]{figures/SFRD_variations_combined.pdf}
+\includegraphics[width=0.8\textwidth]{figures/SFRD_variations_combined.pdf}
 \caption{The primary mass distribution of merging BBH systems from isolated binary evolution for several variations in \SFRDzZ. 
@@
 
-We will now demonstrate the flexibility of our analytical model by systematically varying the parameters in our fiducial \SFRDzZ model, and investigate their effect on the local mass distribution of BBH mergers originating from isolated binaries.
+We will demonstrate the application of our analytical model by systematically varying the parameters in our fiducial \SFRDzZ model, and investigate their effect on the local mass distribution of BBH mergers originating from isolated binaries.
+
+We use the publicly available rapid binary population synthesis simulations presented in \cite{vanson+2022}. 
+These simulations were run using version v02.19.04 of the open source \COMPAS suite \citep{COMPAS_method} \footnote{\url{https://github.com/TeamCOMPAS/COMPAS}}.
+\COMPAS is based on algorithms that model the evolution of massive binary stars following \citet{Hurley+2000, Hurley+2002}, based on detailed evolutionary models by \citet{Pols+1998}.
+We refer the reader to the methods section of \cite{vanson+2022} for a detailed description of our adopted physics parameters and assumptions.
 %
+These simulations provide us with an estimate of the yield of BBH mergers per unit of star-forming mass and metallicity. 
+We sample the metallicities of each binary system from a smooth probability distribution in stead of running batches of binaries at discrete sets of metallicity.
+Smoothly sampling of the birth metallicity avoids artificial peaks in the BH mass distribution \citep[e.g.][]{Dominik2015,Kummer_thesis}.
+
+Lastly, we combine the aforementioned yield with a \SFRDzZ as described in this work.
+By integrating over cosmic history, we obtain the local merger rates of BBH systems, which allow us to construct the distribution of source properties at every redshift.
+The details of this framework are described in \cite{vanson+2022}, and also in \cite{Broekgaarden+2021a} and \cite{Neijssel+2019}.
+
+We consider variations of each of the parameters that determine the shape of the cosmic metallicity distribution \dpdZ (left two columns of Table \ref{tab: fit params}) and two variations of the \SFRDz, where we vary the complete shape of the \SFRDz (i.e.
+all four parameters) at once to match the values used in \todo{Madaufragos} \cite{Neijssel2019}.
+To determine the range of parameters that is reasonably allowed by observations, we compare the \SFRDzZ in the metallicity-redshift plane to the high and low metallicity extreme from \cite{Chruslinska+2021} by eye for every variation.
+\\
+
+In Figure \ref{fig: mass dists} we show the mass distribution of the more massive component from merging BBHs.
+We will refer to the more (less) massive component as the primary (secondary) from hereon.
+In general we note that the main features in the primary mass distribution remain distinguishable throughout all \SFRDzZ variations.
+
+% Low masses are less affected
+Changes in the \SFRDzZ have the largest impact on the high mass end of the primary mass distribution, while the impact on the low mass is relatively modest.
+To quantify this, we annotate the ratio between the maximum and minimum rate at three reference masses; $10\Msun$, $25\Msun$ and $40\Msun$. 
+At $\Mbheen=10\Msun$, we find that the rate changes by at most a factor 3 for the variations explored in this work. While we find a factor of at most 11 for the change in rate at $\Mbheen=40\Msun$.
+
+% The normalization at z=0 changes the overal rate / normalization
+We find that parameter variations that affect shape of \SFRDzZ at low redshift primarily change the normalisation of the mass distribution (see also  $\mathcal{R}_{0.2}$, the total BBH merger rate at redshift 0.2, annotated in the legends of Figure \ref{fig: mass dists}).
+These variations include the width of the cosmic metallicity distribution at $z=0$, $\omega_0$, the mean metallicity of the cosmic metallicity distribution at $z=0$, $\mu_0$, and the skewness of the cosmic metallicity distribution, $\alpha$ (left column of Figure \ref{fig: mass dists}).
+Model variations that increase the amount of star formation at low metallicity (i.e.
+for a low mean metallicity $\mu_0=0.015$ and a wide metallicity distribution $\omega_0 = 1.4$ ) increase the predicted BBH merger rate.
+This is consistent with other work \todo{copy ref from wind paper.}
+Although a skewed distribution allows the metallicity distribution to extend to lower values, it simultaniously pushes the expected value of the metallicity distribution to higher values.
+Hence, the local rate of BBH mergers is lower for the skewed distribution ($\alpha = -3.5$) with respect to the more symmetric variation ($\alpha = -0.9$).
+However, the total rate of BBH mergers is only changed by about a factor of 2.
+
+% The paramters that affect the redshift evolution change the slope of high mass BHs
+Parameters that change the evolution of the metallicity distribution \dpdZ with redshift, such as $\omega_z$ and $\mu_z$ (top right and centre right panel), primarily affect the slope of the high mass end of the BBH mass distribution.
+The difference between the effect on the low mass end with respect to the high mass end of the mass distribution is largest for these variations.
+
+% Effect of the star formation 
+Lastly, changing the \SFRDz has a relatively small effect. 
+The \SFRDz from \cite{Madau+2017} and \cite{Neijssel+2019} both peak at approximately redshift 2.
+Our fiducial model (that follows the \SFRDz from TNG) peaks at about redshift 3.
+The overall normalization of \cite{Neijssel+2019} is higher than the normalization of our fiducial model.
+Regardless of these differences, the rate of BBH mergers at $z=0.2$ changes no more than 20\%, and the shape of the primary mass distribution remains almost constant.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Application: systematic variations of \SFRDzZ and the effect on the mass distribution of merging BBHs \label{sec: mass dists}}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}
+\centering
+\script{Plot_Mass_distributions.py}
+\includegraphics[width=0.8\textwidth]{figures/SFRD_variations_combined.pdf}
+\caption{The primary mass distribution of merging BBH systems from isolated binary evolution for several variations in \SFRDzZ. 
+The first five panels show variations of the cosmic metallicity distribution  \dpdZ (eq.
+\ref{eq: z log skew}, parameters listed in the first two columns of Table \ref{tab: fit params}).
+The bottom right panel shows variations in the magnitude of the star formation rate with redshift, i.e.
+\SFRDz.
+For the latter we vary the four fiducial parameters of \SFRDz simultaneously (last two columns of Table \ref{tab: fit params}).
+All panels are shown at a reference redshift of $z=0.2$, with the corresponding predicted BBH merger rate annotated in the legend.
+We show the power-law + peak model from \protect\cite{GWTC3_popPaper2021} in grey.
+Lastly we annotate the relative change in the rate at three reference masses: $10\Msun$, $25\Msun$ and $40\Msun$.
+Variations in \SFRDzZ have the largest impact on the high mass end of the distribution, while around $\Mbheen=10$, variations are smaller than a factor of 3.
+  \label{fig: mass dists}}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+We will now demonstrate the application of our analytical model by systematically varying the parameters in our fiducial \SFRDzZ model, and investigate their effect on the local mass distribution of BBH mergers originating from isolated binaries.
+
 To this end we use the publicly available rapid binary population synthesis simulations as presented in \cite{vanson+2022}. 
@@
 \COMPAS is based on algorithms that model the evolution of massive binary stars following \citet{Hurley+2000, Hurley+2002}, based on detailed evolutionary models by \citet{Pols+1998}.
-The framework used to compute local merger rates of BBH systems is described in \cite{vanson+2022}.
-We refer the reader to their methods section for a detailed description of our adopted physics parameters and assumptions.
+We refer the reader to the methods section of \cite{vanson+2022} for a detailed description of our adopted physics parameters and assumptions.
 
-In Figure \ref{fig: mass dists} we show the mass distribution of the more massive BH from BBH mergers. We will refer to the more (less) massive component as the primary (secondary) from hereon. 
+These simulations provide us with an estimate of the yield of BBH mergers with certain source properties per unit of star-forming mass and metallicity. 
+We sample the metallicities of each binary system from a smooth probability distribution in stead of running batches of binaries at discrete sets of metallicity.
+Smoothly sampling of the birth metallicity avoids artificial peaks in the BH mass distribution \citep[e.g.][]{Dominik2015,Kummer_thesis}.
+
+Lastly, we combine the aforementioned yield with a \SFRDzZ as described in this work.
+By integrating over cosmic history, we obtain the local merger rates of BBH systems, which allow us to construct the distribution of source properties at every redshift.
+The details of this framework are described in \cite{vanson+2022}, but also in \cite{Broekgaarden+2021a} and \cite{Neijssel+2019}.
+
+We consider variations of each of the parameters that determine the shape of the cosmic metallicity distribution \dpdZ (left two columns of Table \ref{tab: fit params}) and two variations of the \SFRDz, where we vary all four parameters at once.
+We have determined reasonable variations by comparing the \SFRDzZ to the high and low metallicity extreme from \cite{Chruslinska+2021} by eye.
+\\
+
+In Figure \ref{fig: mass dists} we show the mass distribution of the more massive component from merging BBHs.
+We will refer to the more (less) massive component as the primary (secondary) from hereon.
 In general we note that the main features in the primary mass distribution remain distinguishable throughout all \SFRDzZ variations. 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Summary and conclusions}
+\section{Discussion and summary \label{sec: summary}}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 We present a flexible analytic expression for the metallicity-dependent starformation rate.
-Such an analytical expression allows 
-we find the low mass end of the mass distribution is least affected the change in the \SFRDzZ.
+Large uncertainties remain in the shape and normalisation of the star formation rate density throughout the Universe.
+
+As an example, we apply our model to calculate the local rate and mass distribution of the more massive components from merging BBHs in Figure \ref{fig: mass dists}). 
+We systematically vary all parameters that shape the cosmic metallicity distribution (\dpdZ), and explore three variations of \SFRDz. 
+We find the low mass end of the mass distribution is least affected the change in the \SFRDzZ. 
+%
+We furthermore conclude that parameters that effect the amount of low metallicity star formation at low redshift mostly affect the local rate $\mathcal{R}_{0.2}$, and normalization of the BBH mass distribution.
+
+%
+Lastly, changing the \SFRDz has a relatively small effect.
 

### 2022-06-27 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Application: systematic variations of \SFRDzZ and the effect on the mass distribution of merging BBHs \label{sec: mass dists}}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}
-\centering
-\script{Plot_Mass_distributions.py}
-\includegraphics[width=0.8\textwidth]{figures/SFRD_variations_combined.pdf}
-\caption{The primary mass distribution of merging BBH systems from isolated binary evolution for several variations in \SFRDzZ. 
-The first five panels show variations of the cosmic metallicity distribution  \dpdZ (eq.
-\ref{eq: z log skew}, parameters listed in the first two columns of Table \ref{tab: fit params}).
-The bottom right panel shows variations in the magnitude of the star formation rate with redshift, i.e.
-\SFRDz.
-For the latter we vary the four fiducial parameters of \SFRDz simultaneously (last two columns of Table \ref{tab: fit params}).
-All panels are shown at a reference redshift of $z=0.2$, with the corresponding predicted BBH merger rate annotated in the legend.
-We show the power-law + peak model from \protect\cite{GWTC3_popPaper2021} in grey.
-Lastly we annotate the relative change in the rate at three reference masses: $10\Msun$, $25\Msun$ and $40\Msun$.
-Variations in \SFRDzZ have the largest impact on the high mass end of the distribution, while around $\Mbheen=10$, variations are smaller than a factor of 3.
-  \label{fig: mass dists}}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-We will now demonstrate the application of our analytical model by systematically varying the parameters in our fiducial \SFRDzZ model, and investigate their effect on the local mass distribution of BBH mergers originating from isolated binaries.
-
-To this end we use the publicly available rapid binary population synthesis simulations as presented in \cite{vanson+2022}. 
-These simulations were run using version v02.19.04 of the open source \COMPAS suite \citep{COMPAS_method} \footnote{\url{https://github.com/TeamCOMPAS/COMPAS}}.
-\COMPAS is based on algorithms that model the evolution of massive binary stars following \citet{Hurley+2000, Hurley+2002}, based on detailed evolutionary models by \citet{Pols+1998}.
-We refer the reader to the methods section of \cite{vanson+2022} for a detailed description of our adopted physics parameters and assumptions.
-
-These simulations provide us with an estimate of the yield of BBH mergers with certain source properties per unit of star-forming mass and metallicity. 
-We sample the metallicities of each binary system from a smooth probability distribution in stead of running batches of binaries at discrete sets of metallicity.
-Smoothly sampling of the birth metallicity avoids artificial peaks in the BH mass distribution \citep[e.g.][]{Dominik2015,Kummer_thesis}.
-
-Lastly, we combine the aforementioned yield with a \SFRDzZ as described in this work.
-By integrating over cosmic history, we obtain the local merger rates of BBH systems, which allow us to construct the distribution of source properties at every redshift.
-The details of this framework are described in \cite{vanson+2022}, but also in \cite{Broekgaarden+2021a} and \cite{Neijssel+2019}.
-
-We consider variations of each of the parameters that determine the shape of the cosmic metallicity distribution \dpdZ (left two columns of Table \ref{tab: fit params}) and two variations of the \SFRDz, where we vary all four parameters at once.
-We have determined reasonable variations by comparing the \SFRDzZ to the high and low metallicity extreme from \cite{Chruslinska+2021} by eye.
-\\
-
-In Figure \ref{fig: mass dists} we show the mass distribution of the more massive component from merging BBHs.
-We will refer to the more (less) massive component as the primary (secondary) from hereon.
-In general we note that the main features in the primary mass distribution remain distinguishable throughout all \SFRDzZ variations. 
-We annotate the relative change between models at three reference masses: $10\Msun$, $25\Msun$ and $40\Msun$. 
-This shows that changes in \SFRDzZ have the largest impact on the high mass end of the primary mass distribution, while at $\Mbheen=10\Msun$, we find at most a factor 3 between the differen \SFRDzZ models.
-
-We find that parameter variations that affect shape of \SFRDzZ at low redshift primarily change the normalisation of the mass distribution.
-These include the width of the cosmic metallicity distribution at $z=0$, $\omega_0$, the mean metallicity of the cosmic metallicity distribution at $z=0$, $\mu_0$, and the skewness of the cosmic metallicity distribution, $\alpha$ (left column of Figure \ref{fig: mass dists}).
-Model variations that increase the amount of star formation at low metallicity (i.e.
-for a low mean metallicity $\mu_0=0.015$ and a wide metallicity distribution $\omega_0 = 1.4$ ) increase the predicted BBH merger rate.
- This is consistent with other work \todo{copy ref from wind paper.}
-
-On the other hand, parameters that change the evolution of the metallicity distribution \dpdZ with redshift, such as $\omega_z$ and $\mu_z$ (top right and centre right panel), primarily affect the slope of the high mass end of the BBH mass distribution.
-Changing the \SFRDz has a surprisingly small effect. 
-\todo{describe difference between 3 papers}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Discussion and summary \label{sec: summary}}

### 2022-06-27 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+\centering
+\script{SFR_z.py}
+\includegraphics[width=\textwidth]{figures/SFR_redshift.pdf}
+\caption{Comparison of different \SFRDz
+ \label{fig: SFR(z)}}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 for a low mean metallicity $\mu_0=0.015$ and a wide metallicity distribution $\omega_0 = 1.4$ ) increase the predicted BBH merger rate.
-This is consistent with other work \todo{copy ref from wind paper.}
+This is consistent with other work that finds merging BBHs form more efficiently at low metallicities \citep[e.g.][]{BelczynskiVink2010, Stevenson+2017,Mapelli2017,Chruslinska2019_effectCO,Broekgaarden+2021b}.
+
 Although a skewed distribution allows the metallicity distribution to extend to lower values, it simultaniously pushes the expected value of the metallicity distribution to higher values.
@@
 
-We present a flexible analytic expression for the metallicity-dependent starformation rate.
-Large uncertainties remain in the shape and normalisation of the star formation rate density throughout the Universe.
+We present a flexible analytic expression for the metallicity-dependent starformation rate, \SFRDzZ (equations \ref{eq: z log skew}, \ref{eq: sfr1} and \ref{eq: total sfrd}).
+A flexible model captures the large uncertainties that remain in the shape and normalisation of the star formation rate density throughout the Universe.
+The novelty of the model presented in this work is that it adopts a skewed-lognormal for the distribution of metallicities at every redshift (\dpdZ).
+The advantage of an analytical expression is that it allows for controlled experiments of the effect of \SFRDzZ on dependent rates, such as the rate and mass distribution of merging BBHs.
+
+We fit our analytical expression for \SFRDzZ to the starforming-gas in the TNG100 simulation, and provide the best fit parameters in Table \ref{tab: fit params}.
+We show that our model captures the shape and general behaviour of the cosmological simulations well (see Figure \ref{fig: fit SFRD}).
 

### 2022-06-27 src/scripts/SFR_z.py
added new figure for sfr

@@ -1,0 +1,191 @@
+# 1D SFR comparison
+import h5py as h5
+import numpy as np
+import matplotlib.pyplot as plt
+import astropy.units as u
+
+from astropy.cosmology import Planck18  as cosmo# Planck 2018
+from astropy.cosmology import z_at_value
+
+from matplotlib import ticker, cm
+from matplotlib import rc
+import matplotlib
+
+# Custom scripts
+import get_ZdepSFRD as Z_SFRD
+
+######################################
+## locations
+save_loc    =  '/Users/lieke/surfdrive/Documents'+'/SFRD_fit/src/tex/figures/' #/n/home04/lvanson/
+TNGlocation = '/Users/lieke/surfdrive/Documents/CompareCOMPAS/'
+
+
+############################
+##PLOT setttings
+matplotlib.rcParams['mathtext.fontset'] = 'stix'
+matplotlib.rcParams['font.family'] = 'STIXGeneral'
+rc('font',**{'family':'sans-serif','sans-serif':['Helvetica']})
+plt.rc('font', family='serif')
+rc('text', usetex=True)
+fsize, SMALL_SIZE, MEDIUM_SIZE, BIGGER_SIZE = 30,20,20,30
+for obj in ['axes','xtick','ytick']:
+    plt.rc(obj, labelsize=MEDIUM_SIZE)          # controls default text sizes
+for obj in ['figure','axes']:
+    plt.rc(obj, titlesize=BIGGER_SIZE)    # fontsize of the tick labels
+plt.rc('font', size=MEDIUM_SIZE)          # controls default text sizes
+plt.rc('legend', fontsize=SMALL_SIZE)    # legend fontsize
+
+
+
+########################################################
+# plot different SFRs
+########################################################
+def plot_SFR(sf_a = 0.017, sf_b = 1.481, sf_c = 4.452,  sf_d = 5.913,
+             redshift_list  = np.linspace(0,15, num=100), x_redshift = True, tmin=0.0, tmax = 13.7):
+    ########################################################
+    # Start plotting
+    fig, ax = plt.subplots(figsize=(12,10))
+
+    if x_redshift:
+        x1  = redshift_list
+    else:
+        x1 = cosmo.lookback_time(redshift_list)
+
+
+    # M&D 14
[…]

### 2022-06-27 src/scripts/SFR_z.py
changing fontsizes etc

@@ -44,7 +44,7 @@ def plot_SFR(sf_a = 0.017, sf_b = 1.481, sf_c = 4.452,  sf_d = 5.913,
              redshift_list  = np.linspace(0,15, num=100), x_redshift = True, tmin=0.0, tmax = 13.7):
     ########################################################
     # Start plotting
-    fig, ax = plt.subplots(figsize=(12,10))
+    fig, ax = plt.subplots(figsize=(10,8))
 
     if x_redshift:
         x1  = redshift_list

### 2022-06-27 src/scripts/SFR_z.py
minor plot change

@@ -27,7 +27,7 @@ matplotlib.rcParams['font.family'] = 'STIXGeneral'
 rc('font',**{'family':'sans-serif','sans-serif':['Helvetica']})
 plt.rc('font', family='serif')
 rc('text', usetex=True)
-fsize, SMALL_SIZE, MEDIUM_SIZE, BIGGER_SIZE = 30,20,20,30
+fsize, SMALL_SIZE, MEDIUM_SIZE, BIGGER_SIZE = 30,30,20,30
 for obj in ['axes','xtick','ytick']:
     plt.rc(obj, labelsize=MEDIUM_SIZE)          # controls default text sizes
 for obj in ['figure','axes']:
@@ -44,7 +44,7 @@ def plot_SFR(sf_a = 0.017, sf_b = 1.481, sf_c = 4.452,  sf_d = 5.913,
              redshift_list  = np.linspace(0,15, num=100), x_redshift = True, tmin=0.0, tmax = 13.7):
     ########################################################
     # Start plotting
-    fig, ax = plt.subplots(figsize=(10,8))
+    fig, ax = plt.subplots(figsize=(12,10))
 
     if x_redshift:
         x1  = redshift_list
@@ -135,19 +135,19 @@ def plot_SFR(sf_a = 0.017, sf_b = 1.481, sf_c = 4.452,  sf_d = 5.913,
     if x_redshift:
         ###################
         #Plotvalues
-        ax.set_xlabel('$\mathrm{redshift}$', fontsize = 30)
+        ax.set_xlabel('$\mathrm{redshift}$', fontsize = 35)
 
         # Find loockback location for each of our redshifts
         redshift_tick_list = [0, 0.5, 2, 3, 6, 10, 12]#[0, 0.5, 1.0, 1.5, 2, 3, 6, 10, 12]
         # And annotate the tick labels :)
         ax2.set_xticks([z for z in redshift_tick_list])
         ax2.set_xticklabels(['${:.1f}$'.format(cosmo.lookback_time(z).value) for z in redshift_tick_list])
-        ax2.set_xlabel('$\mathrm{Lookback \ time \ [Gyr]}$', fontsize = 20)
+        ax2.set_xlabel('$\mathrm{Lookback \ time \ [Gyr]}$', fontsize = 35)
 
     else:
         ###################
[…]

### 2022-06-27 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 \begin{equation}
-\label{eq: SFRD1}
+\label{eq: total sfrd}
+\boxed{
         \SFRDzZ = \SFRDz \times \dPdZ.
+        }
 \end{equation}
@@
 This introduces four parameters, $a$ which sets the overal normalisation and which has the same units as \SFRDz and $b,c$ and $d$ which are unitless and which govern the shape of the overal cosmic starformation rate density with redshift.
+\\
 
-\subsection{Combined function}
-We combine equations \ref{eq: z log skew} and \ref{eq: sfr1} to form a full metallicity specific starformation rate density 
-\begin{equation}
-\label{eq: total sfrd}
-\boxed{
-    \SFRDzZ = \dPdZ \times \SFRDz
-    } \ , 
-\end{equation}
-
-\noindent We fit for the following nine free parameters $\alpha, \mu_0, \mu_z, \omega_0, \omega_z$, which govern the metallicity dependence and $a,b, c$ and $d$, which set the overall starformation rate.
+% \subsection{Combined function}
+Lastly, we combine equations \ref{eq: z log skew} and \ref{eq: sfr1} to form a full metallicity specific starformation rate density as described in equation \ref{eq: total sfrd}.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Analytical fit against Cosmological simulation \label{sec: fit against tng}}
+\section{Fit against Cosmological simulation \label{sec: fit against tng}}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-We fit our newly defined functional form of \SFRDzZ as defined in the previous section to the Illustris-TNG cosmological simulations.
-Below we briefly summarise relevant physics behind the Illustris-TNG simulations, and we elaborate on our choices made during the fitting procedure.
+We fit our newly defined functional form of \SFRDzZ as defined by equations \ref{eq: total sfrd}, \ref{eq: z log skew} and \ref{eq: sfr1} to the Illustris-TNG cosmological simulations. 
+We fit for the following nine free parameters $\alpha, \mu_0, \mu_z, \omega_0, \omega_z$, which govern the metallicity dependence and $a,b, c$ and $d$, which set the overall starformation rate.
+
+Below we briefly discuss the Illustris-TNG simulations, and elaborate on our fitting procedure.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+The IllustrisTNG-project \citep[or TNG in short][]{FirstResTNG_Springel2018,FirstResTNG_Marinacci2018, FirstResTNG_Nelson2018,FirstResTNG_Pillepich2018, FirstResTNG_Naiman2018} considers galaxy formation and evolution through large-scale cosmological hydrodynamical simulations.
+Such simulations provide the tools to study parts of the Universe that are not easily accessible by observations.
+In particular of interest for this work, they simulate the high redshift enrichment of galaxies and the tail of low metallicity star formation at low redshift.
 
-The IllustrisTNG-project considers galaxy formation and evolution through large-scale cosmological hydrodynamical simulations.
-
-\SdM{Insert a description of enrichment and gas recycling. }
-They have been shown to reproduce many of the global properties of galaxies and their scaling relations for a representative portion of the Universe \citep[e.g.][]{FirstResTNG_Naiman2018,Torrey+2021,Genel+2018,Hemler+2021}.These simulations are publicly available\footnote{ \url{https://www.tng-project.org/}} \citep{FirstResTNG_Springel2018,FirstResTNG_Marinacci2018, FirstResTNG_Nelson2018,FirstResTNG_Pillepich2018, FirstResTNG_Naiman2018}.
-
-Different cosmological simulations produce varying \SFRDzZ which lead to different redshift evolution of the BBH merger rate with redshift.
-\cite{Briel+2021} find that the EAGLE and TNG simulation provide the best \SFRDzZ based on the predicted cosmic rates for electromagnetic and gravitational-wave transients.
-Although we only consider our model to describe the IllustrisTNG100 simulation and the phenomenological fit from \cite{Neijssel+2019}, our prescription can be easily be used to fit other observational or simulated data of the metallicity dependent star formation rate density.
+Different cosmological simulations produce varying \SFRDzZ, depending on the adopted assumptions about the creation and distribution of metals.
+For a detailed discussion of the processes that govern the creation, distribution and mixing of metals in in the TNG simulations we refer to \cite{Pakmor+2022}.
+We have chosen to fit of our analytical model to the illustris simulations because I) they have been shown to reproduce many of the global properties of galaxies and their scaling relations for a representative portion of the Universe \citep[e.g.][]{FirstResTNG_Naiman2018,Torrey+2021,Genel+2018,Hemler+2021}.
+II) \cite{Briel+2021} find that the \SFRDzZ from the EAGLE \citep{Schaye+2015,Crain+2015} and TNG simulations provide the best agreement between observed and predicted cosmic rates for electromagnetic and gravitational-wave transients.
+And III) the simulation output is publicly available.\footnote{ \url{https://www.tng-project.org/}}
+Although in this work, we only fit our model to the IllustrisTNG100 simulation, our prescription can be easily be used to fit other observational or simulated data of the metallicity dependent star formation rate density.
 
@@
 
-We use the \texttt{scipy.optimize.minimize} 
-from SciPy v1.6.3 implementation of the optimized quasi-Newton method of Broyden, Fletcher, Goldfarb, and Shanno (BFGS).
-\footnote{\url{http://www.apmath.spbu.ru/cnsa/pdf/monograf/Numerical_Optimization2006.pdf}}
+To minimize this cost funciton, we use \texttt{scipy.optimize.minimize} from SciPy v1.6.3 which implements the quasi-Newton method of Broyden, Fletcher, Goldfarb, and Shanno \citep[BFGS,][]{NocedalWright_numerical_optimization}.
+% \footnote{\url{http://www.apmath.spbu.ru/cnsa/pdf/monograf/Numerical_Optimization2006.pdf}}
 
@@
 
-\begin{deluxetable}{cccc}
+\begin{deluxetable}{clc | cc}
 \label{tab: fit params}
 \tablecaption{Best fitting parameters for our \SFRDzZ fit to TNG100 data.}
-\tablehead{\colhead{dP/dZ param.} & \colhead{best fit} & \colhead{SFRD(z) param.} & \colhead{best fit} } 
+\tablehead{\colhead{dP/dZ } & \colhead{description} & \colhead{best fit} & \colhead{SFRD(z)} & \colhead{best fit} } 
 \startdata
-$\mu_0$ &  0.025 &  $a$ &  0.02 \\
-$\mu_z$ &  -0.048 &  $b$ &  1.48 \\
-$\alpha$ &  -1.767 &  $c$ &  4.45 \\
-$\omega_0$  & 1.125       &  $d$ &  5.90 \\
-$\omega_z$ &  0.048 &   \\
+$\mu_0$    & mean metallicity $z=0$     & 0.025 &  $a$ &  0.02 \\
+$\mu_z$    & mean metallicity $z$ evol. & -0.048 &  $b$ &  1.48 \\
+$\alpha$   & shape (skewness)           & -1.767 &  $c$ &  4.45 \\
+$\omega_0$ & scale $z=0$                & 1.125 &  $d$ &  5.90 \\
+$\omega_z$ & scale $z$ evol.            & 0.048 &   \\
 \enddata
@@
 \script{SFR_z.py}
-\includegraphics[width=\textwidth]{figures/SFR_redshift.pdf}
+\includegraphics[width=0.49\textwidth]{figures/SFR_redshift.pdf}
 \caption{Comparison of different \SFRDz
@@
 We consider variations of each of the parameters that determine the shape of the cosmic metallicity distribution \dpdZ (left two columns of Table \ref{tab: fit params}) and two variations of the \SFRDz, where we vary the complete shape of the \SFRDz (i.e.
-all four parameters) at once to match the values used in \todo{Madaufragos} \cite{Neijssel2019}.
+all four parameters) at once to match the values used in \cite{Madau+2017} and \cite{Neijssel2019} respectively.
 To determine the range of parameters that is reasonably allowed by observations, we compare the \SFRDzZ in the metallicity-redshift plane to the high and low metallicity extreme from \cite{Chruslinska+2021} by eye for every variation.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-We present a flexible analytic expression for the metallicity-dependent starformation rate, \SFRDzZ (equations \ref{eq: z log skew}, \ref{eq: sfr1} and \ref{eq: total sfrd}).
-A flexible model captures the large uncertainties that remain in the shape and normalisation of the star formation rate density throughout the Universe.
+We present a flexible analytic expression for the metallicity-dependent starformation rate, \SFRDzZ (equations \ref{eq: total sfrd}, \ref{eq: z log skew} and \ref{eq: sfr1}).
+Such a flexible model can capture the large uncertainties that remain in the shape and normalisation of the star formation rate density throughout the Universe.
+Moreover, an analytical expression allows for controlled experiments of the effect of \SFRDzZ on dependent rates, such as the rate and mass distribution of merging BBHs.
 The novelty of the model presented in this work is that it adopts a skewed-lognormal for the distribution of metallicities at every redshift (\dpdZ).
-The advantage of an analytical expression is that it allows for controlled experiments of the effect of \SFRDzZ on dependent rates, such as the rate and mass distribution of merging BBHs.
 
 We fit our analytical expression for \SFRDzZ to the starforming-gas in the TNG100 simulation, and provide the best fit parameters in Table \ref{tab: fit params}.
-We show that our model captures the shape and general behaviour of the cosmological simulations well (see Figure \ref{fig: fit SFRD}).
+We show that our model captures the shape and general behaviour of the cosmological simulations well (Figure \ref{fig: fit SFRD}).
 
-As an example, we apply our model to calculate the local rate and mass distribution of the more massive components from merging BBHs in Figure \ref{fig: mass dists}). 
-We systematically vary all parameters that shape the cosmic metallicity distribution (\dpdZ), and explore three variations of \SFRDz. 
-We find the low mass end of the mass distribution is least affected the change in the \SFRDzZ. 
+As an example, we apply our model to calculate the local rate and mass distribution of the more massive components from merging BBHs (\Mbheen) in Figure \ref{fig: mass dists}). 
+We systematically vary all five parameters ($\alpha, \mu_0, \mu_z, \omega_0 and \omega_z$) that shape the cosmic metallicity distribution \dpdZ, and explore two addition variations of \SFRDz \citep[following][respectively]{Madau+2017,Neijssel+2019}.
+
+We find that for all variations, the low mass end of the mass distribution is least affected the change in the \SFRDzZ. 
 %
-We furthermore conclude that parameters that effect the amount of low metallicity star formation at low redshift mostly affect the local rate $\mathcal{R}_{0.2}$, and normalization of the BBH mass distribution.
-
+We furthermore find that the metallicity distribution of star formation at \textit{low redshift}, primarily impacts the \textit{normalisation} of the \Mbheen distribution (i.e.
+the total local rate $\mathcal{R}_{0.2}$).
+On the other hand, parameters that influence the \textit{redshift evolution} of the metallicity distribution, affect the \textit{slope} of the \Mbheen distribution.
+The latter is specifically effective beyond the peak of the \Mbheen distribution which occurs at approximately 18\Msun.
 %
 Lastly, changing the \SFRDz has a relatively small effect.
+
+Star formation is really uncertiain,
 

### 2022-06-27 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 Transient phenomena, including core collapse supernovae, (pulsational) pair-instability supernovae, long gamma-ray bursts and gravitational wave (GW) events are particularly sensitive to the metallicity at which star formation occurs at different epochs throughout the Universe.
-The field of transient astronomy has seen explosive growth in the past few decades due to increased observational capabilities.
-But in order to correctly model and interpret these observations, it is fundamental to know rate of star formation at different metallicities throughout cosmic history (i.e.
-the metallicity-dependent star formation rate density, \SFRDzZ).
+In particular, the field of gravitational astronomy has seen explosive growth in the past decade \citep[][]{GWTC1,GWTC2,GWTC3}.
+In order to correctly model and interpret these observations, it is fundamental to know rate of star formation at different metallicities throughout cosmic history, i.e.
+the metallicity-dependent star formation rate density \SFRDzZ \citep[see also the recent review by][]{chruslinska2022_review}.
 
@@
 
-In Figure \ref{fig: fit SFRD} we show our fiducial \SFRDzZ model at different redshifts and metallicities.
+In Figure \ref{fig: fit SFRD} we show our fiducial \SFRDzZ model at different redshifts and metallicities. For clarity, 
 In general, our analytical model captures the metallicity dependent star formation in the TNG100 simulations well (bottom panels). 
@@
 The \SFRDzZ from \cite{Neijssel+2019} was optimised to match the local rate of double compact object mergers as presented in the second gravitational-wave catalogue.
-However, the resulting symmetric distribution cuts-off virtually all low-metallicity ($Z\leq 10^{-2.5}$) star formation which is inconsistent with \todo{other observations}.
+However, the resulting symmetric distribution cuts-off virtually all low-metallicity ($Z\leq 10^{-2.5}$) star formation.
 % For both \SFRDzZ distributions, most star formation happens at metallicities above $Z \geq 10^{-2}$ (top panel).
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Discussion and summary \label{sec: summary}}
+\section{Summary \label{sec: summary}}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 We present a flexible analytic expression for the metallicity-dependent starformation rate, \SFRDzZ (equations \ref{eq: total sfrd}, \ref{eq: z log skew} and \ref{eq: sfr1}).
-Such a flexible model can capture the large uncertainties that remain in the shape and normalisation of the star formation rate density throughout the Universe.
-Moreover, an analytical expression allows for controlled experiments of the effect of \SFRDzZ on dependent rates, such as the rate and mass distribution of merging BBHs.
+An analytical expression allows for controlled experiments of the effect of \SFRDzZ on dependent rates, such as the rate and mass distribution of merging BBHs.
 The novelty of the model presented in this work is that it adopts a skewed-lognormal for the distribution of metallicities at every redshift (\dpdZ).
@@
 
-Star formation is really uncertiain,
+The flexibility of the model presented in this work can capture the large uncertainties that remain in the shape and normalisation of the metallicity dependent cosmic star formation history.
+As such, we anticipate that it will be a helpful tool in other works that present \SFRDzZ dependent rates.
 

### 2022-06-27 src/scripts/Plot_Mass_distributions.py
small beautifying changes to plots

@@ -150,19 +150,18 @@ def plot_mass_distribution(sim_dir = '', x_key = 'M_moreMassive', rate_keys = ['
 		print('rate_key', rate_key)
 
 		# ### ## Reading Rate data ##
-		# try:
-		#     DCO_mask, redshifts, intrinsic_rate_density, intrinsic_rate_density_z0  = mfunc.read_rate_data(loc = sim_dir + '/Rate_info.hdf5', rate_key = rate_key)
-		## Open hdf5 file
-		with h5.File(sim_dir + '/Rate_info.hdf5' ,'r') as File:
-			redshifts                 = File['redshifts'][()]
-			# Different per rate key:
-			DCO_mask                  = File[rate_key]['DCOmask'][()] # Mask from DCO to merging systems  
-			#(contains filter for RLOF>CE and optimistic CE)
-			intrinsic_rate_density    = File[rate_key]['merger_rate'][()]
+		try:
+			#     DCO_mask, redshifts, intrinsic_rate_density, intrinsic_rate_density_z0  = mfunc.read_rate_data(loc = sim_dir + '/Rate_info.hdf5', rate_key = rate_key)
+			with h5.File(sim_dir + '/Rate_info.hdf5' ,'r') as File:
+				redshifts                 = File['redshifts'][()]
+				# Different per rate key:
+				DCO_mask                  = File[rate_key]['DCOmask'][()] # Mask from DCO to merging systems  
+				#(contains filter for RLOF>CE and optimistic CE)
+				intrinsic_rate_density    = File[rate_key]['merger_rate'][()]
 
-		# except:
-			# print('\n error reading', rate_key)
-			# continue
+		except:
+			print('\n error reading', rate_key)
+			continue
 	    
 		# # # # # # # # # # # # # # # # # # 
 		#first bring it to the same shape as the rate table
@@ -250,7 +249,7 @@ def plot_mass_distribution(sim_dir = '', x_key = 'M_moreMassive', rate_keys = ['
 
 	#########################################
 	# plot values
-	plt.text(0.90, 0.90, titletext, ha = 'right', transform=ax.transAxes, size = 25)
+	plt.text(0.70, 0.85, titletext, ha = 'center', transform=ax.transAxes, size = 25)
 
 	ax.set_xlim(x_lim)
 	ax.set_ylim(y_lim)
[…]

### 2022-06-27 src/scripts/SFR_z.py

@@ -27,7 +27,7 @@ matplotlib.rcParams['font.family'] = 'STIXGeneral'
 rc('font',**{'family':'sans-serif','sans-serif':['Helvetica']})
 plt.rc('font', family='serif')
 rc('text', usetex=True)
-fsize, SMALL_SIZE, MEDIUM_SIZE, BIGGER_SIZE = 30,30,20,30
+fsize, SMALL_SIZE, MEDIUM_SIZE, BIGGER_SIZE = 30,20,20,30
 for obj in ['axes','xtick','ytick']:
     plt.rc(obj, labelsize=MEDIUM_SIZE)          # controls default text sizes
 for obj in ['figure','axes']:
@@ -65,7 +65,7 @@ def plot_SFR(sf_a = 0.017, sf_b = 1.481, sf_c = 4.452,  sf_d = 5.913,
     #default Coen
     ax.plot(x1, Z_SFRD.Madau_Dickinson2014(redshift_list, a=0.01, b=2.77, c=2.9, d=4.7), 
              label = 'Neijssel et al 2019\n $a=%.2f, b=%.2f, c=%.2f, d=%.2f$'% (0.01,2.77,2.9,4.7)
-             , c = '#aacfdd', lw=5, ls = '--')
+             , c = 'grey', lw=5, ls = ':')#aacfdd
 
 
     # BEST FIT
@@ -135,19 +135,19 @@ def plot_SFR(sf_a = 0.017, sf_b = 1.481, sf_c = 4.452,  sf_d = 5.913,
     if x_redshift:
         ###################
         #Plotvalues
-        ax.set_xlabel('$\mathrm{redshift}$', fontsize = 35)
+        ax.set_xlabel('$\mathrm{redshift}$', fontsize = 30)
 
         # Find loockback location for each of our redshifts
-        redshift_tick_list = [0, 0.5, 2, 3, 6, 10, 12]#[0, 0.5, 1.0, 1.5, 2, 3, 6, 10, 12]
+        redshift_tick_list = [0, 1.0, 2, 3, 6, 10, 12]#[0, 0.5, 1.0, 1.5, 2, 3, 6, 10, 12]
         # And annotate the tick labels :)
         ax2.set_xticks([z for z in redshift_tick_list])
-        ax2.set_xticklabels(['${:.1f}$'.format(cosmo.lookback_time(z).value) for z in redshift_tick_list])
[…]

### 2022-06-27 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 % Title
-\title{ A convenient, flexible and intuitive analytic expression for the metallicity-dependent cosmic star formation rate  }
+\title{ A flexible and intuitive analytic expression for the metallicity-dependent cosmic star formation rate  }
 
@@
 \begin{abstract}
-New observational facilities are probing star formation and stellar transients and gravitational wave sources at ever increasing redshifts.
-Comparing these observations with predictions from model for stellar populations or the channels for the formation of gravitational wave sources require assumptions for the cosmic starformation rate density and, in particular, how this depends on metallicity.
-Various approaches exist ranging from fully empirical prescriptions to prescriptions that are based on cosmological simulations.
-Both these approaches come with advantages and disadvantages and inherent uncertainties.
+New observational facilities are probing astrophysical transients such as gravitational wave (GW) sources at ever increasing redshifts.
+To interpret these observation we need to compare them to predictions from stellar population models.
+These models are very sensitive to the metallicity-dependent star formation rate density (\SFRDzZ).
+% Large uncertainties remain in the value and shape of the \SFRDzZ, especially at the low metallicities that are crucial to the formation of GW events.
+Understanding the behaviour of the adopted \SFRDzZ is thus essential to explain simulation results. 
+%
+% Various approaches to approximate \SFRDzZ exist, ranging from fully empirical prescriptions to prescriptions that are based on cosmological simulations.
+In this work, we propose a simple analytical form for \SFRDzZ.
+The novelty of this model lies in a skewed-lognormal distribution of metallicities, that captures the tail of low metallicity star formation at low redshift.
+Variations of this analytical form can be easily interpreted, because the parameters are intuitively linked to the shape of \SFRDzZ.
+%Our hope is that this expression provides a useful starting point for making predictions and comparison with observations.
+%
+We fit our analytical form to the starforming gas of the cosmological TNG100 simulations and find our model is able to capture the main behaviour. 
+%
+As an example, we investigate the effect of systematic variations in the \SFRDzZ parameters on the predicted mass distribution of locally merging binary black holes (BBH).
+Our main findings are I) the low mass end is least affected by variations in \SFRDzZ, II) the distribution of metallicities at low redshift affects the normalisation of of the BBH merger rate, while III) the redshift evolution of the metallicity distribution affects the slope of the mass distribution beyond the peak value.
+\end{abstract}
 
-To make it easier to produce model predictions we propose a simple analytical prescription that captures the main behaviour of the advanced simulations.
-At the same time, the prescription comes with parameters that allow for variations in the overall shape and which can be easily interpreted.
-Our hope is that this expression provides a useful starting point for making predictions and comparison with observations.
-\end{abstract}
+% Interpreting these observations requires comparison to predictions from stellar population models.
+However, the model predictions  are very sensitive to the adopted assumptions about the metallicity-dependent star formation rate density.
+Hence in order to
+% Comparing these observations to predictions from stellar population models requires assumptions about the metallicity-dependent star formation rate density. Various approaches exist 
+% ranging from fully empirical prescriptions to prescriptions that are based on cosmological simulations. Both these approaches come with advantages and disadvantages and inherent uncertainties.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Since the delay time of binary black holes (BBHs) can range from Myrs to multiple Gyrs, the birth environment of BBHs varies significantly and we cannot ignore the cosmological (metallicity) evolution of the Universe.
-% The rate of Binary Black Hole (BBH) mergers at different redshifts depends both on the delay time distribution as well as the metallicity dependent star-formation rate density (\SFRDzZ).
-% The assumed cosmic star formation rate density (SFRD) will therefore greatly influence the observed rate of double compact object mergers \citep{Neijssel+2019, Chruslinska2019_obs, Boco2020,Broekgaarden+2021a}.
-% Moreover, it is the nuclear reactions in massive stars are responsible for the metal enrichment of the Universe at high redshift.
-The birth of massive stars, and their death as BHs are thus inseparable from the evolution of the metallicity distribution of the Universe.
-
-% %%  metallicity density distribution %%
-% Merging BBHs are found to form more efficiently at low metallicities e.g.
-\citep[e.g.][]{BelczynskiVink2010, Stevenson+2017,Mapelli2017,Chruslinska2019_effectCO}.
-Therefore the assumed metallicity specific star formation rate will in particular have a large impact on the inferred merger rate \citep[e.g.][]{Chruslinska2019_obs,Chruslinska2019_effectCO, Neijssel2019, Broekgaarden+2021a}.
-
 A myriad of astrophysical phenomena depend critically on the rate of star formation throughout the cosmic history of the Universe.
@@
 in units of $\left[ \Msun \,yr^{-1} \,cMpc^{-3} \right]$.
-This introduces four parameters, $a$ which sets the overal normalisation and which has the same units as \SFRDz and $b,c$ and $d$ which are unitless and which govern the shape of the overal cosmic starformation rate density with redshift.
+This introduces four parameters, $a$ which sets the overal normalisation and which has the same units as \SFRDz and $b,c$ and $d$ which are unitless and which govern the shape of the overal cosmic star formation rate density with redshift.
 \\
@@
 % \subsection{Combined function}
-Lastly, we combine equations \ref{eq: z log skew} and \ref{eq: sfr1} to form a full metallicity specific starformation rate density as described in equation \ref{eq: total sfrd}.
+Lastly, we combine equations \ref{eq: z log skew} and \ref{eq: sfr1} to form a full metallicity specific star formation rate density as described in equation \ref{eq: total sfrd}.
 
@@
 \script{FitComparison_3panelPlot.py}
-\includegraphics[width=\textwidth]{figures/SFRD_FIT_evaluation_compare.pdf}
+\includegraphics[width=0.9\textwidth]{figures/SFRD_FIT_evaluation_compare.pdf}
 \caption{Our fiducial \SFRDzZ model, adopting the best fitting parameters (listed on the top right) to fit the TNG100 simulations.
@@
 We fit our newly defined functional form of \SFRDzZ as defined by equations \ref{eq: total sfrd}, \ref{eq: z log skew} and \ref{eq: sfr1} to the Illustris-TNG cosmological simulations. 
-We fit for the following nine free parameters $\alpha, \mu_0, \mu_z, \omega_0, \omega_z$, which govern the metallicity dependence and $a,b, c$ and $d$, which set the overall starformation rate.
+We fit for the following nine free parameters $\alpha, \mu_0, \mu_z, \omega_0, \omega_z$, which govern the metallicity dependence and $a,b, c$ and $d$, which set the overall star formation rate.
 
@@
 For the purposes we have in mind, it will be more important to prioritise fitting the large scale trends, while we are not so interested in smaller scale fluctuations.
-We further prioritise getting the bulk of the cosmic star formation right and are less interested in capturing the behaviour in metallicity and redshift bins where the cosmic starformation rate is very low and thus insignificant for the overall picture.
+We further prioritise getting the bulk of the cosmic star formation right and are less interested in capturing the behaviour in metallicity and redshift bins where the cosmic star formation rate is very low and thus insignificant for the overall picture.
 Finally, we are especially interested in capturing the asymmetry of the metallicity distribution.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-We fit equation \ref{eq: total sfrd} to the metallicity-dependent starformation rate of the starforming gas in the TNG100 simulation.
+We fit equation \ref{eq: total sfrd} to the metallicity-dependent star formation rate of the starforming gas in the TNG100 simulation.
 For this we use a binned version of the TNG data $\SFRDzZ_{\rm sim}$.
 We consider metallicities between $Z= -5$ to $\log_{10} Z= 0$ in 30 bins, where we use $Z_i$ to refer to the logarithmic centers of the bins.
-We ignore star formation in metallicities $\log_{10} Z \le -5$ as this accounts for less than 1\% of the total cosmic starformation rate in these simulations.
-
+We ignore star formation in metallicities $\log_{10} Z \le -5$ as this accounts for less than 1\% of the total cosmic star formation rate in these simulations.
 We consider bins in redshifts between $z=0$ and $z=10$, with a step size of $dz=0.05$, where $z_j$ refers to the centers of the bins.
@@
 To find a solution we use a method based on the sum of the quadratic differences between the simulations and our fit function.
-Using a vanilla $\chi$-squared approach does not serve our purposes very well as it does a poor job in fitting regions where the starformation is very low.
-Using a $\chi$-squared approach on the logarithm of the function instead places far too much weight on trying to fit the starformation rate in regions where the rate is very low or not even significant.
+Using a vanilla $\chi$-squared approach does not serve our purposes very well as it does a poor job in fitting regions where the star formation is very low.
+Using a $\chi$-squared approach on the logarithm of the function instead places far too much weight on trying to fit the star formation rate in regions where the rate is very low or not even significant.
 After experimenting, we find that the following approach gives us satisfactory results.
@@
 %
-Here, the variable $Z_i$ runs over all redshift bins, but excludes bins where the starformation rate density is lower $10^{-10} \Msun \yr \Mpc^{-3}$ per bin.
+Here, the variable $Z_i$ runs over all redshift bins, but excludes bins where the star formation rate density is lower $10^{-10} \Msun \yr \Mpc^{-3}$ per bin.
 
 Subsequently we sum the $\chi^2 (z_j)$ for all redshift bins $z_j$.
-To ensure that our fit procedure gives sufficient weight to the behaviour at all redshifts, we find that we need to introduce a penalisation factor to somewhat reduce the contribution of redshifts where the peak of cosmic starformation occurs, while increasing the weight where at redshifts where the overal cosmic starformation rate is lower.
-To achieve this we divide $\chi^2 (z_j)$ by the starformation $\sum_{Z_i} \mathcal{S}(Z_i,z_j)$ per redshift bin before adding the contribution of all redshifts.
+To ensure that our fit procedure gives sufficient weight to the behaviour at all redshifts, we find that we need to introduce a penalisation factor to somewhat reduce the contribution of redshifts where the peak of cosmic star formation occurs, while increasing the weight where at redshifts where the overal cosmic star formation rate is lower.
+To achieve this we divide $\chi^2 (z_j)$ by the star formation $\sum_{Z_i} \mathcal{S}(Z_i,z_j)$ per redshift bin before adding the contribution of all redshifts.
 Our final expression for the cost function reads
@@
 
-In Figure \ref{fig: fit SFRD} we show our fiducial \SFRDzZ model at different redshifts and metallicities. For clarity, 
-In general, our analytical model captures the metallicity dependent star formation in the TNG100 simulations well (bottom panels). 
+In Figure \ref{fig: fit SFRD} we show our fiducial \SFRDzZ model at different redshifts and metallicities.
+For clarity, we also show the overal rate of star formation \SFRDz in Figure \ref{fig: SFR(z)}.
+In general, our analytical model captures the metallicity dependent star formation in the TNG100 simulations well (bottom panels of Figure \ref{fig: fit SFRD}). 
 The skewed-log normal metallicity distribution is able to reproduce the overall behaviour that is observed in TNG100 \citep[bottom left panel, but cf.
@@
 \script{SFR_z.py}
-\includegraphics[width=0.49\textwidth]{figures/SFR_redshift.pdf}
+\includegraphics[width=0.47\textwidth]{figures/SFR_redshift.pdf}
 \caption{Comparison of different \SFRDz
@@
 
-We consider variations of each of the parameters that determine the shape of the cosmic metallicity distribution \dpdZ (left two columns of Table \ref{tab: fit params}) and two variations of the \SFRDz, where we vary the complete shape of the \SFRDz (i.e.
-all four parameters) at once to match the values used in \cite{Madau+2017} and \cite{Neijssel2019} respectively.
+We consider variations of each of the parameters that determine the shape of the cosmic metallicity distribution \dpdZ (left two columns of Table \ref{tab: fit params}) and two variations of the \SFRDz, where we keep the metallicity distribution \dpdZ fixed, but we vary the complete shape of the \SFRDz (i.e.
+all four parameters) at once to match the values used in \cite{Madau+2017} and \cite{Neijssel2019} respectively (see Figure \ref{fig: SFR(z)} for reference).
 To determine the range of parameters that is reasonably allowed by observations, we compare the \SFRDzZ in the metallicity-redshift plane to the high and low metallicity extreme from \cite{Chruslinska+2021} by eye for every variation.
@@
 
-% The normalization at z=0 changes the overal rate / normalization
+% The normalisation at z=0 changes the overal rate / normalisation
 We find that parameter variations that affect shape of \SFRDzZ at low redshift primarily change the normalisation of the mass distribution (see also  $\mathcal{R}_{0.2}$, the total BBH merger rate at redshift 0.2, annotated in the legends of Figure \ref{fig: mass dists}).
@@
 % Effect of the star formation 
-Lastly, changing the \SFRDz has a relatively small effect. 
+Lastly, changing the \SFRDz has a relatively small effect. We vary 
 The \SFRDz from \cite{Madau+2017} and \cite{Neijssel+2019} both peak at approximately redshift 2.
 Our fiducial model (that follows the \SFRDz from TNG) peaks at about redshift 3.
-The overall normalization of \cite{Neijssel+2019} is higher than the normalization of our fiducial model.
+The overall normalisation of \cite{Neijssel+2019} is higher than the normalisation of our fiducial model.
 Regardless of these differences, the rate of BBH mergers at $z=0.2$ changes no more than 20\%, and the shape of the primary mass distribution remains almost constant.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-We present a flexible analytic expression for the metallicity-dependent starformation rate, \SFRDzZ (equations \ref{eq: total sfrd}, \ref{eq: z log skew} and \ref{eq: sfr1}).
+We present a flexible analytic expression for the metallicity-dependent star formation rate, \SFRDzZ (equations \ref{eq: total sfrd}, \ref{eq: z log skew} and \ref{eq: sfr1}).
 An analytical expression allows for controlled experiments of the effect of \SFRDzZ on dependent rates, such as the rate and mass distribution of merging BBHs.
@@
 
-We fit our analytical expression for \SFRDzZ to the starforming-gas in the TNG100 simulation, and provide the best fit parameters in Table \ref{tab: fit params}.
+We fit our analytical expression for \SFRDzZ to the star-forming gas in the TNG100 simulation, and provide the best fit parameters in Table \ref{tab: fit params}.
 We show that our model captures the shape and general behaviour of the cosmological simulations well (Figure \ref{fig: fit SFRD}).
@@
 As an example, we apply our model to calculate the local rate and mass distribution of the more massive components from merging BBHs (\Mbheen) in Figure \ref{fig: mass dists}). 
-We systematically vary all five parameters ($\alpha, \mu_0, \mu_z, \omega_0 and \omega_z$) that shape the cosmic metallicity distribution \dpdZ, and explore two addition variations of \SFRDz \citep[following][respectively]{Madau+2017,Neijssel+2019}.
+We systematically vary all five parameters ($\alpha, \mu_0, \mu_z, \omega_0$ and $\omega_z$) that shape the cosmic metallicity distribution \dpdZ, and explore two addition variations of \SFRDz, following \cite{Madau+2017} and \cite{Neijssel+2019} respectively.
 
@@
 The flexibility of the model presented in this work can capture the large uncertainties that remain in the shape and normalisation of the metallicity dependent cosmic star formation history. 
-As such, we anticipate that it will be a helpful tool in other works that present \SFRDzZ dependent rates.
+Our hope is that this expression will provide a useful starting point for making predictions and comparison with observations.
+% As such, we anticipate that it will be a helpful tool in other works that present \SFRDzZ dependent rates.
 

### 2022-06-28 src/scripts/Plot_Mass_distributions.py
removed files and renamed plot

@@ -97,7 +97,7 @@ def plot_mass_distribution(sim_dir = '', x_key = 'M_moreMassive', rate_keys = ['
 	# GWTC-3 Powerlaw + Peak Mass distribution
 	################################################ 
 	if plot_LIGO:
-		LIGO_data_dir = '/Volumes/StorageSpac/CompasOutput//output/'#'/n/home04/lvanson/LowMBH_peak/output/'
+		LIGO_data_dir = '/Volumes/StorageSpac/CompasOutput/output/'#'/n/home04/lvanson/LowMBH_peak/output/'
 		#################################################
 		## prep to grab Powerlaw + Peak data from O3
 		#################################################
@@ -389,7 +389,7 @@ ax6 = plot_mass_distribution(sim_dir = data_dir, x_key = 'M_moreMassive',
 
 ####################################################
 # Final plot properties
-fig.savefig(save_loc+'/SFRD_variations_combined.pdf' , bbox_inches='tight')
+fig.savefig(save_loc+'/Mass_distributions_all_SFRD_variations.pdf' , bbox_inches='tight')
 # plt.show()
 
 

### 2022-06-28 src/scripts/TestZenodoData.py
trying to get zenodo data incorporated

@@ -1,0 +1,16 @@
+# Trying to get Zenodo data to work
+import h5py as h5
+import numpy as np
+
+save_loc    =  '/Users/lieke/surfdrive/Documents'+'/SFRD_fit/src/tex/figures/' #/n/home04/lvanson/
+
+data_dir = 'src/data/vanSon21/COMPAS_Output_wRates/'
+data = h5.File(data_dir + 'COMPAS_Output_wWeights.h5', 'r')
+
+print(data.keys())
+
+data.close
+
+fix,ax = plt.subplots()
+ax.plot(np.linspace(0,1,10),np.linspace(0,1,10))
+plt.savefig(save_loc + 'testdata.jpg')

### 2022-06-28 src/scripts/CosmicIntegration/ClassCOMPAS.py
further testing of zenodo data

@@ -1,0 +1,431 @@
+#!/usr/bin/env python3
+import numpy as np
+import h5py as h5
+import os
+import totalMassEvolvedPerZ as MPZ
+import astropy.units as u
+
+class COMPASData(object):
+    def __init__(
+        self,
+        path=None,
+        fileName="COMPAS_Output.h5",
+        lazyData=True,
+        Mlower=None,
+        Mupper=None,
+        m2_min=None,
+        binaryFraction=None,
+        suppress_reminder=False,
+    ):
+        self.path = path
+        self.fileName = fileName
+        if self.path is None:
+            print("Just to double check you create instance of ClassCOMPAS without path/Data")
+        elif not os.path.isfile(path + fileName):
+            raise ValueError(
+                "h5 file not found. Wrong path given? %s" % (path + fileName)
+            )
+
+        # Crucial values to be able to calculate MSSFR
+        self.metallicityGrid = None
+        self.metallicitySystems = None
+        self.delayTimes = None  # Myr
+        # Crucial values I need for selection effects
+        self.mass1 = None  # Msun
+        self.mass2 = None  # Msun
+        self.DCOmask = None
+        self.allTypesMask = None
+        self.BBHmask = None
+        self.DNSmask = None
+        self.BHNSmask = None
+        self.initialZ = None
+        self.sw_weights = None
+        self.n_systems = None
+
+        # Additional arrays that might be nice to store
+        # to more quickly make some plots.
+        # If you need more memory might help a tiny bit to not do
+        self.lazyData = lazyData
+        self.mChirp = None  # Msun
+        self.q = None
+        self.optimisticmask = None
+
+        # Needed to recover true solar mass evolved
+        self.Mlower = Mlower  # Msun
+        self.Mupper = Mupper  # Msun
+        self.m2_min = m2_min # Msun
+        self.binaryFraction = binaryFraction
+        self.totalMassEvolvedPerZ = None  # Msun
+        self.mass_evolved_per_binary = None # Msun
+
+        if not suppress_reminder:
+            print("ClassCOMPAS: Remember to self.setCOMPASDCOmask()")
+            print("                    then self.setCOMPASData()")
+            print("          and optionally self.setGridAndMassEvolved() if using a metallicity grid")
+
+    def setCOMPASDCOmask(
[…]

### 2022-06-28 src/scripts/CosmicIntegration/FastCosmicIntegration.py

@@ -1,0 +1,863 @@
+import numpy as np
+import h5py  as h5
+import os
+import time
+import matplotlib.pyplot as plt
+from astropy.cosmology import WMAP9 as cosmology
+import scipy
+from scipy.interpolate import interp1d
+from scipy.stats import norm as NormDist
+import ClassCOMPAS
+import selection_effects
+import warnings
+import astropy.units as u
+import argparse
+
+def calculate_redshift_related_params(max_redshift=10.0, max_redshift_detection=1.0, redshift_step=0.001, z_first_SF = 10.0):
+    """ 
+        Given limits on the redshift, create an array of redshifts, times, distances and volumes
+
+        Args:
+            max_redshift           --> [float]          Maximum redshift to use for calculations
+            max_redshift_detection --> [float]          Maximum redshift to calculate detection rates (must be <= max_redshift)
+            redshift_step          --> [float]          size of step to take in redshift
+            z_first_SF             --> [float]          redshift of first star formation
+
+        Returns:
+            redshifts              --> [list of floats] List of redshifts between limits supplied
+            n_redshifts_detection  --> [int]            Number of redshifts in list that should be used to calculate detection rates
+            times                  --> [list of floats] Equivalent of redshifts but converted to age of Universe
+            distances              --> [list of floats] Equivalent of redshifts but converted to luminosity distances
+            shell_volumes          --> [list of floats] Equivalent of redshifts but converted to shell volumes
+    """
+    # create a list of redshifts and record lengths
+    redshifts = np.arange(0, max_redshift + redshift_step, redshift_step)
+    n_redshifts_detection = int(max_redshift_detection / redshift_step)
+
+    # convert redshifts to times and ensure all times are in Myr
+    times = cosmology.age(redshifts).to(u.Myr).value
+
+    # and time of first Sf
+    time_first_SF = cosmology.age(z_first_SF).to(u.Myr).value
+
+    # convert redshifts to distances and ensure all distances are in Mpc (also avoid D=0 because division by 0)
+    distances = cosmology.luminosity_distance(redshifts).to(u.Mpc).value
+    distances[0] = 0.001
+
+    # convert redshifts to volumnes and ensure all volumes are in Gpc^3
+    volumes = cosmology.comoving_volume(redshifts).to(u.Gpc**3).value
+
[…]

### 2022-06-28 src/scripts/TestZenodoData.py

@@ -1,15 +1,16 @@
 # Trying to get Zenodo data to work
 import h5py as h5
 import numpy as np
+import matplotlib.pyplot as plt
 
 save_loc    =  '/Users/lieke/surfdrive/Documents'+'/SFRD_fit/src/tex/figures/' #/n/home04/lvanson/
 
-data_dir = 'src/data/vanSon21/COMPAS_Output_wRates/'
-data = h5.File(data_dir + 'COMPAS_Output_wWeights.h5', 'r')
+data_dir = 'src/data/vanSon21/'
+# data = h5.File(data_dir + 'COMPAS_Output_wWeights.h5', 'r')
 
-print(data.keys())
+# print(data.keys())
 
-data.close
+# data.close
 
 fix,ax = plt.subplots()
 ax.plot(np.linspace(0,1,10),np.linspace(0,1,10))

### 2022-06-28 src/scripts/TestZenodoData.py
last try local

@@ -6,7 +6,26 @@ import matplotlib.pyplot as plt
 save_loc    =  '/Users/lieke/surfdrive/Documents'+'/SFRD_fit/src/tex/figures/' #/n/home04/lvanson/
 
 data_dir = 'src/data/vanSon21/'
-data = h5.File(data_dir + 'COMPAS_Output_wWeights.h5', 'r')
+
+
+
+
+# import tarfile
+
+# tar = tarfile.open(data_dir + 'COMPAS_Output_wRates.tar.gz', "r:gz")
+
+# for tarinfo in tar:
+#     print(tarinfo.name, "is", tarinfo.size, "bytes in size and is")
+#     if tarinfo.isreg():
+#         print("a regular file.")
+#     elif tarinfo.isdir():
+#         print("a directory.")
+#     else:
+#         print("something else.")
+# tar.close()
+
+
+data = h5.File(data_dir + 'COMPAS_Output_wRates.tar.gz', 'r')#'COMPAS_Output_wWeights.h5', 'r')
 
 print(data.keys())
 
@@ -17,3 +36,4 @@ data.close
 fix,ax = plt.subplots()
 ax.plot(np.linspace(0,1,10),np.linspace(0,1,10))
 plt.savefig(save_loc + 'testdata.jpg')
+

### 2022-06-28 src/scripts/TestZenodoData.py
switching to extracting through python instead

@@ -8,24 +8,20 @@ save_loc    =  '/Users/lieke/surfdrive/Documents'+'/SFRD_fit/src/tex/figures/' #
 data_dir = 'src/data/vanSon21/'
 
 
+# importing the "tarfile" module
+import tarfile
+  
+# open file
+file = tarfile.open(data_dir + 'COMPAS_Output_wRates.tar.gz')
+  
+# extracting file
+file.extractall(data_dir)
+print('extracting data to',data_dir)
+file.close()
 
 
-# import tarfile
 
-# tar = tarfile.open(data_dir + 'COMPAS_Output_wRates.tar.gz', "r:gz")
-
-# for tarinfo in tar:
-#     print(tarinfo.name, "is", tarinfo.size, "bytes in size and is")
-#     if tarinfo.isreg():
-#         print("a regular file.")
-#     elif tarinfo.isdir():
-#         print("a directory.")
-#     else:
-#         print("something else.")
-# tar.close()
-
-
-data = h5.File(data_dir + 'COMPAS_Output_wRates.tar.gz', 'r')#'COMPAS_Output_wWeights.h5', 'r')
+data = h5.File(data_dir + 'COMPAS_Output_wWeights.h5', 'r')#'COMPAS_Output_wWeights.h5', 'r')
 
 print(data.keys())
 

### 2022-06-28 src/scripts/TestZenodoData.py
improving extract

@@ -2,30 +2,33 @@
 import h5py as h5
 import numpy as np
 import matplotlib.pyplot as plt
+import os
+import tarfile
 
 save_loc    =  '/Users/lieke/surfdrive/Documents'+'/SFRD_fit/src/tex/figures/' #/n/home04/lvanson/
-
 data_dir = 'src/data/vanSon21/'
 
 
-# importing the "tarfile" module
-import tarfile
-  
-# open file
-file = tarfile.open(data_dir + 'COMPAS_Output_wRates.tar.gz')
-  
-# extracting file
-file.extractall(data_dir)
-print('extracting data to',data_dir)
-file.close()
+out_fname = data_dir +'COMPAS_Output_wWeights.h5'
+tar_name  = data_dir + 'COMPAS_Output_wRates.tar.gz'
 
 
+# check if file exists, if not, extract it
+if not os.path.isfile(out_fname):
+    print('file %s does not exist, extract', out_fname)
+	# open file
+	file = tarfile.open(tar_name)
+	 
+	# extracting file
+	file.extractall(data_dir)
+	file.close()
+else:
+    print('file %s exists, nothing to do', out_fname)
 
-data = h5.File(data_dir + 'COMPAS_Output_wWeights.h5', 'r')#'COMPAS_Output_wWeights.h5', 'r')
-
-print(data.keys())
 
 print('!!! Je bent nu in deze file!!!!')
+data = h5.File(out_fname, 'r')
+print(data.keys())
 
 data.close
 

### 2022-06-29 src/scripts/CallCosmicIntegration.py
fixed the cosmic integration from start to finish

@@ -1,128 +1,0 @@
-"""
-This script makes a slrum job to run FastCosmicIntegration with a specified set of 
-"""
-#####################################
-# dpdZ_parameters = [mu0_best, muz_best, sigma0_best, sigmaz_best, alpha0_best]
-#####################################
-mu0_best     = 0.025
-muz_best     = -0.049
-sigma0_best  = 1.129
-sigmaz_best  = 0.048
-alpha0_best  = -1.778
-
-#####################################
-# sfr_parameters  = [sf_a_best, sf_b_best, sf_c_best, sf_d_best]
-#####################################
-sf_a_best     = 0.017
-sf_b_best     = 1.481
-sf_c_best     = 4.452
-sf_d_best     = 5.913
-
-user_email = 'aac.van.son@gmail.com'
-
-###############################################
-###
-###############################################
-def RunSlurmBatch(run_dir = None, job_name = "stroopwafel_interface", dependency = False, dependent_ID = None):
-    if not dependency:
-        sbatchArrayCommand = 'sbatch ' + os.path.join(run_dir+job_name+'.sbatch') 
-    else:
-        sbatchArrayCommand = 'sbatch --dependency=afterok:' + str(int(dependent_ID)) + ' ' + os.path.join(run_dir+job_name+'.sbatch') 
-
-    # Open a pipe to the sbatch command.
-    proc = Popen(sbatchArrayCommand, shell=True, stdin=PIPE, stdout=PIPE, stderr=PIPE, close_fds=True)
-
-    # Send job_string to sbatch
-    if (sys.version_info > (3, 0)):
-        proc.stdin.write(sbatchArrayCommand.encode('utf-8'))
-    else:
-        proc.stdin.write(sbatchArrayCommand)
-
-    print('sbatchArrayCommand:', sbatchArrayCommand)
-    out, err = proc.communicate()
-    print("out = ", out)
-    job_id = out.split()[-1]
-    print("job_id", job_id)
-    return job_id
-
-
-#########################################################
-# Assuming you have The COMPAS simulation data output
-# Make a slurm job to call 
-def Call_Cosmic_Integration(root_out_dir, COMPASfilename, rate_file_name, 
-                            ZdepSFRD_param_sets = [[dpdZ_parameters, sfr_parameters]]
-                           partitions = 'demink,conroy,hernquist,shared', Wtime = "5:00:00", mem = "150000"):
-        """
-        Call slurm batch 
-
-        Args:
[…]

### 2022-06-29 src/scripts/CosmicIntegration/CallCosmicIntegration.py

@@ -1,0 +1,225 @@
+"""
+This script makes a slrum job to run FastCosmicIntegration with a specified set of 
+"""
+import numpy as np
+import os
+from subprocess import Popen, PIPE, call
+import subprocess
+import sys
+
+
+#####################################
+# dpdZ_parameters = [mu0_best, muz_best, sigma0_best, sigmaz_best, alpha0_best]
+#####################################
+mu0_best     = 0.025
+muz_best     = -0.049
+sigma0_best  = 1.129
+sigmaz_best  = 0.048
+alpha0_best  = -1.778
+
+#####################################
+# sfr_parameters  = [sf_a_best, sf_b_best, sf_c_best, sf_d_best]
+#####################################
+sf_a_best     = 0.017
+sf_b_best     = 1.481
+sf_c_best     = 4.452
+sf_d_best     = 5.913
+
+
+#################################################################
+## 
+##   Should be Changed by user ##
+##
+#################################################################
+#################################################################
+root_dir     = '/n/home04/lvanson/SFRD_fit/'
+root_out_dir = root_dir+'src/data/'
+# "/n/holystore01/LABS/hernquist_lab/Users/lvanson/CompasOutput/v02.19.04/SFRD_fit_data/"
+
+COMPASfilename  = 'COMPAS_Output_wWeights.h5'
+rate_file_name  = 'Rate_info.hdf5'
+user_email      = "aac.van.son@gmail.com"
+
+fid_dpdZ_parameters = [mu0_best, muz_best, sigma0_best, sigmaz_best, alpha0_best]
+fid_sfr_parameters  = [sf_a_best, sf_b_best, sf_c_best, sf_d_best]
+
+
+##################################################################
+# This is the slurm script youre using
+#SBATCH --partition=%s              # Partition to submit to
+##################################################################
+SlurmJobString="""#!/bin/bash
+#SBATCH --job-name=%s          #job name
+#SBATCH --nodes=%s             # Number of nodes
+#SBATCH --ntasks=%s            # Number of cores
+#SBATCH --output=%s            # output storage file
+#SBATCH --error=%s             # error storage file
+#SBATCH --time=%s              # Runtime in minutes
+#SBATCH --mem=%s               # Memory per cpu in MB (see also --mem-per-cpu)
+#SBATCH -p %s
+#SBATCH --mail-user=%s         # Send email to user
+#SBATCH --mail-type=FAIL       #
+#
+#Print some stuff on screen
+echo $SLURM_JOB_ID
[…]

### 2022-06-29 src/scripts/CosmicIntegration/FastCosmicIntegration.py

@@ -472,7 +472,7 @@ def find_detection_rate(path, filename="COMPAS_Output.h5", dco_type="BBH", weigh
     return detection_rate, formation_rate, merger_rate, redshifts, COMPAS, Average_SF_mass_needed, shell_volumes
 
 
-def append_rates(path, filename, detection_rate, formation_rate, merger_rate, redshifts, COMPAS, Average_SF_mass_needed, shell_volumes, n_redshifts_detection,
+def append_rates(path, filename, outfilename, detection_rate, formation_rate, merger_rate, redshifts, COMPAS, Average_SF_mass_needed, shell_volumes, n_redshifts_detection,
     maxz=5., sensitivity="O1", dco_type="BHBH", mu0=0.035, muz=-0.23, sigma0=0.39, sigmaz=0., alpha=0., aSF = 0.01, bSF = 2.77, cSF = 2.90, dSF = 4.70,
     append_binned_by_z = False, redshift_binsize=0.1):
     """
@@ -481,6 +481,7 @@ def append_rates(path, filename, detection_rate, formation_rate, merger_rate, re
         Args:
             path                   --> [string] Path to the COMPAS file that contains the output
             filename               --> [string] Name of the COMPAS file
+            outfilename            --> [string] Name of the hdf5 file that you want to write your rates to
             detection_rate         --> [2D float array] Detection rate for each binary at each redshift in 1/yr
             formation_rate         --> [2D float array] Formation rate for each binary at each redshift in 1/yr/Gpc^3
             merger_rate            --> [2D float array] Merger rate for each binary at each redshift in 1/yr/Gpc^3
@@ -512,21 +513,32 @@ def append_rates(path, filename, detection_rate, formation_rate, merger_rate, re
     print('path', path)
 
     #################################################
-    #Open hdf5 file that we will write on
+    #Open hdf5 file that we will read from
     print('filename', filename)
-    with h5.File(path +'/'+ filename, 'r+') as h_new:
+    with h5.File(path +'/'+ filename, 'r+') as f_COMPAS:
+        
+        # Would you like to write your rates to a different file? 
+        if filename != outfilename:
+            #'you want to save your output to a different file!'
[…]

### 2022-06-29 src/scripts/Plot_Mass_distributions.py

@@ -103,7 +103,7 @@ def plot_mass_distribution(sim_dir = '', x_key = 'M_moreMassive', rate_keys = ['
         ## grab Powerlaw + Peak data from O3
         #################################################  
         #'/Volumes/StorageSpac/CompasOutput/output/'#'/n/home04/lvanson/LowMBH_peak/output/GWTC-3-population-data/analyses/PowerLawPeak/'
-        input_fname = LIGO_data_dir+'o3only_mass_c_iid_mag_iid_tilt_powerlaw_redshift_mass_data.h5'
+        input_fname = data_dir+'o3only_mass_c_iid_mag_iid_tilt_powerlaw_redshift_mass_data.h5'
         mass_1 = np.linspace(2, 100, 1000)
         mass_ratio = np.linspace(0.1, 1, 500)
         with h5.File(input_fname, "r") as f:
@@ -139,18 +139,18 @@ def plot_mass_distribution(sim_dir = '', x_key = 'M_moreMassive', rate_keys = ['
         print('rate_key', rate_key)
 
         # ### ## Reading Rate data ##
-        try:
+#         try:
             #     DCO_mask, redshifts, intrinsic_rate_density, intrinsic_rate_density_z0  = mfunc.read_rate_data(loc = sim_dir + '/Rate_info.hdf5', rate_key = rate_key)
-            with h5.File(sim_dir + '/Rate_info.hdf5' ,'r') as File:
-                redshifts                 = File['redshifts'][()]
-                # Different per rate key:
-                DCO_mask                  = File[rate_key]['DCOmask'][()] # Mask from DCO to merging systems  
-                #(contains filter for RLOF>CE and optimistic CE)
-                intrinsic_rate_density    = File[rate_key]['merger_rate'][()]
+        with h5.File(sim_dir + '/Rate_info.hdf5' ,'r') as File:
+            redshifts                 = File[rate_key]['redshifts'][()]
+            # Different per rate key:
+            DCO_mask                  = File[rate_key]['DCOmask'][()] # Mask from DCO to merging systems  
+            #(contains filter for RLOF>CE and optimistic CE)
+            intrinsic_rate_density    = File[rate_key]['merger_rate'][()]
 
-        except:
-            print('\n error reading', rate_key)
-            continue
+#         except:
[…]

### 2022-06-29 src/scripts/FitComparison_3panelPlot.py
trying to fix build

@@ -31,9 +31,9 @@ def Mchirp(m1, m2):
     chirp_mass = np.divide(np.power(np.multiply(m1, m2), 3./5.), np.power(np.add(m1, m2), 1./5.))
     return chirp_mass    
    
-base_dir    = '/Users/lieke/surfdrive/Documents/RateMassRedshiftEvolution/'
-save_loc    =  base_dir+'/plots/'
-TNGlocation = '/Users/lieke/surfdrive/Documents/CompareCOMPAS/'
+# base_dir    = '/Users/lieke/surfdrive/Documents/RateMassRedshiftEvolution/'
+# save_loc    =  base_dir+'/plots/'
+TNGlocation = 'src/data/'#'/Users/lieke/surfdrive/Documents/CompareCOMPAS/'
 
 ############################
 # Custom scripts

### 2022-06-29 src/scripts/SFR_z.py

@@ -16,8 +16,8 @@ import get_ZdepSFRD as Z_SFRD
 
 ######################################
 ## locations
-save_loc    =  '/Users/lieke/surfdrive/Documents'+'/SFRD_fit/src/tex/figures/' #/n/home04/lvanson/
-TNGlocation = '/Users/lieke/surfdrive/Documents/CompareCOMPAS/'
+save_loc    =  'src/tex/figures/' #/n/home04/lvanson/ '/Users/lieke/surfdrive/Documents'+SFRD_fit
+TNGlocation = 'src/data/' #'/Users/lieke/surfdrive/Documents/CompareCOMPAS/'
 
 
 ############################

### 2022-06-30 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 
+\author[0000-0002-8901-6994]{Martyna Chru{\'s}li{\'n}ska}
+\affiliation{Max Planck Institute for Astrophysics, Karl-Schwarzschild-Str. 1, 85748 Garching, Germany}
+
 \author{et al?}
@@
 % Large uncertainties remain in the value and shape of the \SFRDzZ, especially at the low metallicities that are crucial to the formation of GW events.
-Understanding the behaviour of the adopted \SFRDzZ is thus essential to explain simulation results. 
+Understanding the behaviour of the adopted \SFRDzZ is essential to explain simulation results. 
 %
@@
 \script{Plot_Mass_distributions.py}
-\includegraphics[width=0.8\textwidth]{figures/SFRD_variations_combined.pdf}
+\includegraphics[width=0.8\textwidth]{figures/Mass_distributions_all_SFRD_variations.pdf}
 \caption{The primary mass distribution of merging BBH systems from isolated binary evolution for several variations in \SFRDzZ. 

### 2022-07-01 src/scripts/ExtractZenodoData.py
added option to split dist by channel

@@ -4,10 +4,9 @@ import numpy as np
 import matplotlib.pyplot as plt
 import os
 import tarfile
+import paths
 
-save_loc    =  '/Users/lieke/surfdrive/Documents'+'/SFRD_fit/src/tex/figures/' #/n/home04/lvanson/
-data_dir = 'src/data/vanSon21/'
-
+data_dir = paths.data 
 
 out_fname = data_dir +'COMPAS_Output_wWeights.h5'
 tar_name  = data_dir + 'COMPAS_Output_wRates.tar.gz'
@@ -32,7 +31,5 @@ print(data.keys())
 
 data.close
 
-fix,ax = plt.subplots()
-ax.plot(np.linspace(0,1,10),np.linspace(0,1,10))
-plt.savefig(save_loc + 'testdata.jpg')
+
 

### 2022-07-01 src/scripts/Plot_Mass_distributions.py

@@ -8,6 +8,10 @@ import sys
 import numpy as np
 import matplotlib.pyplot as plt
 
+import matplotlib
+# configure backend here
+matplotlib.use('Agg')
+
 import seaborn as sns
 from scipy import stats
 
@@ -29,14 +33,27 @@ import MassDistHelperFunctions as mfunc
 importlib.reload(mfunc)
 
 import gc
+import paths
 
 
 ######################################
 ## locations
-save_loc    =  'src/tex/figures/'#'/Users/lieke/surfdrive/Documents'+'/SFRD_fit/src/tex/figures/' #/n/home04/lvanson/
-data_dir    =  'src/data/'
-# '/Volumes/StorageSpac'+'/CompasOutput/v02.19.04/SFRD_fit_data/fWR1.0coolWind1.0/output/' # '/n/holystore01/LABS/hernquist_lab/Users/lvanson/'
+save_loc    =  str(paths.figures) + '/'
+data_dir    =  str(paths.data) + '/'
 
+rate_file       = '/Rate_info.hdf5'#'small_Rate_info.hdf5' #
+simulation_data = '/COMPAS_Output_wWeights.h5'#'/small_COMPAS_Output_wWeights.h5' 
+
+only_stable = True 
+only_CE = True
+ 
+
+if np.logical_and(only_stable, only_CE):
+    channel_string = 'all'
+elif only_stable:
+    channel_string = 'stable'
+elif only_CE:
+    channel_string = 'CE'
 
 ######################################
 ## PLOT setttings
@@ -64,6 +81,7 @@ plt.rc('legend', fontsize=SMALL_SIZE)    # legend fontsize
 def plot_mass_distribution(sim_dir = '', x_key = 'M_moreMassive', rate_keys = ['Rates_mu00.025_muz-0.05_alpha-1.77_sigma0%s_sigmaz0.05_zBinned'%(x) for x in [0.8, 1.125, 1.4]],
                    bins = np.arange(0.,55,2.5), z_bin_edges = [0,0.25], 
                    plot_LIGO = False, show_hist = False, show_KDE = True, kde_width = 0.1,  
+                   only_stable = True, only_CE = True, 
                    bootstrap = False, bootstraps = 10, x_lim=(0.,50),  y_lim = (1e-2,30), 
                    Color = '#e388b0', linestyles = ['--','-', ':'], titletext = '',
[…]

### 2022-07-01 src/scripts/CosmicIntegration/CallCosmicIntegration.py
setting up zenodo cachinn

@@ -6,7 +6,6 @@ import os
 from subprocess import Popen, PIPE, call
 import subprocess
 import sys
-sys.path.insert(0,'../')
 import paths
 
 
@@ -34,9 +33,7 @@ sf_d_best     = 5.913
 ##
 #################################################################
 #################################################################
-# root_dir     = '/n/home04/lvanson/SFRD_fit/'
-root_out_dir = str(paths.data) + '/' #root_dir+'src/data/'
-# "/n/holystore01/LABS/hernquist_lab/Users/lvanson/CompasOutput/v02.19.04/SFRD_fit_data/"
+root_out_dir = str(paths.data) + '/' 
 
 COMPASfilename  = 'COMPAS_Output_wWeights.h5'
 rate_file_name  = 'Rate_info.hdf5'

### 2022-07-01 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 Traditionally the metallicity density distribution is estimated by combining a mass-metallicity relation (MZ-relation) and a galaxy stellar mass function (GSMF) \citep[see also][]{Chruslinska+2018, Chruslinska2019_effectCO, Broekgaarden+2021a}.
-Another way is to extract the metallicity density fraction from cosmological simulations \citep[e.g.]{Mapelli2017, Schneider+2017}
+Another way is to extract the metallicity density fraction from cosmological simulations \citep[e.g.]{Mapelli2017, Briel+2021}.
+% A third option is extract this information from cosmological simulations \citep[e.g.][]{Mapelli+2017,Schneider+2017}.
 Alternatively, one can combine an observed star formation rate, \SFRDz, like from \cite{MadauDickinson2014} or \cite{Madau+2017}, and convolve this with some belief about the shape of the metallicity density distribution, such as was was done in \cite{Neijssel+2019}.
-A third option is extract this information from cosmological simulations \citep[e.g.][]{Mapelli+2017,Schneider+2017}.
+
+%Arguments: cosmological simulations work at high z,  but are they real? observations 
 In this work we provide an analytical model which we fit to the \SFRDzZ based on the TNG 100 simulation \citep{Pillepich2018, Weinberger2017}.
+% %
+\todo{add motivation for this shape and paper (use some of the text below) .}
+The task we have at hand here is not a standard textbook fitting problem given the specific aims and requirements that we have that are driven by the astrophysical applications we have in mind.
+Qualitatively, our aims are the following.
+Our main aim is to find solution for the free parameters, for which the expression reproduces the overall behaviour that is observed in the cosmological simulations.
+For the purposes we have in mind, it will be more important to prioritise fitting the large scale trends, while we are not so interested in smaller scale fluctuations.
+We further prioritise getting the bulk of the cosmic star formation right and are less interested in capturing the behaviour in metallicity and redshift bins where the cosmic star formation rate is very low and thus insignificant for the overall picture.
+Finally, we are especially interested in capturing the asymmetry of the metallicity distribution.
+There is not one unique procedure that will full fill these criteria.
+After experimenting with different criteria we have adopted the procedure below, which we believe works well for the aims we have in mind.
+%%
 
@@
 
-% %
-% The task we have at hand here is not a standard textbook fitting problem given the specific aims and requirements that we have that are driven by the astrophysical applications we have in mind.
-Qualitatively, our aims are the following.
-Our main aim is to find solution for the free parameters, for which the expression reproduces the overall behaviour that is observed in the cosmological simulations.
-For the purposes we have in mind, it will be more important to prioritise fitting the large scale trends, while we are not so interested in smaller scale fluctuations.
-We further prioritise getting the bulk of the cosmic star formation right and are less interested in capturing the behaviour in metallicity and redshift bins where the cosmic star formation rate is very low and thus insignificant for the overall picture.
-Finally, we are especially interested in capturing the asymmetry of the metallicity distribution.
-% There is not one unique procedure that will full fill these criteria.
-After experimenting with different criteria we have adopted the procedure below, which we believe works well for the aims we have in mind.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 For a detailed discussion of the processes that govern the creation, distribution and mixing of metals in in the TNG simulations we refer to \cite{Pakmor+2022}.
-We have chosen to fit of our analytical model to the illustris simulations because I) they have been shown to reproduce many of the global properties of galaxies and their scaling relations for a representative portion of the Universe \citep[e.g.][]{FirstResTNG_Naiman2018,Torrey+2021,Genel+2018,Hemler+2021}.
+We have chosen to fit of our analytical model to the publicly available illustris simulations\footnote{ \url{https://www.tng-project.org/}}  because I) they have been shown to reproduce many of the \todo{geef concrete list (appendix other paper) }
+% The simulations were originally calibrated against the observed total cosmic star formation rate density and the stellar mass function of galaxies \citep{Pillepich2018}.
+They reproduce the evolution of the sizes of galaxies with redshift \citep{Genel+2018} and with observational constraints on the mass-metallicity relation of
+% galaxies up to z = 2 \citep{Torrey+2019} as well as iron abundances \citep{FirstResTNG_Naiman2018} and
+% the metallicity gradients within galaxies at low redshift \citep{Hemler+2021}.
+These simulations have also already been used to make predictions for gravitational wave sources through pairing with  predictions for the outcomes of binary evaluation obtained with the BPASS code \citet{Briel+2021}.
+global properties of galaxies and their scaling relations for a representative portion of the Universe \citep[e.g.][]{FirstResTNG_Naiman2018,Torrey+2021,Genel+2018,Hemler+2021}. 
 II) \cite{Briel+2021} find that the \SFRDzZ from the EAGLE \citep{Schaye+2015,Crain+2015} and TNG simulations provide the best agreement between observed and predicted cosmic rates for electromagnetic and gravitational-wave transients.
-And III) the simulation output is publicly available.\footnote{ \url{https://www.tng-project.org/}}
+% And III) the simulation output is publicly available.\footnote{ \url{https://www.tng-project.org/}} 
+%
 Although in this work, we only fit our model to the IllustrisTNG100 simulation, our prescription can be easily be used to fit other observational or simulated data of the metallicity dependent star formation rate density.
@@
 The first five panels show variations of the cosmic metallicity distribution  \dpdZ (eq.
-\ref{eq: z log skew}, parameters listed in the first two columns of Table \ref{tab: fit params}).
+\ref{eq: z log skew}, parameters listed in the first three columns of Table \ref{tab: fit params}).
 The bottom right panel shows variations in the magnitude of the star formation rate with redshift, i.e.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\todo{bullet point met one liners : paragraaf }
 We present a flexible analytic expression for the metallicity-dependent star formation rate, \SFRDzZ (equations \ref{eq: total sfrd}, \ref{eq: z log skew} and \ref{eq: sfr1}).

### 2022-07-01 src/scripts/Plot_Mass_distributions.py
testing dependencies

@@ -41,8 +41,8 @@ import paths
 save_loc    =  str(paths.figures) + '/'
 data_dir    =  str(paths.data) + '/'
 
-rate_file       = '/Rate_info.hdf5'#'small_Rate_info.hdf5' #
-simulation_data = '/COMPAS_Output_wWeights.h5'#'/small_COMPAS_Output_wWeights.h5' 
+rate_file       = 'small_Rate_info.hdf5' #'/Rate_info.hdf5'#
+simulation_data = '/small_COMPAS_Output_wWeights.h5' #'/COMPAS_Output_wWeights.h5'#
 
 only_stable = True 
 only_CE = True
@@ -176,15 +176,14 @@ def plot_mass_distribution(sim_dir = '', x_key = 'M_moreMassive', rate_keys = ['
 
         #apply the additional mask based on your prefs
         if np.logical_and(only_stable, only_CE):
-            raise ValueError("Both only_stable and only_CE, I assume you just want both")
+            print("Both only_stable and only_CE, I assume you just want both")
             channel_bool = np.full(len(merging_BBH), True)
         elif only_stable:
             channel_bool = merging_BBH['CE_Event_Count'] == 0
         elif only_CE:
             channel_bool = merging_BBH['CE_Event_Count'] > 0
         else:
-            #Apparently you don't want to plot anything
-            channel_bool = np.full(len(merging_BBH), False)
+            raise ValueError("Both only_stable =%s and only_CE=%s, set at least one to true"%(only_stable,only_CE))
 
         # we exclude CHE systems
         not_CHE = merging_BBH['Stellar_Type@ZAMS(1)'] != 16

### 2022-07-01 src/scripts/ExtractZenodoData.py
fixing extract

@@ -6,10 +6,10 @@ import os
 import tarfile
 import paths
 
-data_dir = paths.data 
+data_dir = str(paths.data)
 
-out_fname = data_dir +'COMPAS_Output_wWeights.h5'
-tar_name  = data_dir + 'COMPAS_Output_wRates.tar.gz'
+out_fname = data_dir +'/COMPAS_Output_wWeights.h5'
+tar_name  = data_dir + '/COMPAS_Output_wRates.tar.gz'
 
 
 # check if file exists, if not, extract it

### 2022-07-01 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 In particular of interest for this work, they simulate the high redshift enrichment of galaxies and the tail of low metallicity star formation at low redshift.
+Different cosmological simulations produce varying \SFRDzZ, depending on the adopted assumptions about the creation and distribution of metals.
 
-Different cosmological simulations produce varying \SFRDzZ, depending on the adopted assumptions about the creation and distribution of metals.
-For a detailed discussion of the processes that govern the creation, distribution and mixing of metals in in the TNG simulations we refer to \cite{Pakmor+2022}.
-We have chosen to fit of our analytical model to the publicly available illustris simulations\footnote{ \url{https://www.tng-project.org/}}  because I) they have been shown to reproduce many of the \todo{geef concrete list (appendix other paper) }
-% The simulations were originally calibrated against the observed total cosmic star formation rate density and the stellar mass function of galaxies \citep{Pillepich2018}.
-They reproduce the evolution of the sizes of galaxies with redshift \citep{Genel+2018} and with observational constraints on the mass-metallicity relation of
-% galaxies up to z = 2 \citep{Torrey+2019} as well as iron abundances \citep{FirstResTNG_Naiman2018} and
-% the metallicity gradients within galaxies at low redshift \citep{Hemler+2021}.
-These simulations have also already been used to make predictions for gravitational wave sources through pairing with  predictions for the outcomes of binary evaluation obtained with the BPASS code \citet{Briel+2021}.
-global properties of galaxies and their scaling relations for a representative portion of the Universe \citep[e.g.][]{FirstResTNG_Naiman2018,Torrey+2021,Genel+2018,Hemler+2021}. 
-II) \cite{Briel+2021} find that the \SFRDzZ from the EAGLE \citep{Schaye+2015,Crain+2015} and TNG simulations provide the best agreement between observed and predicted cosmic rates for electromagnetic and gravitational-wave transients.
-% And III) the simulation output is publicly available.\footnote{ \url{https://www.tng-project.org/}} 
-%
-Although in this work, we only fit our model to the IllustrisTNG100 simulation, our prescription can be easily be used to fit other observational or simulated data of the metallicity dependent star formation rate density.
+The models implemented in the publicly available TNG simulations\footnote{ \url{https://www.tng-project.org/}} have lead to many successes.
+For a more extended discussion focused on the processes that govern the creation, distribution and mixing of metals in in the TNG simulations we refer to \cite{Pakmor+2022}.
+In short, star formation in the TNG simulations is calibrated against the Kennicutt–Schmidt relation \citep[][]{Schmidt1959,Kennicutt1989}.
+The stellar metallicity yields were updated with respect to the original Illustris simulations as described in \cite{Pillepich2018}.
+Star particles deposit metals into the gas through Type Ia and Type II supernovae, as well as through Asymptotic Giant Branch mass loss.
+% Positives on TNG
+The TNG simulations have been shown to match observational constraints on the mass-metallicity relation of galaxies up to $z = 2$ \citep{Torrey+2019}, as well as iron abundances \citep{FirstResTNG_Naiman2018} and the metallicity gradients within galaxies at low redshift \citep{Hemler+2021}.
+%They reproduce the evolution of the sizes of galaxies with redshift \citep{Genel+2018}
+Several studies have already used the TNG simulations to make predictions for astronomical transient sources \citep[e.g.][]{Briel+2021,Bavera+2022}.
+In particular, \cite{Briel+2021} find that the \SFRDzZ from the TNG and the EAGLE \citep{Schaye+2015,Crain+2015} simulations provide the best agreement between observed and predicted cosmic rates for electromagnetic and gravitational-wave transients.
+
+% Downsides of TNG100 
+On the other hand, large uncertainties and crude approximations remain, also in the TNG simulations.
+For example, dust is not included in the TNG simulations, which could mean that metallicity of the star-forming gas is overestimated.
+Moreover, all mass loss from massive stellar winds \citep[e.g.][]{Dray+2003}, pair-pulsational supernovae \citep[e.g.][]{Renzo+2020} and binary interactions \citep[e.g.][]{Farmer2021_carbonfootprint} are ignored.
+Furthermore, the ionising background is turned on abruptly at $z=6$, again not accounting for the ionising contribution from stripped stars \citep[][]{Gotberg+2020,DoughtyFinlator2021}.
+
+These large uncertainties call for a generalised form of the \SFRDzZ that can be easily updated when new information becomes available, which is the motivation for this work.
+Although here, we only fit our model to the TNG100 simulation, our prescription can be easily be used to fit other simulated data or observational data of the metallicity dependent star formation rate density \footnote{We provide a Jupyter notebook to facilitate this fit here \todo{add link}}.
 

### 2022-07-04 src/scripts/Plot_Mass_distributions.py
trying to make workflow work

@@ -41,8 +41,8 @@ import paths
 save_loc    =  str(paths.figures) + '/'
 data_dir    =  str(paths.data) + '/'
 
-rate_file       = '/small_Rate_info.h5'#'small_Rate_info.h5' #'/Rate_info.h5'#
-simulation_data = '//small_COMPAS_Output_wWeights.h5'#'/small_COMPAS_Output_wWeights.h5' #'/COMPAS_Output_wWeights.h5'#
+rate_file       = '/RateData/small_Rate_info.h5'#'small_Rate_info.h5' #'/Rate_info.h5'#
+simulation_data = '/small_COMPAS_Output_wWeights.h5'#'/small_COMPAS_Output_wWeights.h5' #'/COMPAS_Output_wWeights.h5'#
 
 only_stable = True 
 only_CE = True

### 2022-07-04 src/scripts/CosmicIntegration/LinkHdf5Files.py
fixing child issue

@@ -18,40 +18,40 @@ if __name__ == "__main__":
 	# Initialize values
 	CI.init()
 
-    ###############################
-    ###############################
-    print('Now link all rate files in one final file')
-    if os.path.isfile(CI.root_out_dir+'/RateData/'+CI.rate_file_name):
-        dest_file = h5py.File(CI.root_out_dir+'/RateData/'+CI.rate_file_name,'r+')                                                                         # Open the final file that will contain all the links
-    else:
-        dest_file = h5py.File(CI.root_out_dir+'/RateData/'+CI.rate_file_name,'w')                                                                         # Create a new final file that will contain all the links
+	###############################
+	###############################
+	print('Now link all rate files in one final file')
+	if os.path.isfile(CI.root_out_dir+'/RateData/'+CI.rate_file_name):
+		dest_file = h5py.File(CI.root_out_dir+'/RateData/'+CI.rate_file_name,'r+')                                                                         # Open the final file that will contain all the links
+	else:
+		dest_file = h5py.File(CI.root_out_dir+'/RateData/'+CI.rate_file_name,'w')                                                                         # Create a new final file that will contain all the links
 
-    for dirpath, dirnames, filenames in os.walk(CI.root_out_dir+'/RateData/'):                                                                          # walk directory
-        absDirpath = os.path.abspath(dirpath)                                                                                       # absolute path
-        print('Processing directory', absDirpath)                                                                                   # announce directory being processed
-        #
-        for filename in filenames:                                                                                                  # for each filename
-            if fnmatch(filename, '*_' + CI.rate_file_name):                                                                               # filename matches filter?
-                src_filename = absDirpath + '/' + filename
-                print('you will be copying file',src_filename)
-                src_data     = h5py.File(absDirpath+'/'+filename, 'r')
-                #
-                for srcGroupName in src_data.keys():                                                                                 # For every group
-                    #
-                    for srcdataName in src_data[srcGroupName].keys():                                                                 # And every data set
-                        #
-                        if srcGroupName +'/'+srcdataName in  dest_file :         # Check if link already existst
-                            print('link exists, delete it before recreating')
[…]

### 2022-07-04 src/scripts/CosmicIntegration/LinkHdf5Files.py
fixing child issue

@@ -21,12 +21,12 @@ if __name__ == "__main__":
 	###############################
 	###############################
 	print('Now link all rate files in one final file')
-	if os.path.isfile(CI.root_out_dir+'/RateData/'+CI.rate_file_name):
-		dest_file = h5py.File(CI.root_out_dir+'/RateData/'+CI.rate_file_name,'r+')                                                                         # Open the final file that will contain all the links
+	if os.path.isfile(CI.data_dir+'/RateData/'+CI.rate_file_name):
+		dest_file = h5py.File(CI.data_dir+'/RateData/'+CI.rate_file_name,'r+')                                                                         # Open the final file that will contain all the links
 	else:
-		dest_file = h5py.File(CI.root_out_dir+'/RateData/'+CI.rate_file_name,'w')                                                                         # Create a new final file that will contain all the links
+		dest_file = h5py.File(CI.data_dir+'/RateData/'+CI.rate_file_name,'w')                                                                         # Create a new final file that will contain all the links
 
-	for dirpath, dirnames, filenames in os.walk(CI.root_out_dir+'/RateData/'):                                                                          # walk directory
+	for dirpath, dirnames, filenames in os.walk(CI.data_dir+'/RateData/'):                                                                          # walk directory
 		absDirpath = os.path.abspath(dirpath)                                                                                       # absolute path
 		print('Processing directory', absDirpath)                                                                                   # announce directory being processed
 		#

### 2022-07-04 src/tex/ms.tex
[showyourwork] overleaf sync

--- 2022-06-30 src/tex/ms.tex
@@
 %
-We fit our analytical form to the starforming gas of the cosmological TNG100 simulations and find our model is able to capture the main behaviour. 
+We fit our analytical form to the star-forming gas of the cosmological TNG100 simulations and find that it is able to capture the main behaviour well. 
 %
-As an example, we investigate the effect of systematic variations in the \SFRDzZ parameters on the predicted mass distribution of locally merging binary black holes (BBH).
-Our main findings are I) the low mass end is least affected by variations in \SFRDzZ, II) the distribution of metallicities at low redshift affects the normalisation of of the BBH merger rate, while III) the redshift evolution of the metallicity distribution affects the slope of the mass distribution beyond the peak value.
+As an example application, we investigate the effect of systematic variations in the \SFRDzZ parameters on the predicted mass distribution of locally merging binary black holes (BBH).
+Our main findings are I) the low mass end is least affected by variations in \SFRDzZ, II) the distribution of metallicities at low redshift affects the normalisation of of the BBH merger rate, while III) the redshift evolution of the metallicity distribution affects the high-mass slope of the mass distribution and IV) the shape of the overall star-formation rate has a small impact on the local mass distribution.
 \end{abstract}
@@
 A myriad of astrophysical phenomena depend critically on the rate of star formation throughout the cosmic history of the Universe.
-Transient phenomena, including core collapse supernovae, (pulsational) pair-instability supernovae, long gamma-ray bursts and gravitational wave (GW) events are particularly sensitive to the metallicity at which star formation occurs at different epochs throughout the Universe.
-In particular, the field of gravitational astronomy has seen explosive growth in the past decade \citep[][]{GWTC1,GWTC2,GWTC3}.
-In order to correctly model and interpret these observations, it is fundamental to know rate of star formation at different metallicities throughout cosmic history, i.e.
+Transient phenomena, including core collapse supernovae, (pulsational) pair-instability supernovae, long gamma-ray bursts and gravitational wave (GW) events are especially sensitive to the metallicity at which star formation occurs at different epochs throughout the Universe.
+Gravitational astronomy in particular has seen explosive growth in the number of detections in the past decade \citep[][]{GWTC1,GWTC2,GWTC3}.
+In order to correctly model and interpret these observations, it is fundamental to know the rate of star formation at different metallicities throughout cosmic history, i.e.
 the metallicity-dependent star formation rate density \SFRDzZ \citep[see also the recent review by][]{chruslinska2022_review}.
@@
 Even at low redshifts, the low metallicity part of the distribution is poorly constrained \citep{Chruslinska+2021}.
-Traditionally the metallicity density distribution is estimated by combining a mass-metallicity relation (MZ-relation) and a galaxy stellar mass function (GSMF) \citep[see also][]{Chruslinska+2018, Chruslinska2019_effectCO, Broekgaarden+2021a}.
-Another way is to extract the metallicity density fraction from cosmological simulations \citep[e.g.]{Mapelli2017, Schneider+2017}
+Nonetheless, several methods exist to estimate the metallicity dependent star-formation rate.
+The first method combines a mass-metallicity relation (MZ-relation) and a galaxy stellar mass function (GSMF) \citep[see e.g.][]{Chruslinska+2018, Chruslinska2019_effectCO, Broekgaarden+2021a}.
+Another way is to directly extract the metallicity density fraction from cosmological simulations \citep[e.g.]{Mapelli2017, Briel+2021}.
 Alternatively, one can combine an observed star formation rate, \SFRDz, like from \cite{MadauDickinson2014} or \cite{Madau+2017}, and convolve this with some belief about the shape of the metallicity density distribution, such as was was done in \cite{Neijssel+2019}.
-A third option is extract this information from cosmological simulations \citep[e.g.][]{Mapelli+2017,Schneider+2017}.
-In this work we provide an analytical model which we fit to the \SFRDzZ based on the TNG 100 simulation \citep{Pillepich2018, Weinberger2017}.
 
+%Arguments: cosmological simulations work at high z,  but are they real? observations 
+In this work we follow the latter approach and propose a flexible analytical model for the \SFRDzZ that can be fit to the output of both cosmological simulations, and observational data constraints where available.
+The novelty of this model lies in a skewed-lognormal distribution of metallicities, that captures the tail of low metallicity star formation at low redshift.
+The purpose of this model is to allow for an intuitive interpretation of the effects of the \SFRDzZ on the inferred rates of astrophysical transients.
+By adopting an analytical, parametrized form for \SFRDzZ, the large uncertainties in \SFRDzZ can be systematically explored.% through varying the parameters that control its shape.
+
+We describe our model for \SFRDzZ in Section \ref{sec: model for sfrd(zZ)}.
+We fit our model to to the star-forming gas in the Illustris TNG100 simulation in Section \ref{sec: mass dists} we demonstrate an example application of our model by systematically varying the parameters that determine the shape of \SFRDzZ and investigate their impact on the local distribution of merging BBH masses.
+We summarise our findings in Section \ref{sec: summary}.
+
+% %
+% The task we have at hand here is not a standard textbook fitting problem given the specific aims and requirements that we have that are driven by the astrophysical applications we have in mind.
+Qualitatively, our aims are the following.
+Our main aim is to find solution for the free parameters, for which the expression reproduces the overall behaviour that is observed in the cosmological simulations.
+For the purposes we have in mind, it will be more important to prioritise fitting the large scale trends, while we are not so interested in smaller scale fluctuations.
+We further prioritise getting the bulk of the cosmic star formation right and are less interested in capturing the behaviour in metallicity and redshift bins where the cosmic star formation rate is very low and thus insignificant for the overall picture.
+Finally, we are especially interested in capturing the asymmetry of the metallicity distribution.
+% There is not one unique procedure that will full fill these criteria.
+After experimenting with different criteria we have adopted the procedure below, which we believe works well for the aims we have in mind.
+%%
 % Large uncertainties exist in the shape and redshift evolution of both \SFRDz, and the cosmic distribution of metallicities \dpdZ (see e.g.
@@
 Alternatively, one could extract \SFRDzZ directly from cosmological simulations \citep[e.g.][]{Mapelli2017, Briel+2021}.
-
 % \citet{Mapelli2017} and \cite{Briel+2021}  but instead of directly extracting the \SFRDzZ from a cosmological simulation 
-
 % we take an approach similar to \cite{LangerNorman}, but instead of following the observed mean metallicity with redshift, we fit our combined analytical representations of \SFRDz and \dpdZ to simulation data.
-
-In this work, we present a convenient flexible model for the \SFRDzZ that can be fit to both simulation and observational data.
-By adopting an analytical, parametrized form for \SFRDzZ, the large uncertainties in \SFRDzZ can be systematically explored through smoothly varying the parameters that control its shape.
-
-We describe our model for \SFRDzZ in Section \ref{sec: model for sfrd(zZ)}.
-We fit our model to to the starforming gas in the illustris TNG simulation in Section \ref{sec: fit against tng}.
-In Section \ref{sec: mass dists} we demonstrate an example application of our model by systematically varying the parameters that determine the shape of \SFRDzZ and investigate their impact on the local distribution of merging BBH masses.
-We summarise in Section \ref{sec: summary}.
 
@@
 For the probability distribution of metallicities we draw inspiration from the approach by \citep[e.g.\ ][]{Neijssel+2019} who used a log-normal distribution.
-Unfortunately, this expression does not capture the asymmetry well that we see in the results of the cosmological simulations, which show an extended tail towards low metallicity combined with a very limited tail towards higher metallicity, when plotted as a function of $\log_10 Z$.
+Unfortunately, this expression does not capture the asymmetry well that we see in the results of the cosmological simulations, which show an extended tail towards low metallicity combined with a very limited tail towards higher metallicity, when plotted as a function of $\log_{10} Z$.
 To capture this behavior we adopt a skewed-log-normal distribution instead.
 This is an extension of the normal distribution that introduces an additional shape parameter, $\alpha$, that regulates the skewness \citep{Ohagan+1976}.
-This allows us to more accurately capture the asymmetry in the metallicity distribution at each redshift.
+%This allows us to more accurately capture the asymmetry in the metallicity distribution at each redshift.
 
@@
 
-\noindent For the evolution of the mean metallicity with redshift we follow \cite{Neijssel+2019} and \cite{Langer2006} in assuming that the mean of the probability density function of metallicities evolves with redshift as:
+\noindent For the evolution of the mean metallicity with redshift we follow \cite{Langer2006} and \cite{Neijssel+2019} in assuming that the mean of the probability density function of metallicities evolves with redshift as:
 \begin{equation}
@@
 
-We will also allow the ``scale'' $w$ also evolves with redshift in a similar manner, 
+We will also allow the ``scale'' $\omega$ to evolve with redshift in a similar manner, 
 \begin{equation}
@@
 in units of $\left[ \Msun \,yr^{-1} \,cMpc^{-3} \right]$.
-This introduces four parameters, $a$ which sets the overal normalisation and which has the same units as \SFRDz and $b,c$ and $d$ which are unitless and which govern the shape of the overal cosmic star formation rate density with redshift.
+This introduces four parameters; $a$ which sets the overal normalisation and which has the same units as \SFRDz and $b,c$ and $d$ which are unitless and which govern the shape of the overal cosmic star formation rate density with redshift.
 \\
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-We fit our newly defined functional form of \SFRDzZ as defined by equations \ref{eq: total sfrd}, \ref{eq: z log skew} and \ref{eq: sfr1} to the Illustris-TNG cosmological simulations. 
+We fit our new functional form of \SFRDzZ as defined by equations \ref{eq: total sfrd}, \ref{eq: z log skew} and \ref{eq: sfr1} to the Illustris-TNG cosmological simulations. 
 We fit for the following nine free parameters $\alpha, \mu_0, \mu_z, \omega_0, \omega_z$, which govern the metallicity dependence and $a,b, c$ and $d$, which set the overall star formation rate.
@@
 Below we briefly discuss the Illustris-TNG simulations, and elaborate on our fitting procedure.
-
-% %
-% The task we have at hand here is not a standard textbook fitting problem given the specific aims and requirements that we have that are driven by the astrophysical applications we have in mind.
-Qualitatively, our aims are the following.
-Our main aim is to find solution for the free parameters, for which the expression reproduces the overall behaviour that is observed in the cosmological simulations.
-For the purposes we have in mind, it will be more important to prioritise fitting the large scale trends, while we are not so interested in smaller scale fluctuations.
-We further prioritise getting the bulk of the cosmic star formation right and are less interested in capturing the behaviour in metallicity and redshift bins where the cosmic star formation rate is very low and thus insignificant for the overall picture.
-Finally, we are especially interested in capturing the asymmetry of the metallicity distribution.
-% There is not one unique procedure that will full fill these criteria.
-After experimenting with different criteria we have adopted the procedure below, which we believe works well for the aims we have in mind.
 
@@
 In particular of interest for this work, they simulate the high redshift enrichment of galaxies and the tail of low metallicity star formation at low redshift.
+Different cosmological simulations produce varying \SFRDzZ, depending on the adopted assumptions about the creation and distribution of metals.
 
-Different cosmological simulations produce varying \SFRDzZ, depending on the adopted assumptions about the creation and distribution of metals.
-For a detailed discussion of the processes that govern the creation, distribution and mixing of metals in in the TNG simulations we refer to \cite{Pakmor+2022}.
-We have chosen to fit of our analytical model to the illustris simulations because I) they have been shown to reproduce many of the global properties of galaxies and their scaling relations for a representative portion of the Universe \citep[e.g.][]{FirstResTNG_Naiman2018,Torrey+2021,Genel+2018,Hemler+2021}.
-II) \cite{Briel+2021} find that the \SFRDzZ from the EAGLE \citep{Schaye+2015,Crain+2015} and TNG simulations provide the best agreement between observed and predicted cosmic rates for electromagnetic and gravitational-wave transients.
-And III) the simulation output is publicly available.\footnote{ \url{https://www.tng-project.org/}}
-Although in this work, we only fit our model to the IllustrisTNG100 simulation, our prescription can be easily be used to fit other observational or simulated data of the metallicity dependent star formation rate density.
+The models implemented in the publicly available TNG simulations\footnote{ \url{https://www.tng-project.org/}} have lead to many successes.
+For a more extended discussion focused on the processes that govern the creation, distribution and mixing of metals in in the TNG simulations we refer to \cite{Pakmor+2022}.
+In short, star formation in the TNG simulations is calibrated against the Kennicutt–Schmidt relation \citep[][]{Schmidt1959,Kennicutt1989}.
+The stellar metallicity yields are and updated version of the original Illustris simulations as described in \cite{Pillepich2018}.
+Star particles deposit metals into the gas through Type Ia and Type II supernovae, as well as through Asymptotic Giant Branch mass loss.
+% Positives on TNG
+The TNG simulations have been shown to match observational constraints on the mass-metallicity relation of galaxies up to $z = 2$ \citep{Torrey+2019}, as well as iron abundances \citep{FirstResTNG_Naiman2018} and the metallicity gradients within galaxies at low redshift \citep{Hemler+2021}.
+%They reproduce the evolution of the sizes of galaxies with redshift \citep{Genel+2018}
+Several studies have already used the TNG simulations to make predictions for astronomical transient sources \citep[e.g.][]{Briel+2021,Bavera+2022}.
+In particular, \cite{Briel+2021} show that the \SFRDzZ from the TNG and the EAGLE \citep{Schaye+2015,Crain+2015} simulations provide the best agreement between observed and predicted cosmic rates for electromagnetic and gravitational-wave transients.
+
+% Downsides of TNG100 
+On the other hand, large uncertainties and crude approximations remain in all contemporary cosmological simulations, thus also in the TNG simulations.
+For example, dust is not included in the TNG simulations, which could mean that metallicity of the star-forming gas is overestimated.
+Furthermore, all mass loss from massive stellar winds \citep[e.g.][]{Dray+2003}, pair-pulsational supernovae \citep[e.g.][]{Renzo+2020} binary interactions \citep[e.g.][]{Farmer2021_carbonfootprint} and their ionising effects \citep[][]{Gotberg+2020,DoughtyFinlator2021} are ignored.
+Moreover, the uniform ionising UV background is turned on abruptly at $z=6$, which crucially impacts the amount of low metallicity star formation at low redshift.
+
+These large uncertainties call for a generalised form of the \SFRDzZ that can be easily updated when new information becomes available, which is the motivation for this work.
+Although here, we only fit our model to the TNG100 simulation, our prescription can be easily be used to fit other simulated data or observational data of the metallicity dependent star formation rate density \footnote{We provide a Jupyter notebook to facilitate this fit here \todo{add link}}.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-We fit equation \ref{eq: total sfrd} to the metallicity-dependent star formation rate of the starforming gas in the TNG100 simulation.
+We fit equation \ref{eq: total sfrd} to the metallicity-dependent star formation rate of the star-forming gas in the TNG100 simulation.
 For this we use a binned version of the TNG data $\SFRDzZ_{\rm sim}$.
-We consider metallicities between $Z= -5$ to $\log_{10} Z= 0$ in 30 bins, where we use $Z_i$ to refer to the logarithmic centers of the bins.
+We consider metallicities between $Z= -5$ to $\log_{10} Z= 0$ in 30 bins, where we use $Z_i$ to refer to the logarithmic centres of the bins.
 We ignore star formation in metallicities $\log_{10} Z \le -5$ as this accounts for less than 1\% of the total cosmic star formation rate in these simulations.
-We consider bins in redshifts between $z=0$ and $z=10$, with a step size of $dz=0.05$, where $z_j$ refers to the centers of the bins.
+We consider bins in redshifts between $z=0$ and $z=10$, with a step size of $dz=0.05$, where $z_j$ refers to the centres of the bins.
 
@@
 Subsequently we sum the $\chi^2 (z_j)$ for all redshift bins $z_j$.
-To ensure that our fit procedure gives sufficient weight to the behaviour at all redshifts, we find that we need to introduce a penalisation factor to somewhat reduce the contribution of redshifts where the peak of cosmic star formation occurs, while increasing the weight where at redshifts where the overal cosmic star formation rate is lower.
+To ensure that our fit procedure gives sufficient weight to the behaviour at all redshifts, we find that we need to introduce a penalisation factor to somewhat reduce the contribution of redshifts where the peak of cosmic star formation occurs, while increasing the weight where at redshifts where the overall cosmic star formation rate is lower.
 To achieve this we divide $\chi^2 (z_j)$ by the star formation $\sum_{Z_i} \mathcal{S}(Z_i,z_j)$ per redshift bin before adding the contribution of all redshifts.
@@
 With these fit parameters, $\chi^2(z_j)$ is smaller than $2\cdot 10^{-4}$ at any given redshift.
-We will refer to the \SFRDzZ with the parameters listed in Table \ref{tab: fit params} as our fiducial \SFRDzZ model.
+We will refer to the \SFRDzZ with the parameters listed in Table \ref{tab: fit params} as our fiducial model.
 % With the fit parameters as mentioned above, we find a maximum residual between the model and the TNG100 data of $2.3\cdot 10^{-3} \Msun \yr^{-1} \Mpc^{-3}$ at any given redshift.
@@
 
-In Figure \ref{fig: fit SFRD} we show our fiducial \SFRDzZ model at different redshifts and metallicities.
-For clarity, we also show the overal rate of star formation \SFRDz in Figure \ref{fig: SFR(z)}.
+In Figure \ref{fig: fit SFRD} we show our fiducial  model at different redshifts and metallicities. For clarity, we also show the overall rate of star formation \SFRDz in Figure \ref{fig: SFR(z)}.
 In general, our analytical model captures the metallicity dependent star formation in the TNG100 simulations well (bottom panels of Figure \ref{fig: fit SFRD}). 
 The skewed-log normal metallicity distribution is able to reproduce the overall behaviour that is observed in TNG100 \citep[bottom left panel, but cf.
-][for an in-depth discussion of low metallicity star formation in the TNG50 simulation]{Pakmor+2022}
+][for an in-depth discussion of low metallicity star formation in the TNG50 simulation]{Pakmor+2022}.
 Only minor features like the additional bump just above $\log_{10}(Z) = -2$ at redshift 2 are missed. 
@@
 }
-The \SFRDzZ from \cite{Neijssel+2019} was optimised to match the local rate of double compact object mergers as presented in the second gravitational-wave catalogue.
+% The \SFRDzZ from \cite{Neijssel+2019} was optimised to match the local rate of double compact object mergers as presented in the second gravitational-wave catalogue.
 However, the resulting symmetric distribution cuts-off virtually all low-metallicity ($Z\leq 10^{-2.5}$) star formation.
+
 % For both \SFRDzZ distributions, most star formation happens at metallicities above $Z \geq 10^{-2}$ (top panel).
@@
 
-We will demonstrate the application of our analytical model by systematically varying the parameters in our fiducial \SFRDzZ model, and investigate their effect on the local mass distribution of BBH mergers originating from isolated binaries.
+We will now demonstrate the application of our analytical model by systematically varying the parameters in our fiducial \SFRDzZ model, and investigate their effect on the local mass distribution of BBH mergers originating from isolated binaries.
 
@@
 %
+Metallicities of each binary system were sampled from a smooth probability distribution to avoid artificial peaks in the BH mass distribution \citep[e.g.][]{Dominik2015,Kummer_thesis}. 
 These simulations provide us with an estimate of the yield of BBH mergers per unit of star-forming mass and metallicity.
-We sample the metallicities of each binary system from a smooth probability distribution in stead of running batches of binaries at discrete sets of metallicity.
-Smoothly sampling of the birth metallicity avoids artificial peaks in the BH mass distribution \citep[e.g.][]{Dominik2015,Kummer_thesis}.
 
-Lastly, we combine the aforementioned yield with a \SFRDzZ as described in this work.
+We combine the aforementioned yield with a variation of the fiducial \SFRDzZ model described in this work.
 By integrating over cosmic history, we obtain the local merger rates of BBH systems, which allow us to construct the distribution of source properties at every redshift.
@@
 
-We consider variations of each of the parameters that determine the shape of the cosmic metallicity distribution \dpdZ (left two columns of Table \ref{tab: fit params}) and two variations of the \SFRDz, where we keep the metallicity distribution \dpdZ fixed, but we vary the complete shape of the \SFRDz (i.e.
-all four parameters) at once to match the values used in \cite{Madau+2017} and \cite{Neijssel2019} respectively (see Figure \ref{fig: SFR(z)} for reference).
-To determine the range of parameters that is reasonably allowed by observations, we compare the \SFRDzZ in the metallicity-redshift plane to the high and low metallicity extreme from \cite{Chruslinska+2021} by eye for every variation.
+We consider variations of each of the parameters that determine the shape of the cosmic metallicity distribution \dpdZ (left two columns of Table \ref{tab: fit params}) and two variations of the \SFRDz, where we keep the metallicity distribution \dpdZ fixed, but vary the overall star-formation rate history  \SFRDz (i.e.
+all four \SFRDz parameters at once), to match the values used in \cite{Madau+2017} and \cite{Neijssel2019} respectively (see Figure \ref{fig: SFR(z)} for reference).
+To determine the range of parameters that is reasonably allowed by observations, we have compared the \SFRDzZ in the metallicity-redshift plane to the high and low metallicity extreme from \cite{Chruslinska+2021} by eye for every variation.
 \\
 
-In Figure \ref{fig: mass dists} we show the mass distribution of the more massive component from merging BBHs.
+In Figure \ref{fig: mass dists} we show the resulting mass distribution of the more massive component from merging BBHs.
 We will refer to the more (less) massive component as the primary (secondary) from hereon.
@@
 Changes in the \SFRDzZ have the largest impact on the high mass end of the primary mass distribution, while the impact on the low mass is relatively modest.
-To quantify this, we annotate the ratio between the maximum and minimum rate at three reference masses; $10\Msun$, $25\Msun$ and $40\Msun$. 
+To quantify this, we annotate the ratio between the maximum and minimum rate at three reference masses; \Mbheen = $10, 25$, and $40\Msun$.
 At $\Mbheen=10\Msun$, we find that the rate changes by at most a factor 3 for the variations explored in this work. While we find a factor of at most 11 for the change in rate at $\Mbheen=40\Msun$.
@@
 % The normalisation at z=0 changes the overal rate / normalisation
-We find that parameter variations that affect shape of \SFRDzZ at low redshift primarily change the normalisation of the mass distribution (see also  $\mathcal{R}_{0.2}$, the total BBH merger rate at redshift 0.2, annotated in the legends of Figure \ref{fig: mass dists}).
-These variations include the width of the cosmic metallicity distribution at $z=0$, $\omega_0$, the mean metallicity of the cosmic metallicity distribution at $z=0$, $\mu_0$, and the skewness of the cosmic metallicity distribution, $\alpha$ (left column of Figure \ref{fig: mass dists}).
-Model variations that increase the amount of star formation at low metallicity (i.e.
+Parameter variations that affect shape of \SFRDzZ at low redshift primarily change the normalisation of the mass distribution.
+See also  $\mathcal{R}_{0.2}$, the total BBH merger rate at redshift 0.2, annotated in the legends of Figure \ref{fig: mass dists} ($z=0.2$ is where the observations are best constrained by the data \citealt{GWTC3_popPaper2021}).
+This is visible for variations that impact the width of the cosmic metallicity distribution at $z=0$, $\omega_0$, the mean metallicity of the cosmic metallicity distribution at $z=0$, $\mu_0$, and the skewness of the cosmic metallicity distribution, $\alpha$ (left column of Figure \ref{fig: mass dists}).
+Variations that \textit{increase} the amount of star formation at low metallicity (i.e.
 for a low mean metallicity $\mu_0=0.015$ and a wide metallicity distribution $\omega_0 = 1.4$ ) increase the predicted BBH merger rate.
@@
 Parameters that change the evolution of the metallicity distribution \dpdZ with redshift, such as $\omega_z$ and $\mu_z$ (top right and centre right panel), primarily affect the slope of the high mass end of the BBH mass distribution.
-The difference between the effect on the low mass end with respect to the high mass end of the mass distribution is largest for these variations.
+By reducing the amount of low-metallicity star formation at high redshifts, formation channels with long delay times are excluded.
+In these simulations, the higher mass systems come from the `stable mass transfer channel' which is characterised by longer delay times \citep[][see also their Figure 6]{vanson+2022}.
+% This is similar to the redshift evolution of the mass distribution as discussed in \cite{vanson+2022} (Figure 6). 
+% The difference between the effect on the low mass end with respect to the high mass end of the mass distribution is largest for these variations.
 
 % Effect of the star formation 
-Lastly, changing the \SFRDz has a relatively small effect. We vary 
-The \SFRDz from \cite{Madau+2017} and \cite{Neijssel+2019} both peak at approximately redshift 2.
-Our fiducial model (that follows the \SFRDz from TNG) peaks at about redshift 3.
+Lastly, changing the \SFRDz has a relatively small effect.
+We vary the \SFRDz to match the form described in \cite{Madau+2017} and \cite{Neijssel+2019} respectively.
+Both these variations peak at approximately redshift 2.
+Our fiducial model (that follows the \SFRDz from TNG) peaks at about redshift 2.8.
 The overall normalisation of \cite{Neijssel+2019} is higher than the normalisation of our fiducial model.
-Regardless of these differences, the rate of BBH mergers at $z=0.2$ changes no more than 20\%, and the shape of the primary mass distribution remains almost constant.
+Regardless of these differences, the rate of BBH mergers at $z=0.2$ changes no more than $20\%$, and the shape of the primary mass distribution remains almost constant.
+We understand this small effect as follows: our fiducial metallicity distribution \dpdZ is almost constant up to redshift $\sim3$.
+Hence shifting the location of the peak \SFRDz from 2.8 to 2 has a small effect.
+Furthermore, even though these models have varying peak values for \SFRDz, the integrated total stellar mass formed is similar between the models.
+%\todo{add value here}
 
@@
 We present a flexible analytic expression for the metallicity-dependent star formation rate, \SFRDzZ (equations \ref{eq: total sfrd}, \ref{eq: z log skew} and \ref{eq: sfr1}).
-An analytical expression allows for controlled experiments of the effect of \SFRDzZ on dependent rates, such as the rate and mass distribution of merging BBHs.
+An analytical expression allows for controlled experiments of the effect of \SFRDzZ on dependent values, such as the rate and mass distribution of merging BBHs.
 The novelty of the model presented in this work is that it adopts a skewed-lognormal for the distribution of metallicities at every redshift (\dpdZ).
 
+\paragraph{The model can capture the general behaviour of cosmological simulations, such as TNG100}
 We fit our analytical expression for \SFRDzZ to the star-forming gas in the TNG100 simulation, and provide the best fit parameters in Table \ref{tab: fit params}.
@@
 
-As an example, we apply our model to calculate the local rate and mass distribution of the more massive components from merging BBHs (\Mbheen) in Figure \ref{fig: mass dists}). 
-We systematically vary all five parameters ($\alpha, \mu_0, \mu_z, \omega_0$ and $\omega_z$) that shape the cosmic metallicity distribution \dpdZ, and explore two addition variations of \SFRDz, following \cite{Madau+2017} and \cite{Neijssel+2019} respectively.
+\paragraph{We preform a controlled experiment on the effect of \SFRDzZ on the local distribution of merging BBH}
+As an example, we apply our model to calculate the local rate and mass distribution of the more massive components from merging BBHs (\Mbheen) in Figure \ref{fig: mass dists}. 
+We systematically vary all five parameters ($\alpha, \mu_0, \mu_z, \omega_0$ and $\omega_z$) that shape the cosmic metallicity distribution \dpdZ, and explore two additional variations of the overall star-formation rate \SFRDz, following \cite{Madau+2017} and \cite{Neijssel+2019} respectively.
+Our main conclusions are as follows:
+\begin{itemize}
 
-We find that for all variations, the low mass end of the mass distribution is least affected the change in the \SFRDzZ. 
-%
-We furthermore find that the metallicity distribution of star formation at \textit{low redshift}, primarily impacts the \textit{normalisation} of the \Mbheen distribution (i.e.
-the total local rate $\mathcal{R}_{0.2}$).
-On the other hand, parameters that influence the \textit{redshift evolution} of the metallicity distribution, affect the \textit{slope} of the \Mbheen distribution.
-The latter is specifically effective beyond the peak of the \Mbheen distribution which occurs at approximately 18\Msun.
-%
-Lastly, changing the \SFRDz has a relatively small effect.
+    \item For all variations, the low mass end of the mass distribution is least affected the change in the \SFRDzZ.
+
+    \item The metallicity distribution of star formation at low redshift, primarily impacts the normalisation of the \Mbheen distribution (i.e. the total local rate $\mathcal{R}_{0.2}$).
+
+    \item Parameters that influence the redshift evolution of the metallicity distribution, affect the slope of the high mass end of the \Mbheen distribution.
+%Specifically this impacts the for masses above the peak of the \Mbheen distribution which occurs at approximately 18\Msun.
+
+    \item Changing the overall star-formation history, \SFRDz has a small effect on the local mass distribution.
+This is because reasonable variations of the \SFRDz have a similar value for the total local star-formation rate density, which is relatively well constrained by observations.
+
+\end{itemize}
 

### 2022-07-04 src/scripts/Plot_Mass_distributions.py
changing to the full res files

@@ -41,8 +41,8 @@ import paths
 save_loc    =  str(paths.figures) + '/'
 data_dir    =  str(paths.data) + '/'
 
-rate_file       = '/RateData/small_Rate_info.h5'#'small_Rate_info.h5' #'/Rate_info.h5'#
-simulation_data = '/small_COMPAS_Output_wWeights.h5'#'/small_COMPAS_Output_wWeights.h5' #'/COMPAS_Output_wWeights.h5'#
+rate_file       = '/RateData/Rate_info.h5'#'/RateData/small_Rate_info.h5' #
+simulation_data = '/COMPAS_Output_wWeights.h5'#'/small_COMPAS_Output_wWeights.h5' #
 
 only_stable = True 
 only_CE = True

### 2022-07-28 src/scripts/SFR_z.py
updated 1d sfrd

@@ -37,6 +37,7 @@ plt.rc('legend', fontsize=SMALL_SIZE)    # legend fontsize
 
 
 
+
 ########################################################
 # plot different SFRs
 ########################################################
@@ -52,21 +53,27 @@ def plot_SFR(sf_a = 0.017, sf_b = 1.481, sf_c = 4.452,  sf_d = 5.913,
         x1 = cosmo.lookback_time(redshift_list)
 
 
-    # M&D 14
-    #ax.plot(x1, Z_SFRD.Madau_Dickinson2014(redshift_list), 
-    #         label = 'Madau $\&$ Dickinson 2014\n $a=%.2f, b=%.2f, c=%.2f, d=%.2f$'% (0.015,2.77,2.9,5.6)
-    #         , c = 'royalblue', ls = '--',lw=2)
+#     #default M&D 14
+#     ax.plot(x1, Z_SFRD.Madau_Dickinson2014(redshift_list), 
+#              label = 'Madau $\&$ Dickinson 2014\n $a=%.2f, b=%.2f, c=%.2f, d=%.2f$'% (0.015,2.77,2.9,5.6)
+#              , c = 'royalblue', ls = '--',lw=2)
 
     #default Madau & Fragos 17
     ax.plot(x1, Z_SFRD.Madau_Dickinson2014(redshift_list, a=0.01, b=2.6, c=3.2, d=6.2), 
              label = 'Madau $\&$ Fragos 2017\n $a=%.2f, b=%.2f, c=%.2f, d=%.2f$'% (0.01,2.6,3.2,6.2)
-             , c = '#356288', ls = '-',lw=6)
+             , c = '#356288', ls = ':',lw=6)
 
-    #default Coen
-    ax.plot(x1, Z_SFRD.Madau_Dickinson2014(redshift_list, a=0.01, b=2.77, c=2.9, d=4.7), 
-             label = 'Neijssel et al 2019\n $a=%.2f, b=%.2f, c=%.2f, d=%.2f$'% (0.01,2.77,2.9,4.7)
-             , c = 'grey', lw=5, ls = ':')#aacfdd
+#     #default Coen
+#     ax.plot(x1, Z_SFRD.Madau_Dickinson2014(redshift_list, a=0.01, b=2.77, c=2.9, d=4.7), 
+#              label = 'Neijssel et al 2019\n $a=%.2f, b=%.2f, c=%.2f, d=%.2f$'% (0.01,2.77,2.9,4.7)
[…]

### 2022-07-28 src/scripts/Plot_Mass_distributions.py
added a bit of wait time for the figure, because the snakemake doesnt find it in 5 sec

@@ -35,6 +35,7 @@ importlib.reload(mfunc)
 import gc
 import paths
 
+import time
 
 ######################################
 ## locations
@@ -421,5 +422,8 @@ ax6 = plot_mass_distribution(sim_dir = data_dir, x_key = 'M_moreMassive',
 # Final plot properties
 fig.savefig(save_loc + '/Mass_distributions_'+ channel_string+'_SFRD_variations.pdf' , bbox_inches='tight')
 # plt.show()
+
+time.sleep(30)
+
 
 

### 2022-07-28 src/scripts/FitComparison_3panelPlot.py
sigma to omega

@@ -65,8 +65,8 @@ plt.rc('legend', fontsize=SMALL_SIZE)    # legend fontsize
 #####################################
 mu0_best     = 0.025
 muz_best     = -0.049
-sigma0_best  = 1.129
-sigmaz_best  = 0.048
+omega0_best  = 1.129
+omegaz_best  = 0.048
 alpha0_best  = -1.778
 
 #####################################
@@ -82,7 +82,7 @@ sf_d_best     = 5.913
 ######################################
 # SFRD comparison plot
 ######################################
-def three_panel_SFRD_plot(obs_SFRD = [], mu_0=0.025, mu_z=-0.49,alpha = -1.77, sigma_0=1.129, sigma_z =0.048,
+def three_panel_SFRD_plot(obs_SFRD = [], mu_0=0.025, mu_z=-0.49,alpha = -1.77, omega_0=1.129, omega_z =0.048,
                     a=0.017, b=1.481, c=4.452,  d=5.913,
                     min_logZ  = -12.0, max_logZ  =0.0, step_logZ = 0.01,
                     tmin = 0.0, tmax = 13.7, add_TNG = True, 
@@ -112,8 +112,8 @@ def three_panel_SFRD_plot(obs_SFRD = [], mu_0=0.025, mu_z=-0.49,alpha = -1.77, s
     fit_values_string = r'$\mathrm{Cosmic \ metallicity \ dist.}$'+'\n'+\
                     r'$\mu_0=%s,$'%(np.round(mu_0,3)) +'\n'+\
                     r'$\mu_z=%s,$'%(np.round(mu_z,3)) +'\n'+\
-                    r'$\omega_0=%s,$'%(np.round(sigma_0,3)) +'\n'\
-                    r'$\omega_z=%s,$'%(np.round(sigma_z,3)) +'\n'\
+                    r'$\omega_0=%s,$'%(np.round(omega_0,3)) +'\n'\
+                    r'$\omega_z=%s,$'%(np.round(omega_z,3)) +'\n'\
                     r'$a_0=%s$'%(np.round(alpha,3))
 
     SFR_fit_string = r'$\mathrm{Star \ formation \ rate}$'+'\n'+\
@@ -204,7 +204,7 @@ def three_panel_SFRD_plot(obs_SFRD = [], mu_0=0.025, mu_z=-0.49,alpha = -1.77, s
         # Get dPdZ 
[…]

### 2022-07-28 src/scripts/FitComparison_3panelPlot.py
updated skew metal function calls

@@ -203,9 +203,9 @@ def three_panel_SFRD_plot(obs_SFRD = [], mu_0=0.025, mu_z=-0.49,alpha = -1.77, o
         #####################################
         # Get dPdZ 
         dPdlogZ, redshifts, metallicities, step_logZ, p_draw_metallicity = \
-                        Z_SFRD.skew_metallicity_distribution(mu_0=mu_0, mu_z=mu_z,alpha = alpha, 
+                        Z_SFRD.skew_metallicity_distribution(high_res_redshifts, mu_0=mu_0, mu_z=mu_z,alpha = alpha, 
                                                       omega_0=omega_0, omega_z =omega_z, 
-                                                      metals = high_res_metals, redsh = high_res_redshifts)
+                                                      metals = high_res_metals)
         # Get the SFR
         sfr        = Z_SFRD.Madau_Dickinson2014(redshifts, a=a, b=b, c=c,  d=d) # Msun year-1 Mpc-3 
         # Combine it into a SFRD
@@ -240,8 +240,8 @@ def three_panel_SFRD_plot(obs_SFRD = [], mu_0=0.025, mu_z=-0.49,alpha = -1.77, o
         #####################################
         # Get dPdZ   #         neijssel_metals = np.logspace(-5., -0.5, 50)
         neijssel_dPdlogZ, neijssel_redshifts, neijssel_metallicities, neijssel_step_logZ, p_draw_metallicity = \
-                        Z_SFRD.skew_metallicity_distribution(mu_0=0.035, mu_z=-0.23, alpha = 0, omega_0=0.39, omega_z =0, 
-                            min_logZ  =-12.0, max_logZ  =0.0, step_logZ = 0.01, metals=high_res_metals, redsh = high_res_redshifts)
+                        Z_SFRD.skew_metallicity_distribution(high_res_redshifts, mu_0=0.035, mu_z=-0.23, alpha = 0, omega_0=0.39, omega_z =0, 
+                            min_logZ  =-12.0, max_logZ  =0.0, step_logZ = 0.01, metals=high_res_metals)
         # Get the SFR Neijssel et al 2019:
[…]

### 2022-07-28 src/scripts/Plot_Mass_distributions.py
remove try except in plot mass dist

@@ -143,10 +143,7 @@ def plot_mass_distribution(sim_dir = '', x_key = 'M_moreMassive', rate_keys = ['
     ################################################
     # My Simulations
     ################################################
-    try:
-        DCO = mfunc.read_data(loc = sim_dir + '/' + simulation_data)
-    except:
-        print('data not found')
+    DCO = mfunc.read_data(loc = sim_dir + '/' + simulation_data)
 
     # We'll show the change in rate between SFRD at several reference masses
     m10, m25, m40 = [], [], []

### 2022-07-28 src/scripts/FitComparison_3panelPlot.py
remove try except in plot mass dist

@@ -202,12 +202,12 @@ def three_panel_SFRD_plot(obs_SFRD = [], mu_0=0.025, mu_z=-0.49,alpha = -1.77, o
         # Get data for your model 
         #####################################
         # Get dPdZ 
-        dPdlogZ, redshifts, metallicities, step_logZ, p_draw_metallicity = \
+        dPdlogZ, metallicities, step_logZ, p_draw_metallicity = \
                         Z_SFRD.skew_metallicity_distribution(high_res_redshifts, mu_0=mu_0, mu_z=mu_z,alpha = alpha, 
                                                       omega_0=omega_0, omega_z =omega_z, 
                                                       metals = high_res_metals)
         # Get the SFR
-        sfr        = Z_SFRD.Madau_Dickinson2014(redshifts, a=a, b=b, c=c,  d=d) # Msun year-1 Mpc-3 
+        sfr        = Z_SFRD.Madau_Dickinson2014(high_res_redshifts, a=a, b=b, c=c,  d=d) # Msun year-1 Mpc-3 
         # Combine it into a SFRD
         model_SFRD = (sfr* dPdlogZ.T).value
 
@@ -239,11 +239,11 @@ def three_panel_SFRD_plot(obs_SFRD = [], mu_0=0.025, mu_z=-0.49,alpha = -1.77, o
         # Get the data for Z-dep SFRD
         #####################################
         # Get dPdZ   #         neijssel_metals = np.logspace(-5., -0.5, 50)
-        neijssel_dPdlogZ, neijssel_redshifts, neijssel_metallicities, neijssel_step_logZ, p_draw_metallicity = \
+        neijssel_dPdlogZ, neijssel_metallicities, neijssel_step_logZ, p_draw_metallicity = \
                         Z_SFRD.skew_metallicity_distribution(high_res_redshifts, mu_0=0.035, mu_z=-0.23, alpha = 0, omega_0=0.39, omega_z =0, 
                             min_logZ  =-12.0, max_logZ  =0.0, step_logZ = 0.01, metals=high_res_metals)
         # Get the SFR Neijssel et al 2019:
-        neijssel_sfr = Z_SFRD.Madau_Dickinson2014(neijssel_redshifts, a=0.01, b=2.77, c=2.9, d=4.7) # Msun year-1 Mpc-3 
[…]

### 2022-07-28 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 To capture this behavior we adopt a skewed-log-normal distribution instead.
-This is an extension of the normal distribution that introduces an additional shape parameter, $\alpha$, that regulates the skewness \citep{Ohagan+1976}.
+This is an extension of the normal distribution that introduces an additional shape parameter, $\alpha$, that regulates the skewness \citep[first introduced by][]{Ohagan+1976}.
+%for a more clear derivation
 %This allows us to more accurately capture the asymmetry in the metallicity distribution at each redshift.
@@
 The skewed-log-normal distribution of metallicities is defined as:
-
+% See eq. 1 here: https://www.emis.de/journals/RCE/V36/v36n1a03.pdf
 \begin{equation}
@@
 \mathrm{\frac{dP}{dZ}}(Z) &= \frac{1}{Z} \times \frac{\rm dP}{{\rm d}\ln Z}  \\
-&= \frac{2}{Z} \times
+&= \frac{1}{Z} \times \frac{2}{\omega}
     \underbrace { \phi \left(\frac{\ln Z - \xi}{\omega}\right)
@@
 % \underbrace{
-    \frac{1}{\omega \sqrt{2 \pi}} 
+    \frac{1}{\sqrt{2 \pi}} 
     \exp{
@@
     \frac{1}{2} 
-    \left( 
+    \left[ 
         1 + {\rm erf}
@@
             \right\} 
-    \right) \\
+    \right] \\
     %}_{(2)}.
-  &=    \frac{1}{2} 
-       \int_{\infty}^{\alpha\left( \frac{\ln Z -\xi}{\omega}\right)}
-       \frac{1}{\sqrt{2\pi}}e^{-t^2/2}dt
+%   &=    %%% I dont think this belongs here: \frac{1}{2} 
+%       \int_{\infty}^{\alpha\left( \frac{\ln Z -\xi}{\omega}\right)}
+%       \frac{1}{\sqrt{2\pi}}e^{-t^2/2}dt
     \end{array}
@@
 To obtain a useful expression for the redshift dependence of the ``location'' $\xi(z)$ we first express the expectation value or mean metallicity at a given redshift
-
+% eq. 8 here: https://www-sciencedirect-com.ezp-prod1.hul.harvard.edu/science/article/pii/S0021850219300400
+% Using k = 1 for the first moment
 \begin{equation}
@@
  = 2 \exp
-        \left( \frac{\xi\,\omega^2}{2} \right)
+        \left(\xi +  \frac{\omega^2}{2} \right)
          \Phi\left(\beta\, \omega\right)
@@
 \end{equation}
+
+For a more extended derivation of the moments of the skewed-log-normal, see e.g., \cite{WANG201995}.
 
@@
 
+% \begin{equation}
+% \label{eq mu z}
+%     \xi(z) = -\frac{\omega^2}{2}\, \ln\left(\frac{  \mu_0 \cdot 10^{\mu_z \cdot z} }{2\, \Phi(\beta\, \omega)}  \right).
+% \end{equation}
+
 \begin{equation}
 \label{eq mu z}
-    \xi(z) = -\frac{\omega^2}{2}\, \ln\left(\frac{  \mu_0 \cdot 10^{\mu_z \cdot z} }{2\, \Phi(\beta\, \omega)}  \right).
+    \xi(z) = \ln\left(\frac{  \mu_0 \cdot 10^{\mu_z \cdot z} }{2\, \Phi(\beta\, \omega)}  \right) - \frac{\omega^2}{2}.
 \end{equation}
@@
 \boxed{
-    \dPdZ = \frac{2}{Z} \times \phi \left(\frac{\ln Z - \xi(z)}{\omega(z)}\right) \Phi\left(\alpha \frac{\ln Z - \xi(z)}{\omega(z)} \right)
+    \dPdZ = \frac{2}{\omega(z) Z} \times \phi \left(\frac{\ln Z - \xi(z)}{\omega(z)}\right) \Phi\left(\alpha \frac{\ln Z - \xi(z)}{\omega(z)} \right)
     } \ , 
@@
 %
-Here, the variable $Z_i$ runs over all redshift bins, but excludes bins where the star formation rate density is lower $10^{-10} \Msun \yr \Mpc^{-3}$ per bin.
-
-Subsequently we sum the $\chi^2 (z_j)$ for all redshift bins $z_j$.
-To ensure that our fit procedure gives sufficient weight to the behaviour at all redshifts, we find that we need to introduce a penalisation factor to somewhat reduce the contribution of redshifts where the peak of cosmic star formation occurs, while increasing the weight where at redshifts where the overall cosmic star formation rate is lower.
+Here, the variable $Z_i$ runs over all redshift bins.
+%, but excludes bins where the star formation rate density is lower $10^{-10} \Msun \yr \Mpc^{-3}$ per bin. 
+% Subsequently we sum the $\chi^2 (z_j)$ for all redshift bins $z_j$. 
+We are particularly interested in properly fitting the low metallicity star formation at high redshifts.
+At high redshifts, the overall cosmic star formation rate is generally lower.
+To ensure that our fit procedure gives sufficient weight to the behaviour at all redshifts, we introduce a penalisation factor to somewhat reduce the contribution of redshifts where the peak of cosmic star formation occurs, while increasing the weight where at redshifts where the overall cosmic star formation rate is lower.
 To achieve this we divide $\chi^2 (z_j)$ by the star formation $\sum_{Z_i} \mathcal{S}(Z_i,z_j)$ per redshift bin before adding the contribution of all redshifts.
@@
 \script{Plot_Mass_distributions.py}
-\includegraphics[width=0.8\textwidth]{figures/Mass_distributions_all_SFRD_variations.pdf}
+\includegraphics[width=0.8\textwidth]{figures/Mass_distributions_stable_SFRD_variations.pdf}
+% \includegraphics[width=0.8\textwidth]{figures/Mass_distributions_all_SFRD_variations.pdf}
 \caption{The primary mass distribution of merging BBH systems from isolated binary evolution for several variations in \SFRDzZ. 
@@
 Lastly, changing the \SFRDz has a relatively small effect. 
+\todo{this is in line with findings from \citep{Tang+2020}.}
 We vary the \SFRDz to match the form described in \cite{Madau+2017} and \cite{Neijssel+2019} respectively.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Summary \label{sec: summary}}
+\section{Discussion \& ? Summary \label{sec: summary}}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\todo{\cite{chruslinska2022_review} Fig. 5 actually shows that the \textit{shape} of the mass distribution is \textit{not at all} impacted that much by the SFRD!!}
+
 We present a flexible analytic expression for the metallicity-dependent star formation rate, \SFRDzZ (equations \ref{eq: total sfrd}, \ref{eq: z log skew} and \ref{eq: sfr1}).
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\appendix
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Yield per metallicity and mass \label{app: mass metal yield}}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+The yield of merging BBH with certain masses, per star forming mass per metallicity
+
+%%%%%%%%%%%%%%%%%%%%%
+% Rate - mass
+% \begin{figure}
+% \includegraphics[width=0.49\textwidth]{figures/yield_per_mass_and_metals.png} 
+% \caption{The yield of merging BBH with certain masses, per star forming mass per metallicity}
+% \end{figure}
+%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \bibliography{my_bib,main_bib}

### 2022-07-29 src/scripts/Plot_Mass_distributions.py
plotted result

@@ -45,8 +45,8 @@ data_dir    =  str(paths.data) + '/'
 rate_file       = '/RateData/Rate_info.h5'#'/RateData/small_Rate_info.h5' #
 simulation_data = '/COMPAS_Output_wWeights.h5'#'/small_COMPAS_Output_wWeights.h5' #
 
-only_stable = True 
-only_CE = False
+only_stable = False
+only_CE = True
  
 
 if np.logical_and(only_stable, only_CE):

### 2022-07-29 src/scripts/Plot_Mass_distributions.py
changed to produce both channels

@@ -45,16 +45,6 @@ data_dir    =  str(paths.data) + '/'
 rate_file       = '/RateData/small_Rate_info.h5'#'/RateData/small_Rate_info.h5' #
 simulation_data = '/small_COMPAS_Output_wWeights.h5'#'/small_COMPAS_Output_wWeights.h5' #
 
-only_stable = False
-only_CE = True
- 
-
-if np.logical_and(only_stable, only_CE):
-    channel_string = 'all'
-elif only_stable:
-    channel_string = 'stable'
-elif only_CE:
-    channel_string = 'CE'
 
 ######################################
 ## PLOT setttings
@@ -319,117 +309,128 @@ def plot_mass_distribution(sim_dir = '', x_key = 'M_moreMassive', rate_keys = ['
 #################################################################################################
 
 
+# Run once for each channel
+for i in range(len(2)):
+    
+    if i ==0:
+        only_stable = True
+        only_CE     = False
+        channel_string = 'stable'
+        
+    if i ==0:
+        only_stable = False
+        only_CE     = True
+        channel_string = 'CE'
 
-fig = plt.figure( figsize = (24, 28))
+    fig = plt.figure( figsize = (24, 28))
 
-####################################################
-# width of SFRD at z=0
-####################################################
-#add first subplot in layout that has 3 rows and 2 columns
-subplot1 = fig.add_subplot(321)
+    ####################################################
+    # width of SFRD at z=0
+    ####################################################
+    #add first subplot in layout that has 3 rows and 2 columns
+    subplot1 = fig.add_subplot(321)
 
-ax1 = plot_mass_distribution(sim_dir = data_dir, x_key = 'M_moreMassive',  rate_keys  = ['Rates_mu00.025_muz-0.049_alpha-1.778_sigma0%s_sigmaz0.048_a0.017_b1.481_c4.452_d5.913'%(x) for x in [0.7, 1.129, 2.0]],
-                       show_hist = False, show_KDE = True, kde_width = 0.1, plot_LIGO = True, Color =  'navy',
-                       only_CE = only_CE, only_stable = only_stable, 
[…]

### 2022-07-29 src/scripts/Plot_Mass_distributions.py
reran with low res both channels

@@ -310,17 +310,19 @@ def plot_mass_distribution(sim_dir = '', x_key = 'M_moreMassive', rate_keys = ['
 
 
 # Run once for each channel
-for i in range(len(2)):
+for i in range(2):
     
     if i ==0:
         only_stable = True
         only_CE     = False
         channel_string = 'stable'
         
-    if i ==0:
+    else:
         only_stable = False
         only_CE     = True
         channel_string = 'CE'
+
+    print('making Figure ', save_loc + '/Mass_distributions_'+ channel_string+'_SFRD_variations.pdf')
 
     fig = plt.figure( figsize = (24, 28))
 

### 2022-07-29 src/tex/ms.tex
ran stuf
writing

@@
 \includegraphics[width=0.8\textwidth]{figures/Mass_distributions_stable_SFRD_variations.pdf}
-% \includegraphics[width=0.8\textwidth]{figures/Mass_distributions_all_SFRD_variations.pdf}
-\caption{The primary mass distribution of merging BBH systems from isolated binary evolution for several variations in \SFRDzZ. 
+\caption{The primary mass distribution of merging BBH systems from the stable mass transfer channel for several variations in \SFRDzZ. 
 The first five panels show variations of the cosmic metallicity distribution  \dpdZ (eq.
@@
 \end{figure*}
+
+\begin{figure*}
+\centering
+\script{Plot_Mass_distributions.py}
+\includegraphics[width=0.8\textwidth]{figures/Mass_distributions_CE_SFRD_variations.pdf}
+\caption{Same as Figure \ref{fig: mass dists}, but for the Common envelope channel. 
+   \label{fig: mass dists}
+  }
+\end{figure*}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
+\section{Determining reasonable variations of the \SFRDzZ}
+
+\begin{figure}
+\centering
+\script{LowHighZ_fraction.py}
+\includegraphics[width=0.8\textwidth]{figures/High_Low_metalFractionSFMass.pdf}
+\caption{Fraction of high vs low metallicity stellar mass.
+   \label{fig: low high Z fraction}
+  }
+\end{figure}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2022-07-29 src/scripts/LowHighZ_fraction.py

@@ -1,0 +1,582 @@
+# Notebook to make plot comparing fractional contribution low and high metallicities
+# Code from Ruediger, original plot is by Martyna
+import os
+import h5py
+import numpy as np 
+import matplotlib.pyplot as plt
+import paths
+from pylab import *
+import seaborn as sns
+
+from scipy import interpolate
+
+from astropy.table import Table
+
+import astropy.units as u
+# from astropy.cosmology import WMAP9, z_at_value
+from astropy.cosmology import Planck18  as cosmo# Planck 2018
+from astropy.cosmology import z_at_value
+
+############################
+# Custom scripts
+import get_ZdepSFRD as Z_SFRD
+import importlib
+importlib.reload(Z_SFRD)
+
+############################
+##PLOT setttings
+from matplotlib import rc
+import matplotlib
+matplotlib.rcParams['mathtext.fontset'] = 'stix'
+matplotlib.rcParams['font.family'] = 'STIXGeneral'
+rc('font',**{'family':'sans-serif','sans-serif':['Helvetica']})
+plt.rc('font', family='serif')
+rc('text', usetex=True)
+fsize, SMALL_SIZE, MEDIUM_SIZE, BIGGER_SIZE = 30,20,20,30
+for obj in ['axes','xtick','ytick']:
+    plt.rc(obj, labelsize=MEDIUM_SIZE)          # controls default text sizes
+for obj in ['figure','axes']:
+    plt.rc(obj, titlesize=BIGGER_SIZE)    # fontsize of the tick labels
+plt.rc('font', size=MEDIUM_SIZE)          # controls default text sizes
+plt.rc('legend', fontsize=SMALL_SIZE)    # legend fontsize
+
+
+#######################
+# Definitions
+SOLAR_METALLICITY = 0.0127
+outdir = str(paths.data) +'/RuedigerFig2/' #"./"
+TNG               = 50
+lvl               = 1
+
+
+##############################
+def getStellarMassMetallicityTNG():
+    fout = outdir + "StellarMassMetallicityTNG%d-%d.hdf5" % (TNG,lvl)
+    if os.path.exists( fout ):
+        return
+  
+    print( "Computing data TNG%d" % TNG )
+
+    snap = 99
[…]

### 2022-07-29 src/scripts/Plot_Mass_distributions.py

@@ -69,7 +69,7 @@ plt.rc('legend', fontsize=SMALL_SIZE)    # legend fontsize
 ######################################
 # Distribution plot function
 ######################################
-def plot_mass_distribution(sim_dir = '', x_key = 'M_moreMassive', rate_keys = ['Rates_mu00.025_muz-0.05_alpha-1.77_sigma0%s_sigmaz0.05_zBinned'%(x) for x in [0.8, 1.125, 1.4]],
+def plot_mass_distribution(sim_dir = '', x_key = 'M_moreMassive', rate_keys = ['Rates_mu00.025_muz-0.05_alpha-1.77_sigma0%s_sigmaz0.05_zBinned'%(x) for x in [0.8, 1.125, 1.4]],channel_string = 'all',
                    bins = np.arange(0.,55,2.5), z_bin_edges = [0,0.25], 
                    plot_LIGO = False, show_hist = False, show_KDE = True, kde_width = 0.1,  
                    only_stable = True, only_CE = True, 
@@ -262,15 +262,18 @@ def plot_mass_distribution(sim_dir = '', x_key = 'M_moreMassive', rate_keys = ['
         print()
         ax.vlines(x=reference_masses[m], ymin=min(mpoint), ymax=max(mpoint), colors='k', lw=3, zorder = 20)
         ax.hlines(y=[min(mpoint), max(mpoint)], xmin=reference_masses[m]-0.5, xmax=reference_masses[m]+0.5, linewidth=3, color='k', zorder = 20)
-        ax.text(reference_masses[m] - 0.7, (max(mpoint)+min(mpoint))/2 , r'%s $\times $'%(np.round( (max(mpoint)/min(mpoint))[0] , 1)) ,
-            bbox=dict(facecolor='white', edgecolor='none', boxstyle='round,pad=0.1', alpha = 0.5), ha = 'right', size = 25, zorder = 20)
+        ax.text(reference_masses[m] - 0.7, (max(mpoint)+min(mpoint))/2 , r'%s $\times $'%(np.round( (max(mpoint)/min(mpoint))[0] , 1)), 
+            bbox=dict(facecolor='white', edgecolor='none', boxstyle='round,pad=0.1', alpha = 0.5), clip_on=True, ha = 'right', size = 25, zorder = 20)
 
     #########################################
     # plot values
-    plt.text(0.63, 0.85, titletext, ha = 'center', transform=ax.transAxes, size = 25)
-
[…]

### 2022-07-29 src/scripts/SFR_z.py

@@ -61,7 +61,7 @@ def plot_SFR(sf_a = 0.017, sf_b = 1.481, sf_c = 4.452,  sf_d = 5.913,
     #default Madau & Fragos 17
     ax.plot(x1, Z_SFRD.Madau_Dickinson2014(redshift_list, a=0.01, b=2.6, c=3.2, d=6.2), 
              label = 'Madau $\&$ Fragos 2017\n $a=%.2f, b=%.2f, c=%.2f, d=%.2f$'% (0.01,2.6,3.2,6.2)
-             , c = '#356288', ls = ':',lw=6)
+             , c = 'grey', ls = ':',lw=6)
 
 #     #default Coen
 #     ax.plot(x1, Z_SFRD.Madau_Dickinson2014(redshift_list, a=0.01, b=2.77, c=2.9, d=4.7), 
@@ -72,8 +72,8 @@ def plot_SFR(sf_a = 0.017, sf_b = 1.481, sf_c = 4.452,  sf_d = 5.913,
     #Resembling thick brown line in Fig. 11 Chruslinska + 2021
     a_max, b_max, c_max, d_max = 0.04,2.5,2.9,4.5 
     ax.plot(x1, Z_SFRD.Madau_Dickinson2014(redshift_list, a=a_max, b=b_max, c=c_max, d=d_max), 
-             label = 'Maximum SFRD \n $a=%.2f, b=%.2f, c=%.2f, d=%.2f$'% (a_max, b_max, c_max, d_max)
-             , c = 'brown', lw=5, ls = '-')
+             label = 'Max, \ Chruslinska \ et \ al. \ 2021:  \n $a=%.2f, b=%.2f, c=%.2f, d=%.2f$'% (a_max, b_max, c_max, d_max)
+             , c = '#356288', lw=5, ls = '-')
 
     # BEST FIT
     try:

### 2022-08-14 src/tex/ms.tex
worked through selmas comments

@@
 % Title
-\title{ A flexible and intuitive analytic expression for the metallicity-dependent cosmic star formation rate  }
+% \title{ A flexible and intuitive analytic expression for the metallicity-dependent cosmic star formation rate  }
+% \title{ A flexible expression for the metallicity-dependent cosmic star formation rate: }
+\title{The location of features in the mass distribution of merging binary black holes does not depend on the metallicity-dependent cosmic star formation rate}
 
@@
 
+\author[0000-0002-8901-6994]{M. Chru{\'s}li{\'n}ska}
+\affiliation{Max Planck Institute for Astrophysics, Karl-Schwarzschild-Str. 1, 85748 Garching, Germany}
+
+\author[0000-0002-8901-6994]{L. Hernquist}
+
  \author[0000-0003-3308-2420]{R. Pakmor}
  \affiliation{Max Planck Institute for Astrophysics, Karl-Schwarzschild-Str. 1, 85748 Garching, Germany}
-
-\author[0000-0002-8901-6994]{Martyna Chru{\'s}li{\'n}ska}
-\affiliation{Max Planck Institute for Astrophysics, Karl-Schwarzschild-Str. 1, 85748 Garching, Germany}
-
-\author{et al?}
 
@@
 \begin{abstract}
-New observational facilities are probing astrophysical transients such as gravitational wave (GW) sources at ever increasing redshifts.
+New observational facilities are probing astrophysical transients such as stellar explosions and gravitational wave (GW) sources at ever increasing redshifts.
 To interpret these observation we need to compare them to predictions from stellar population models.
-These models are very sensitive to the metallicity-dependent star formation rate density (\SFRDzZ).
+These models, require the metallicity-dependent star formation rate density (\SFRDzZ) as an input.
+Large uncertainties remain in the shape and evolution of this function, and understanding its behaviour is essential to explain simulation results.
 % Large uncertainties remain in the value and shape of the \SFRDzZ, especially at the low metallicities that are crucial to the formation of GW events.
-Understanding the behaviour of the adopted \SFRDzZ is essential to explain simulation results. 
-%
+% Understanding the behaviour of the adopted metallicity distribution with which stars form is essential to explain simulation results. 
 % Various approaches to approximate \SFRDzZ exist, ranging from fully empirical prescriptions to prescriptions that are based on cosmological simulations.
-In this work, we propose a simple analytical form for \SFRDzZ. 
-The novelty of this model lies in a skewed-lognormal distribution of metallicities, that captures the tail of low metallicity star formation at low redshift. 
-Variations of this analytical form can be easily interpreted, because the parameters are intuitively linked to the shape of \SFRDzZ.
+In this work, we propose a simple analytical function for \SFRDzZ. 
+% The novelty of this model lies in a skewed-lognormal distribution of metallicities, that captures the tail of low metallicity star formation at low redshift. 
+Variations of this function can be easily interpreted, because the parameters link to its shape in an intuitive way.
 %Our hope is that this expression provides a useful starting point for making predictions and comparison with observations.
-%
-We fit our analytical form to the star-forming gas of the cosmological TNG100 simulations and find that it is able to capture the main behaviour well. 
+We fit our analytical function to the star-forming gas of the cosmological TNG100 simulations and find that it is able to capture the main behaviour well. 
 %
 As an example application, we investigate the effect of systematic variations in the \SFRDzZ parameters on the predicted mass distribution of locally merging binary black holes (BBH).
-Our main findings are I) the low mass end is least affected by variations in \SFRDzZ, II) the distribution of metallicities at low redshift affects the normalisation of of the BBH merger rate, while III) the redshift evolution of the metallicity distribution affects the high-mass slope of the mass distribution and IV) the shape of the overall star-formation rate has a small impact on the local mass distribution.
+Our main findings are I) the location of features is remarkably robust against variations in the metallicity-dependent star formation rate and II) the low mass end is least affected by these variations.
+This is promising as it increases our chances to constrain the physics that governs the formation of these objects.
+We further find that III) the skewness, mean, and width of the metallicity distribution at low redshift affect the overall rate, while IV) the redshift evolution of the width and the mean of the metallicity distribution affects the slope at the high-mass end of the distribution.
+% IV) the shape of the overall star-formation rate has a small impact on the local mass distribution.
 \end{abstract}
-
-% Interpreting these observations requires comparison to predictions from stellar population models.
-However, the model predictions  are very sensitive to the adopted assumptions about the metallicity-dependent star formation rate density.
-Hence in order to
-% Comparing these observations to predictions from stellar population models requires assumptions about the metallicity-dependent star formation rate density. Various approaches exist 
-% ranging from fully empirical prescriptions to prescriptions that are based on cosmological simulations. Both these approaches come with advantages and disadvantages and inherent uncertainties.
 
@@
 A myriad of astrophysical phenomena depend critically on the rate of star formation throughout the cosmic history of the Universe.
-Transient phenomena, including core collapse supernovae, (pulsational) pair-instability supernovae, long gamma-ray bursts and gravitational wave (GW) events are especially sensitive to the metallicity at which star formation occurs at different epochs throughout the Universe.
+Exotic transient phenomena, including (pulsational) pair-instability supernovae, long gamma-ray bursts and gravitational wave (GW) events appear to be especially sensitive to the metallicity at which star formation occurs at different epochs throughout the Universe \citep[e.g.,][]{Langer+2007,Fruchter+2006,LIGO2016_implications}.
 Gravitational astronomy in particular has seen explosive growth in the number of detections in the past decade \citep[][]{GWTC1,GWTC2,GWTC3}.
 In order to correctly model and interpret these observations, it is fundamental to know the rate of star formation at different metallicities throughout cosmic history, i.e.
-the metallicity-dependent star formation rate density \SFRDzZ \citep[see also the recent review by][]{chruslinska2022_review}.
+the metallicity-dependent star formation rate density  \citep[\SFRDzZ, see also the recent review by][]{chruslinska2022_review}.
+Throughout this work little $z$ refers to the redshift and $Z$ the metallicity of star formation.
 
-It is difficult to observationally constrain the shape of \SFRDzZ (see \cite{Chruslinska2019_obs} for an extensive overview and discussion of relevant observational caveats).
+It is difficult to observationally constrain the shape of \SFRDzZ, see \cite{Chruslinska2019_obs} for an extensive overview and discussion of relevant observational caveats.
 Even at low redshifts, the low metallicity part of the distribution is poorly constrained \citep{Chruslinska+2021}.
 Nonetheless, several methods exist to estimate the metallicity dependent star-formation rate.
-The first method combines a mass-metallicity relation (MZ-relation) and a galaxy stellar mass function (GSMF) \citep[see e.g.][]{Chruslinska+2018, Chruslinska2019_effectCO, Broekgaarden+2021a}.
-Another way is to directly extract the metallicity density fraction from cosmological simulations \citep[e.g.]{Mapelli2017, Briel+2021}.
-Alternatively, one can combine an observed star formation rate, \SFRDz, like from \cite{MadauDickinson2014} or \cite{Madau+2017}, and convolve this with some belief about the shape of the metallicity density distribution, such as was was done in \cite{Neijssel+2019}.
+The first method combines a galaxy mass-metallicity relation, MZ-relation and a galaxy stellar mass function, GSMF \citep[see e.g.][]{Dominik+2013}.
+% \citep[see e.g.][]{Chruslinska+2018, Chruslinska2019_effectCO, Broekgaarden+2021a}.
+On can also directly extract the metallicity density fraction from cosmological simulations \citep[e.g.][]{Mapelli2017, Briel+2021}.
+Alternatively, one can combine an observed star formation rate, \SFRDz, like from \cite{MadauDickinson2014} or \cite{Madau+2017}, and convolve this with an assumed function for the shape of the shape of the metallicity density distribution, such as was was done in \cite{LangerNorman, Neijssel+2019}.
 
@@
 In this work we follow the latter approach and propose a flexible analytical model for the \SFRDzZ that can be fit to the output of both cosmological simulations, and observational data constraints where available.
-The novelty of this model lies in a skewed-lognormal distribution of metallicities, that captures the tail of low metallicity star formation at low redshift.
-The purpose of this model is to allow for an intuitive interpretation of the effects of the \SFRDzZ on the inferred rates of astrophysical transients.
+In contrast to earlier work  \citep{LangerNorman, Neijssel+2019}, we adopt a skewed-lognormal distribution of metallicities that can capture the asymmetry in the low and high metallicity tails.
+%to capture the tail of low metallicity star formation at low redshift.
+% The novelty of this model lies in a skewed-lognormal distribution of metallicities, that captures the tail of low metallicity star formation at low redshift.
+
+The purpose of this proposed form is twofold.  
+First of all, the form we propose allows for an intuitive interpretation of the free parameters.
+This allows us to get better insight of the impact of changes in these parameters on the inferred ranges of astrophysical transients (as we demonstrate in this work using GW predictions as an example).
+By adopting an analytical, parametrized form for \SFRDzZ, the large uncertainties in \SFRDzZ can be systematically explored.
+Secondly, we hope that this form will facilitate a more sensible way for useful inference on large (future) datasets of astrophysical transients, such as the ever growing catalogue of gravitational wave transients.
+Our hope is that the constraints on the free parameters in the analytical form we propose, can provide a more useful guidance when comparing with the outcome of the predictions of cosmological simulations.
+% is to allow for an intuitive interpretation of the effects of the \SFRDzZ on the inferred rates of astrophysical transients.
 By adopting an analytical, parametrized form for \SFRDzZ, the large uncertainties in \SFRDzZ can be systematically explored.% through varying the parameters that control its shape.
@@
 We summarise our findings in Section \ref{sec: summary}.
-
-% %
-% The task we have at hand here is not a standard textbook fitting problem given the specific aims and requirements that we have that are driven by the astrophysical applications we have in mind.
-Qualitatively, our aims are the following.
-Our main aim is to find solution for the free parameters, for which the expression reproduces the overall behaviour that is observed in the cosmological simulations.
-For the purposes we have in mind, it will be more important to prioritise fitting the large scale trends, while we are not so interested in smaller scale fluctuations.
-We further prioritise getting the bulk of the cosmic star formation right and are less interested in capturing the behaviour in metallicity and redshift bins where the cosmic star formation rate is very low and thus insignificant for the overall picture.
-Finally, we are especially interested in capturing the asymmetry of the metallicity distribution.
-% There is not one unique procedure that will full fill these criteria.
-After experimenting with different criteria we have adopted the procedure below, which we believe works well for the aims we have in mind.
-%%
-% Large uncertainties exist in the shape and redshift evolution of both \SFRDz, and the cosmic distribution of metallicities \dpdZ (see e.g.
-\citealt{Chruslinska2019_obs}, \citealt{Boco2021} and \citealt{Chruslinska+2021} for an extended discussion on the metallicity dependent star formation rate density, in light of empirical data).
-
-% To construct \SFRDzZ from empirical data, one can estimate \dpdZ by combining observed mass-metallicity relations with galaxy stellar mass functions \citep[see e.g.][]{Chruslinska+2018, Chruslinska2019_obs, Broekgaarden+2021b}.
-Alternatively, one could extract \SFRDzZ directly from cosmological simulations \citep[e.g.][]{Mapelli2017, Briel+2021}.
-% \citet{Mapelli2017} and \cite{Briel+2021}  but instead of directly extracting the \SFRDzZ from a cosmological simulation 
-% we take an approach similar to \cite{LangerNorman}, but instead of following the observed mean metallicity with redshift, we fit our combined analytical representations of \SFRDz and \dpdZ to simulation data.
 
@@
 \end{equation}
-The first term is the star formation rate density, \SFRDz, that is the amount of mass formed in stars per unit time and per unit comoving volume at each redshift.
-The second term, \dpdZ, is a probability density function that expresses what fraction of star formation occurs at which metallicity, at each redshift.
+The first term is the star formation rate density, \SFRDz, that is the amount of mass formed in stars per unit time and per unit comoving volume at each redshift, $z$.
+The second term, \dpdZ, is a probability density function that expresses what fraction of star formation occurs at which metallicity, $Z$, at each redshift.
 
@@
 For the probability distribution of metallicities we draw inspiration from the approach by \citep[e.g.\ ][]{Neijssel+2019} who used a log-normal distribution.
-Unfortunately, this expression does not capture the asymmetry well that we see in the results of the cosmological simulations, which show an extended tail towards low metallicity combined with a very limited tail towards higher metallicity, when plotted as a function of $\log_{10} Z$.
-To capture this behavior we adopt a skewed-log-normal distribution instead.
+Unfortunately, this expression does not capture the asymmetry well that we see in the results of the cosmological simulations, which show an extended tail in  $\log_{10} Z$ towards low metallicity combined with a very limited tail towards higher metallicity.
+To capture this behaviour we adopt a skewed-log-normal distribution instead.
 This is an extension of the normal distribution that introduces an additional shape parameter, $\alpha$, that regulates the skewness \citep[first introduced by][]{Ohagan+1976}.
-%for a more clear derivation
-%This allows us to more accurately capture the asymmetry in the metallicity distribution at each redshift.
 
@@
     \underbrace { \phi \left(\frac{\ln Z - \xi}{\omega}\right)
-                 }_{(1)}
+                 }_{(a)}
     \underbrace {
                 \Phi\left(\alpha \frac{\ln Z - \xi}{\omega} \right)
-                }_{(2)},
+                }_{(b)},
 \end{aligned}
@@
 
-\noindent where (1) is the standard log-normal distribution, $\phi$,
+\noindent where (a) is the standard log-normal distribution, $\phi$,
 %
@@
     \end{equation}
-and (2) is the new term that allows for asymmetry, which is equal to the cumulative of the log-normal distribution, $\Phi$,
+and (b) is the new term that allows for asymmetry, which is equal to the cumulative of the log-normal distribution, $\Phi$,
     \begin{equation}
@@
  \Phi\left(\alpha \frac{\ln Z - \xi}{\omega} \right) &\equiv 
-% \underbrace {
     \frac{1}{2} 
@@
             \left\{
-%                \frac{ \left(\alpha \frac{\ln(Z) - \xi}{\omega} \right)  }{\sqrt{2}} 
                 \alpha \frac{\ln Z - \xi}{\omega \sqrt{2}}
@@
     \right] \\
-    %}_{(2)}.
-%   &=    %%% I dont think this belongs here: \frac{1}{2} 
-%       \int_{\infty}^{\alpha\left( \frac{\ln Z -\xi}{\omega}\right)}
-%       \frac{1}{\sqrt{2\pi}}e^{-t^2/2}dt
     \end{array}
@@
 %
-\noindent This introduces three parameters, $\alpha, \omega$ and $\xi$ each of which may depend on redshift.
+\noindent This introduces three parameters, $\alpha, \omega$ and $\xi$, each of which may depend on redshift.
 The first parameter, $\alpha$, is known as the ``shape''.
@@
 \begin{equation}
-\label{eq: sigma z}
+\label{eq: omega z}
     \omega(z) = \omega_0 \cdot 10^{\omega_z \cdot z}.
@@
 \paragraph{Asymmetry of the metallicity distribution: $\alpha$}
-We have considered variations where the ``skewness'' $\alpha$ varies with redshift but we did not find very significant improvements compared to the simpler assumption where $\alpha$ is kept constant.
-
-%We allow the mean metallicity and the spread of metallicities to evolve with redshift by allowing the ``location'' $\xi(z)$ and ``scale'' $\omega(z)$ to vary as functions of redshift.
-We have also considered to allow the ``skewness'' to vary with redshift, but we did not find a very significant improvement and we opted to keep this constant.
+The skewness $\alpha$ could in principle also be allowed to evolve with redshift (e.g., $\alpha (z) = \alpha(z=0) 10^{\alpha_z \cdot z}$). 
+However, we find no significant improvement over the simpler assumption where alpha is kept constant. 
+Note that the redshift evolution of the `scale' (eq. \ref{eq: omega z}), already captures similar behaviour in our current formalism. We therefore adopt $ \alpha = \alpha(z=0)$ and $\alpha_z = 0$.
 
@@
 
-\noindent where $\xi(z)$ and $\omega(z)$ are defined in Equations~\ref{eq mu z} and \ref{eq: sigma z} respectively and we have assumed $\alpha$ to be constant.
+\noindent where $\xi(z)$ and $\omega(z)$ are defined in Equations~\ref{eq mu z} and \ref{eq: omega z} respectively and we have assumed $\alpha$ to be constant.
 
-%, and our fit value for $\alpha = -1.77$. Our set of parameters for \dpdZ is thus:  $\mu_0 = 0.025, \mu_z = -0.048, \sigma_0 = 1.125, \sigma_z = 0.048$ and $\alpha = -1.77$.
+%, and our fit value for $\alpha = -1.77$. Our set of parameters for \dpdZ is thus:  $\mu_0 = 0.025, \mu_z = -0.048, \omega_0 = 1.125, \omega_z = 0.048$ and $\alpha = -1.77$.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-The IllustrisTNG-project \citep[or TNG in short][]{FirstResTNG_Springel2018,FirstResTNG_Marinacci2018, FirstResTNG_Nelson2018,FirstResTNG_Pillepich2018, FirstResTNG_Naiman2018} considers galaxy formation and evolution through large-scale cosmological hydrodynamical simulations.
+Both the large observational uncertainties in \SFRDzZ (as discussed in section \ref{sec: intro}), and the many uncertainties in cosmological simulations (as discussed below) call for a generalised form of the \SFRDzZ that can be easily updated when new information becomes available, which is the motivation for this work.
+Although here, we only fit our model to the TNG100 simulation, our prescription can be easily be used to fit other simulated or observational data of the metallicity dependent star formation rate density \footnote{We provide a Jupyter notebook to facilitate this fit here: \url{https://github.com/LiekeVanSon/SFRD_fit/blob/main/src/scripts/Fit_To_Cosmological_Simulation.ipynb} }.
+
+The IllustrisTNG-project \citep[or TNG in short,][]{FirstResTNG_Springel2018,FirstResTNG_Marinacci2018, FirstResTNG_Nelson2018,FirstResTNG_Pillepich2018, FirstResTNG_Naiman2018} considers galaxy formation and evolution through large-scale cosmological hydrodynamical simulations.
 Such simulations provide the tools to study parts of the Universe that are not easily accessible by observations.
 In particular of interest for this work, they simulate the high redshift enrichment of galaxies and the tail of low metallicity star formation at low redshift.
-Different cosmological simulations produce varying \SFRDzZ, depending on the adopted assumptions about the creation and distribution of metals.
+% Different cosmological simulations produce varying \SFRDzZ, depending on the adopted assumptions about the creation and distribution of metals.
 
@@
 In short, star formation in the TNG simulations is calibrated against the Kennicutt–Schmidt relation \citep[][]{Schmidt1959,Kennicutt1989}.
-The stellar metallicity yields are and updated version of the original Illustris simulations as described in \cite{Pillepich2018}.
-Star particles deposit metals into the gas through Type Ia and Type II supernovae, as well as through Asymptotic Giant Branch mass loss.
+The stellar metallicity yields are an updated version of the original Illustris simulations as described in \cite{Pillepich2018}.
+Star particles deposit metals into the gas through type Ia and type II supernovae, as well as through asymptotic giant branch stars.
 % Positives on TNG
@@
 %They reproduce the evolution of the sizes of galaxies with redshift \citep{Genel+2018}
-Several studies have already used the TNG simulations to make predictions for astronomical transient sources \citep[e.g.][]{Briel+2021,Bavera+2022}.
+Several studies have used the TNG simulations to make predictions for astronomical transient sources \citep[e.g.][]{Briel+2021,Bavera+2022,vanson+2022}.
 In particular, \cite{Briel+2021} show that the \SFRDzZ from the TNG and the EAGLE \citep{Schaye+2015,Crain+2015} simulations provide the best agreement between observed and predicted cosmic rates for electromagnetic and gravitational-wave transients.
@@
 For example, dust is not included in the TNG simulations, which could mean that metallicity of the star-forming gas is overestimated.
-Furthermore, all mass loss from massive stellar winds \citep[e.g.][]{Dray+2003}, pair-pulsational supernovae \citep[e.g.][]{Renzo+2020} binary interactions \citep[e.g.][]{Farmer2021_carbonfootprint} and their ionising effects \citep[][]{Gotberg+2020,DoughtyFinlator2021} are ignored.
+Furthermore, all stellar winds mass loss from massive stars, binary interactions and their ionising effects are ignored \citep[e.g.][]{Dray+2003,Smith2014,Gotberg+2020,DoughtyFinlator2021,Farmer2021_carbonfootprint,Goswami+2022}.
+% pair-pulsational supernovae \citep[e.g.][]{Renzo+2020} .  
 Moreover, the uniform ionising UV background is turned on abruptly at $z=6$, which crucially impacts the amount of low metallicity star formation at low redshift.
 
-These large uncertainties call for a generalised form of the \SFRDzZ that can be easily updated when new information becomes available, which is the motivation for this work.
-Although here, we only fit our model to the TNG100 simulation, our prescription can be easily be used to fit other simulated data or observational data of the metallicity dependent star formation rate density \footnote{We provide a Jupyter notebook to facilitate this fit here \todo{add link}}.
+% These large uncertainties call for a generalised form of the \SFRDzZ that can be easily updated when new information becomes available, which is the motivation for this work.
+Although here, we only fit our model to the TNG100 simulation, our prescription can be easily be used to fit other simulated data or observational data of the metallicity dependent star formation rate density \footnote{We provide a Jupyter notebook to facilitate this fit here: \url{https://github.com/LiekeVanSon/SFRD_fit/blob/main/src/scripts/Fit_To_Cosmological_Simulation.ipynb} }.
 
@@
 
-\begin{deluxetable}{clc | cc}
+\begin{deluxetable*}{cll | cl}
 \label{tab: fit params}
@@
 \startdata
-$\mu_0$    & mean metallicity $z=0$     & 0.025 &  $a$ &  0.02 \\
-$\mu_z$    & mean metallicity $z$ evol. & -0.048 &  $b$ &  1.48 \\
-$\alpha$   & shape (skewness)           & -1.767 &  $c$ &  4.45 \\
-$\omega_0$ & scale $z=0$                & 1.125 &  $d$ &  5.90 \\
-$\omega_z$ & scale $z$ evol.            & 0.048 &   \\
+$\mu_0$    & mean metallicity at $z=0$    & $0.025  \pm 0.001$ &  $a$ &  $0.02 \pm 0.05 \, \Msun\yr^{-1}\Mpc^{-3}$\\
+$\mu_z$    & $z$-dependence of the mean   & $-0.048 \pm 0.001$ &  $b$ &  $1.48 \pm 0.01$\\
+$\alpha$   & shape (skewness)             & $-1.767 \pm 0.05 $ &  $c$ &  $4.45 \pm 0.01$\\
+$\omega_0$ & scale at $z=0$               & $1.125  \pm 0.005$ &  $d$ &  $5.90 \pm 0.02$\\
+$\omega_z$ & $z$-dependence of the scale  & $0.048  \pm 0.0001$ &   \\
 \enddata
-\end{deluxetable}
+\end{deluxetable*}
 
@@
 To emphasise the difference between a skewed-lognormal and a symmetric lognormal distribution, we show the phenomenological model from \cite{Neijssel+2019} in dotted grey.
-Their model falls within the family of functions that is encompassed by our model described in Section \ref{sec: model for sfrd(zZ)}.
+Their model falls within the family of functions that is encompassed by our model described in Section \ref{sec: model for sfrd(zZ)}, but we note that their model is distinctly different.
 \footnote{The phenomenological model from \cite{Neijssel+2019} is recovered by adopting $\mu_0= 0.035$, $\mu_z=-0.23$, $\omega_0=0.39 $, $\omega_z = 0$, $\alpha = 0$, $a=0.01$, $b=2.77$, $c=2.9$ and $d=4.7$.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
+\begin{figure*}
 \centering
@@
 \includegraphics[width=0.47\textwidth]{figures/SFR_redshift.pdf}
+\includegraphics[width=0.47\textwidth]{figures/SFR_tlookback.pdf}
 \caption{Comparison of different \SFRDz
  \label{fig: SFR(z)}}
-\end{figure}
+\end{figure*}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 We use the publicly available rapid binary population synthesis simulations presented in \cite{vanson+2022}. 
-These simulations were run using version v02.19.04 of the open source \COMPAS suite \citep{COMPAS_method} \footnote{\url{https://github.com/TeamCOMPAS/COMPAS}}.
+These simulations were run using version v02.19.04 of the open source \COMPAS suite \citep{COMPAS_method}\footnote{\url{https://github.com/TeamCOMPAS/COMPAS}}.
 \COMPAS is based on algorithms that model the evolution of massive binary stars following \citet{Hurley+2000, Hurley+2002}, based on detailed evolutionary models by \citet{Pols+1998}.
@@
 We will refer to the more (less) massive component as the primary (secondary) from hereon.
-In general we note that the main features in the primary mass distribution remain distinguishable throughout all \SFRDzZ variations.
+
+Most notably, we see that the main features in the primary mass distribution remain distinguishable throughout all \SFRDzZ variations.
+\todo{\cite{chruslinska2022_review} Fig.
+5 actually shows that the \textit{shape} of the mass distribution is \textit{not at all} impacted that much by the SFRD!!}
+\todo{ This is in particular hopeful to measure cosmology with third generation detectors \cite{MariaEzquiaga2022} }
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Discussion \& ? Summary \label{sec: summary}}
+\section{Discussion \& Summary \label{sec: summary}}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\todo{\cite{chruslinska2022_review} Fig. 5 actually shows that the \textit{shape} of the mass distribution is \textit{not at all} impacted that much by the SFRD!!}
-
 We present a flexible analytic expression for the metallicity-dependent star formation rate, \SFRDzZ (equations \ref{eq: total sfrd}, \ref{eq: z log skew} and \ref{eq: sfr1}).
 An analytical expression allows for controlled experiments of the effect of \SFRDzZ on dependent values, such as the rate and mass distribution of merging BBHs.
-The novelty of the model presented in this work is that it adopts a skewed-lognormal for the distribution of metallicities at every redshift (\dpdZ).
+The model presented in this work adopts a skewed-lognormal for the distribution of metallicities at every redshift (\dpdZ).
 
 \paragraph{The model can capture the general behaviour of cosmological simulations, such as TNG100}
+Our analytical expression for \SFRDzZ is composed of a cosmic metallicity distribution that is determined by a mean, scale and skewness and their redshift dependence, as well as parameters governing the overall cosmic star formation rate.
 We fit our analytical expression for \SFRDzZ to the star-forming gas in the TNG100 simulation, and provide the best fit parameters in Table \ref{tab: fit params}.
+% We fit our analytical expression for \SFRDzZ to the star-forming gas in the TNG100 simulation.
 We show that our model captures the shape and general behaviour of the cosmological simulations well (Figure \ref{fig: fit SFRD}).
 
-\paragraph{We preform a controlled experiment on the effect of \SFRDzZ on the local distribution of merging BBH}
+\paragraph{The model allows for a controlled experiment on the effect of \SFRDzZ on the local distribution of merging BBH}
 As an example, we apply our model to calculate the local rate and mass distribution of the more massive components from merging BBHs (\Mbheen) in Figure \ref{fig: mass dists}. 
-We systematically vary all five parameters ($\alpha, \mu_0, \mu_z, \omega_0$ and $\omega_z$) that shape the cosmic metallicity distribution \dpdZ, and explore two additional variations of the overall star-formation rate \SFRDz, following \cite{Madau+2017} and \cite{Neijssel+2019} respectively.
+We systematically vary all five parameters that shape the cosmic metallicity distribution, and explore two additional variations of the overall star-formation rate \SFRDz, following \cite{Madau+2017} and \cite{Neijssel+2019} respectively.
 Our main conclusions are as follows:
@@
 
-    \item For all variations, the low mass end of the mass distribution is least affected the change in the \SFRDzZ.
+    \item The location of features in the distribution of primary BH masses are robust against variations in the \SFRDzZ.
+The location of features in the mass distribution of BHs could thus be used as tell-tale signatures of their formation channel.
 
-    \item The metallicity distribution of star formation at low redshift, primarily impacts the normalisation of the \Mbheen distribution (i.e. the total local rate $\mathcal{R}_{0.2}$).
+    \item For all variations, the low mass end of the mass distribution is least affected by changes in the \SFRDzZ.
+This suggest that lower end of the BH mass distribution (component masses of $\leq 15\Msun$) is potentially very powerful for constraining the physics of the formation channels, irrespective of the cosmic star formation rate uncertainties.
 
-    \item Parameters that influence the redshift evolution of the metallicity distribution, affect the slope of the high mass end of the \Mbheen distribution.
+    \item The metallicity distribution of star formation at low redshift, primarily impacts the normalisation of the primary BH mass distribution (i.e. the total rate of BBH mergers at redshift 0.2).
+
+    \item Parameters that influence the redshift evolution of the mean and the width of the metallicity distribution, affect the slope of the high mass end of the \Mbheen distribution.
 %Specifically this impacts the for masses above the peak of the \Mbheen distribution which occurs at approximately 18\Msun.
-
-    \item Changing the overall star-formation history, \SFRDz has a small effect on the local mass distribution.
+    \item Changing the overall star-formation history, \SFRDz varies the normalisation of the rate by at most a factor of about 5.
 This is because reasonable variations of the \SFRDz have a similar value for the total local star-formation rate density, which is relatively well constrained by observations.
@@
 \script{LowHighZ_fraction.py}
-\includegraphics[width=0.8\textwidth]{figures/High_Low_metalFractionSFMass.pdf}
+\includegraphics[width=\textwidth]{figures/High_Low_metalFractionSFMass.pdf}
 \caption{Fraction of high vs low metallicity stellar mass.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\bibliography{my_bib,main_bib}
+\bibliography{main_bib}
 

### 2022-08-14 src/scripts/Plot_Mass_distributions.py

@@ -207,7 +207,7 @@ def plot_mass_distribution(sim_dir = '', x_key = 'M_moreMassive', rate_keys = ['
         center_bins = (bin_edge[:-1] + bin_edge[1:])/2.
 
         # And the KDE
-        kernel = stats.gaussian_kde(x_vals, bw_method=kde_width, weights=Weights)
+        kernel = stats.gaussian_kde(x_vals, bw_method='scott', weights=Weights)
         binwidth = np.diff(bin_edge)
 
         m10.append(kernel(10)*sum(hist)) # append value at reference mass 

### 2022-08-14 src/scripts/SFR_z.py

@@ -42,10 +42,10 @@ plt.rc('legend', fontsize=SMALL_SIZE)    # legend fontsize
 # plot different SFRs
 ########################################################
 def plot_SFR(sf_a = 0.017, sf_b = 1.481, sf_c = 4.452,  sf_d = 5.913,
-             redshift_list  = np.linspace(0,15, num=100), x_redshift = True, tmin=0.0, tmax = 13.7):
+             redshift_list  = np.linspace(0,15, num=100), x_redshift = True, tmin=0.0, tmax = 13.7, show_legend = True):
     ########################################################
     # Start plotting
-    fig, ax = plt.subplots(figsize=(12,10))
+    fig, ax = plt.subplots(figsize=(10,8))
 
     if x_redshift:
         x1  = redshift_list
@@ -150,7 +150,7 @@ def plot_SFR(sf_a = 0.017, sf_b = 1.481, sf_c = 4.452,  sf_d = 5.913,
         # And annotate the tick labels :)
         ax2.set_xticks([z for z in redshift_tick_list])
         ax2.set_xticklabels(['${:.1f}$'.format(cosmo.lookback_time(z).value) for z in redshift_tick_list])
-        ax2.set_xlabel('$\mathrm{Lookback \ time \ [Gyr]}$', fontsize = 20)
+        ax2.set_xlabel('$\mathrm{Lookback \ time \ [Gyr]}$', fontsize = 30)
 
     else:
         ###################
@@ -177,7 +177,9 @@ def plot_SFR(sf_a = 0.017, sf_b = 1.481, sf_c = 4.452,  sf_d = 5.913,
         plt.yscale('log')
     ax.set_ylabel(r'$\frac{dM}{dt dV_c}$ $\mathrm{[M_{\odot} yr^{-1} Mpc^{-3}]}$', fontsize = 30)
     ax.set_ylim(1e-3, 1.)
-    ax.legend()
+    
+    if show_legend:
+        ax.legend()
     if x_redshift:
         print('saving here', save_loc + 'SFR_redshift'+'.pdf')
         plt.savefig(save_loc + 'SFR_redshift'+'.pdf',  bbox_inches='tight')
@@ -190,10 +192,10 @@ def plot_SFR(sf_a = 0.017, sf_b = 1.481, sf_c = 4.452,  sf_d = 5.913,
     
 
 # redshift axis
[…]

### 2022-08-16 src/tex/ms.tex
wrote results and conclusions

@@
 Both the large observational uncertainties in \SFRDzZ (as discussed in section \ref{sec: intro}), and the many uncertainties in cosmological simulations (as discussed below) call for a generalised form of the \SFRDzZ that can be easily updated when new information becomes available, which is the motivation for this work.
-Although here, we only fit our model to the TNG100 simulation, our prescription can be easily be used to fit other simulated or observational data of the metallicity dependent star formation rate density \footnote{We provide a Jupyter notebook to facilitate this fit here: \url{https://github.com/LiekeVanSon/SFRD_fit/blob/main/src/scripts/Fit_To_Cosmological_Simulation.ipynb} }.
+Although here, we only fit our model to the TNG100 simulation, our prescription can be easily be used to fit other simulated or observational data of the metallicity dependent star formation rate density\footnote{We provide a Jupyter notebook to facilitate this fit here: \url{https://github.com/LiekeVanSon/SFRD_fit/blob/main/src/scripts/Fit_To_Cosmological_Simulation.ipynb} }.
 
@@
 \includegraphics[width=0.47\textwidth]{figures/SFR_tlookback.pdf}
-\caption{Comparison of different \SFRDz
+\caption{Comparison of different overall star-formation histories with redshift, \SFRDz.
+The solid orange and dashed red lines respectively show the star formation data from TNG100 and our corresponding fit adopting eq.
+\ref{eq: sfr1} (fiducial model).
+The dotted gray and solid blue lines are variations of eq.
+\ref{eq: sfr1} used to approximate the lower and upper edge of possible star-formation histories.
+The dotted gray line shows the model from \cite{Madau+2017}, while the solid blue line mimics the behaviour of the powerlaw-fit to the \texttt{SB: B18/C17} variations with a non-evolving low-mass end of the galaxy stellar mass function from \cite{Chruslinska+2021}.
 \label{fig: SFR(z)}}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+We will now demonstrate the application of our analytical model by systematically varying the parameters in our fiducial \SFRDzZ model, and investigate their effect on the local mass distribution of BBH mergers originating from isolated binaries.
+
+We use the publicly available rapid binary population synthesis simulations presented in \cite{vanson+2022}. 
+These simulations were run using version v02.19.04 of the open source \COMPAS suite \citep{COMPAS_method}\footnote{\url{https://github.com/TeamCOMPAS/COMPAS}}.
+\COMPAS is based on algorithms that model the evolution of massive binary stars following \citet{Hurley+2000, Hurley+2002} using detailed evolutionary models by \citet{Pols+1998}.
+We refer the reader to the methods section of \cite{vanson+2022} for a detailed description of our adopted physics parameters and assumptions.
+%
+Metallicities of each binary system were sampled from a smooth probability distribution to avoid artificial peaks in the BH mass distribution \citep[e.g.][]{Dominik2015,Kummer_thesis}. 
+These simulations provide us with an estimate of the yield of BBH mergers per unit of star-forming mass and metallicity.
+
+We combine the aforementioned yield with variations of the fiducial \SFRDzZ model described in this work.
+By integrating over cosmic history, we obtain the local merger rates of BBH systems, which allow us to construct the distribution of source properties at every redshift.
+The details of this framework are described in \cite{vanson+2022}, but also in \cite{Broekgaarden+2021a} and \cite{Neijssel+2019}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Determining reasonable variations of \SFRDzZ \label{ss: reasonable var}}
+We consider variations in both the shape of the cosmic metallicity distribution \dpdZ, and the shape of the overall star-formation history, \SFRDz.
+To determine the range that is reasonably allowed by observations, we compare our variations to the observation-based \SFRDzZ models described in \cite{Chruslinska+2021}.
+
+For the cosmic metallicity distribution, we vary every parameter that determines the shape of \dpdZ independently (left two columns of Table \ref{tab: fit params}).
+For every variation, we inspect the fraction of stellar mass that is formed at low-metallicity ($Z<0.1 Z_{\odot}$) versus the fraction of stellar mass that is formed at high-metallicity ($Z> Z_{\odot}$), for all star formation that occurred below a certain threshold redshift.
+We compare this to the models from \cite{Chruslinska+2021} in Figure \ref{fig: low high Z fraction} in Appendix \ref{app: reasonable var}.
+We have chosen our variations such that they span the range of reasonable cosmic metallicity distributions as determined by observation-based and cosmological simulations-based models.
+For completeness, we furthermore inspect every variation by eye, and make sure none of the variations significantly exceeds the low and high metallicity extremes from \cite{Chruslinska+2021}.\footnote{We  compare to the low metallicity extreme model: \texttt{214f14SBBiC\_FMR270\_FOH\_z\_dM.dat}, and the high metallicity extreme model: \texttt{302f14SBBoco\_FMR270\_FOH\_z\_dM.dat}.}
+
+Lastly, we consider two variations of the overall star-formation history, \SFRDz, where we keep the metallicity distribution \dpdZ fixed, but vary all four \SFRDz parameters at once (right two columns of Table \ref{tab: fit params}).
+We use Figure 11 from \cite{Chruslinska+2021} to determine approximate upper and lower bounds to the overall star-formation history.
+We choose \cite{Madau+2017} as an approximation of the lower limit.
+For the upper limit, we use the \texttt{SB: B18/C17} model variations with a non-evolving low-mass end of the galaxy stellar mass function from \cite{Chruslinska+2021} (thick brown line in their Fig.
+11).
+To approximate these models, we fit equation \ref{eq: sfr1} by eye to the broken power law description for the  \texttt{SB: B18/C17} model variations as presented in appendix B1 from \cite{Chruslinska+2021}.
+We show all \SFRDz variations in Figure \ref{fig: SFR(z)}. \\
+%30*f14SBBiC
+% low_Z_file = '214f14SBBiC_FMR270_FOH_z_dM.dat'            
+% high_Z_file = '302f14SBBoco_FMR270_FOH_z_dM.dat'
 
@@
 Variations in \SFRDzZ have the largest impact on the high mass end of the distribution, while around $\Mbheen=10$, variations are smaller than a factor of 3.
-  \label{fig: mass dists}}
+  \label{fig: stable mass dists}}
 \end{figure*}
@@
 \includegraphics[width=0.8\textwidth]{figures/Mass_distributions_CE_SFRD_variations.pdf}
-\caption{Same as Figure \ref{fig: mass dists}, but for the Common envelope channel. 
-   \label{fig: mass dists}
+\caption{Same as Figure \ref{fig: stable mass dists}, but for the Common envelope channel. 
+   \label{fig: CE mass dists}
   }
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{The effect of the \SFRDzZ on the primary BH mass distribution}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+To isolate the effect of the \SFRDzZ from the effects of mixing different formation channels, we split the data from \cite{vanson+2022} between the stable mass transfer channel \citep[e.g.,][]{van-den-Heuvel+2017,Inayoshi2017,Bavera2021,Marchant2021,GallegosGarcia2021,vanson+2022}, and the `classical' common-envelope channel \citep[or CE channel, e.g.,\  ][]{Belczynski+2007,PostnovYungelson2014,Belczynski+2016Natur,vignaGomez+2018}.
+These channels are distinguished based on whether the binary experiences common envelope evolution (CE channel) or only stable mass transfer (stable channel in short from now on).
 
-We will now demonstrate the application of our analytical model by systematically varying the parameters in our fiducial \SFRDzZ model, and investigate their effect on the local mass distribution of BBH mergers originating from isolated binaries.
+In Figures \ref{fig: stable mass dists} and \ref{fig: CE mass dists}, we show the resulting primary mass distribution of merging BBHs from the stable channel and CE channel respectively.
+The primary (secondary) component refers to the more (less) massive component of merging BBHs. 
+Each panel varies one aspect of the \SFRDzZ.
 
-We use the publicly available rapid binary population synthesis simulations presented in \cite{vanson+2022}. 
-These simulations were run using version v02.19.04 of the open source \COMPAS suite \citep{COMPAS_method}\footnote{\url{https://github.com/TeamCOMPAS/COMPAS}}.
-\COMPAS is based on algorithms that model the evolution of massive binary stars following \citet{Hurley+2000, Hurley+2002}, based on detailed evolutionary models by \citet{Pols+1998}.
-We refer the reader to the methods section of \cite{vanson+2022} for a detailed description of our adopted physics parameters and assumptions.
+% The location of features is robust
+The first thing we note is that the location of the features in the primary mass distribution are robust against variations in the \SFRDzZ.
+For the CE channel, the global peak of the mass distribution remains at approximately $\Mbheen=16\Msun$ for all variations.
+Similarly, the stable channel displays two peaks that are visible in all variations: a peak at $\Mbheen\approx9\Msun$ and a peak at $\Mbheen\approx22\Msun$. 
+Two more peaks are visible in the stable channel at the high mass end for almost all \SFRDzZ (at $\Mbheen\approx35\Msun$ and $\Mbheen\approx45\Msun$), these peaks only fade for variations where the rate of high mass BHs is generally suppressed (dashed lines in top panel of Fig.
+\ref{fig: stable mass dists}).
 %
-Metallicities of each binary system were sampled from a smooth probability distribution to avoid artificial peaks in the BH mass distribution \citep[e.g.][]{Dominik2015,Kummer_thesis}. 
-These simulations provide us with an estimate of the yield of BBH mergers per unit of star-forming mass and metallicity.
-
-We combine the aforementioned yield with a variation of the fiducial \SFRDzZ model described in this work.
-By integrating over cosmic history, we obtain the local merger rates of BBH systems, which allow us to construct the distribution of source properties at every redshift.
-The details of this framework are described in \cite{vanson+2022}, and also in \cite{Broekgaarden+2021a} and \cite{Neijssel+2019}.
-
-We consider variations of each of the parameters that determine the shape of the cosmic metallicity distribution \dpdZ (left two columns of Table \ref{tab: fit params}) and two variations of the \SFRDz, where we keep the metallicity distribution \dpdZ fixed, but vary the overall star-formation rate history  \SFRDz (i.e.
-all four \SFRDz parameters at once), to match the values used in \cite{Madau+2017} and \cite{Neijssel2019} respectively (see Figure \ref{fig: SFR(z)} for reference).
-To determine the range of parameters that is reasonably allowed by observations, we have compared the \SFRDzZ in the metallicity-redshift plane to the high and low metallicity extreme from \cite{Chruslinska+2021} by eye for every variation.
-\\
-
-In Figure \ref{fig: mass dists} we show the resulting mass distribution of the more massive component from merging BBHs.
-We will refer to the more (less) massive component as the primary (secondary) from hereon.
-
-Most notably, we see that the main features in the primary mass distribution remain distinguishable throughout all \SFRDzZ variations.
-\todo{\cite{chruslinska2022_review} Fig.
-5 actually shows that the \textit{shape} of the mass distribution is \textit{not at all} impacted that much by the SFRD!!}
-\todo{ This is in particular hopeful to measure cosmology with third generation detectors \cite{MariaEzquiaga2022} }
+This is consistent with the results in \cite{Broekgaarden+2021b}.
+Although peaks in the probability distribution of chirp masses as shown in their Fig.
+4 can disappear when a the \SFRDzZ prohibits the formation of certain (typically higher) mass BHs, the \textit{location} of features remains the same.
+%
+This result is furthermore consistent with recent findings in \cite{chruslinska2022_review}.
+In their Figure 5, they compare two very different models of \SFRDzZ and find that, although the normalisation between the two BBH merger rates is completely different, the location of the peaks remains the same.
+%
+This implies that the \textit{locations} of features in the mass distribution of BBHs are determined by the formation channel and its underlying stellar and binary physics.
+The location of features could therefore serve as tell tales of the underlying physics.
 
 % Low masses are less affected
-Changes in the \SFRDzZ have the largest impact on the high mass end of the primary mass distribution, while the impact on the low mass is relatively modest.
+Second, we see that the low mass end of the primary mass distribution is relatively robust against variations in the \SFRDzZ. 
 To quantify this, we annotate the ratio between the maximum and minimum rate at three reference masses; \Mbheen = $10, 25$, and $40\Msun$.
-At $\Mbheen=10\Msun$, we find that the rate changes by at most a factor 3 for the variations explored in this work. While we find a factor of at most 11 for the change in rate at $\Mbheen=40\Msun$.
+At $\Mbheen=10\Msun$, we find that the rate changes by at most a factor of about 3.5 for the stable channel, and at most about a factor of 6.5 for the CE channel. 
+On the other hand, the change in rate at $\Mbheen=40\Msun$ can scale up to a factor of about 110 and 60 for the stable and CE channel respectively. 
+The low mass end of the mass distribution of merging double compact objects will also provide a particularly powerful cosmological constraint in the era of third generation gravitational wave telescopes \citep{MariaEzquiaga2022}.
+Our finding that the low mass end is more robust against variations in \SFRDzZ supports this claim.
 
@@
 Parameter variations that affect shape of \SFRDzZ at low redshift primarily change the normalisation of the mass distribution.
-See also  $\mathcal{R}_{0.2}$, the total BBH merger rate at redshift 0.2, annotated in the legends of Figure \ref{fig: mass dists} ($z=0.2$ is where the observations are best constrained by the data \citealt{GWTC3_popPaper2021}).
-This is visible for variations that impact the width of the cosmic metallicity distribution at $z=0$, $\omega_0$, the mean metallicity of the cosmic metallicity distribution at $z=0$, $\mu_0$, and the skewness of the cosmic metallicity distribution, $\alpha$ (left column of Figure \ref{fig: mass dists}).
+This is the case for variations of the width of the cosmic metallicity distribution at $z=0$ ($\omega_0$), the mean metallicity of the cosmic metallicity distribution at $z=0$ ($\mu_0$), and the skewness of the cosmic metallicity distribution ($\alpha$, left columns of Figures \ref{fig: stable mass dists} and \ref{fig: CE mass dists}).
+To emphasise this point, we annotate the total BBH merger rate at redshift 0.2, $\mathcal{R}_{0.2}$, in the legends of Figures \ref{fig: stable mass dists} and \ref{fig: CE mass dists} (0.2 if the redshift where the observations are best constrained \citealt{GWTC3_popPaper2021}).
+%
 Variations that \textit{increase} the amount of star formation at low metallicity (i.e.
-for a low mean metallicity $\mu_0=0.015$ and a wide metallicity distribution $\omega_0 = 1.4$ ) increase the predicted BBH merger rate.
+for a low mean metallicity $\mu_0=0.007$ and a wide metallicity distribution $\omega_0 = 2.0$ ) increase the predicted BBH merger rate.
 This is consistent with other work that finds merging BBHs form more efficiently at low metallicities \citep[e.g.][]{BelczynskiVink2010, Stevenson+2017,Mapelli2017,Chruslinska2019_effectCO,Broekgaarden+2021b}.
+A more skewed cosmic metallicity distribution pushes the peak of the distribution to higher metallicities and thus forms overall more stars at high metallicity when compared to a symmetric distribution.
+Hence, the local rate of BBH mergers is lower for the skewed distribution ($\alpha = -6$) with respect to the symmetric variation ($\alpha = 0.0$).
+% However, the total rate of BBH mergers is only changed by about a factor of 2.
 
-Although a skewed distribution allows the metallicity distribution to extend to lower values, it simultaniously pushes the expected value of the metallicity distribution to higher values.
-Hence, the local rate of BBH mergers is lower for the skewed distribution ($\alpha = -3.5$) with respect to the more symmetric variation ($\alpha = -0.9$).
-However, the total rate of BBH mergers is only changed by about a factor of 2.
+% Effect of the star formation 
+Changing the overall star-formation history (\SFRDz, bottom right panels of Figures \ref{fig: stable mass dists} and \ref{fig: CE mass dists}) also affects the overall normalisation of the mass distribution, but has a smaller effect than the width and the mean of the cosmic metallicity distribution at $z=0$ ($\omega_0$ and $\mu_0$).
+This underlines the importance of the amount of low-metallicity star formation \citep[e.g.,][]{chruslinska2022_review}, and is furthermore in line with findings from \cite{Tang+2020}.
+As discussed in Section \ref{ss: reasonable var}, we use \cite{Madau+2017} and the solid blue line in Figure \ref{fig: SFR(z)} as an approximate lower and upper bound to the \SFRDz respectively. 
+The model from \cite{Madau+2017} is very similar to our Fiducial model (Figure \ref{fig: SFR(z)}), and the differences between the resulting mass distributions are correspondingly small.
+Our approximation of the upper limit to the allowed \SFRDz leads to an overall increase of the BBH merger rate by a factor of about 3.
 
 % The paramters that affect the redshift evolution change the slope of high mass BHs
-Parameters that change the evolution of the metallicity distribution \dpdZ with redshift, such as $\omega_z$ and $\mu_z$ (top right and centre right panel), primarily affect the slope of the high mass end of the BBH mass distribution.
-By reducing the amount of low-metallicity star formation at high redshifts, formation channels with long delay times are excluded.
-In these simulations, the higher mass systems come from the `stable mass transfer channel' which is characterised by longer delay times \citep[][see also their Figure 6]{vanson+2022}.
-% This is similar to the redshift evolution of the mass distribution as discussed in \cite{vanson+2022} (Figure 6). 
-% The difference between the effect on the low mass end with respect to the high mass end of the mass distribution is largest for these variations.
-
-% Effect of the star formation 
-Lastly, changing the \SFRDz has a relatively small effect. 
-\todo{this is in line with findings from \citep{Tang+2020}.}
-We vary the \SFRDz to match the form described in \cite{Madau+2017} and \cite{Neijssel+2019} respectively.
-Both these variations peak at approximately redshift 2.
-Our fiducial model (that follows the \SFRDz from TNG) peaks at about redshift 2.8.
-The overall normalisation of \cite{Neijssel+2019} is higher than the normalisation of our fiducial model.
-Regardless of these differences, the rate of BBH mergers at $z=0.2$ changes no more than $20\%$, and the shape of the primary mass distribution remains almost constant.
-We understand this small effect as follows: our fiducial metallicity distribution \dpdZ is almost constant up to redshift $\sim3$.
-Hence shifting the location of the peak \SFRDz from 2.8 to 2 has a small effect.
-Furthermore, even though these models have varying peak values for \SFRDz, the integrated total stellar mass formed is similar between the models.
-%\todo{add value here}
+Parameters that change the evolution of the metallicity distribution \dpdZ with redshift, such as the redshift dependence of the with and mean; $\omega_z$ and $\mu_z$ (top right and centre right panels of Figures \ref{fig: stable mass dists} and \ref{fig: CE mass dists}) primarily affect the high mass end of the stable channel.
+We understand this as an effect of the different delay time distributions for both formation channels.
+Namely, $\omega_z$ and $\mu_z$ both influence the amount of low metallicity stellar mass formed at high redshifts, and hence they will mostly affect systems with longer delay times.
+The stable channel has been shown to produce more high mass BHs with longer delay times when compared to the CE channel \citep{vanson+2022, Briel+2022}.
+Hence we find these variations affect the slope of the high mass end of the BBH mass distribution for the stable channel, while they have a relatively small impact on the CE channel.
 
@@
 \paragraph{The model allows for a controlled experiment on the effect of \SFRDzZ on the local distribution of merging BBH}
-As an example, we apply our model to calculate the local rate and mass distribution of the more massive components from merging BBHs (\Mbheen) in Figure \ref{fig: mass dists}. 
-We systematically vary all five parameters that shape the cosmic metallicity distribution, and explore two additional variations of the overall star-formation rate \SFRDz, following \cite{Madau+2017} and \cite{Neijssel+2019} respectively.
-Our main conclusions are as follows:
+As an example, we apply our model to calculate the local rate and mass distribution of the more massive components from merging BBHs (\Mbheen) in Figures \ref{fig: stable mass dists} and \ref{fig: CE mass dists}.
+We systematically vary all five parameters that shape the cosmic metallicity distribution, and explore two additional variations of the overall star-formation history \SFRDz.
+Our main findings are as follows:
 \begin{itemize}
@@
 
-    \item The metallicity distribution of star formation at low redshift, primarily impacts the normalisation of the primary BH mass distribution (i.e. the total rate of BBH mergers at redshift 0.2).
+    \item The metallicity distribution of star formation at low redshift, primarily impacts the normalisation of the BBH merger rate.
+Changing the overall star-formation history, \SFRDz also affects the rate, but to a lesser degree.
+This underlines how low-metallicity star formation at low redshifts dominates the overall normalisation of the BBH merger rate.
 
-    \item Parameters that influence the redshift evolution of the mean and the width of the metallicity distribution, affect the slope of the high mass end of the \Mbheen distribution.
-%Specifically this impacts the for masses above the peak of the \Mbheen distribution which occurs at approximately 18\Msun.
-    \item Changing the overall star-formation history, \SFRDz varies the normalisation of the rate by at most a factor of about 5.
-This is because reasonable variations of the \SFRDz have a similar value for the total local star-formation rate density, which is relatively well constrained by observations.
+    \item Parameters that influence the redshift evolution of the mean and the width of the metallicity distribution, affect the slope of the high mass end of the primary BH mass distribution for the stable channel.
+This reflects the longer delay times of the stable channel with respect to the CE channel.
 
@@
 
-\section{Determining reasonable variations of the \SFRDzZ}
+\section{Determining reasonable variations of the \SFRDzZ \label{app: reasonable var}}
+
+To determine reasonable variations of our fiducial model for \SFRDzZ
+Fig. 2 in \cite{Pakmor+2022} which builds on Fig. 9 from \cite{Chruslinska2019_obs}
 
@@
 \includegraphics[width=\textwidth]{figures/High_Low_metalFractionSFMass.pdf}
-\caption{Fraction of high vs low metallicity stellar mass.
+\caption{Percentage of stellar mass formed at low metallicity ($Z < 0.1 \rm{Z_{\odot}}$) , versus high metallicity ($Z>\rm{Z_{\odot}}$) for all star formation below a certain threshold redshift: $z<0.5$ (left), $z < 3.0$ (middle) and $z<10$ (right).
+Data from observation-based variations are shown with semi-transparent thick crosses,  \citep[][]{Chruslinska2019_obs} and semi-transparent thick plus signs \citep[][]{Chruslinska+2021}, the low- and high-metallicity extremes are indicated with opague symbols.
+For data from cosmological simulations, we follow \cite{Pakmor+2022} and show Illustris \citep[][squares]{Vogelsberger+2014}, Simba \citep[][diamonds]{Dave+2019}, EAGLE \citep[][triangles]{Schaye+2015}, TNG50 and TNG100 \citep[][filled and open circles respectively]{FirstResTNG_Springel2018}.
+Black thin crosses display variations of the cosmic metallicity distribution that is part of our fiducial \SFRDzZ.
+The parameter that is varied with respect to the fiducial and its new value are annotated.
+This shows that our \SFRDzZ variations span the range of reasonable cosmic metallicity distributions as determined by observation-based and cosmological simulations-based models.
 \label{fig: low high Z fraction}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Yield per metallicity and mass \label{app: mass metal yield}}
+% \section{Yield per metallicity and mass \label{app: mass metal yield}}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-The yield of merging BBH with certain masses, per star forming mass per metallicity
+% The yield of merging BBH with certain masses, per star forming mass per metallicity
 

### 2022-08-16 src/scripts/Plot_Mass_distributions.py

@@ -427,7 +427,7 @@ for i in range(2):
                            bootstrap = False, bootstraps = 50, save_name = 'SFRD_skewness_variations.pdf', titletext = "Overall SFR history"+"\n"+ r'$ \mathrm{SFRD(}z\rm{)} \ [a,b,c,d]$', 
                            labels = [r'$\mathrm{Madau \ \& \ Fragos \ 2017: } \phantom{xxxx} \ \mathcal{R}_{0.2}= \ $', 
                                      r'$\mathrm{Fiducial: \ } \phantom{xxxxx-xxxxx-} \ \mathcal{R}_{0.2}= \ $', 
-                                     r'$\mathrm{Approximation \ Max, \ Chruslinska \ et \ al. \ 2021:}  \ \mathcal{R}_{0.2} = \ $'],
+                                     r'$\mathrm{Approx. \ to \ upper \ limit:}  \ \mathcal{R}_{0.2} = \ $'],
                             multipanel = True, subplot = subplot6)
 
 

### 2022-08-16 src/scripts/SFR_z.py

@@ -62,6 +62,7 @@ def powerlaw_fit_Chruslinska21(z_bounds= [0,1.0,1.8,4.0,7.0,8.8, 10.0],
     return redshifts, SFRD # Msun /yr /Mpc^3    
 
 
+
 ########################################################
 # plot different SFRs
 ########################################################
@@ -108,13 +109,13 @@ def plot_SFR(sf_a = 0.017, sf_b = 1.481, sf_c = 4.452,  sf_d = 5.913, show_legen
     #Resembling thick brown line in Fig. 11 Chruslinska + 2021
     a_max, b_max, c_max, d_max = 0.025,2.6,3.3,5.9 #2.5,2.9,4.5 
     ax.plot(x1, Z_SFRD.Madau_Dickinson2014(redshift_list, a=a_max, b=b_max, c=c_max, d=d_max), 
-             label = 'Approximation \ to \ upper \ limit: \n $a=%.2f, b=%.2f, c=%.2f, d=%.2f$'% (a_max, b_max, c_max, d_max)
+             label = 'Approx. \ to \ upper \ limit: \n $a=%.2f, b=%.2f, c=%.2f, d=%.2f$'% (a_max, b_max, c_max, d_max)
              , c = '#356288', lw=5, ls = '-')
 
     # BEST FIT
     try:
         y_vals = Z_SFRD.Madau_Dickinson2014(redshift_list, a=sf_a, b=sf_b, c=sf_c,  d=sf_d)
-        ax.plot(x1, y_vals,label = 'Using best fit parameters \n $a=%.2f, b=%.2f, c=%.2f, d=%.2f$'% (sf_a,sf_b,sf_c, sf_d), 
+        ax.plot(x1, y_vals,label = 'Using best fit parameters \ (fiducial) \n $a=%.2f, b=%.2f, c=%.2f, d=%.2f$'% (sf_a,sf_b,sf_c, sf_d), 
                  c = '#fe1100', lw=5, ls = '--', zorder =10)
         print('max value', y_vals[np.argmax(y_vals)], ' at x_max = ', x1[np.argmax(y_vals)])
     except:
@@ -233,4 +234,3 @@ plot_SFR(sf_a = 0.017, sf_b = 1.481, sf_c = 4.452,  sf_d = 5.913,show_legend = T
 # redshift axis
 plot_SFR(sf_a = 0.017, sf_b = 1.481, sf_c = 4.452,  sf_d = 5.913,show_legend = False,
[…]

### 2022-08-17 src/tex/ms.tex
some final changes to text

@@
 \newcommand{\Gyr}{\ensuremath{\,\rm{Gyr}}\xspace}
-\newcommand{\Mpc}{\ensuremath{\,\rm{Gpc}}\xspace}
+\newcommand{\Mpc}{\ensuremath{\,\rm{Mpc}}\xspace}
 \newcommand{\Gpc}{\ensuremath{\,\rm{Gpc}}\xspace}
@@
 % \title{ A flexible expression for the metallicity-dependent cosmic star formation rate: }
-\title{The location of features in the mass distribution of merging binary black holes does not depend on the metallicity-dependent cosmic star formation rate}
+\title{The location of features in the mass distribution of merging binary black holes does not depend on the metallicity-dependent cosmic star formation.}
 
@@
 
+%%%%%%%%%%%%%%%
 \author[0000-0001-5484-4987]{L.~A.~C.~van~Son}
@@
 \affiliation{Max Planck Institute for Astrophysics, Karl-Schwarzschild-Str. 1, 85748 Garching, Germany}
-
- \author[0000-0001-9336-2825]{S. E. de Mink}
- \affiliation{Max Planck Institute for Astrophysics, Karl-Schwarzschild-Str. 1, 85748 Garching, Germany}
-\affiliation{Anton Pannekoek Institute of Astronomy and GRAPPA, Science Park 904, University of Amsterdam, 1098XH Amsterdam, The Netherlands}
-\affiliation{Center for Astrophysics $|$ Harvard $\&$ Smithsonian, 60 Garden St., Cambridge, MA 02138, USA}
-% %%%%%
-
-\author[0000-0002-8901-6994]{M. Chru{\'s}li{\'n}ska}
-\affiliation{Max Planck Institute for Astrophysics, Karl-Schwarzschild-Str. 1, 85748 Garching, Germany}
-
-\author[0000-0002-8901-6994]{L. Hernquist}
-
- \author[0000-0003-3308-2420]{R. Pakmor}
- \affiliation{Max Planck Institute for Astrophysics, Karl-Schwarzschild-Str. 1, 85748 Garching, Germany}
+\author[0000-0001-5484-4987]{et. al}
+% %%%%%%%%%%%%%%%
+% \author[0000-0001-9336-2825]{S. E. de Mink}
+% \affiliation{Max Planck Institute for Astrophysics, Karl-Schwarzschild-Str. 1, 85748 Garching, Germany}
+% \affiliation{Anton Pannekoek Institute of Astronomy and GRAPPA, Science Park 904, University of Amsterdam, 1098XH Amsterdam, The Netherlands}
+% \affiliation{Center for Astrophysics $|$ Harvard $\&$ Smithsonian, 60 Garden St., Cambridge, MA 02138, USA}
+% %%%%%%%%%%%%%%%
+% \author[0000-0002-8901-6994]{M. Chru{\'s}li{\'n}ska}
+% \affiliation{Max Planck Institute for Astrophysics, Karl-Schwarzschild-Str. 1, 85748 Garching, Germany}
+% %%%%%%%%%%%%%%%
+% \author[0000-0002-8901-6994]{L. Hernquist}
+% \affiliation{Center for Astrophysics $|$ Harvard $\&$ Smithsonian,
+% 60 Garden St., Cambridge, MA 02138, USA}
+% %%%%%%%%%%%%%%%
+% \author[0000-0003-3308-2420]{R. Pakmor}
+% \affiliation{Max Planck Institute for Astrophysics, Karl-Schwarzschild-Str. 1, 85748 Garching, Germany}
+%%%%%%%%%%%%%%%
 
@@
 Nonetheless, several methods exist to estimate the metallicity dependent star-formation rate.
+
 The first method combines a galaxy mass-metallicity relation, MZ-relation and a galaxy stellar mass function, GSMF \citep[see e.g.][]{Dominik+2013}.
+However, the applied methods to infer galaxy properties and subsequently scaling relations such as the MZ-relation differ greatly, which makes it difficult to interpret these results in a consistent way \citep[e.g.,][]{KewleyEllison2008,MaiolinoMannucci2019,Cresci+2019}.
+Moreover, observations are generally incomplete at high redshifts and low galaxy luminosity \citep[e.g.,][]{Chruslinska+2021}.
+
 % \citep[see e.g.][]{Chruslinska+2018, Chruslinska2019_effectCO, Broekgaarden+2021a}.
-On can also directly extract the metallicity density fraction from cosmological simulations \citep[e.g.][]{Mapelli2017, Briel+2021}.
-Alternatively, one can combine an observed star formation rate, \SFRDz, like from \cite{MadauDickinson2014} or \cite{Madau+2017}, and convolve this with an assumed function for the shape of the shape of the metallicity density distribution, such as was was done in \cite{LangerNorman, Neijssel+2019}.
+One can also directly extract the metallicity density fraction from cosmological simulations \citep[e.g.][]{Mapelli2017, Briel+2021}.
+However, these simulations currently lack the resolution to resolve the lowest mass galaxies, and their variations in \SFRDzZ span a smaller range than those observed in observationally-based models \citep{Pakmor+2022}.
+
+Alternatively, one can combine analytical models for the observed star formation rate, \SFRDz, like those from \cite{MadauDickinson2014} or \cite{Madau+2017}, and convolve this with an assumed function for the shape of the shape of the metallicity density distribution, such as was was done in e.g., \cite{LangerNorman, Neijssel+2019}.
 
@@
 In this work we follow the latter approach and propose a flexible analytical model for the \SFRDzZ that can be fit to the output of both cosmological simulations, and observational data constraints where available.
-In contrast to earlier work  \citep{LangerNorman, Neijssel+2019}, we adopt a skewed-lognormal distribution of metallicities that can capture the asymmetry in the low and high metallicity tails.
-%to capture the tail of low metallicity star formation at low redshift.
-% The novelty of this model lies in a skewed-lognormal distribution of metallicities, that captures the tail of low metallicity star formation at low redshift.
+In contrast to earlier work, we adopt a skewed-lognormal distribution of metallicities that can capture the asymmetry in the low and high metallicity tails. %\citep{LangerNorman, Neijssel+2019}
 
@@
 First of all, the form we propose allows for an intuitive interpretation of the free parameters.
-This allows us to get better insight of the impact of changes in these parameters on the inferred ranges of astrophysical transients (as we demonstrate in this work using GW predictions as an example).
-By adopting an analytical, parametrized form for \SFRDzZ, the large uncertainties in \SFRDzZ can be systematically explored.
-Secondly, we hope that this form will facilitate a more sensible way for useful inference on large (future) datasets of astrophysical transients, such as the ever growing catalogue of gravitational wave transients.
+This allows us to get better insight of the impact of changes in these parameters on the inferred ranges of astrophysical transients (as we demonstrate in Section \ref{sec: mass dists} using GW predictions as an example).
+By adopting an analytical, parametrized form for \SFRDzZ, the large uncertainties can be systematically explored.
+%
+Secondly, both the large complications in observational constraints, and the many uncertainties in cosmological simulations call for a generalised form of the \SFRDzZ that can be easily updated when new information becomes available.
+% which is the motivation for this work.
+In particular, the advent of observations with the James Webb Space Telescope promises a new era of high-redshift
+metallicity studies of previously unexplored regimes \citep[e.g.,][]{Sanders+2022}. We hope that this form will facilitate the flexibility needed to keep up with observations. 
+% we hope that this form will facilitate a more sensible way for useful inference on large (future) datasets of astrophysical transients, such as the ever growing catalogue of gravitational wave transients.
 Our hope is that the constraints on the free parameters in the analytical form we propose, can provide a more useful guidance when comparing with the outcome of the predictions of cosmological simulations.
+
 % is to allow for an intuitive interpretation of the effects of the \SFRDzZ on the inferred rates of astrophysical transients.
@@
 We describe our model for \SFRDzZ in Section \ref{sec: model for sfrd(zZ)}.
-We fit our model to to the star-forming gas in the Illustris TNG100 simulation in Section \ref{sec: mass dists} we demonstrate an example application of our model by systematically varying the parameters that determine the shape of \SFRDzZ and investigate their impact on the local distribution of merging BBH masses.
+We fit our model to to the star-forming gas in the Illustris TNG100 simulation in Section \ref{sec: fit against tng} we demonstrate an example application of our model by systematically varying the parameters that determine the shape of \SFRDzZ and investigate their impact on the local distribution of merging BBH masses in Section \ref{sec: mass dists}.
 We summarise our findings in Section \ref{sec: summary}.
+
+Throughout this work, we adopt a Kroupa initial mass function \citep{Kroupa2001} and a flat $\Lambda$CDM cosmology with $\Omega_{\rm{M}}=0.31$, $\Omega_{\rm{\Lambda}}=0.69$ and $H_0=67.7\rm{km\,s^{-1}\,Mpc^{-1}}$ \citep{Planck18_VI}.
 
@@
 \subsection{The metallicity probability density function}
-For the probability distribution of metallicities we draw inspiration from the approach by \citep[e.g.\ ][]{Neijssel+2019} who used a log-normal distribution.
-Unfortunately, this expression does not capture the asymmetry well that we see in the results of the cosmological simulations, which show an extended tail in  $\log_{10} Z$ towards low metallicity combined with a very limited tail towards higher metallicity.
+For the probability distribution of metallicities we draw inspiration from the approach by e.g., \cite{Neijssel+2019} who used a log-normal distribution.
+Unfortunately, this expression does not capture the asymmetry well that we see in the results of the cosmological simulations, which show an extended tail in  $\log_{10} Z$ towards low metallicity, combined with a very limited tail towards higher metallicity.
 To capture this behaviour we adopt a skewed-log-normal distribution instead.
@@
 We fit our new functional form of \SFRDzZ as defined by equations \ref{eq: total sfrd}, \ref{eq: z log skew} and \ref{eq: sfr1} to the Illustris-TNG cosmological simulations. 
-We fit for the following nine free parameters $\alpha, \mu_0, \mu_z, \omega_0, \omega_z$, which govern the metallicity dependence and $a,b, c$ and $d$, which set the overall star formation rate.
+We simultaneously fit for the following nine free parameters $\alpha, \mu_0, \mu_z, \omega_0, \omega_z$, which govern the metallicity dependence and $a,b, c$ and $d$, which set the overall star formation rate.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Both the large observational uncertainties in \SFRDzZ (as discussed in section \ref{sec: intro}), and the many uncertainties in cosmological simulations (as discussed below) call for a generalised form of the \SFRDzZ that can be easily updated when new information becomes available, which is the motivation for this work.
+% Both the large observational uncertainties in \SFRDzZ (as discussed in section \ref{sec: intro}), and the many uncertainties in cosmological simulations (as discussed below) call for a generalised form of the \SFRDzZ that can be easily updated when new information becomes available, which is the motivation for this work.
+% In particular, the advent of observations with the James Webb Space Telescope promises a new era of high-redshift% metallicity studies in previously unexplored regimes \citep[e.g.,][]{Sanders+2022}.
+%
 Although here, we only fit our model to the TNG100 simulation, our prescription can be easily be used to fit other simulated or observational data of the metallicity dependent star formation rate density\footnote{We provide a Jupyter notebook to facilitate this fit here: \url{https://github.com/LiekeVanSon/SFRD_fit/blob/main/src/scripts/Fit_To_Cosmological_Simulation.ipynb} }.
@@
 For this we use a binned version of the TNG data $\SFRDzZ_{\rm sim}$.
-We consider metallicities between $Z= -5$ to $\log_{10} Z= 0$ in 30 bins, where we use $Z_i$ to refer to the logarithmic centres of the bins.
+We consider metallicities between $\log_{10} Z= -5$ to $\log_{10} Z= 0$ in 30 bins, where we use $Z_i$ to refer to the logarithmic centres of the bins.
 We ignore star formation in metallicities $\log_{10} Z \le -5$ as this accounts for less than 1\% of the total cosmic star formation rate in these simulations.
@@
 
-In Figure \ref{fig: fit SFRD} we show our fiducial  model at different redshifts and metallicities. For clarity, we also show the overall rate of star formation \SFRDz in Figure \ref{fig: SFR(z)}.
+In Figure \ref{fig: fit SFRD} we show our fiducial  model at different redshifts and metallicities. We also show the overall rate of star formation \SFRDz in Figure \ref{fig: SFR(z)}.
 In general, our analytical model captures the metallicity dependent star formation in the TNG100 simulations well (bottom panels of Figure \ref{fig: fit SFRD}). 
@@
 To emphasise the difference between a skewed-lognormal and a symmetric lognormal distribution, we show the phenomenological model from \cite{Neijssel+2019} in dotted grey.
-Their model falls within the family of functions that is encompassed by our model described in Section \ref{sec: model for sfrd(zZ)}, but we note that their model is distinctly different.
-\footnote{The phenomenological model from \cite{Neijssel+2019} is recovered by adopting $\mu_0= 0.035$, $\mu_z=-0.23$, $\omega_0=0.39 $, $\omega_z = 0$, $\alpha = 0$, $a=0.01$, $b=2.77$, $c=2.9$ and $d=4.7$.
+Their model falls within the family of functions that is encompassed by our model described in Section \ref{sec: model for sfrd(zZ)}, but we note that their model is very distinctly different.\footnote{The phenomenological model from \cite{Neijssel+2019} is recovered by adopting $\mu_0= 0.035$, $\mu_z=-0.23$, $\omega_0=0.39 $, $\omega_z = 0$, $\alpha = 0$, $a=0.01$, $b=2.77$, $c=2.9$ and $d=4.7$.
 }
@@
 To approximate these models, we fit equation \ref{eq: sfr1} by eye to the broken power law description for the  \texttt{SB: B18/C17} model variations as presented in appendix B1 from \cite{Chruslinska+2021}.
-We show all \SFRDz variations in Figure \ref{fig: SFR(z)}. \\
+We show all \SFRDz variations in Figure~\ref{fig: SFR(z)}. \\
 %30*f14SBBiC
@@
 \caption{The primary mass distribution of merging BBH systems from the stable mass transfer channel for several variations in \SFRDzZ. 
-The first five panels show variations of the cosmic metallicity distribution  \dpdZ (eq.
-\ref{eq: z log skew}, parameters listed in the first three columns of Table \ref{tab: fit params}).
+The first five panels show variations of the cosmic metallicity distribution  \dpdZ, eq.
+\ref{eq: z log skew}, (parameters listed in the first three columns of Table \ref{tab: fit params}).
 The bottom right panel shows variations in the magnitude of the star formation rate with redshift, i.e.
@@
 All panels are shown at a reference redshift of $z=0.2$, with the corresponding predicted BBH merger rate annotated in the legend.
-We show the power-law + peak model from \protect\cite{GWTC3_popPaper2021} in grey.
-Lastly we annotate the relative change in the rate at three reference masses: $10\Msun$, $25\Msun$ and $40\Msun$.
-Variations in \SFRDzZ have the largest impact on the high mass end of the distribution, while around $\Mbheen=10$, variations are smaller than a factor of 3.
+For reference, we show the power-law + peak model from \protect\cite{GWTC3_popPaper2021} in grey.
+We annotate the relative change in the rate at three reference masses: $10\Msun$, $25\Msun$ and $40\Msun$.
   \label{fig: stable mass dists}}
@@
 \caption{Same as Figure \ref{fig: stable mass dists}, but for the Common envelope channel.
+These Figures show that the low mass end of the primary mass distribution is least affected by the adopted \SFRDzZ.
+Moreover, the \textit{location} of features in the mass distribution are robust against all explored variations.
    \label{fig: CE mass dists}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-To isolate the effect of the \SFRDzZ from the effects of mixing different formation channels, we split the data from \cite{vanson+2022} between the stable mass transfer channel \citep[e.g.,][]{van-den-Heuvel+2017,Inayoshi2017,Bavera2021,Marchant2021,GallegosGarcia2021,vanson+2022}, and the `classical' common-envelope channel \citep[or CE channel, e.g.,\  ][]{Belczynski+2007,PostnovYungelson2014,Belczynski+2016Natur,vignaGomez+2018}.
-These channels are distinguished based on whether the binary experiences common envelope evolution (CE channel) or only stable mass transfer (stable channel in short from now on).
+To isolate the effect of the \SFRDzZ from the effects of different formation channels, we split the data from \cite{vanson+2022} between the stable mass transfer channel \citep[e.g.,][]{van-den-Heuvel+2017,Inayoshi2017,Bavera2021,Marchant2021,GallegosGarcia2021,vanson+2022}, and the `classical' common-envelope channel \citep[or CE channel, e.g.,\  ][]{Belczynski+2007,PostnovYungelson2014,Belczynski+2016Natur,vignaGomez+2018}.
+These channels are distinguished based on whether the binary system has experienced a common envelope phase (CE channel) or only stable mass transfer (stable channel in short from now on).
 
@@
 The first thing we note is that the location of the features in the primary mass distribution are robust against variations in the \SFRDzZ.
-For the CE channel, the global peak of the mass distribution remains at approximately $\Mbheen=16\Msun$ for all variations.
+For the CE channel, the global peak of the mass distribution remains at approximately $\Mbheen\approx16\Msun$ for all variations.
 Similarly, the stable channel displays two peaks that are visible in all variations: a peak at $\Mbheen\approx9\Msun$ and a peak at $\Mbheen\approx22\Msun$. 
@@
 At $\Mbheen=10\Msun$, we find that the rate changes by at most a factor of about 3.5 for the stable channel, and at most about a factor of 6.5 for the CE channel. 
-On the other hand, the change in rate at $\Mbheen=40\Msun$ can scale up to a factor of about 110 and 60 for the stable and CE channel respectively. 
+On the other hand, the change in rate at $\Mbheen=40\Msun$ can be as high as a factor of about 110 and 60 for the stable and CE channel respectively. 
 The low mass end of the mass distribution of merging double compact objects will also provide a particularly powerful cosmological constraint in the era of third generation gravitational wave telescopes \citep{MariaEzquiaga2022}.
@@
 We understand this as an effect of the different delay time distributions for both formation channels.
-Namely, $\omega_z$ and $\mu_z$ both influence the amount of low metallicity stellar mass formed at high redshifts, and hence they will mostly affect systems with longer delay times.
+Since both, $\omega_z$ and $\mu_z$ influence the amount of low metallicity stellar mass formed at high redshifts they will mostly affect systems with longer delay times.
 The stable channel has been shown to produce more high mass BHs with longer delay times when compared to the CE channel \citep{vanson+2022, Briel+2022}.
@@
 \section{Determining reasonable variations of the \SFRDzZ \label{app: reasonable var}}
-
-To determine reasonable variations of our fiducial model for \SFRDzZ
-Fig. 2 in \cite{Pakmor+2022} which builds on Fig. 9 from \cite{Chruslinska2019_obs}
+To determine reasonable variations of our fiducial model for \SFRDzZ, we compute the fraction of low and high metallicity stellar mass formed for redshifts below $z<0.5$, $z < 3.0$ and $z<10$.
+We show the results in Figure \ref{fig: low high Z fraction}, which is an adaptation of Fig.
+2 in \cite{Pakmor+2022}, which in turn builds on Fig.
+9 from \cite{Chruslinska2019_obs}.
 

### 2022-08-17 src/scripts/SFR_z.py

@@ -79,7 +79,9 @@ def plot_SFR(sf_a = 0.017, sf_b = 1.481, sf_c = 4.452,  sf_d = 5.913, show_legen
         x1 = cosmo.lookback_time(redshift_list)
 
 #     #default M&D 14
-#     ax.plot(x1, Z_SFRD.Madau_Dickinson2014(redshift_list), 
+#     # Because MD14 was computed using a salpeter IMF, you need to correct the SFRD!
+#     salpeter_to_kroupa = (1./1.55) 
+#     ax.plot(x1, salpeter_to_kroupa*Z_SFRD.Madau_Dickinson2014(redshift_list), 
 #              label = 'Madau $\&$ Dickinson 2014\n $a=%.3f, b=%.2f, c=%.2f, d=%.2f$'% (0.015,2.7,2.9,5.6)
 #              , c = 'royalblue', ls = '--',lw=2)
 

### 2022-09-01 src/tex/ms.tex
comments verwerkt

@@
 % Title
-% \title{ A flexible and intuitive analytic expression for the metallicity-dependent cosmic star formation rate  }
-% \title{ A flexible expression for the metallicity-dependent cosmic star formation rate: }
-\title{The location of features in the mass distribution of merging binary black holes does not depend on the metallicity-dependent cosmic star formation.}
+% \title{ A flexible and intuitive analytic expression for the metallicity-dependent cosmic star formation history  }
+% \title{ A flexible expression for the metallicity-dependent cosmic star formation history: }
+\title{The location of features in the mass distribution of merging binary black holes does not depend on the metallicity-dependent cosmic star formation history.}
 
@@
 60 Garden St., Cambridge, MA 02138, USA}
-\affiliation{Anton Pannekoek Institute of Astronomy and GRAPPA, Science Park 904, University of Amsterdam, 1098XH Amsterdam, The Netherlands}
+\affiliation{Anton Pannekoek Institute of Astronomy, Science Park 904, University of Amsterdam, 1098XH Amsterdam, The Netherlands}
 \affiliation{Max Planck Institute for Astrophysics, Karl-Schwarzschild-Str. 1, 85748 Garching, Germany}
-\author[0000-0001-5484-4987]{et. al}
-% %%%%%%%%%%%%%%%
-% \author[0000-0001-9336-2825]{S. E. de Mink}
-% \affiliation{Max Planck Institute for Astrophysics, Karl-Schwarzschild-Str. 1, 85748 Garching, Germany}
-% \affiliation{Anton Pannekoek Institute of Astronomy and GRAPPA, Science Park 904, University of Amsterdam, 1098XH Amsterdam, The Netherlands}
-% \affiliation{Center for Astrophysics $|$ Harvard $\&$ Smithsonian, 60 Garden St., Cambridge, MA 02138, USA}
-% %%%%%%%%%%%%%%%
-% \author[0000-0002-8901-6994]{M. Chru{\'s}li{\'n}ska}
-% \affiliation{Max Planck Institute for Astrophysics, Karl-Schwarzschild-Str. 1, 85748 Garching, Germany}
-% %%%%%%%%%%%%%%%
-% \author[0000-0002-8901-6994]{L. Hernquist}
-% \affiliation{Center for Astrophysics $|$ Harvard $\&$ Smithsonian,
-% 60 Garden St., Cambridge, MA 02138, USA}
-% %%%%%%%%%%%%%%%
-% \author[0000-0003-3308-2420]{R. Pakmor}
-% \affiliation{Max Planck Institute for Astrophysics, Karl-Schwarzschild-Str. 1, 85748 Garching, Germany}
 %%%%%%%%%%%%%%%
+\author[0000-0001-9336-2825]{S. E. de Mink}
+\affiliation{Max Planck Institute for Astrophysics, Karl-Schwarzschild-Str. 1, 85748 Garching, Germany}
+\affiliation{Anton Pannekoek Institute of Astronomy, Science Park 904, University of Amsterdam, 1098XH Amsterdam, The Netherlands}
+\affiliation{Center for Astrophysics $|$ Harvard $\&$ Smithsonian, 60 Garden St., Cambridge, MA 02138, USA}
+%%%%%%%%%%%%%%%
+\author[0000-0002-8901-6994]{M. Chru{\'s}li{\'n}ska}
+\affiliation{Max Planck Institute for Astrophysics, Karl-Schwarzschild-Str. 1, 85748 Garching, Germany}
+%%%%%%%%%%%%%%%
+\author[0000-0002-8901-6994]{L. Hernquist}
+\affiliation{Center for Astrophysics $|$ Harvard $\&$ Smithsonian,
+60 Garden St., Cambridge, MA 02138, USA}
+%%%%%%%%%%%%%%%
+\author[0000-0003-3308-2420]{R. Pakmor}
+\affiliation{Max Planck Institute for Astrophysics, Karl-Schwarzschild-Str. 1, 85748 Garching, Germany}
+%%%%%%%%%%%%%%
 
@@
 New observational facilities are probing astrophysical transients such as stellar explosions and gravitational wave (GW) sources at ever increasing redshifts.
-To interpret these observation we need to compare them to predictions from stellar population models.
-These models, require the metallicity-dependent star formation rate density (\SFRDzZ) as an input.
+To interpret these observations we need to compare them to predictions from stellar population models.
+Such models require the metallicity-dependent cosmic star formation history (\SFRDzZ) as an input.
 Large uncertainties remain in the shape and evolution of this function, and understanding its behaviour is essential to explain simulation results.
@@
 %Our hope is that this expression provides a useful starting point for making predictions and comparison with observations.
-We fit our analytical function to the star-forming gas of the cosmological TNG100 simulations and find that it is able to capture the main behaviour well. 
+We fit our analytical function to the star-forming gas of the cosmological TNG100 simulation and find that it is able to capture the main behaviour well. 
 %
 As an example application, we investigate the effect of systematic variations in the \SFRDzZ parameters on the predicted mass distribution of locally merging binary black holes (BBH).
-Our main findings are I) the location of features is remarkably robust against variations in the metallicity-dependent star formation rate and II) the low mass end is least affected by these variations.
+Our main findings are: I) the location of features is remarkably robust against variations in the metallicity-dependent cosmic star formation history, and II) the low mass end is least affected by these variations.
 This is promising as it increases our chances to constrain the physics that governs the formation of these objects.
-We further find that III) the skewness, mean, and width of the metallicity distribution at low redshift affect the overall rate, while IV) the redshift evolution of the width and the mean of the metallicity distribution affects the slope at the high-mass end of the distribution.
-% IV) the shape of the overall star-formation rate has a small impact on the local mass distribution.
+% We further find that: III) the skewness, mean, and width of the metallicity distribution at low redshift affect the overall rate, while IV) the redshift evolution of the width and the mean of the metallicity distribution affects the slope at the high-mass end of the distribution.
+% IV) the shape of the overall star-formation rate density has a small impact on the local mass distribution.
 \end{abstract}
@@
 Exotic transient phenomena, including (pulsational) pair-instability supernovae, long gamma-ray bursts and gravitational wave (GW) events appear to be especially sensitive to the metallicity at which star formation occurs at different epochs throughout the Universe \citep[e.g.,][]{Langer+2007,Fruchter+2006,LIGO2016_implications}.
-Gravitational astronomy in particular has seen explosive growth in the number of detections in the past decade \citep[][]{GWTC1,GWTC2,GWTC3}.
-In order to correctly model and interpret these observations, it is fundamental to know the rate of star formation at different metallicities throughout cosmic history, i.e.
-the metallicity-dependent star formation rate density  \citep[\SFRDzZ, see also the recent review by][]{chruslinska2022_review}.
-Throughout this work little $z$ refers to the redshift and $Z$ the metallicity of star formation.
+Gravitational astronomy in particular has seen explosive growth in the number of detections in the past decade \citep[][]{GWTC1,GWTC2,GWTC3}, while theoretical predictions vary greatly due to uncertainties in the aforementioned metallicity of star formation \citep[e.g.,][]{Santoliquido+2021,Broekgaarden+2021b}.
+In order to correctly model and interpret these observations, it is thus fundamental to know the rate of star formation at different metallicities throughout cosmic history; i.e.
+the metallicity-dependent cosmic star formation history \citep[\SFRDzZ, see also the recent review by][]{chruslinska2022_review}.
+Throughout this work little $z$ refers to the redshift and $Z$ to the metallicity of star formation.
 
-It is difficult to observationally constrain the shape of \SFRDzZ, see \cite{Chruslinska2019_obs} for an extensive overview and discussion of relevant observational caveats.
+It is difficult to observationally constrain the shape of \SFRDzZ\ -- \citep[see e.g., ][for discussion of relevant observational caveats]{Chruslinska2019_obs,Boco+2021}.
 Even at low redshifts, the low metallicity part of the distribution is poorly constrained \citep{Chruslinska+2021}.
-Nonetheless, several methods exist to estimate the metallicity dependent star-formation rate.
+Nonetheless, several methods exist to estimate the metallicity-dependent cosmic star formation history.
 
-The first method combines a galaxy mass-metallicity relation, MZ-relation and a galaxy stellar mass function, GSMF \citep[see e.g.][]{Dominik+2013}.
+% combines a  with an approximation of the metallicity distribution that
+The first method is based on empirical scaling relations, linking galaxy properties like stellar mass $M_{\star}$, metallicity $Z$, and overall star-formation rate density \SFRDz, with the GSMF galaxy stellar mass function, GSMF \citep[see e.g.][]{Dominik+2013}.
 However, the applied methods to infer galaxy properties and subsequently scaling relations such as the MZ-relation differ greatly, which makes it difficult to interpret these results in a consistent way \citep[e.g.,][]{KewleyEllison2008,MaiolinoMannucci2019,Cresci+2019}.
@@
 % \citep[see e.g.][]{Chruslinska+2018, Chruslinska2019_effectCO, Broekgaarden+2021a}.
-One can also directly extract the metallicity density fraction from cosmological simulations \citep[e.g.][]{Mapelli2017, Briel+2021}.
+One can also directly extract the metallicity-dependent cosmic star formation history from cosmological simulations \citep[e.g.][]{Mapelli2017, Briel+2022_rates}.
 However, these simulations currently lack the resolution to resolve the lowest mass galaxies, and their variations in \SFRDzZ span a smaller range than those observed in observationally-based models \citep{Pakmor+2022}.
 
-Alternatively, one can combine analytical models for the observed star formation rate, \SFRDz, like those from \cite{MadauDickinson2014} or \cite{Madau+2017}, and convolve this with an assumed function for the shape of the shape of the metallicity density distribution, such as was was done in e.g., \cite{LangerNorman, Neijssel+2019}.
+Alternatively, one can combine analytical models for the observed overall star-formation rate density, \SFRDz, like those from \cite{MadauDickinson2014} or \cite{Madau+2017}, and convolve this with an assumed function for the shape of the cosmic metallicity density distribution, such as was was done in e.g., \cite{LangerNorman2006} and the phenomenological model in \cite{Neijssel+2019}.
 
 %Arguments: cosmological simulations work at high z,  but are they real? observations 
-In this work we follow the latter approach and propose a flexible analytical model for the \SFRDzZ that can be fit to the output of both cosmological simulations, and observational data constraints where available.
-In contrast to earlier work, we adopt a skewed-lognormal distribution of metallicities that can capture the asymmetry in the low and high metallicity tails. %\citep{LangerNorman, Neijssel+2019}
+In this work we follow the latter approach and propose a flexible analytical model for \SFRDzZ that can be fit to the output of both cosmological simulations, and observational data constraints where available.
+In contrast to earlier work, we adopt a skewed-lognormal distribution of metallicities that can capture the asymmetry in the low and high metallicity tails.
 
@@
 %
-Secondly, both the large complications in observational constraints, and the many uncertainties in cosmological simulations call for a generalised form of the \SFRDzZ that can be easily updated when new information becomes available.
+Secondly, both the large complications in observational constraints, and the many uncertainties in cosmological simulations call for a generalised form of \SFRDzZ that can be easily updated when new information becomes available.
 % which is the motivation for this work.
@@
 We describe our model for \SFRDzZ in Section \ref{sec: model for sfrd(zZ)}.
-We fit our model to to the star-forming gas in the Illustris TNG100 simulation in Section \ref{sec: fit against tng} we demonstrate an example application of our model by systematically varying the parameters that determine the shape of \SFRDzZ and investigate their impact on the local distribution of merging BBH masses in Section \ref{sec: mass dists}.
+We fit our model to the star-forming gas in the Illustris TNG100 simulation in Section \ref{sec: fit against tng}, and demonstrate an example application of our model by systematically varying the parameters that determine the shape of \SFRDzZ and investigate their impact on the local distribution of merging BBH masses in Section \ref{sec: mass dists}.
 We summarise our findings in Section \ref{sec: summary}.
 
-Throughout this work, we adopt a Kroupa initial mass function \citep{Kroupa2001} and a flat $\Lambda$CDM cosmology with $\Omega_{\rm{M}}=0.31$, $\Omega_{\rm{\Lambda}}=0.69$ and $H_0=67.7\rm{km\,s^{-1}\,Mpc^{-1}}$ \citep{Planck18_VI}.
+Throughout this work, we adopt a universal Kroupa initial mass function \citep{Kroupa2001} with the mass
+limits $0.01–200\Msun$ and a flat $\Lambda$CDM cosmology with $\Omega_{\rm{M}}=0.31$, $\Omega_{\rm{\Lambda}}=0.69$ and $H_0=67.7\rm{km\,s^{-1}\,Mpc^{-1}}$ \citep{Planck18_VI}.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{A convenient analytic expression for the metallicity-dependent star formation rate density \label{sec: model for sfrd(zZ)} }
+\section{A convenient analytic expression for the metallicity-dependent cosmic star formation history \label{sec: model for sfrd(zZ)} }
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-We assume that the metallicity dependent star formation rate density can be separated into two independent functions \citep[e.g.\ ][]{Langer2006},
+We assume that the metallicity-dependent cosmic star formation history can be separated into two independent functions 
+(as was assumed in e.g., \citealt{LangerNorman2006}, but cf. \citealt{chruslinska2022_review} for a discussion on the validity on this assumption).
 
@@
 The first term is the star formation rate density, \SFRDz, that is the amount of mass formed in stars per unit time and per unit comoving volume at each redshift, $z$.
-The second term, \dpdZ, is a probability density function that expresses what fraction of star formation occurs at which metallicity, $Z$, at each redshift.
+The second term, \dpdZ, is a probability density distribution that expresses what fraction of star formation occurs at which metallicity, $Z$, at each redshift.
 
@@
 % $a=0.02$, $b=1.48$, $c=4.45$ and $d=5.9$ as best fitting parameters,
-\subsection{The metallicity probability density function}
-For the probability distribution of metallicities we draw inspiration from the approach by e.g., \cite{Neijssel+2019} who used a log-normal distribution.
+\subsection{The cosmic metallicity density distribution}
+For the probability distribution of metallicities we draw inspiration from the approach by e.g., \cite{Neijssel+2019} who used a log-normal distribution for their phenomenological model.
 Unfortunately, this expression does not capture the asymmetry well that we see in the results of the cosmological simulations, which show an extended tail in  $\log_{10} Z$ towards low metallicity, combined with a very limited tail towards higher metallicity.
@@
             \right\} 
-    \right] \\
+    \right] . \\
     \end{array}
@@
 \end{equation}
+(For a more extended derivation of the moments of the skewed-log-normal, see e.g., \cite{WANG201995}.)
 
-For a more extended derivation of the moments of the skewed-log-normal, see e.g., \cite{WANG201995}.
-
-\noindent For the evolution of the mean metallicity with redshift we follow \cite{Langer2006} and \cite{Neijssel+2019} in assuming that the mean of the probability density function of metallicities evolves with redshift as:
+For the evolution of the mean metallicity with redshift we follow \cite{LangerNorman2006} and the phenomenological model from \cite{Neijssel+2019} in assuming that the mean of the probability density function of metallicities evolves with redshift as:
 \begin{equation}
@@
 
-Note that the width, $w(z)$ is not the same as the variance. The variance, $\sigma(z)^2$, can be expressed as
+Note that the width, $w(z)$ is not the same as the variance. The variance, $\sigma^2(z)$, can be expressed as
 
 \begin{equation}
-    \sigma(z)^2 = \omega(z)^2 \left( 1 - \frac{2\beta^2}{\pi} \right)
+    \sigma^2(z) = \omega^2(z) \left( 1 - \frac{2\beta^2}{\pi} \right)
 \end{equation}
@@
 in units of $\left[ \Msun \,yr^{-1} \,cMpc^{-3} \right]$.
-This introduces four parameters; $a$ which sets the overal normalisation and which has the same units as \SFRDz and $b,c$ and $d$ which are unitless and which govern the shape of the overal cosmic star formation rate density with redshift.
+This introduces four parameters: $a$ which sets the overal normalisation and which has the same units as \SFRDz and $b,c$ and $d$ which are unitless and which govern the shape of the overal cosmic star formation rate density with redshift.
 \\
@@
 The top panel shows the full two dimensional \SFRDzZ linear in time.
+Contours range from $10^{-7} - 10^{-2} \Msun \yr^{-1}\Mpc^{-3}$.
 The bottom left (right) panel shows slices of the distribution in redshift (metallicity).
-Each slice is displaced by 0.01$\Msun \yr^{-1}\Mpc^{-3}$.
+Each slice is displaced by 0.01$\Msun \yr^{-1}\Mpc^{-3}$ (note the linear scale of \SFRDzZ in the bottom channel).
 We show the TNG100 simulation data with thick gray lines.
-For comparison, we also show the phenomenological model from \protect\cite{Neijssel+2019} in each panel with grey dotted lines.
-For the latter, the contours in the top panel range from $10^{-7} - 10^{-2} \Msun \yr^{-1}\Mpc^{-3}$.
-This shows that our analytical model adequately captures the \SFRDzZ of the TNG100 simulations.
+For comparison, we also show the phenomenological model from \protect\cite{Neijssel+2019} in all panels with grey dotted lines.
+The bottom panels show that our analytical model adequately captures the shape of the \SFRDzZ from TNG100.
  \label{fig: fit SFRD}}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-We fit our new functional form of \SFRDzZ as defined by equations \ref{eq: total sfrd}, \ref{eq: z log skew} and \ref{eq: sfr1} to the Illustris-TNG cosmological simulations. 
-We simultaneously fit for the following nine free parameters $\alpha, \mu_0, \mu_z, \omega_0, \omega_z$, which govern the metallicity dependence and $a,b, c$ and $d$, which set the overall star formation rate.
-
-Below we briefly discuss the Illustris-TNG simulations, and elaborate on our fitting procedure.
+We fit our new functional form of \SFRDzZ as defined by equations \ref{eq: total sfrd}, \ref{eq: z log skew} and \ref{eq: sfr1} to the IllustrisTNG cosmological simulations. 
+We simultaneously fit for the following nine free parameters $\alpha, \mu_0, \mu_z, \omega_0, \omega_z$, which govern the metallicity dependence and $a,b, c$ and $d$, which set the overall star-formation rate density.
+Below we briefly discuss the IllustrisTNG simulations, and elaborate on our fitting procedure.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Illustris-TNG Cosmological simulations}
+\subsection{IllustrisTNG Cosmological simulations}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %
-Although here, we only fit our model to the TNG100 simulation, our prescription can be easily be used to fit other simulated or observational data of the metallicity dependent star formation rate density\footnote{We provide a Jupyter notebook to facilitate this fit here: \url{https://github.com/LiekeVanSon/SFRD_fit/blob/main/src/scripts/Fit_To_Cosmological_Simulation.ipynb} }.
+Although here, we only fit our model to the TNG100 simulation, our prescription can be easily be used to fit other simulated or observational data of the metallicity-dependent cosmic star formation history\footnote{We provide a Jupyter notebook to facilitate this fit here: \url{https://github.com/LiekeVanSon/SFRD_fit/blob/main/src/scripts/Fit_To_Cosmological_Simulation.ipynb} }.
 
-The IllustrisTNG-project \citep[or TNG in short,][]{FirstResTNG_Springel2018,FirstResTNG_Marinacci2018, FirstResTNG_Nelson2018,FirstResTNG_Pillepich2018, FirstResTNG_Naiman2018} considers galaxy formation and evolution through large-scale cosmological hydrodynamical simulations.
+The IllustrisTNG-project (or TNG in short) considers galaxy formation and evolution through large-scale cosmological hydrodynamical simulations \citep[][]{FirstResTNG_Springel2018,FirstResTNG_Marinacci2018, FirstResTNG_Nelson2018,FirstResTNG_Pillepich2018, FirstResTNG_Naiman2018, Nelson2019a, Pillepich2019}.
 Such simulations provide the tools to study parts of the Universe that are not easily accessible by observations.
@@
 
-The models implemented in the publicly available TNG simulations\footnote{ \url{https://www.tng-project.org/}} have lead to many successes.
-For a more extended discussion focused on the processes that govern the creation, distribution and mixing of metals in in the TNG simulations we refer to \cite{Pakmor+2022}.
-In short, star formation in the TNG simulations is calibrated against the Kennicutt–Schmidt relation \citep[][]{Schmidt1959,Kennicutt1989}.
+The models implemented in the publicly available TNG simulations \citep{Nelson2019b}\footnote{ \url{https://www.tng-project.org/}} have lead to many successes. 
+These models where calibrated at the resolution of the TNG100 simulation, hence TNG100 is expected to provide the best overall agreement to global properties (like the star formation rate density).
+This is why we adopt the TNG100 simulation as our fiducial simulation.
+%
+For a more extended discussion focused on the processes that govern the creation, distribution and mixing of metals in in the TNG simulations, we refer to \cite{Pakmor+2022}.
+In short, star formation in the TNG simulations is calibrated against the Kennicutt–Schmidt relation \citep[][]{Schmidt1959,Kennicutt1989}, using an effective equation of state \citep{SpringelHernquist2003}.
 The stellar metallicity yields are an updated version of the original Illustris simulations as described in \cite{Pillepich2018}.
@@
 % Positives on TNG
-The TNG simulations have been shown to match observational constraints on the mass-metallicity relation of galaxies up to $z = 2$ \citep{Torrey+2019}, as well as iron abundances \citep{FirstResTNG_Naiman2018} and the metallicity gradients within galaxies at low redshift \citep{Hemler+2021}.
+The TNG simulations have been shown to match observational constraints on the mass-metallicity relation of galaxies up to $z = 2$ \citep{Torrey+2019}, as well as iron abundances \citep{FirstResTNG_Naiman2018}, metallicity gradients within galaxies at low redshift \citep{Hemler+2021}, and the reduction of star formation in the centers of star-forming galaxies \citep{Nelson2021}.
 %They reproduce the evolution of the sizes of galaxies with redshift \citep{Genel+2018}
-Several studies have used the TNG simulations to make predictions for astronomical transient sources \citep[e.g.][]{Briel+2021,Bavera+2022,vanson+2022}.
-In particular, \cite{Briel+2021} show that the \SFRDzZ from the TNG and the EAGLE \citep{Schaye+2015,Crain+2015} simulations provide the best agreement between observed and predicted cosmic rates for electromagnetic and gravitational-wave transients.
+Several studies have used the TNG simulations to make predictions for astronomical transient sources \citep[e.g.][]{Briel+2022_rates,Bavera+2022,vanson+2022}. 
+Out of the four \SFRDzZ variations explored, \cite{Briel+2022_rates} find that TNG provides one of the best agreements between observed and predicted cosmic rates for electromagnetic and gravitational-wave transients, when combined with their fiducial binary population synthesis model.
+% TNG50 has higher res, but that also leads to higher stellar masses at fixed halo mass."
 
-% Downsides of TNG100 
+% Downsides of TNG (100)
 On the other hand, large uncertainties and crude approximations remain in all contemporary cosmological simulations, thus also in the TNG simulations. 
-For example, dust is not included in the TNG simulations, which could mean that metallicity of the star-forming gas is overestimated.
+Generally, some of the chemical evolution of galaxies in cosmological simulations is unresolved, and thus depends strongly on the implemented `sub-grid physics'.
+A known uncertainty is that dust is not included in the TNG simulations, which could mean that metallicity of the star-forming gas is overestimated. 
+Feedback from active galactic nuclei is not well understood theoretically and is described in an approximate manner \citep{Springel2005, Weinberger2017}.
 Furthermore, all stellar winds mass loss from massive stars, binary interactions and their ionising effects are ignored \citep[e.g.][]{Dray+2003,Smith2014,Gotberg+2020,DoughtyFinlator2021,Farmer2021_carbonfootprint,Goswami+2022}.
-% pair-pulsational supernovae \citep[e.g.][]{Renzo+2020} .  
-Moreover, the uniform ionising UV background is turned on abruptly at $z=6$, which crucially impacts the amount of low metallicity star formation at low redshift.
-
-% These large uncertainties call for a generalised form of the \SFRDzZ that can be easily updated when new information becomes available, which is the motivation for this work.
-Although here, we only fit our model to the TNG100 simulation, our prescription can be easily be used to fit other simulated data or observational data of the metallicity dependent star formation rate density \footnote{We provide a Jupyter notebook to facilitate this fit here: \url{https://github.com/LiekeVanSon/SFRD_fit/blob/main/src/scripts/Fit_To_Cosmological_Simulation.ipynb} }.
+Moreover, the uniform ionising UV background is turned on abruptly at $z=6$.
+This crucially impacts the amount of low metallicity star formation at high redshift as it allows small galaxies to produce more stars than what would be expected for a gradually increasing UV background that reaches full strength at $z=6$.
+%
+All these uncertainties underline the need for a flexible approximation of the \SFRDzZ, that can be easily updated when cosmological models and sub-grid physics are updated.
 
@@
 
-We first consider a given redshift $z_j$.  For this redshift we compute the sum of the squared residuals between the cosmological simulation and our fit.  
+We first consider a given redshift $z_j$.
+For this redshift we compute the sum of the squared residuals between the cosmological simulation and our fit.
+This is effectively the square of the $l^2$-norm:
 %
@@
         \mathcal{S}(Z_i,z_j)_{\rm sim} - 
-        \mathcal{S}(Z_i,z_j)_{\rm fit}\right)^2
+        \mathcal{S}(Z_i,z_j)_{\rm fit}\right)^2 .
     %chi_square = ((obs - model )**2)/np.sum(model) 
@@
 %
-Here, the variable $Z_i$ runs over all redshift bins.
+Here, the variable $Z_i$ runs over all metallicity bins.
 %, but excludes bins where the star formation rate density is lower $10^{-10} \Msun \yr \Mpc^{-3}$ per bin. 
@@
 We are particularly interested in properly fitting the low metallicity star formation at high redshifts.
-At high redshifts, the overall cosmic star formation rate is generally lower.
-To ensure that our fit procedure gives sufficient weight to the behaviour at all redshifts, we introduce a penalisation factor to somewhat reduce the contribution of redshifts where the peak of cosmic star formation occurs, while increasing the weight where at redshifts where the overall cosmic star formation rate is lower.
+At high redshifts, the overall star-formation rate density is generally lower.
+To ensure that our fitting procedure gives sufficient weight to the behaviour at all redshifts, we introduce a penalisation factor to somewhat reduce the contribution of redshifts where the peak of cosmic star formation occurs, while increasing the weight at redshifts where the overall star-formation rate density is lower.
 To achieve this we divide $\chi^2 (z_j)$ by the star formation $\sum_{Z_i} \mathcal{S}(Z_i,z_j)$ per redshift bin before adding the contribution of all redshifts.
@@
 
-In Figure \ref{fig: fit SFRD} we show our fiducial  model at different redshifts and metallicities. We also show the overall rate of star formation \SFRDz in Figure \ref{fig: SFR(z)}.
-In general, our analytical model captures the metallicity dependent star formation in the TNG100 simulations well (bottom panels of Figure \ref{fig: fit SFRD}). 
+In Figure \ref{fig: fit SFRD} we show our fiducial  model at different redshifts and metallicities. We also show the overall star-formation rate density \SFRDz in Figure \ref{fig: SFR(z)}.
+In general, our analytical model captures the metallicity-dependent cosmic star formation history in the TNG100 simulations well (bottom panels of Figure \ref{fig: fit SFRD}). 
 The skewed-log normal metallicity distribution is able to reproduce the overall behaviour that is observed in TNG100 \citep[bottom left panel, but cf.
@@
 To emphasise the difference between a skewed-lognormal and a symmetric lognormal distribution, we show the phenomenological model from \cite{Neijssel+2019} in dotted grey.
-Their model falls within the family of functions that is encompassed by our model described in Section \ref{sec: model for sfrd(zZ)}, but we note that their model is very distinctly different.\footnote{The phenomenological model from \cite{Neijssel+2019} is recovered by adopting $\mu_0= 0.035$, $\mu_z=-0.23$, $\omega_0=0.39 $, $\omega_z = 0$, $\alpha = 0$, $a=0.01$, $b=2.77$, $c=2.9$ and $d=4.7$.
+Their model falls within the family of functions that is encompassed by our model described in Section \ref{sec: model for sfrd(zZ)}, but we note that their model is distinctly different.\footnote{The phenomenological model from \cite{Neijssel+2019} is recovered by adopting $\mu_0= 0.035$, $\mu_z=-0.23$, $\omega_0=0.39 $, $\omega_z = 0$, $\alpha = 0$, $a=0.01$, $b=2.77$, $c=2.9$ and $d=4.7$.
 }
@@
 % For both \SFRDzZ distributions, most star formation happens at metallicities above $Z \geq 10^{-2}$ (top panel).
+
+Although our model preforms well at reproducing the large scale trends seen in TNG, we acknowledge that more complex features as suggested by some observational studies could be missed.
+One example is that the \SFRDz shape we adopt from \cite{MadauDickinson2014} does not account for starburst galaxies \citep[see discussion in][]{Chruslinska2019_obs}.
+Moreover, our model cannot capture inflection points in the mean metallicity, because we assume both $\mu_0$ and $\mu_z$ are constants with redshift (equation \ref{eq: mean Z}).
+Contrarily, \cite{Chruslinska2019_obs} find an upturn in the amount of low metallicity star formation above $z=4$ if the power law of the GSMF is allowed to evolve with redshift.
+Hence, although our model is more broadly applicable than previous models, in it's current form, it does not capture the complete range of observationally-allowed variations. 
+Incorporating more complex functional forms for our the mean metallicity could possibly capture such behaviour, but this analysis is beyond the scope of this paper.
 
@@
 \includegraphics[width=0.47\textwidth]{figures/SFR_tlookback.pdf}
-\caption{Comparison of different overall star-formation histories with redshift, \SFRDz.
+\caption{Comparison of several overall star-formation rate densities, \SFRDz,  with redshift (left panel) and with lookback time (right panel).
 The solid orange and dashed red lines respectively show the star formation data from TNG100 and our corresponding fit adopting eq.
@@
 \subsection{Determining reasonable variations of \SFRDzZ \label{ss: reasonable var}}
-We consider variations in both the shape of the cosmic metallicity distribution \dpdZ, and the shape of the overall star-formation history, \SFRDz.
+We consider variations in both the shape of the cosmic metallicity density distribution \dpdZ, and the shape of the overall star-formation rate density, \SFRDz.
 To determine the range that is reasonably allowed by observations, we compare our variations to the observation-based \SFRDzZ models described in \cite{Chruslinska+2021}.
 
-For the cosmic metallicity distribution, we vary every parameter that determines the shape of \dpdZ independently (left two columns of Table \ref{tab: fit params}).
-For every variation, we inspect the fraction of stellar mass that is formed at low-metallicity ($Z<0.1 Z_{\odot}$) versus the fraction of stellar mass that is formed at high-metallicity ($Z> Z_{\odot}$), for all star formation that occurred below a certain threshold redshift.
-We compare this to the models from \cite{Chruslinska+2021} in Figure \ref{fig: low high Z fraction} in Appendix \ref{app: reasonable var}.
-We have chosen our variations such that they span the range of reasonable cosmic metallicity distributions as determined by observation-based and cosmological simulations-based models.
-For completeness, we furthermore inspect every variation by eye, and make sure none of the variations significantly exceeds the low and high metallicity extremes from \cite{Chruslinska+2021}.\footnote{We  compare to the low metallicity extreme model: \texttt{214f14SBBiC\_FMR270\_FOH\_z\_dM.dat}, and the high metallicity extreme model: \texttt{302f14SBBoco\_FMR270\_FOH\_z\_dM.dat}.}
+For the cosmic metallicity density distribution, we vary every parameter that determines the shape of \dpdZ independently (left two columns of Table \ref{tab: fit params}), while keeping all other parameters fixed at their fiducial value.
+For each variation, we inspect the fraction of stellar mass that is formed at low-metallicity ($Z<0.1 Z_{\odot}$) versus the fraction of stellar mass that is formed at high-metallicity ($Z> Z_{\odot}$), for all star formation that occurred below a certain threshold redshift.
+We compare this to the models from \cite{Chruslinska+2021}\footnote{These models are publicly available at \url{https://ftp.science.ru.nl/astro/mchruslinska/Chruslinska_et_al_2021/}} in Figure \ref{fig: low high Z fraction} in Appendix \ref{app: reasonable var}.
+We have chosen our variations such that they span a reasonable range of cosmic metallicity density distributions as allowed by observation-based and cosmological simulations-based models.
+We use the models \texttt{214f14SBBiC\_FMR270\_FOH\_z\_dM.dat}, and \texttt{302f14SBBoco\_FMR270\_FOH\_z\_dM.dat} from \cite{Chruslinska+2021} as a representation of a very low and high metallicity star formation realisation respectively.
+These models are the low and high metallicity extreme under their fiducial SFR–metallicity correlation.
+For every variation of our model, we inspect both the full \SFRDzZ and slices at redshifts $z = 0, 0.5, 3.0$ and $6$ by eye.
+At each slice we compare our model variation to the aforementioned low and high metallicity models, and ensure that none of our variations significantly exceeds these extremes in \SFRDzZ.
+This also serves as a sanity check for the overall star-formation rate density.
 
-Lastly, we consider two variations of the overall star-formation history, \SFRDz, where we keep the metallicity distribution \dpdZ fixed, but vary all four \SFRDz parameters at once (right two columns of Table \ref{tab: fit params}).
-We use Figure 11 from \cite{Chruslinska+2021} to determine approximate upper and lower bounds to the overall star-formation history.
+Lastly, we consider two variations of the overall star-formation rate density, \SFRDz, where we keep the metallicity distribution \dpdZ fixed, but vary all four \SFRDz parameters at once (right two columns of Table \ref{tab: fit params}).
+We use Figure 11 from \cite{Chruslinska+2021} to determine approximate upper and lower bounds to the overall star-formation rate density.
 We choose \cite{Madau+2017} as an approximation of the lower limit.
-For the upper limit, we use the \texttt{SB: B18/C17} model variations with a non-evolving low-mass end of the galaxy stellar mass function from \cite{Chruslinska+2021} (thick brown line in their Fig.
-11).
+For the upper limit, we use the upper edge for the \texttt{SB: B18/C17} model variations with a non-evolving low-mass end of the galaxy stellar mass function \citep[table B1 from][also shown as thick brown line in their Fig.
+11]{Chruslinska+2021}.
 To approximate these models, we fit equation \ref{eq: sfr1} by eye to the broken power law description for the  \texttt{SB: B18/C17} model variations as presented in appendix B1 from \cite{Chruslinska+2021}.
@@
 \caption{The primary mass distribution of merging BBH systems from the stable mass transfer channel for several variations in \SFRDzZ. 
-The first five panels show variations of the cosmic metallicity distribution  \dpdZ, eq.
-\ref{eq: z log skew}, (parameters listed in the first three columns of Table \ref{tab: fit params}).
-The bottom right panel shows variations in the magnitude of the star formation rate with redshift, i.e.
+The first five panels show variations of the cosmic metallicity density distribution  \dpdZ, eq.
+\ref{eq: z log skew}, (parameters listed in the first three columns of Table \ref{tab: fit params}), where we vary one parameter at a time while keeping the rest fixed at their fiducial value.
+The bottom right panel shows variations in the magnitude of the star formation rate with redshift; i.e.
 \SFRDz.
 For the latter we vary the four fiducial parameters of \SFRDz simultaneously (last two columns of Table \ref{tab: fit params}).
-All panels are shown at a reference redshift of $z=0.2$, with the corresponding predicted BBH merger rate annotated in the legend.
+All panels are shown at a reference redshift of $z=0.2$, with the corresponding predicted BBH merger rate indicated in the legend.
 For reference, we show the power-law + peak model from \protect\cite{GWTC3_popPaper2021} in grey.
@@
 \includegraphics[width=0.8\textwidth]{figures/Mass_distributions_CE_SFRD_variations.pdf}
-\caption{Same as Figure \ref{fig: stable mass dists}, but for the Common envelope channel.
-These Figures show that the low mass end of the primary mass distribution is least affected by the adopted \SFRDzZ.
+\caption{Same as Figure \ref{fig: stable mass dists}, but for the Common Envelope channel.
+These figures show that the low mass end of the primary mass distribution is least affected by the adopted \SFRDzZ.
 Moreover, the \textit{location} of features in the mass distribution are robust against all explored variations.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{The effect of the \SFRDzZ on the primary BH mass distribution}
+\subsection{The effect of the \SFRDzZ on the primary masses of merging BBH}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 To isolate the effect of the \SFRDzZ from the effects of different formation channels, we split the data from \cite{vanson+2022} between the stable mass transfer channel \citep[e.g.,][]{van-den-Heuvel+2017,Inayoshi2017,Bavera2021,Marchant2021,GallegosGarcia2021,vanson+2022}, and the `classical' common-envelope channel \citep[or CE channel, e.g.,\  ][]{Belczynski+2007,PostnovYungelson2014,Belczynski+2016Natur,vignaGomez+2018}.
-These channels are distinguished based on whether the binary system has experienced a common envelope phase (CE channel) or only stable mass transfer (stable channel in short from now on).
+These channels are distinguished based on whether the binary system has experienced a common envelope phase (CE channel) or only stable mass transfer (stable channel in short from now on).\\
 
@@
 Each panel varies one aspect of the \SFRDzZ.
+In the first five panels of Figures \ref{fig: stable mass dists} and \ref{fig: CE mass dists}, we vary one of the  parameters that determine the shape of the probability density distribution of metallicities, while keeping all other values fixed at their fiducial values.
+In the last panel of  Figures \ref{fig: stable mass dists} and \ref{fig: CE mass dists}, we vary the shape of the overall star-formation rate densities, \SFRDz, to one of the variations shown in Figure \ref{fig: SFR(z)}, while keeping the probability density distribution of metallicities fixed.
 
 % The location of features is robust
-The first thing we note is that the location of the features in the primary mass distribution are robust against variations in the \SFRDzZ.
+The first thing we note is that the location of the features in the primary mass distribution are robust against variations in \SFRDzZ.
 For the CE channel, the global peak of the mass distribution remains at approximately $\Mbheen\approx16\Msun$ for all variations.
 Similarly, the stable channel displays two peaks that are visible in all variations: a peak at $\Mbheen\approx9\Msun$ and a peak at $\Mbheen\approx22\Msun$. 
-Two more peaks are visible in the stable channel at the high mass end for almost all \SFRDzZ (at $\Mbheen\approx35\Msun$ and $\Mbheen\approx45\Msun$), these peaks only fade for variations where the rate of high mass BHs is generally suppressed (dashed lines in top panel of Fig.
+Two more peaks are visible in the stable channel at the high mass end for almost all \SFRDzZ (at $\Mbheen\approx35\Msun$ and $\Mbheen\approx45\Msun$); these peaks only fade for variations where the rate of high mass BHs is generally suppressed (dashed lines in top panel of Fig.
 \ref{fig: stable mass dists}).
@@
 Although peaks in the probability distribution of chirp masses as shown in their Fig.
-4 can disappear when a the \SFRDzZ prohibits the formation of certain (typically higher) mass BHs, the \textit{location} of features remains the same.
+4 can disappear when \SFRDzZ prohibits the formation of certain (typically higher) mass BHs, the \textit{location} of features remains the same.
 %
@@
 This implies that the \textit{locations} of features in the mass distribution of BBHs are determined by the formation channel and its underlying stellar and binary physics.
-The location of features could therefore serve as tell tales of the underlying physics.
+The location of features could therefore serve as sign posts of the underlying physics.
 
 % Low masses are less affected
-Second, we see that the low mass end of the primary mass distribution is relatively robust against variations in the \SFRDzZ. 
+Second, we see that the low mass end of the primary mass distribution is relatively robust against variations in \SFRDzZ. 
 To quantify this, we annotate the ratio between the maximum and minimum rate at three reference masses; \Mbheen = $10, 25$, and $40\Msun$.
 At $\Mbheen=10\Msun$, we find that the rate changes by at most a factor of about 3.5 for the stable channel, and at most about a factor of 6.5 for the CE channel. 
-On the other hand, the change in rate at $\Mbheen=40\Msun$ can be as high as a factor of about 110 and 60 for the stable and CE channel respectively. 
+On the other hand, the change in rate at $\Mbheen=40\Msun$ can be as high as a factor of about 110 and 60 for the stable and CE channels, respectively. 
+%
+The lowest mass BHs are least affected by the \SFRDzZ because they can be formed from all metallicities above $Z\gtrsim10^{-3}$ \citep[see e.g., Figures 7 and 13 from ][]{vanson+2022}.
+The rate of star formation at metallicities above $\gtrsim 10^{-3}$ is observationally relatively well constrained for redshifts below $0.5$ (which comprises the past $5\Gyr$ of star formation). 
+This is reflected in the top panel of Figure \ref{fig: low high Z fraction}: all models show that $10\%$ or less of the stellar mass was formed at a metallicity below $Z/10 \approx 0.0014$, or in other words, about $90\%$ or more of the stellar mass was formed at a metallicity above $Z/10$.
+Hence the lowest mass BHs derive from the least uncertain parts of the \SFRDzZ.
+%
 The low mass end of the mass distribution of merging double compact objects will also provide a particularly powerful cosmological constraint in the era of third generation gravitational wave telescopes \citep{MariaEzquiaga2022}.
@@
 Parameter variations that affect shape of \SFRDzZ at low redshift primarily change the normalisation of the mass distribution.
-This is the case for variations of the width of the cosmic metallicity distribution at $z=0$ ($\omega_0$), the mean metallicity of the cosmic metallicity distribution at $z=0$ ($\mu_0$), and the skewness of the cosmic metallicity distribution ($\alpha$, left columns of Figures \ref{fig: stable mass dists} and \ref{fig: CE mass dists}).
-To emphasise this point, we annotate the total BBH merger rate at redshift 0.2, $\mathcal{R}_{0.2}$, in the legends of Figures \ref{fig: stable mass dists} and \ref{fig: CE mass dists} (0.2 if the redshift where the observations are best constrained \citealt{GWTC3_popPaper2021}).
+This is the case for variations of the width of the cosmic metallicity density distribution at $z=0$ ($\omega_0$), the mean metallicity of the cosmic metallicity density distribution at $z=0$ ($\mu_0$), and the skewness of the cosmic metallicity density distribution ($\alpha$, left columns of Figures \ref{fig: stable mass dists} and \ref{fig: CE mass dists}).
+To emphasise this point, we annotate the total BBH merger rate at redshift 0.2, $\mathcal{R}_{0.2}$, in the legends of Figures \ref{fig: stable mass dists} and \ref{fig: CE mass dists} (0.2 is the redshift where the observations are best constrained \citealt{GWTC3_popPaper2021}).
 %
@@
 This is consistent with other work that finds merging BBHs form more efficiently at low metallicities \citep[e.g.][]{BelczynskiVink2010, Stevenson+2017,Mapelli2017,Chruslinska2019_effectCO,Broekgaarden+2021b}.
-A more skewed cosmic metallicity distribution pushes the peak of the distribution to higher metallicities and thus forms overall more stars at high metallicity when compared to a symmetric distribution.
+A more skewed cosmic metallicity density distribution pushes the peak of the distribution to higher metallicities and thus forms more stars at high metallicity when compared to a symmetric distribution.
 Hence, the local rate of BBH mergers is lower for the skewed distribution ($\alpha = -6$) with respect to the symmetric variation ($\alpha = 0.0$).
@@
 % Effect of the star formation 
-Changing the overall star-formation history (\SFRDz, bottom right panels of Figures \ref{fig: stable mass dists} and \ref{fig: CE mass dists}) also affects the overall normalisation of the mass distribution, but has a smaller effect than the width and the mean of the cosmic metallicity distribution at $z=0$ ($\omega_0$ and $\mu_0$).
+Changing the overall star-formation rate density (\SFRDz, bottom right panels of Figures \ref{fig: stable mass dists} and \ref{fig: CE mass dists}) also affects the normalisation of the mass distribution, but has a smaller effect than the width and the mean of the cosmic metallicity density distribution at $z=0$ ($\omega_0$ and $\mu_0$).
 This underlines the importance of the amount of low-metallicity star formation \citep[e.g.,][]{chruslinska2022_review}, and is furthermore in line with findings from \cite{Tang+2020}.
 As discussed in Section \ref{ss: reasonable var}, we use \cite{Madau+2017} and the solid blue line in Figure \ref{fig: SFR(z)} as an approximate lower and upper bound to the \SFRDz respectively. 
-The model from \cite{Madau+2017} is very similar to our Fiducial model (Figure \ref{fig: SFR(z)}), and the differences between the resulting mass distributions are correspondingly small.
+The model from \cite{Madau+2017} is very similar to our fiducial model (Figure \ref{fig: SFR(z)}), and the differences between the resulting mass distributions are correspondingly small.
 Our approximation of the upper limit to the allowed \SFRDz leads to an overall increase of the BBH merger rate by a factor of about 3.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-We present a flexible analytic expression for the metallicity-dependent star formation rate, \SFRDzZ (equations \ref{eq: total sfrd}, \ref{eq: z log skew} and \ref{eq: sfr1}).
+We present a flexible analytic expression for the metallicity-dependent cosmic star formation history, \SFRDzZ (equations \ref{eq: total sfrd}, \ref{eq: z log skew} and \ref{eq: sfr1}).
 An analytical expression allows for controlled experiments of the effect of \SFRDzZ on dependent values, such as the rate and mass distribution of merging BBHs.
@@
 \paragraph{The model can capture the general behaviour of cosmological simulations, such as TNG100}
-Our analytical expression for \SFRDzZ is composed of a cosmic metallicity distribution that is determined by a mean, scale and skewness and their redshift dependence, as well as parameters governing the overall cosmic star formation rate.
+Our analytical expression for \SFRDzZ is composed of a cosmic metallicity density distribution that is determined by a mean, scale and skewness and their redshift dependence, as well as parameters governing the overall star-formation rate density.
 We fit our analytical expression for \SFRDzZ to the star-forming gas in the TNG100 simulation, and provide the best fit parameters in Table \ref{tab: fit params}.
@@
 We show that our model captures the shape and general behaviour of the cosmological simulations well (Figure \ref{fig: fit SFRD}). 
+Although our model is more broadly applicable than previous models, we acknowledge that it does not capture the \textit{complete} range of observationally-allowed variations in it's current form.
+Incorporating more complex functions for the redshift evolution of the metallicity could solve this issue, but this is left for future research.
 
@@
 As an example, we apply our model to calculate the local rate and mass distribution of the more massive components from merging BBHs (\Mbheen) in Figures \ref{fig: stable mass dists} and \ref{fig: CE mass dists}.
-We systematically vary all five parameters that shape the cosmic metallicity distribution, and explore two additional variations of the overall star-formation history \SFRDz.
+We systematically vary all five parameters that shape the cosmic metallicity density distribution, and explore two additional variations of the overall star-formation rate density \SFRDz.
 Our main findings are as follows:
@@
 
-    \item The location of features in the distribution of primary BH masses are robust against variations in the \SFRDzZ.
-The location of features in the mass distribution of BHs could thus be used as tell-tale signatures of their formation channel.
+    \item The location of features in the distribution of primary BH masses are robust against variations in \SFRDzZ.
+The location of features in the mass distribution of BHs could thus be used as sign posts of their formation channel.
 
-    \item For all variations, the low mass end of the mass distribution is least affected by changes in the \SFRDzZ.
-This suggest that lower end of the BH mass distribution (component masses of $\leq 15\Msun$) is potentially very powerful for constraining the physics of the formation channels, irrespective of the cosmic star formation rate uncertainties.
+    \item For all variations, the low mass end of the mass distribution is least influenced by changes in the \SFRDzZ.
+    This is because the lowest mass BHs can be formed from all metallicities above $Z~\gtrsim~10^{-3}$, for which the star formation rate is relatively well constrained in the recent Universe. 
+    This suggests that lower end of the BH mass distribution (component masses of $\leq 15\Msun$) is potentially very powerful for constraining the physics of the formation channels, irrespective of the cosmic star formation rate uncertainties.
 
-    \item The metallicity distribution of star formation at low redshift, primarily impacts the normalisation of the BBH merger rate.
-Changing the overall star-formation history, \SFRDz also affects the rate, but to a lesser degree.
+    \item The metallicity distribution of star formation at low redshift primarily impacts the normalisation of the BBH merger rate.
+Changing the overall star-formation rate density, \SFRDz also affects the rate, but to a lesser degree.
 This underlines how low-metallicity star formation at low redshifts dominates the overall normalisation of the BBH merger rate.
 
-    \item Parameters that influence the redshift evolution of the mean and the width of the metallicity distribution, affect the slope of the high mass end of the primary BH mass distribution for the stable channel.
+    \item Parameters that influence the redshift evolution of the mean and the width of the metallicity distribution affect the slope of the high mass end of the primary BH mass distribution for the stable channel.
 This reflects the longer delay times of the stable channel with respect to the CE channel.
@@
 
-The flexibility of the model presented in this work can capture the large uncertainties that remain in the shape and normalisation of the metallicity dependent cosmic star formation history. 
-Our hope is that this expression will provide a useful starting point for making predictions and comparison with observations.
+The flexibility of the model presented in this work can capture the large uncertainties that remain in the shape and normalisation of the metallicity-dependent cosmic star formation history. 
+Our hope is that this expression will provide a useful starting point for making predictions and comparisons with observations.
 % As such, we anticipate that it will be a helpful tool in other works that present \SFRDzZ dependent rates.
@@
 \end{acknowledgments}
+
+\section*{Software and Data}
+% Code and Data 
+The data used in this work is available on Zenodo under an open-source Creative Commons Attribution license at \todo{dataset}.
+% \dataset[doi:10.5281/zenodo.5544170]{https://doi.org/10.5281/zenodo.5544170}.
+Data from \cite{Chruslinska+2021} for the observational stuff can be found: \url{https://ftp.science.ru.nl/astro/mchruslinska/Chruslinska_et_al_2021/}
+
+This research has made use of GW data provided by the Gravitational Wave Open Science Center (\url{https://www.gw-openscience.org/}), a service of LIGO Laboratory, the LIGO Scientific Collaboration and the Virgo Collaboration.
+% LIGO Laboratory and Advanced LIGO are funded by the United States National Science Foundation (NSF) as well as the Science and Technology Facilities Council (STFC) of the United Kingdom, the Max-Planck-Society (MPS), and the State of Niedersachsen/Germany for support of the construction of Advanced LIGO and construction and operation of the GEO600 detector.
+Additional support for Advanced LIGO was provided by the Australian Research Council.
+Virgo is funded, through the European Gravitational Observatory (EGO), by the French Centre National de Recherche Scientifique (CNRS), the Italian Istituto Nazionale di Fisica Nucleare (INFN) and the Dutch Nikhef, with contributions by institutions from Belgium, Germany, Greece, Hungary, Ireland, Japan, Monaco, Poland, Portugal, Spain.
+
+Further software used in this work: Python \citep{PythonReferenceManual},  Astropy \citep{astropy:2013,astropy:2018} Matplotlib \citep{2007CSE.....9...90H},  {NumPy} \citep{2020NumPy-Array}, SciPy \citep{2020SciPy-NMeth}, \texttt{ipython$/$jupyter} \citep{2007CSE.....9c..21P, Kluyver2016jupyter},  Seaborn \citep{waskom2020seaborn}  and  {hdf5}   \citep{collette_python_hdf5_2019}.
 
@@
 \script{LowHighZ_fraction.py}
-\includegraphics[width=\textwidth]{figures/High_Low_metalFractionSFMass.pdf}
+\includegraphics[width=0.75\textwidth]{figures/High_Low_metalFractionSFMass.pdf}
 \caption{Percentage of stellar mass formed at low metallicity ($Z < 0.1 \rm{Z_{\odot}}$) , versus high metallicity ($Z>\rm{Z_{\odot}}$) for all star formation below a certain threshold redshift: $z<0.5$ (left), $z < 3.0$ (middle) and $z<10$ (right).
@@
 For data from cosmological simulations, we follow \cite{Pakmor+2022} and show Illustris \citep[][squares]{Vogelsberger+2014}, Simba \citep[][diamonds]{Dave+2019}, EAGLE \citep[][triangles]{Schaye+2015}, TNG50 and TNG100 \citep[][filled and open circles respectively]{FirstResTNG_Springel2018}.
-Black thin crosses display variations of the cosmic metallicity distribution that is part of our fiducial \SFRDzZ.
+Black thin crosses display variations of the cosmic metallicity density distribution that is part of our fiducial \SFRDzZ.
 The parameter that is varied with respect to the fiducial and its new value are annotated.
-This shows that our \SFRDzZ variations span the range of reasonable cosmic metallicity distributions as determined by observation-based and cosmological simulations-based models.
+This shows that our \SFRDzZ variations span the range of reasonable cosmic metallicity density distributions as determined by observation-based and cosmological simulations-based models.
 \label{fig: low high Z fraction}

### 2022-09-01 src/scripts/FitComparison_3panelPlot.py

@@ -376,7 +376,8 @@ def three_panel_SFRD_plot(obs_SFRD = [], mu_0=0.025, mu_z=-0.49,alpha = -1.77, o
 
     ax_metals.set_ylim(-0.005, 0.075)
     ax_metals.set_xlim(-4, -0.5)
-    
+    ax_metals.set_yscale('log')
+
     
     ##################################################################################
     ##                                                                              ##
@@ -435,11 +436,12 @@ def three_panel_SFRD_plot(obs_SFRD = [], mu_0=0.025, mu_z=-0.49,alpha = -1.77, o
     
     ax_redsh.set_xlim(0, 10)
     ax_redsh.set_ylim(-0.005, 0.075)
+    ax_redsh.set_yscale('log')
     
     
     ##############################################################################
     print('saving here', paths.figures / 'SFRD_FIT_evaluation_compare.pdf')
-    fig.savefig(paths.figures / 'SFRD_FIT_evaluation_compare.pdf',  bbox_inches='tight', dpi=300)
+    fig.savefig(paths.figures / 'testSFRD_FIT_evaluation_compare.pdf',  bbox_inches='tight', dpi=300)
     
     # plt.show()
 

### 2022-09-01 src/scripts/LowHighZ_fraction_1.py

@@ -1,0 +1,606 @@
+
+import os
+import h5py
+import numpy as np 
+import matplotlib.pyplot as plt
+import paths
+from pylab import *
+import seaborn as sns
+
+from scipy import interpolate
+
+from astropy.table import Table
+
+import astropy.units as u
+# from astropy.cosmology import WMAP9, z_at_value
+from astropy.cosmology import Planck18  as cosmo# Planck 2018
+from astropy.cosmology import z_at_value
+
+############################
+# Custom scripts
+import get_ZdepSFRD as Z_SFRD
+import importlib
+importlib.reload(Z_SFRD)
+
+############################
+##PLOT setttings
+from matplotlib import rc
+import matplotlib
+matplotlib.rcParams['mathtext.fontset'] = 'stix'
+matplotlib.rcParams['font.family'] = 'STIXGeneral'
+rc('font',**{'family':'sans-serif','sans-serif':['Helvetica']})
+plt.rc('font', family='serif')
+rc('text', usetex=True)
+fsize, SMALL_SIZE, MEDIUM_SIZE, BIGGER_SIZE = 30,20,20,30
+for obj in ['axes','xtick','ytick']:
+    plt.rc(obj, labelsize=MEDIUM_SIZE)          # controls default text sizes
+for obj in ['figure','axes']:
+    plt.rc(obj, titlesize=BIGGER_SIZE)    # fontsize of the tick labels
+plt.rc('font', size=MEDIUM_SIZE)          # controls default text sizes
+plt.rc('legend', fontsize=SMALL_SIZE)    # legend fontsize
+
+
+######################################
+## Widescreen jupyter notebook
+from IPython.core.display import display, HTML
+display(HTML("<style>.container { width:100% !important; }</style>"))
+
+
+#######################
+# Definitions
+SOLAR_METALLICITY = 0.0127
+outdir = str(paths.data) +'/RuedigerFig2/' #"./"
+TNG               = 50
+lvl               = 1
+
+
+
+def getStellarMassMetallicityTNG():
+    fout = outdir + "StellarMassMetallicityTNG%d-%d.hdf5" % (TNG,lvl)
+    if os.path.exists( fout ):
+        return
+  
+    print( "Computing data TNG%d" % TNG )
+
+    snap = 99
[…]

### 2022-09-02 src/scripts/ExtractZenodoData.py
reintroducing extract zenodo data

@@ -5,10 +5,18 @@ import matplotlib.pyplot as plt
 import os
 import tarfile
 import paths
+import init_values as In
 
 data_dir = str(paths.data)
 
-out_fname = data_dir +'/COMPAS_Output_wWeights.h5'
+
+if __name__ == "__main__": 
+
+    # Initialize values
+    In.init()
+
+
+out_fname = data_dir + In.COMPASfilename #'/COMPAS_Output_wWeights.h5'
 tar_name  = data_dir + '/COMPAS_Output_wRates.tar.gz'
 
 

### 2022-09-02 src/scripts/ExtractZenodoData.py
reintroducing extract zenodo data

@@ -17,7 +17,7 @@ if __name__ == "__main__":
 
 
 out_fname = data_dir + In.COMPASfilename #'/COMPAS_Output_wWeights.h5'
-tar_name  = data_dir + '/COMPAS_Output_wRates.tar.gz'
+tar_name  = data_dir + '/COMPAS_Output_wWeights.tar.gz'
 
 
 # check if file exists, if not, extract it

### 2022-09-02 src/tex/ms.tex
minor tex changes

@@
 % \title{ A flexible expression for the metallicity-dependent cosmic star formation history: }
-\title{The location of features in the mass distribution of merging binary black holes does not depend on the metallicity-dependent cosmic star formation history.}
+% \title{The location of features in the mass distribution of merging binary black holes does not depend on the metallicity-dependent cosmic star formation history.}
+\title{The locations of features in the mass distribution of merging binary black holes are robust against uncertainties in the metallicity-dependent cosmic star formation history.}
 
@@
 \author[0000-0001-5484-4987]{L.~A.~C.~van~Son}
-\affiliation{Center for Astrophysics $|$ Harvard $\&$ Smithsonian,
-60 Garden St., Cambridge, MA 02138, USA}
+\affiliation{Center for Astrophysics $|$ Harvard $\&$ Smithsonian, 60 Garden St., Cambridge, MA 02138, USA}
 \affiliation{Anton Pannekoek Institute of Astronomy, Science Park 904, University of Amsterdam, 1098XH Amsterdam, The Netherlands}
@@
 %%%%%%%%%%%%%%%
-\author[0000-0002-8901-6994]{L. Hernquist}
-\affiliation{Center for Astrophysics $|$ Harvard $\&$ Smithsonian,
-60 Garden St., Cambridge, MA 02138, USA}
+\author[0000-0002-1590-8551]{C. Conroy}
+\affiliation{Center for Astrophysics $|$ Harvard $\&$ Smithsonian, 60 Garden St., Cambridge, MA 02138, USA}
 %%%%%%%%%%%%%%%
@@
 \affiliation{Max Planck Institute for Astrophysics, Karl-Schwarzschild-Str. 1, 85748 Garching, Germany}
+%%%%%%%%%%%%%%%
+\author[0000-0002-8901-6994]{L. Hernquist}
+\affiliation{Center for Astrophysics $|$ Harvard $\&$ Smithsonian, 60 Garden St., Cambridge, MA 02138, USA}
 %%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Abstract with filler text
+% Abstract 
 \begin{abstract}
-New observational facilities are probing astrophysical transients such as stellar explosions and gravitational wave (GW) sources at ever increasing redshifts.
-To interpret these observations we need to compare them to predictions from stellar population models.
+New observational facilities are probing astrophysical transients such as stellar explosions and gravitational wave (GW) sources at ever increasing redshifts, while also revealing new features in source property distributions.
+To interpret these observations, we need to compare them to predictions from stellar population models.
 Such models require the metallicity-dependent cosmic star formation history (\SFRDzZ) as an input.
-Large uncertainties remain in the shape and evolution of this function, and understanding its behaviour is essential to explain simulation results.
-% Large uncertainties remain in the value and shape of the \SFRDzZ, especially at the low metallicities that are crucial to the formation of GW events.
-% Understanding the behaviour of the adopted metallicity distribution with which stars form is essential to explain simulation results. 
-% Various approaches to approximate \SFRDzZ exist, ranging from fully empirical prescriptions to prescriptions that are based on cosmological simulations.
+Large uncertainties remain in the shape and evolution of this function.%and understanding its behaviour is essential to explain simulation results.
 In this work, we propose a simple analytical function for \SFRDzZ. 
-% The novelty of this model lies in a skewed-lognormal distribution of metallicities, that captures the tail of low metallicity star formation at low redshift. 
 Variations of this function can be easily interpreted, because the parameters link to its shape in an intuitive way. 
@@
 We fit our analytical function to the star-forming gas of the cosmological TNG100 simulation and find that it is able to capture the main behaviour well. 
-%
 As an example application, we investigate the effect of systematic variations in the \SFRDzZ parameters on the predicted mass distribution of locally merging binary black holes (BBH).
-Our main findings are: I) the location of features is remarkably robust against variations in the metallicity-dependent cosmic star formation history, and II) the low mass end is least affected by these variations.
+Our main findings are: I) the locations of features are remarkably robust against variations in the metallicity-dependent cosmic star formation history, and II) the low mass end is least affected by these variations.
 This is promising as it increases our chances to constrain the physics that governs the formation of these objects.
@@
 \paragraph{The model allows for a controlled experiment on the effect of \SFRDzZ on the local distribution of merging BBH}
-As an example, we apply our model to calculate the local rate and mass distribution of the more massive components from merging BBHs (\Mbheen) in Figures \ref{fig: stable mass dists} and \ref{fig: CE mass dists}.
+As an example, we use our model to calculate the local rate and mass distribution of the more massive components from merging BBHs (\Mbheen) in Figures \ref{fig: stable mass dists} and \ref{fig: CE mass dists}.
 We systematically vary all five parameters that shape the cosmic metallicity density distribution, and explore two additional variations of the overall star-formation rate density \SFRDz.
@@
 
-    \item The location of features in the distribution of primary BH masses are robust against variations in \SFRDzZ.
+    \item The locations of features in the distribution of primary BH masses are robust against variations in \SFRDzZ.
 The location of features in the mass distribution of BHs could thus be used as sign posts of their formation channel.
@@
     This is because the lowest mass BHs can be formed from all metallicities above $Z~\gtrsim~10^{-3}$, for which the star formation rate is relatively well constrained in the recent Universe. 
-    This suggests that lower end of the BH mass distribution (component masses of $\leq 15\Msun$) is potentially very powerful for constraining the physics of the formation channels, irrespective of the cosmic star formation rate uncertainties.
+    This suggests that the lower end of the BH mass distribution (component masses of $\leq 15\Msun$) is potentially very powerful for constraining the physics of the formation channels, irrespective of the cosmic star formation rate uncertainties.
 
@@
 Changing the overall star-formation rate density, \SFRDz also affects the rate, but to a lesser degree.
-This underlines how low-metallicity star formation at low redshifts dominates the overall normalisation of the BBH merger rate.
+This shows that low-metallicity star formation at low redshifts dominates the overall normalisation of the BBH merger rate.
 

### 2022-09-02 src/scripts/ExtractZenodoData.py
fixed the extraction

@@ -7,7 +7,7 @@ import tarfile
 import paths
 import init_values as In
 
-data_dir = str(paths.data)
+data_dir = str(paths.data) +'/'
 
 
 if __name__ == "__main__": 

### 2022-09-02 src/scripts/CosmicIntegration/CheckCompletionAndCombine.py
sys path

@@ -9,6 +9,7 @@ import sys
 import time
 from fnmatch import fnmatch
 import h5py
+sys.path.append( str(os.getcwd()) + '/src/scripts/')
 
 import init_values as In
 

### 2022-09-03 src/scripts/CosmicIntegration/CheckCompletionAndCombine.py
made it through the CI

@@ -70,7 +70,7 @@ if __name__ == "__main__":
 
     # Copy your files into one filter for files with rate_file_name, but remove the extension .h5
     input_Ratedata_dir = '/n/holystore01/LABS/hernquist_lab/Users/lvanson/home_output/SFRD_fit/src/data/RateData/'
-    h5_copy_string = 'python %s/h5copy.py  %s -o %s --filter *%s  > %s'%(In.script_dir, input_Ratedata_dir, In.data_dir+'/RateData/'+In.rate_file_name, CI.rate_file_name[:-3] , CI.data_dir+"/slurm_out/combineh5.log" )
+    h5_copy_string = 'python %s/h5copy.py  %s -o %s --filter *%s  > %s'%(In.script_dir, input_Ratedata_dir, In.data_dir+'/RateData/'+In.rate_file_name, In.rate_file_name[:-3] , In.data_dir+"/slurm_out/combineh5.log" )
     
     print(h5_copy_string)
 

### 2022-09-03 src/scripts/FitComparison_3panelPlot.py

@@ -435,7 +435,7 @@ if __name__ == "__main__":
         
         ##############################################################################
         print('saving here', paths.figures / 'SFRD_FIT_evaluation_compare.pdf')
-        fig.savefig(paths.figures / 'testSFRD_FIT_evaluation_compare.pdf',  bbox_inches='tight', dpi=300)
+        fig.savefig(paths.figures / 'SFRD_FIT_evaluation_compare.pdf',  bbox_inches='tight', dpi=300)
         
         # plt.show()
 

### 2022-09-03 src/scripts/Plot_Mass_distributions.py

@@ -34,6 +34,7 @@ importlib.reload(mfunc)
 
 import gc
 import paths
+import init_values as In
 
 import time
 

### 2022-09-03 src/scripts/MassDistHelperFunctions.py
added prints and split CE and stable plot

@@ -72,10 +72,10 @@ def read_data(loc = '', verbose=False):
     DCO[CEcount]                 = File[dcokey][CEcount][()] 
     DCO['Mass(1)']               = File[dcokey]['Mass(1)'][()]
     DCO['Mass(2)']               = File[dcokey]['Mass(2)'][()]
-    DCO['M_tot']                 = DCO['Mass(1)'] + DCO['Mass(2)']
+    #DCO['M_tot']                 = DCO['Mass(1)'] + DCO['Mass(2)']
     DCO['M_moreMassive']         = np.maximum(File[dcokey]['Mass(1)'][()], File[dcokey]['Mass(2)'][()])
-    DCO['M_lessMassive']         = np.minimum(File[dcokey]['Mass(1)'][()], File[dcokey]['Mass(2)'][()])
-    DCO['Mchirp']                = Mchirp(DCO['M_moreMassive'], DCO['M_lessMassive'])
+    #DCO['M_lessMassive']         = np.minimum(File[dcokey]['Mass(1)'][()], File[dcokey]['Mass(2)'][()])
+    #DCO['Mchirp']                = Mchirp(DCO['M_moreMassive'], DCO['M_lessMassive'])
     DCO['Stellar_Type(1)']       = File[dcokey]['Stellar_Type(1)'][()]
     DCO['Stellar_Type(2)']       = File[dcokey]['Stellar_Type(2)'][()]
     DCO['Optimistic_CE']         = File[dcokey]['Optimistic_CE'][()]
@@ -89,6 +89,7 @@ def read_data(loc = '', verbose=False):
     
     File.close()
     
+    print('Done with reading DCO data for this file :)')
     return DCO
 
 
@@ -202,6 +203,5 @@ def get_crude_rate_density(intrinsic_rate_density, fine_redshifts, crude_redshif
     
     return crude_rate_density
 
-
-
+    
 

### 2022-09-03 src/scripts/Plot_CEMass_distributions.py

@@ -1,0 +1,178 @@
+"""
+
+# Plotting the stable BH mass distribution for several SFRD Z-distribution variations
+
+"""
+
+import sys
+import numpy as np
+import matplotlib.pyplot as plt
+
+import matplotlib
+# configure backend here
+matplotlib.use('Agg')
+
+import seaborn as sns
+from scipy import stats
+
+import h5py as h5 
+from astropy.table import Table
+import astropy.units as u
+from astropy import constants as const
+
+# Chosen cosmology 
+from astropy.cosmology import WMAP9 as cosmo
+from astropy.cosmology import z_at_value
+
+import json
+import argparse
+
+# My own helper funcitons:
+import importlib
+import MassDistHelperFunctions as mfunc
+importlib.reload(mfunc)
+
+import gc
+import paths
+import init_values as In
+
+import time
+
+import Plot_Mass_distributions as pltmass
+
+
+#################################################################################################
+#                                                                                               #
+#                                          Call plots                                           #
+#                                                                                               #
+#################################################################################################
+if __name__ == "__main__": 
+
+    # Initialize values
+    In.init()
+
+    only_stable = False
+    only_CE     = True
+    channel_string = 'CE'
+
+    print('making Figure ', save_loc + '/Mass_distributions_'+ channel_string+'_SFRD_variations.pdf')
+
+    fig = plt.figure( figsize = (24, 28))
+
+    ####################################################
+    # width of SFRD at z=0
+    ####################################################
+    #add first subplot in layout that has 3 rows and 2 columns
+    subplot1 = fig.add_subplot(321)
+
+    ax1 = pltmass.plot_mass_distribution(sim_dir = data_dir, rate_file='/RateData/'+str(In.rate_file_name), simulation_data = '/'+str(In.COMPASfilename),
[…]

### 2022-09-03 src/scripts/Plot_Mass_distributions.py

@@ -70,7 +70,7 @@ plt.rc('legend', fontsize=SMALL_SIZE)    # legend fontsize
 def plot_mass_distribution(sim_dir = '', rate_file = '', simulation_data = '', 
                     x_key = 'M_moreMassive', rate_keys = ['Rates_mu00.025_muz-0.05_alpha-1.77_sigma0%s_sigmaz0.05_zBinned'%(x) for x in [0.8, 1.125, 1.4]],channel_string = 'all',
                    bins = np.arange(0.,55,2.5), z_bin_edges = [0,0.25], 
-                   plot_LIGO = False, show_hist = False, show_KDE = True, kde_width = 0.1,  
+                   plot_LIGO = False, show_hist = False, show_KDE = True,   
                    only_stable = True, only_CE = True, 
                    bootstrap = False, bootstraps = 10, x_lim=(0.,50),  y_lim = (1e-2,30), 
                    Color = '#e388b0', linestyles = ['--','-', ':'], titletext = '',
@@ -88,10 +88,8 @@ def plot_mass_distribution(sim_dir = '', rate_file = '', simulation_data = '',
      plot
 
     """
-
     #########################################
     mass_binw = np.diff(bins)[0]
-
     plot_lines = []
     leg_labels = []
 
@@ -106,6 +104,7 @@ def plot_mass_distribution(sim_dir = '', rate_file = '', simulation_data = '',
     # GWTC-3 Powerlaw + Peak Mass distribution
     ################################################ 
     if plot_LIGO:
+        print('plotting LIGO')
         color_plpeak = 'grey'#'#1f78b4'
         #################################################
         ## grab Powerlaw + Peak data from O3
@@ -144,8 +143,6 @@ def plot_mass_distribution(sim_dir = '', rate_file = '', simulation_data = '',
         print('rate_key', rate_key)
 
         # ### ## Reading Rate data ##
-#         try:
-            #     DCO_mask, redshifts, intrinsic_rate_density, intrinsic_rate_density_z0  = mfunc.read_rate_data(loc = sim_dir + '/Rate_info.hdf5', rate_key = rate_key)
         with h5.File(sim_dir + '/' + rate_file ,'r') as File:
             redshifts                 = File[rate_key]['redshifts'][()]
             # Different per rate key:
@@ -153,7 +150,8 @@ def plot_mass_distribution(sim_dir = '', rate_file = '', simulation_data = '',
[…]

### 2022-09-03 src/scripts/Plot_StableMass_distributions.py

@@ -1,0 +1,179 @@
+"""
+
+# Plotting the stable BH mass distribution for several SFRD Z-distribution variations
+
+"""
+
+import sys
+import numpy as np
+import matplotlib.pyplot as plt
+
+import matplotlib
+# configure backend here
+matplotlib.use('Agg')
+
+import seaborn as sns
+from scipy import stats
+
+import h5py as h5 
+from astropy.table import Table
+import astropy.units as u
+from astropy import constants as const
+
+# Chosen cosmology 
+from astropy.cosmology import WMAP9 as cosmo
+from astropy.cosmology import z_at_value
+
+import json
+import argparse
+
+# My own helper funcitons:
+import importlib
+import MassDistHelperFunctions as mfunc
+importlib.reload(mfunc)
+
+import gc
+import paths
+import init_values as In
+
+import time
+
+import Plot_Mass_distributions as pltmass
+
+
+#################################################################################################
+#                                                                                               #
+#                                          Call plots                                           #
+#                                                                                               #
+#################################################################################################
+if __name__ == "__main__": 
+
+    # Initialize values
+    In.init()
+    
+    if i ==0:
+    only_stable = True
+    only_CE     = False
+    channel_string = 'stable'
+
+    print('making Figure ', save_loc + '/Mass_distributions_'+ channel_string+'_SFRD_variations.pdf')
+
+    fig = plt.figure( figsize = (24, 28))
+
+    ####################################################
+    # width of SFRD at z=0
+    ####################################################
+    #add first subplot in layout that has 3 rows and 2 columns
+    subplot1 = fig.add_subplot(321)
+
+    ax1 = pltmass.plot_mass_distribution(sim_dir = data_dir, rate_file='/RateData/'+str(In.rate_file_name), simulation_data = '/'+str(In.COMPASfilename),
[…]

### 2022-09-03 src/scripts/Plot_StableMass_distributions.py
added prints and split CE and stable plot

@@ -51,7 +51,6 @@ if __name__ == "__main__":
     # Initialize values
     In.init()
     
-    if i ==0:
     only_stable = True
     only_CE     = False
     channel_string = 'stable'

### 2022-09-03 src/scripts/Plot_StableMass_distributions.py
added prints and split CE and stable plot

@@ -136,7 +136,7 @@ if __name__ == "__main__":
 
     ax5 = pltmass.plot_mass_distribution(sim_dir = data_dir,rate_file='/RateData/'+str(In.rate_file_name) , simulation_data = '/'+str(In.COMPASfilename),
                            x_key = 'M_moreMassive',  rate_keys = ['Rates_mu00.025_muz-0.049_alpha%s_sigma01.129_sigmaz0.048_a0.017_b1.481_c4.452_d5.913'%(x) for x in [0.0, -1.778, -6.0]],channel_string = channel_string,
-                           show_hist = False, show_KDE = True, , plot_LIGO = True, Color = '#acbf00', 
+                           show_hist = False, show_KDE = True, plot_LIGO = True, Color = '#acbf00', 
                            only_CE = only_CE, only_stable = only_stable,
                            bootstrap = False, bootstraps = 50, save_name = 'SFRD_skewness_variations.pdf', titletext = "Skewness of metallicity dist." +"\n"+ r"$\alpha$, (shape)", 
                            labels = [r'$\mathrm{Symmetric: \ } (\alpha = 0.0)   \ \mathcal{R}_{0.2} = \ $',

### 2022-09-03 src/scripts/Plot_Mass_distributions.py
added prints and split CE and stable plot

@@ -299,146 +299,146 @@ def plot_mass_distribution(sim_dir = '', rate_file = '', simulation_data = '',
 
 
 
-#################################################################################################
-#                                                                                               #
-#                                          Call plots                                           #
-#                                                                                               #
-#################################################################################################
-if __name__ == "__main__": 
+# #################################################################################################
+# #                                                                                               #
+# #                                          Call plots                                           #
+# #                                                                                               #
+# #################################################################################################
+# if __name__ == "__main__": 
 
-    # Initialize values
-    In.init()
+#     # Initialize values
+#     In.init()
 
-    # Run once for each channel
-    for i in range(2):
+#     # Run once for each channel
+#     for i in range(2):
         
-        if i ==0:
-            only_stable = True
-            only_CE     = False
-            channel_string = 'stable'
+#         if i ==0:
+#             only_stable = True
+#             only_CE     = False
+#             channel_string = 'stable'
             
-        else:
-            only_stable = False
-            only_CE     = True
-            channel_string = 'CE'
+#         else:
+#             only_stable = False
+#             only_CE     = True
+#             channel_string = 'CE'
 
-        print('making Figure ', save_loc + '/Mass_distributions_'+ channel_string+'_SFRD_variations.pdf')
+#         print('making Figure ', save_loc + '/Mass_distributions_'+ channel_string+'_SFRD_variations.pdf')
 
-        fig = plt.figure( figsize = (24, 28))
+#         fig = plt.figure( figsize = (24, 28))
 
-        ####################################################
-        # width of SFRD at z=0
-        ####################################################
[…]

### 2022-09-03 src/scripts/Plot_CEMass_distributions.py
added prints and split CE and stable plot

@@ -26,19 +26,37 @@ from astropy.cosmology import z_at_value
 
 import json
 import argparse
-
-# My own helper funcitons:
-import importlib
-import MassDistHelperFunctions as mfunc
-importlib.reload(mfunc)
-
 import gc
+
+# Custum scripts
+import MassDistHelperFunctions as mfunc
 import paths
 import init_values as In
-
-import time
-
 import Plot_Mass_distributions as pltmass
+
+
+######################################
+## locations
+save_loc    =  str(paths.figures) + '/'
+data_dir    =  str(paths.data) + '/'
+
+
+######################################
+## PLOT setttings
+plt.rc('font', family='serif')
+from matplotlib import rc
+import matplotlib
+matplotlib.rcParams['mathtext.fontset'] = 'stix'
+matplotlib.rcParams['font.family'] = 'STIXGeneral'
+rc('font',**{'family':'sans-serif','sans-serif':['Helvetica']})
+rc('text', usetex=True)
+fsize, SMALL_SIZE, MEDIUM_SIZE, BIGGER_SIZE = 30,25,25,30
+for obj in ['axes','xtick','ytick']:
+    plt.rc(obj, labelsize=MEDIUM_SIZE)          # controls default text sizes
+for obj in ['figure','axes']:
+    plt.rc(obj, titlesize=BIGGER_SIZE)    # fontsize of the tick labels
+plt.rc('font', size=MEDIUM_SIZE)          # controls default text sizes
+plt.rc('legend', fontsize=SMALL_SIZE)    # legend fontsize
 
 
 #################################################################################################

### 2022-09-03 src/scripts/Plot_StableMass_distributions.py

@@ -3,7 +3,6 @@
 # Plotting the stable BH mass distribution for several SFRD Z-distribution variations
 
 """
-
 import sys
 import numpy as np
 import matplotlib.pyplot as plt
@@ -26,19 +25,38 @@ from astropy.cosmology import z_at_value
 
 import json
 import argparse
-
-# My own helper funcitons:
-import importlib
-import MassDistHelperFunctions as mfunc
-importlib.reload(mfunc)
-
 import gc
+
+# Custum scripts
+import MassDistHelperFunctions as mfunc
 import paths
 import init_values as In
-
-import time
-
 import Plot_Mass_distributions as pltmass
+
+
+######################################
+## locations
+save_loc    =  str(paths.figures) + '/'
+data_dir    =  str(paths.data) + '/'
+
+
+######################################
+## PLOT setttings
+plt.rc('font', family='serif')
+from matplotlib import rc
+import matplotlib
+matplotlib.rcParams['mathtext.fontset'] = 'stix'
+matplotlib.rcParams['font.family'] = 'STIXGeneral'
+rc('font',**{'family':'sans-serif','sans-serif':['Helvetica']})
+rc('text', usetex=True)
+fsize, SMALL_SIZE, MEDIUM_SIZE, BIGGER_SIZE = 30,25,25,30
+for obj in ['axes','xtick','ytick']:
+    plt.rc(obj, labelsize=MEDIUM_SIZE)          # controls default text sizes
+for obj in ['figure','axes']:
+    plt.rc(obj, titlesize=BIGGER_SIZE)    # fontsize of the tick labels
+plt.rc('font', size=MEDIUM_SIZE)          # controls default text sizes
+plt.rc('legend', fontsize=SMALL_SIZE)    # legend fontsize
+
 
 
 #################################################################################################

### 2022-09-03 src/scripts/Plot_CEMass_distributions.py
added prints and split CE and stable plot

@@ -77,14 +77,14 @@ if __name__ == "__main__":
 
     fig = plt.figure( figsize = (24, 28))
 
-    ####################################################
+   ####################################################
     # width of SFRD at z=0
     ####################################################
     #add first subplot in layout that has 3 rows and 2 columns
     subplot1 = fig.add_subplot(321)
 
     ax1 = pltmass.plot_mass_distribution(sim_dir = data_dir, rate_file='/RateData/'+str(In.rate_file_name), simulation_data = '/'+str(In.COMPASfilename),
-                           x_key = 'M_moreMassive',  rate_keys  = ['Rates_mu00.025_muz-0.049_alpha-1.778_sigma0%s_sigmaz0.048_a0.017_b1.481_c4.452_d5.913'%(x) for x in [0.7, 1.129, 2.0]], channel_string = channel_string,
+                           x_key = 'M_moreMassive',  rate_keys  = ['Rates_mu00.025_muz-0.049_alpha-1.79_sigma0%s_sigmaz0.048_a0.017_b1.487_c4.442_d5.886'%(x) for x in [0.7, 1.129, 2.0]], channel_string = channel_string,
                            show_hist = False, show_KDE = True,  plot_LIGO = True, Color =  'navy',
                            only_CE = only_CE, only_stable = only_stable, 
                            bootstrap = False, bootstraps = 50, save_name = 'SFRD_width_variations.pdf', titletext = "Width of metallicity dist."+"\n"+r"$\omega_0$, (scale $z=0$)",
@@ -93,8 +93,8 @@ if __name__ == "__main__":
                                      r'$\mathrm{Wide: \ } \phantom{xx} (\omega_0 = 2.00) \  \mathcal{R}_{0.2} = \ $'],
                           multipanel = True, subplot = subplot1)
 
-    # 'Rates_mu00.025_muz-0.049_alpha-3.5_sigma01.129_sigmaz0.048_a0.017_b1.481_c4.452_d5.913
-    # Rates_mu00.025_muz-0.049_alpha-1.778_sigma01.129_sigmaz0.048_a0.017_b1.481_c4.452_d5.913
+    # 'Rates_mu00.025_muz-0.049_alpha-3.5_sigma01.129_sigmaz0.048_a0.017_b1.487_c4.442_d5.886
+    # Rates_mu00.025_muz-0.049_alpha-1.79_sigma01.129_sigmaz0.048_a0.017_b1.487_c4.442_d5.886
 
[…]

### 2022-09-03 src/scripts/Plot_StableMass_distributions.py

@@ -84,7 +84,7 @@ if __name__ == "__main__":
     subplot1 = fig.add_subplot(321)
 
     ax1 = pltmass.plot_mass_distribution(sim_dir = data_dir, rate_file='/RateData/'+str(In.rate_file_name), simulation_data = '/'+str(In.COMPASfilename),
-                           x_key = 'M_moreMassive',  rate_keys  = ['Rates_mu00.025_muz-0.049_alpha-1.778_sigma0%s_sigmaz0.048_a0.017_b1.481_c4.452_d5.913'%(x) for x in [0.7, 1.129, 2.0]], channel_string = channel_string,
+                           x_key = 'M_moreMassive',  rate_keys  = ['Rates_mu00.025_muz-0.049_alpha-1.79_sigma0%s_sigmaz0.048_a0.017_b1.487_c4.442_d5.886'%(x) for x in [0.7, 1.129, 2.0]], channel_string = channel_string,
                            show_hist = False, show_KDE = True,  plot_LIGO = True, Color =  'navy',
                            only_CE = only_CE, only_stable = only_stable, 
                            bootstrap = False, bootstraps = 50, save_name = 'SFRD_width_variations.pdf', titletext = "Width of metallicity dist."+"\n"+r"$\omega_0$, (scale $z=0$)",
@@ -93,8 +93,8 @@ if __name__ == "__main__":
                                      r'$\mathrm{Wide: \ } \phantom{xx} (\omega_0 = 2.00) \  \mathcal{R}_{0.2} = \ $'],
                           multipanel = True, subplot = subplot1)
 
-    # 'Rates_mu00.025_muz-0.049_alpha-3.5_sigma01.129_sigmaz0.048_a0.017_b1.481_c4.452_d5.913
-    # Rates_mu00.025_muz-0.049_alpha-1.778_sigma01.129_sigmaz0.048_a0.017_b1.481_c4.452_d5.913
+    # 'Rates_mu00.025_muz-0.049_alpha-3.5_sigma01.129_sigmaz0.048_a0.017_b1.487_c4.442_d5.886
+    # Rates_mu00.025_muz-0.049_alpha-1.79_sigma01.129_sigmaz0.048_a0.017_b1.487_c4.442_d5.886
 
     ####################################################
     # Redshift evolution of the width
@@ -103,7 +103,7 @@ if __name__ == "__main__":
     subplot2 = fig.add_subplot(322)
 
[…]

### 2022-09-04 src/tex/ms.tex
added prints and split CE and stable plot
changed legend and wrote a bit

@@
 \centering
-\script{Plot_Mass_distributions.py}
+\script{Plot_StableMass_distributions.py}
 \includegraphics[width=0.8\textwidth]{figures/Mass_distributions_stable_SFRD_variations.pdf}
@@
 \centering
-\script{Plot_Mass_distributions.py}
+\script{Plot_CEMass_distributions.py}
 \includegraphics[width=0.8\textwidth]{figures/Mass_distributions_CE_SFRD_variations.pdf}
@@
 The first thing we note is that the location of the features in the primary mass distribution are robust against variations in \SFRDzZ.
-For the CE channel, the global peak of the mass distribution remains at approximately $\Mbheen\approx16\Msun$ for all variations.
-Similarly, the stable channel displays two peaks that are visible in all variations: a peak at $\Mbheen\approx9\Msun$ and a peak at $\Mbheen\approx22\Msun$. 
-Two more peaks are visible in the stable channel at the high mass end for almost all \SFRDzZ (at $\Mbheen\approx35\Msun$ and $\Mbheen\approx45\Msun$); these peaks only fade for variations where the rate of high mass BHs is generally suppressed (dashed lines in top panel of Fig.
+For the stable channel, two features are visible in all variations: a peak at $\Mbheen\approx9\Msun$ and a bump at $\Mbheen\approx22\Msun$. 
+Two more features are visible in the stable channel at the high mass end for almost all \SFRDzZ (a knee at $\Mbheen\approx35\Msun$ and another bump at $\Mbheen\approx45\Msun$).
+Athough the locations of these features are constant, these features disappear for variations of  the metallicity-dependent cosmic star formation history where the rate of high mass BHs is suppressed (e.g., dashed lines in the top panels of Fig.
 \ref{fig: stable mass dists}).
+Similarly, the CE channel displays a kink in the distribution at about $9\Msun$, and a peak at approximately $\Mbheen\approx17\Msun$ for all variations.
+The latter peak is the global peak of the mass distribution in almost all variations.
+
+The finding that the locations of features in the mass distribution do not change for different \SFRDzZ is consistent with earlier work. 
 %
-This is consistent with the results in \cite{Broekgaarden+2021b}.
-Although peaks in the probability distribution of chirp masses as shown in their Fig.
-4 can disappear when \SFRDzZ prohibits the formation of certain (typically higher) mass BHs, the \textit{location} of features remains the same.
+Recent work by \cite{chruslinska2022_review} showed that, when comparing two very different models of \SFRDzZ (their Figure 5), the location of the peaks remains the same, even though the normalisation between the two BBH merger rates is completely different.
 %
-This result is furthermore consistent with recent findings in \cite{chruslinska2022_review}.
-In their Figure 5, they compare two very different models of \SFRDzZ and find that, although the normalisation between the two BBH merger rates is completely different, the location of the peaks remains the same.
+\cite{Broekgaarden+2021b} furthermore showed that variations in the \SFRDzZ can induce variations in the rate that are off the same order of magnitude as the variations caused by uncertainties in the binary physics.
+In their Fig.
+4, they show the probability distribution of chirp masses for BBHs.
+Although features can disappear when \SFRDzZ prohibits the formation of certain (typically higher) mass BHs, the \textit{location} of features remains the same
 %
-This implies that the \textit{locations} of features in the mass distribution of BBHs are determined by the formation channel and its underlying stellar and binary physics.
-The location of features could therefore serve as sign posts of the underlying physics.
+This implies that the locations of features in the mass distribution of BBHs are determined by the formation channel and its underlying stellar and binary physics.
+The locations of features could therefore serve as sign posts of the underlying physics.
+\\
 

### 2022-09-04 src/scripts/Plot_StableMass_distributions.py

@@ -179,8 +179,8 @@ if __name__ == "__main__":
                            show_hist = False, show_KDE = True,  plot_LIGO = True, Color = '#ecb05b', 
                            only_CE = only_CE, only_stable = only_stable,
                            bootstrap = False, bootstraps = 50, save_name = 'SFRD_skewness_variations.pdf', titletext = "Overall SFR history"+"\n"+ r'$ \mathrm{SFRD(}z\rm{)} \ [a,b,c,d]$', 
-                           labels = [r'$\mathrm{Madau \ \& \ Fragos \ 2017: } \phantom{xxxx} \ \mathcal{R}_{0.2}= \ $', 
-                                     r'$\mathrm{Fiducial: \ } \phantom{xxxxx-xxxxx-} \ \mathcal{R}_{0.2}= \ $', 
+                           labels = [r'$\mathrm{Madau \ \& \ Fragos \ 2017: } \phantom{x} \ \mathcal{R}_{0.2}= \ $', 
+                                     r'$\mathrm{Fiducial: \ } \phantom{xxxxx-xx} \ \mathcal{R}_{0.2}= \ $', 
                                      r'$\mathrm{Approx. \ to \ upper \ limit:}  \ \mathcal{R}_{0.2} = \ $'],
                             multipanel = True, subplot = subplot6)
 

### 2022-09-04 src/scripts/Plot_StableMass_distributions.py
moved to z binned

@@ -84,7 +84,7 @@ if __name__ == "__main__":
     subplot1 = fig.add_subplot(321)
 
     ax1 = pltmass.plot_mass_distribution(sim_dir = data_dir, rate_file='/RateData/'+str(In.rate_file_name), simulation_data = '/'+str(In.COMPASfilename),
-                           x_key = 'M_moreMassive',  rate_keys  = ['Rates_mu00.025_muz-0.049_alpha-1.79_sigma0%s_sigmaz0.048_a0.017_b1.487_c4.442_d5.886'%(x) for x in [0.7, 1.129, 2.0]], channel_string = channel_string,
+                           x_key = 'M_moreMassive',  rate_keys  = ['Rates_mu00.025_muz-0.049_alpha-1.79_sigma0%s_sigmaz0.048_a0.017_b1.487_c4.442_d5.886_zBinned'%(x) for x in [0.7, 1.129, 2.0]], channel_string = channel_string,
                            show_hist = False, show_KDE = True,  plot_LIGO = True, Color =  'navy',
                            only_CE = only_CE, only_stable = only_stable, 
                            bootstrap = False, bootstraps = 50, save_name = 'SFRD_width_variations.pdf', titletext = "Width of metallicity dist."+"\n"+r"$\omega_0$, (scale $z=0$)",
@@ -103,7 +103,7 @@ if __name__ == "__main__":
     subplot2 = fig.add_subplot(322)
 
     ax2 = pltmass.plot_mass_distribution(sim_dir = data_dir,rate_file='/RateData/'+str(In.rate_file_name) , simulation_data = '/'+str(In.COMPASfilename),
-                           x_key = 'M_moreMassive',  rate_keys = ['Rates_mu00.025_muz-0.049_alpha-1.79_sigma01.129_sigmaz%s_a0.017_b1.487_c4.442_d5.886'%(x) for x in [0.0, 0.048, 0.1]],channel_string = channel_string,
+                           x_key = 'M_moreMassive',  rate_keys = ['Rates_mu00.025_muz-0.049_alpha-1.79_sigma01.129_sigmaz%s_a0.017_b1.487_c4.442_d5.886_zBinned'%(x) for x in [0.0, 0.048, 0.1]],channel_string = channel_string,
                            show_hist = False, show_KDE = True,  plot_LIGO = True, Color = '#00a6a0', 
                            only_CE = only_CE, only_stable = only_stable,
[…]

### 2022-09-06 src/tex/ms.tex
changed to Z per Zsun

@@
 %%%%%%%%%%%%%%%
-\author[0000-0002-8901-6994]{L. Hernquist}
+\author[0000-0001-6950-1629]{L. Hernquist}
 \affiliation{Center for Astrophysics $|$ Harvard $\&$ Smithsonian, 60 Garden St., Cambridge, MA 02138, USA}
@@
 Such models require the metallicity-dependent cosmic star formation history (\SFRDzZ) as an input.
-Large uncertainties remain in the shape and evolution of this function.%and understanding its behaviour is essential to explain simulation results.
+Large uncertainties remain in the shape and evolution of this function.
 In this work, we propose a simple analytical function for \SFRDzZ. 
 Variations of this function can be easily interpreted, because the parameters link to its shape in an intuitive way. 
-%Our hope is that this expression provides a useful starting point for making predictions and comparison with observations.
 We fit our analytical function to the star-forming gas of the cosmological TNG100 simulation and find that it is able to capture the main behaviour well. 
@@
 This is promising as it increases our chances to constrain the physics that governs the formation of these objects.
-% We further find that: III) the skewness, mean, and width of the metallicity distribution at low redshift affect the overall rate, while IV) the redshift evolution of the width and the mean of the metallicity distribution affects the slope at the high-mass end of the distribution.
-% IV) the shape of the overall star-formation rate density has a small impact on the local mass distribution.
 \end{abstract}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%opening from Chruslinska & Nelemans. Crucially needed are simple prescriptions
-% 2 ways in which we can tackle this: observationally or theoretically
-% 3 problemen met waarnemingen: 1) high redshift cant see, 2) metallicity measurements 3) xx?
-% Theoretical: issues with illustris 1, here we provide a simple  fit to 
-% give zenodo + data
-% dan een beetje science 
-% Er zijn allemaal BBH detecties, super leuk
-% Om de rate te bedenken moeten we niet alleen numbe of meging BBH maar ook SFRD
-% In dit paper geven we een nieuwe SFRD fit
-
-% Er zijn vechillende manieren om een SFRD meer te geven
 
@@
 
-% combines a  with an approximation of the metallicity distribution that
 The first method is based on empirical scaling relations, linking galaxy properties like stellar mass $M_{\star}$, metallicity $Z$, and overall star-formation rate density \SFRDz, with the GSMF galaxy stellar mass function, GSMF \citep[see e.g.][]{Dominik+2013}.
@@
 
-% \citep[see e.g.][]{Chruslinska+2018, Chruslinska2019_effectCO, Broekgaarden+2021a}.
 One can also directly extract the metallicity-dependent cosmic star formation history from cosmological simulations \citep[e.g.][]{Mapelli2017, Briel+2022_rates}.
@@
 
-%Arguments: cosmological simulations work at high z,  but are they real? observations 
 In this work we follow the latter approach and propose a flexible analytical model for \SFRDzZ that can be fit to the output of both cosmological simulations, and observational data constraints where available.
@@
 Secondly, both the large complications in observational constraints, and the many uncertainties in cosmological simulations call for a generalised form of \SFRDzZ that can be easily updated when new information becomes available.
-% which is the motivation for this work.
 In particular, the advent of observations with the James Webb Space Telescope promises a new era of high-redshift
 metallicity studies of previously unexplored regimes \citep[e.g.,][]{Sanders+2022}. We hope that this form will facilitate the flexibility needed to keep up with observations.
-% we hope that this form will facilitate a more sensible way for useful inference on large (future) datasets of astrophysical transients, such as the ever growing catalogue of gravitational wave transients.
-Our hope is that the constraints on the free parameters in the analytical form we propose, can provide a more useful guidance when comparing with the outcome of the predictions of cosmological simulations.
-
-% is to allow for an intuitive interpretation of the effects of the \SFRDzZ on the inferred rates of astrophysical transients.
-By adopting an analytical, parametrized form for \SFRDzZ, the large uncertainties in \SFRDzZ can be systematically explored.% through varying the parameters that control its shape.
 
@@
 Throughout this work, we adopt a universal Kroupa initial mass function \citep{Kroupa2001} with the mass
-limits $0.01–200\Msun$ and a flat $\Lambda$CDM cosmology with $\Omega_{\rm{M}}=0.31$, $\Omega_{\rm{\Lambda}}=0.69$ and $H_0=67.7\rm{km\,s^{-1}\,Mpc^{-1}}$ \citep{Planck18_VI}.
+limits $0.01 - 200\Msun$ and a flat $\Lambda$CDM cosmology with $\Omega_{\rm{M}}=0.31$, $\Omega_{\rm{\Lambda}}=0.69$ and $H_0=67.7\rm{km\,s^{-1}\,Mpc^{-1}}$ \citep{Planck18_VI}.
 
@@
 %% SFR(z) %%
-
-% $a=0.02$, $b=1.48$, $c=4.45$ and $d=5.9$ as best fitting parameters,
 \subsection{The cosmic metallicity density distribution}
@@
 The skewed-log-normal distribution of metallicities is defined as:
-% See eq. 1 here: https://www.emis.de/journals/RCE/V36/v36n1a03.pdf
 \begin{equation}
@@
  \phi \left(\frac{\ln Z - \xi}{\omega}\right) \equiv 
-% \underbrace{
     \frac{1}{\sqrt{2 \pi}} 
@@
         }
-  %  }_{(1)} 
     \end{equation}
@@
 where $\mu_0
-%= 0.025 
 $ is the mean metallicity at redshift 0, and $\mu_z
-%= -0.048
 $ determines redshift evolution of the location. Equating this to Equation~\ref{eqn:Zmean}, we get an expression for $\xi(z)$,
-
-% \begin{equation}
-% \label{eq mu z}
-%     \xi(z) = -\frac{\omega^2}{2}\, \ln\left(\frac{  \mu_0 \cdot 10^{\mu_z \cdot z} }{2\, \Phi(\beta\, \omega)}  \right).
-% \end{equation}
 
@@
 where $\omega_0$ is
-%$\omega_0 = 1.125$, 
 the width of the metallicity distribution at $z=0$, and $\omega_z$
-%$\omega_z = 0.048$, 
 the redshift evolution of the scale.
@@
 
-%, and our fit value for $\alpha = -1.77$. Our set of parameters for \dpdZ is thus:  $\mu_0 = 0.025, \mu_z = -0.048, \omega_0 = 1.125, \omega_z = 0.048$ and $\alpha = -1.77$.
-
 \subsection{The overall cosmic star formation rate density}
@@
 
-% \subsection{Combined function}
 Lastly, we combine equations \ref{eq: z log skew} and \ref{eq: sfr1} to form a full metallicity specific star formation rate density as described in equation \ref{eq: total sfrd}.
@@
 The bottom left (right) panel shows slices of the distribution in redshift (metallicity).
-Each slice is displaced by 0.01$\Msun \yr^{-1}\Mpc^{-3}$ (note the linear scale of \SFRDzZ in the bottom channel).
+Each slice is displaced by 0.01$\Msun \yr^{-1}\Mpc^{-3}$ (note the linear scale of \SFRDzZ in the bottom panel).
 We show the TNG100 simulation data with thick gray lines.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Both the large observational uncertainties in \SFRDzZ (as discussed in section \ref{sec: intro}), and the many uncertainties in cosmological simulations (as discussed below) call for a generalised form of the \SFRDzZ that can be easily updated when new information becomes available, which is the motivation for this work.
-% In particular, the advent of observations with the James Webb Space Telescope promises a new era of high-redshift% metallicity studies in previously unexplored regimes \citep[e.g.,][]{Sanders+2022}.
-%
 Although here, we only fit our model to the TNG100 simulation, our prescription can be easily be used to fit other simulated or observational data of the metallicity-dependent cosmic star formation history\footnote{We provide a Jupyter notebook to facilitate this fit here: \url{https://github.com/LiekeVanSon/SFRD_fit/blob/main/src/scripts/Fit_To_Cosmological_Simulation.ipynb} }.
@@
 In particular of interest for this work, they simulate the high redshift enrichment of galaxies and the tail of low metallicity star formation at low redshift.
-% Different cosmological simulations produce varying \SFRDzZ, depending on the adopted assumptions about the creation and distribution of metals.
 
@@
 The TNG simulations have been shown to match observational constraints on the mass-metallicity relation of galaxies up to $z = 2$ \citep{Torrey+2019}, as well as iron abundances \citep{FirstResTNG_Naiman2018}, metallicity gradients within galaxies at low redshift \citep{Hemler+2021}, and the reduction of star formation in the centers of star-forming galaxies \citep{Nelson2021}.
-%They reproduce the evolution of the sizes of galaxies with redshift \citep{Genel+2018}
 Several studies have used the TNG simulations to make predictions for astronomical transient sources \citep[e.g.][]{Briel+2022_rates,Bavera+2022,vanson+2022}. 
 Out of the four \SFRDzZ variations explored, \cite{Briel+2022_rates} find that TNG provides one of the best agreements between observed and predicted cosmic rates for electromagnetic and gravitational-wave transients, when combined with their fiducial binary population synthesis model.
-% TNG50 has higher res, but that also leads to higher stellar masses at fixed halo mass."
 
@@
 Here, the variable $Z_i$ runs over all metallicity bins.
-%, but excludes bins where the star formation rate density is lower $10^{-10} \Msun \yr \Mpc^{-3}$ per bin. 
-% Subsequently we sum the $\chi^2 (z_j)$ for all redshift bins $z_j$. 
 We are particularly interested in properly fitting the low metallicity star formation at high redshifts.
@@
         {\sum_{Z_i} \mathcal{S}(Z_i,z_j)}
-    %chi_square = ((obs - model )**2)/np.sum(model) 
 \end{equation}
@@
 We will refer to the \SFRDzZ with the parameters listed in Table \ref{tab: fit params} as our fiducial model.
-% With the fit parameters as mentioned above, we find a maximum residual between the model and the TNG100 data of $2.3\cdot 10^{-3} \Msun \yr^{-1} \Mpc^{-3}$ at any given redshift.
 
@@
 }
-% The \SFRDzZ from \cite{Neijssel+2019} was optimised to match the local rate of double compact object mergers as presented in the second gravitational-wave catalogue.
-However, the resulting symmetric distribution cuts-off virtually all low-metallicity ($Z\leq 10^{-2.5}$) star formation.
-
-% For both \SFRDzZ distributions, most star formation happens at metallicities above $Z \geq 10^{-2}$ (top panel).
 
 Although our model preforms well at reproducing the large scale trends seen in TNG, we acknowledge that more complex features as suggested by some observational studies could be missed.
-One example is that the \SFRDz shape we adopt from \cite{MadauDickinson2014} does not account for starburst galaxies \citep[see discussion in][]{Chruslinska2019_obs}.
+One example is that the \SFRDz shape we adopt from \cite{MadauDickinson2014} does not account for starburst galaxies \citep[see discussion in][]{Chruslinska+2021}.
 Moreover, our model cannot capture inflection points in the mean metallicity, because we assume both $\mu_0$ and $\mu_z$ are constants with redshift (equation \ref{eq: mean Z}).
@@
 
-We use the publicly available rapid binary population synthesis simulations presented in \cite{vanson+2022}. 
-These simulations were run using version v02.19.04 of the open source \COMPAS suite \citep{COMPAS_method}\footnote{\url{https://github.com/TeamCOMPAS/COMPAS}}.
+We use the publicly available rapid binary population synthesis simulations presented in van Son et al (in prep).\footnote{Available for download at \url{https://doi.org/10.5072/zenodo.1098287},  see also the Software and Data section in the acknowledgements}
+These simulations were run using version v02.26.03 of the open source \COMPAS suite \citep{COMPAS_method}\footnote{\url{https://github.com/TeamCOMPAS/COMPAS}}.
 \COMPAS is based on algorithms that model the evolution of massive binary stars following \citet{Hurley+2000, Hurley+2002} using detailed evolutionary models by \citet{Pols+1998}.
@@
 We show all \SFRDz variations in Figure~\ref{fig: SFR(z)}. \\
-%30*f14SBBiC
-% low_Z_file = '214f14SBBiC_FMR270_FOH_z_dM.dat'            
-% high_Z_file = '302f14SBBoco_FMR270_FOH_z_dM.dat'
 
@@
 For the stable channel, two features are visible in all variations: a peak at $\Mbheen\approx9\Msun$ and a bump at $\Mbheen\approx22\Msun$. 
-Two more features are visible in the stable channel at the high mass end for almost all \SFRDzZ (a knee at $\Mbheen\approx35\Msun$ and another bump at $\Mbheen\approx45\Msun$).
-Athough the locations of these features are constant, these features disappear for variations of  the metallicity-dependent cosmic star formation history where the rate of high mass BHs is suppressed (e.g., dashed lines in the top panels of Fig.
+Two more features are visible in at the high mass end for almost all \SFRDzZ; a knee at $\Mbheen\approx35\Msun$ and another bump at $\Mbheen\approx45\Msun$.
+Although the locations of these features are constant, the features themself can disappear for variations that suppress the rate of high mass BHs (e.g., dashed lines in the top panels of Fig.
 \ref{fig: stable mass dists}).
@@
 %
-\cite{Broekgaarden+2021b} furthermore showed that variations in the \SFRDzZ can induce variations in the rate that are off the same order of magnitude as the variations caused by uncertainties in the binary physics.
-In their Fig.
-4, they show the probability distribution of chirp masses for BBHs.
-Although features can disappear when \SFRDzZ prohibits the formation of certain (typically higher) mass BHs, the \textit{location} of features remains the same
+Furthermore, \cite{Broekgaarden+2021b} show the probability distribution of chirp masses for BBHs in their Fig.
+4.
+Although features can disappear when the \SFRDzZ prohibits the formation of certain (typically higher) mass BHs, the \textit{location} of features remains the same.
 %
@@
 To quantify this, we annotate the ratio between the maximum and minimum rate at three reference masses; \Mbheen = $10, 25$, and $40\Msun$.
-At $\Mbheen=10\Msun$, we find that the rate changes by at most a factor of about 3.5 for the stable channel, and at most about a factor of 6.5 for the CE channel. 
-On the other hand, the change in rate at $\Mbheen=40\Msun$ can be as high as a factor of about 110 and 60 for the stable and CE channels, respectively. 
+At $\Mbheen=10\Msun$, we find that the rate changes by at most a factor of about 3.7 for the stable channel, and at most about a factor of 3.8 for the CE channel. 
+On the other hand, the change in rate at $\Mbheen=40\Msun$ can be as high as a factor of about 200 and 150 for the stable and CE channels, respectively. 
 %
@@
 %
-The low mass end of the mass distribution of merging double compact objects will also provide a particularly powerful cosmological constraint in the era of third generation gravitational wave telescopes \citep{MariaEzquiaga2022}.
+The low-mass end of the mass distribution of merging double compact objects will also provide a particularly powerful cosmological constraint in the era of third generation gravitational wave telescopes \citep{MariaEzquiaga2022}.
 Our finding that the low mass end is more robust against variations in \SFRDzZ supports this claim.
@@
 %
-Variations that \textit{increase} the amount of star formation at low metallicity (i.e.
+Variations that increase the amount of star formation at low metallicity (i.e.
 for a low mean metallicity $\mu_0=0.007$ and a wide metallicity distribution $\omega_0 = 2.0$ ) increase the predicted BBH merger rate.
@@
 Hence, the local rate of BBH mergers is lower for the skewed distribution ($\alpha = -6$) with respect to the symmetric variation ($\alpha = 0.0$).
-% However, the total rate of BBH mergers is only changed by about a factor of 2.
 
@@
 As discussed in Section \ref{ss: reasonable var}, we use \cite{Madau+2017} and the solid blue line in Figure \ref{fig: SFR(z)} as an approximate lower and upper bound to the \SFRDz respectively. 
-The model from \cite{Madau+2017} is very similar to our fiducial model (Figure \ref{fig: SFR(z)}), and the differences between the resulting mass distributions are correspondingly small.
+The overall cosmic star formation rate density from \cite{Madau+2017} is very similar to our fiducial model (Figure \ref{fig: SFR(z)}), and the differences between the resulting mass distributions are correspondingly small.
 Our approximation of the upper limit to the allowed \SFRDz leads to an overall increase of the BBH merger rate by a factor of about 3.
@@
 We fit our analytical expression for \SFRDzZ to the star-forming gas in the TNG100 simulation, and provide the best fit parameters in Table \ref{tab: fit params}.
-% We fit our analytical expression for \SFRDzZ to the star-forming gas in the TNG100 simulation.
 We show that our model captures the shape and general behaviour of the cosmological simulations well (Figure \ref{fig: fit SFRD}). 
@@
 Our hope is that this expression will provide a useful starting point for making predictions and comparisons with observations.
-% As such, we anticipate that it will be a helpful tool in other works that present \SFRDzZ dependent rates.
 
@@
 % Code and Data 
-The data used in this work is available on Zenodo under an open-source Creative Commons Attribution license at \todo{dataset}.
+All code associated to reproduce the data and plots in this paper is publicly available at \url{https://github.com/LiekeVanSon/SFRD_fit}.
+The data used in this work is available on Zenodo under an open-source Creative Commons Attribution license at \dataset[doi:10.5072/zenodo.1098287]{https://doi.org/10.5072/zenodo.1098287}.
 % \dataset[doi:10.5281/zenodo.5544170]{https://doi.org/10.5281/zenodo.5544170}.
-Data from \cite{Chruslinska+2021} for the observational stuff can be found: \url{https://ftp.science.ru.nl/astro/mchruslinska/Chruslinska_et_al_2021/}
+All observationally constrained models of the \SFRDzZ from \cite{Chruslinska+2021} can be found online at: \url{https://ftp.science.ru.nl/astro/mchruslinska/Chruslinska_et_al_2021/}.
 
@@
 Virgo is funded, through the European Gravitational Observatory (EGO), by the French Centre National de Recherche Scientifique (CNRS), the Italian Istituto Nazionale di Fisica Nucleare (INFN) and the Dutch Nikhef, with contributions by institutions from Belgium, Germany, Greece, Hungary, Ireland, Japan, Monaco, Poland, Portugal, Spain.
-
 Further software used in this work: Python \citep{PythonReferenceManual},  Astropy \citep{astropy:2013,astropy:2018} Matplotlib \citep{2007CSE.....9...90H},  {NumPy} \citep{2020NumPy-Array}, SciPy \citep{2020SciPy-NMeth}, \texttt{ipython$/$jupyter} \citep{2007CSE.....9c..21P, Kluyver2016jupyter},  Seaborn \citep{waskom2020seaborn}  and  {hdf5}   \citep{collette_python_hdf5_2019}.
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \section{Yield per metallicity and mass \label{app: mass metal yield}}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% The yield of merging BBH with certain masses, per star forming mass per metallicity
-
-%%%%%%%%%%%%%%%%%%%%%
-% Rate - mass
-% \begin{figure}
-% \includegraphics[width=0.49\textwidth]{figures/yield_per_mass_and_metals.png} 
-% \caption{The yield of merging BBH with certain masses, per star forming mass per metallicity}
-% \end{figure}
-%%%%%%%%%%%%%%%%%%%%%
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2022-09-06 src/scripts/FitComparison_3panelPlot.py

@@ -54,6 +54,8 @@ if __name__ == "__main__":
     # Initialize values
     In.init()
 
+    Zsun = 0.014 # Solar metallicity
+
     mu0_best, muz_best, omega0_best, omegaz_best, alpha0_best,sf_a_best, sf_b_best, sf_c_best, sf_d_best = np.loadtxt(str(paths.data)+'/'+In.fit_param_filename,unpack=True, delimiter=',')
     # mu0_best, muz_best, sigma0_best, sigmaz_best, alpha0_best,sf_a_best, sf_b_best, sf_c_best, sf_d_best = np.loadtxt(data_dir+ '/best_fit_parameters.txt',unpack=True)
     # #####################################
@@ -180,7 +182,7 @@ if __name__ == "__main__":
             ######################################
             # now actually plot it
             tng_color = sns.light_palette("#fe875d", as_cmap=True, n_colors = 7) # construct smooth cmap from one colour
-            TNG = ax.pcolormesh(Obs_Lookbacktimes, Obs_center_Zbin, Obs_cosmic_SFR/step_obs_logZ, 
+            TNG = ax.pcolormesh(Obs_Lookbacktimes, Obs_center_Zbin/Zsun, Obs_cosmic_SFR/step_obs_logZ, 
                                 rasterized=True, norm=matplotlib.colors.LogNorm(vmin=1e-8,vmax=1e-1), 
                                 cmap=tng_color, alpha=0.95 ) #matplotlib.cm.YlGnBu
             cbaxes1 = fig.add_axes([0.925, 0.1, 0.03, 0.8]) #[left, bottom, width, height]
@@ -210,7 +212,7 @@ if __name__ == "__main__":
             #####################################
             COMPAS_cmap = sns.color_palette(FITkleur, as_cmap=True)
             
-            cs = ax.contour(high_res_t, high_res_metals, model_SFRD/step_logZ, levels, linewidths=4, cmap=COMPAS_cmap,
+            cs = ax.contour(high_res_t, high_res_metals/Zsun, model_SFRD/step_logZ, levels, linewidths=4, cmap=COMPAS_cmap,
                              locator=ticker.LogLocator(), alpha = 0.95, zorder=0)
             ax.clabel(cs,inline=1,fontsize=20, levels = levels, use_clabeltext=True, fmt = '%.0e')
 
@@ -242,7 +244,7 @@ if __name__ == "__main__":
 
             greys = cm.get_cmap('Greys')
[…]

### 2022-09-07 src/tex/ms.tex
made rate data static

@@
 % Define document class
-\documentclass[twocolumn]{aastex631}
+\documentclass[linenumbers,twocolumn]{aastex631}
 \usepackage{showyourwork}
@@
 
-% Title
-% \title{ A flexible and intuitive analytic expression for the metallicity-dependent cosmic star formation history  }
-% \title{ A flexible expression for the metallicity-dependent cosmic star formation history: }
-% \title{The location of features in the mass distribution of merging binary black holes does not depend on the metallicity-dependent cosmic star formation history.}
 \title{The locations of features in the mass distribution of merging binary black holes are robust against uncertainties in the metallicity-dependent cosmic star formation history.}
@@
 
-We use the publicly available rapid binary population synthesis simulations presented in van Son et al (in prep).\footnote{Available for download at \url{https://doi.org/10.5072/zenodo.1098287},  see also the Software and Data section in the acknowledgements}
+We use the publicly available rapid binary population synthesis simulations presented in van Son et al (in prep).\footnote{Available for download at \url{https://sandbox.zenodo.org/record/1101303},  see also the Software and Data section in the acknowledgements}
 These simulations were run using version v02.26.03 of the open source \COMPAS suite \citep{COMPAS_method}\footnote{\url{https://github.com/TeamCOMPAS/COMPAS}}.
@@
 By integrating over cosmic history, we obtain the local merger rates of BBH systems, which allow us to construct the distribution of source properties at every redshift.
-The details of this framework are described in \cite{vanson+2022}, but also in \cite{Broekgaarden+2021a} and \cite{Neijssel+2019}.
+We use the cosmic integration scheme that is part of the publicly available \COMPAS suite.
+The details of this framework are described in \cite{Neijssel+2019}, but also in \cite{vanson+2022}, where more similar settings to this work are used.
 
@@
 All code associated to reproduce the data and plots in this paper is publicly available at \url{https://github.com/LiekeVanSon/SFRD_fit}.
-The data used in this work is available on Zenodo under an open-source Creative Commons Attribution license at \dataset[doi:10.5072/zenodo.1098287]{https://doi.org/10.5072/zenodo.1098287}.
+The data used in this work is available on Zenodo under an open-source Creative Commons Attribution license at \dataset[10.5072/zenodo.1101303]{https://sandbox.zenodo.org/record/1101303}.
 % \dataset[doi:10.5281/zenodo.5544170]{https://doi.org/10.5281/zenodo.5544170}.

### 2022-09-07 src/scripts/FitComparison_3panelPlot.py

@@ -15,7 +15,6 @@ from astropy.cosmology import Planck18  as cosmo# Planck 2018
 from astropy.cosmology import z_at_value
 from astropy.table import Table
 
-
 from matplotlib import rc
 import matplotlib
 from matplotlib import ticker, cm

### 2022-09-07 src/scripts/LowHighZ_fraction.py

@@ -23,7 +23,6 @@ import get_ZdepSFRD as Z_SFRD
 import importlib
 import init_values as In
 
-
 ############################
 ##PLOT setttings
 from matplotlib import rc

### 2022-09-07 src/scripts/Plot_StableMass_distributions.py

@@ -1,7 +1,5 @@
 """
-
 # Plotting the stable BH mass distribution for several SFRD Z-distribution variations
-
 """
 import sys
 import numpy as np

### 2022-09-07 src/scripts/SFR_z.py

@@ -16,7 +16,6 @@ import get_ZdepSFRD as Z_SFRD
 import paths
 import init_values as In
 
-
 ######################################
 ## locations
 save_loc    =  str(paths.figures) +'/'

### 2022-09-07 src/scripts/LowHighZ_fraction.py
usetex false

@@ -31,7 +31,7 @@ matplotlib.rcParams['mathtext.fontset'] = 'stix'
 matplotlib.rcParams['font.family'] = 'STIXGeneral'
 rc('font',**{'family':'sans-serif','sans-serif':['Helvetica']})
 plt.rc('font', family='serif')
-rc('text', usetex=True)
+rc('text', usetex=False)
 fsize, SMALL_SIZE, MEDIUM_SIZE, BIGGER_SIZE = 30,20,20,30
 for obj in ['axes','xtick','ytick']:
     plt.rc(obj, labelsize=MEDIUM_SIZE)          # controls default text sizes

### 2022-09-07 src/scripts/SFR_z.py

@@ -27,7 +27,7 @@ matplotlib.rcParams['mathtext.fontset'] = 'stix'
 matplotlib.rcParams['font.family'] = 'STIXGeneral'
 rc('font',**{'family':'sans-serif','sans-serif':['Helvetica']})
 plt.rc('font', family='serif')
-rc('text', usetex=True)
+rc('text', usetex=False)
 fsize, SMALL_SIZE, MEDIUM_SIZE, BIGGER_SIZE = 30,20,20,30
 for obj in ['axes','xtick','ytick']:
     plt.rc(obj, labelsize=MEDIUM_SIZE)          # controls default text sizes

### 2023-01-24 src/tex/ms.tex
added talks to ignore
addressed minor comments from review

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\todo{Make sure to address the difference in rate between this paper and \citep{vanson2022_lowMbh}!}
 A myriad of astrophysical phenomena depend critically on the rate of star formation throughout the cosmic history of the Universe.
@@
 
-The first method is based on empirical scaling relations, linking galaxy properties like stellar mass $M_{\star}$, metallicity $Z$, and overall star-formation rate density \SFRDz, with the GSMF galaxy stellar mass function, GSMF \citep[see e.g.][]{Dominik+2013}.
+The first method is based on empirical scaling relations, linking galaxy properties like stellar mass $M_{\star}$, metallicity $Z$, and overall star-formation rate density \SFRDz, with the galaxy stellar mass function, GSMF \citep[see e.g.][]{Dominik+2013}.
 However, the applied methods to infer galaxy properties and subsequently scaling relations such as the MZ-relation differ greatly, which makes it difficult to interpret these results in a consistent way \citep[e.g.,][]{KewleyEllison2008,MaiolinoMannucci2019,Cresci+2019}.
@@
 For the probability distribution of metallicities we draw inspiration from the approach by e.g., \cite{Neijssel+2019} who used a log-normal distribution for their phenomenological model.
-Unfortunately, this expression does not capture the asymmetry well that we see in the results of the cosmological simulations, which show an extended tail in  $\log_{10} Z$ towards low metallicity, combined with a very limited tail towards higher metallicity.
+\edit1{Unfortunately, a simple log-normal distribution cannot capture the asymmetry that we see in the cosmological simulations}, which show an extended tail in  $\log_{10} Z$ towards low metallicity, combined with a very limited tail towards higher metallicity.
 To capture this behaviour we adopt a skewed-log-normal distribution instead.
@@
 \label{eq: pure log skew}
-\mathrm{\frac{dP}{dZ}}(Z) &= \frac{1}{Z} \times \frac{\rm dP}{{\rm d}\ln Z}  \\
+\mathrm{\frac{dP}{dZ}}(Z, z) &= \frac{1}{Z} \times \frac{\mathrm{dP(}Z,z) }{{\rm d}\ln Z}  \\
 &= \frac{1}{Z} \times \frac{2}{\omega}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}
-\centering
-\script{FitComparison_3panelPlot.py}
-\includegraphics[width=0.9\textwidth]{figures/SFRD_FIT_evaluation_compare.pdf}
-\caption{Our fiducial \SFRDzZ model, adopting the best fitting parameters (listed on the top right) to fit the TNG100 simulations.
-The top panel shows the full two dimensional \SFRDzZ linear in time.
-Contours range from $10^{-7} - 10^{-2} \Msun \yr^{-1}\Mpc^{-3}$.
-The bottom left (right) panel shows slices of the distribution in redshift (metallicity).
-Each slice is displaced by 0.01$\Msun \yr^{-1}\Mpc^{-3}$ (note the linear scale of \SFRDzZ in the bottom panel).
-We show the TNG100 simulation data with thick gray lines.
-For comparison, we also show the phenomenological model from \protect\cite{Neijssel+2019} in all panels with grey dotted lines.
-The bottom panels show that our analytical model adequately captures the shape of the \SFRDzZ from TNG100.
- \label{fig: fit SFRD}}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 We fit our new functional form of \SFRDzZ as defined by equations \ref{eq: total sfrd}, \ref{eq: z log skew} and \ref{eq: sfr1} to the IllustrisTNG cosmological simulations. 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Although here, we only fit our model to the TNG100 simulation, our prescription can be easily be used to fit other simulated or observational data of the metallicity-dependent cosmic star formation history\footnote{We provide a Jupyter notebook to facilitate this fit here: \url{https://github.com/LiekeVanSon/SFRD_fit/blob/main/src/scripts/Fit_To_Cosmological_Simulation.ipynb} }.
+Although here, we only fit our model to the TNG100 simulation, our prescription can be easily be used to fit other simulated or observational data of the metallicity-dependent cosmic star formation history\footnote{\edit1{We provide a Jupyter notebook to facilitate this fit here: \url{https://github.com/LiekeVanSon/SFRD_fit/blob/main/src/scripts/Notebooks/Fit_model_to_sfrdzZ.ipynb} } }.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}
+\centering
+\script{FitComparison_3panelPlot.py}
+\includegraphics[width=0.9\textwidth]{figures/SFRD_FIT_evaluation_compare.pdf}
+\caption{Our fiducial \SFRDzZ model, adopting the best fitting parameters (listed on the top right) to fit the TNG100 simulations.
+The top panel shows the full two dimensional \SFRDzZ linear in time.
+Contours range from $10^{-7} - 10^{-2} \Msun \yr^{-1}\Mpc^{-3}$.
+The bottom left (right) panel shows slices of the distribution in redshift (metallicity).
+Each slice is displaced by 0.01$\Msun \yr^{-1}\Mpc^{-3}$ (note the linear scale of \SFRDzZ in the bottom panel).
+We show the TNG100 simulation data with thick gray lines.
+For comparison, we also show the phenomenological model from \protect\cite{Neijssel+2019} in all panels with grey dotted lines.
+The bottom panels show that our analytical model adequately captures the shape of the \SFRDzZ from TNG100.
+ \label{fig: fit SFRD}}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 Our best fitting parameters are listed in Table \ref{tab: fit params}.
@@
 \tablecaption{Best fitting parameters for our \SFRDzZ fit to TNG100 data.}
-\tablehead{\colhead{dP/dZ } & \colhead{description} & \colhead{best fit} & \colhead{SFRD(z)} & \colhead{best fit} } 
+\tablehead{\colhead{dP/dZ } & \colhead{description} & \colhead{best fit} &  \colhead{SFRD(z)} & \colhead{best fit} \\
+ \colhead{ } & \colhead{} & \colhead{}  & \colhead{$\Msun\yr^{-1}\Mpc^{-3}$} & \colhead{} } 
 \startdata
-$\mu_0$    & mean metallicity at $z=0$    & $0.025  \pm 0.001$ &  $a$ &  $0.02 \pm 0.05 \, \Msun\yr^{-1}\Mpc^{-3}$\\
+$\mu_0$    & mean metallicity at $z=0$    & $0.025  \pm 0.001$ &  $a$ &  $0.02 \pm 0.05$ \\% \, \Msun\yr^{-1}\Mpc^{-3}$\\
 $\mu_z$    & $z$-dependence of the mean   & $-0.048 \pm 0.001$ &  $b$ &  $1.48 \pm 0.01$\\
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}
-\centering
-\script{SFR_z.py}
-\includegraphics[width=0.47\textwidth]{figures/SFR_redshift.pdf}
-\includegraphics[width=0.47\textwidth]{figures/SFR_tlookback.pdf}
-\caption{Comparison of several overall star-formation rate densities, \SFRDz,  with redshift (left panel) and with lookback time (right panel).
-The solid orange and dashed red lines respectively show the star formation data from TNG100 and our corresponding fit adopting eq.
-\ref{eq: sfr1} (fiducial model).
-The dotted gray and solid blue lines are variations of eq.
-\ref{eq: sfr1} used to approximate the lower and upper edge of possible star-formation histories.
-The dotted gray line shows the model from \cite{Madau+2017}, while the solid blue line mimics the behaviour of the powerlaw-fit to the \texttt{SB: B18/C17} variations with a non-evolving low-mass end of the galaxy stellar mass function from \cite{Chruslinska+2021}.
-\label{fig: SFR(z)}}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 To determine the range that is reasonably allowed by observations, we compare our variations to the observation-based \SFRDzZ models described in \cite{Chruslinska+2021}.
+\edit1{An overview of the explored variations is shown in Table \ref{tab: fit variations}. Below we explain how we arrive at these values.  }
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{deluxetable}{cccc}
+\label{tab: fit variations}
+\tablewidth{0.5\textwidth} 
+\tablecaption{\edit1{Variations on \SFRDzZ. 
+For every variation, we either swap the value of an individual \dpdZ parameter, or exchange the set of four \SFRDz parameters, and replace them by the the min/max values listed here.
+All other parameters are kept fixed at their fiducial value.
+}}
+\tablehead{\colhead{} & \colhead{min} & \colhead{fiducial} & \colhead{max} } 
+\startdata
+\dpdZ &       &  &  \\
+$\mu_0$          &   0.007   & $0.025$  &  0.035  \\
+$\mu_z$          &   0.0   & $-0.048$ &   -0.5 \\
+$\alpha$         &   -6.0   & $-1.767$ &  0.0  \\
+$\omega_0$       &   0.7   & $1.125$  &  2.0  \\
+$\omega_z$       &   0.0   & $0.048$  &  0.1  \\ \hline
+\SFRDz &       &  &  \\
+($a$,$b$ ... &  ($0.01$, $2.60$   & ($0.02$, $1.48$ &  ($0.03$, $2.6$ \\
+... $c$,$d$) &  $3.20$, $6.20$)   & $4.45$, $5.90$) &   $3.3$, $5.9$) \\
+% \parbox{1.75cm}{($a$,$b$, \hspace{0.7cm} $c$,$d$)} &  \parbox{1.75cm}{($0.01$, $2.60$, $3.20$, $6.20$)}   & \parbox{1.75cm}{($0.02$, $1.48$, $4.45$, $5.90$)} &  \parbox{1.75cm}{($0.03$, $2.6$, $3.3$, $5.9$)} \\
+\enddata
+\end{deluxetable}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 For each variation, we inspect the fraction of stellar mass that is formed at low-metallicity ($Z<0.1 Z_{\odot}$) versus the fraction of stellar mass that is formed at high-metallicity ($Z> Z_{\odot}$), for all star formation that occurred below a certain threshold redshift.
-We compare this to the models from \cite{Chruslinska+2021}\footnote{These models are publicly available at \url{https://ftp.science.ru.nl/astro/mchruslinska/Chruslinska_et_al_2021/}} in Figure \ref{fig: low high Z fraction} in Appendix \ref{app: reasonable var}.
+We compare this to the models from \cite{Chruslinska+2021} in Figure \ref{fig: low high Z fraction} in Appendix \ref{app: reasonable var}.
 We have chosen our variations such that they span a reasonable range of cosmic metallicity density distributions as allowed by observation-based and cosmological simulations-based models.
-We use the models \texttt{214f14SBBiC\_FMR270\_FOH\_z\_dM.dat}, and \texttt{302f14SBBoco\_FMR270\_FOH\_z\_dM.dat} from \cite{Chruslinska+2021} as a representation of a very low and high metallicity star formation realisation respectively.
-These models are the low and high metallicity extreme under their fiducial SFR–metallicity correlation.
+We use the models \texttt{214-f14SB-BiC\_FMR270\_FOH\_z\_dM.dat}, and \texttt{302-f14SB-Boco\_FMR270\_FOH\_z\_dM.dat} from \cite{Chruslinska+2021}\footnote{These models \edit1{ including a detailed description of their contents } are publicly available at \url{https://ftp.science.ru.nl/astro/mchruslinska/Chruslinska_et_al_2021/} } as a representation of a very low and high metallicity star formation realisation respectively.
+These models are the low and high metallicity extreme under their fiducial SFR–metallicity correlation,
+%
+\edit1{and so we will refer to them as \texttt{Chr21\_lowZ} and \texttt{Chr21\_highZ} respectively from hereon.
+The difference between these models lies in the assumptions in the underlying empirical galaxy relations.
+In general, low-mass galaxies contribute to low-metallicity star formation and shift the peak of \SFRDzZ to lower metallicities.
+}
+% lowZ model: 2: sharp flattening (high mass part of the SFMR), 1: alpha\_fix(z) (low mass end of the GSMF), 4: PP04 (MZR at $z\approx0$) -- 
+% Starburst galaxies are treated as in BiC : the properties of starbursts are based on the studies of Bisigello+18 and Caputi+17 -- 
+% nabla\_FMR0 = 0.27 dex, describing the strength of the SFR-metallicity correlation in the high SFR, low mass regime. }
+%
+\edit1{\texttt{Chr21\_lowZ} is characterised by a star formation–galaxy mass relation that is flat at high galaxy masses (reducing the star formation rate for the highest-mass galaxies), a galaxy stellar mass function that evolves with redshift (predicting an increasing number density of low-mass galaxies),
+and a galaxy mass-metallicity relation following \cite{PettiniPagel2004}. 
+This model further approximates the contribution of starburst galaxies following \cite{Bisigello+2018} and \cite{Caputi+2017}.
+Including starbursts shift the peak of \SFRDzZ to lower metallicities and broadens the low metallicity part of the distribution.
+}
+% highZ model: 3: no flattening (high mass part of the SFMR), 0: alpha\_fix = -1.45 (low mass end of the GSMF), 2: KK04a (MZR at $z\approx0$) --  
+% Starburst galaxies are treated as in  Boco : the properties of starbursts are based on the studies of Sargent+12/Bethermin+12, as used in Boco+21. -- 
+% nabla\_FMR0 = 0.27 dex, describing the strength of the SFR-metallicity correlation in the high SFR, low mass regime.}
+%
+\edit1{On the other hand, \texttt{Chr21\_highZ} assumes the star formation–galaxy mass relation does not flatten towards higher galaxy masses, a galaxy stellar mass function that is constant over redshift, and a galaxy mass-metallicity relation following \cite{KobulnickyKewley2004}.
+Lastly, this model adopts the starburst prescription from \cite{Boco+2021}, which produces results that are similar to models without starburst galaxies.
+}
+
+%
+
 For every variation of our model, we inspect both the full \SFRDzZ and slices at redshifts $z = 0, 0.5, 3.0$ and $6$ by eye.
-At each slice we compare our model variation to the aforementioned low and high metallicity models, and ensure that none of our variations significantly exceeds these extremes in \SFRDzZ.
+At each slice we compare our model variation to \edit1{\texttt{Chr21\_lowZ} and \texttt{Chr21\_highZ}}, and ensure that none of our variations significantly exceeds these extremes in \SFRDzZ.
 This also serves as a sanity check for the overall star-formation rate density.
@@
 We choose \cite{Madau+2017} as an approximation of the lower limit.
-For the upper limit, we use the upper edge for the \texttt{SB: B18/C17} model variations with a non-evolving low-mass end of the galaxy stellar mass function \citep[table B1 from][also shown as thick brown line in their Fig.
+For the upper limit, we use the upper edge of 
+\edit1{ models that adopt starbursts following \cite{Bisigello+2018} and \cite{Caputi+2017} (\texttt{SB: B18/C17}), combined}
+with a non-evolving low-mass end of the galaxy stellar mass function \citep[shown as a thick brown line in Fig. 11 of ][and described in their table B1]{Chruslinska+2021}.
+% for the \texttt{SB: B18/C17} model variations (i.e.
+) with a non-evolving low-mass end of the galaxy stellar mass function \citep[table B1 from][also shown as thick brown line in their Fig.
 11]{Chruslinska+2021}.
-To approximate these models, we fit equation \ref{eq: sfr1} by eye to the broken power law description for the  \texttt{SB: B18/C17} model variations as presented in appendix B1 from \cite{Chruslinska+2021}.
+To approximate these models, we fit equation \ref{eq: sfr1} by eye to the broken power law description of this model as presented in appendix B1 of \cite{Chruslinska+2021}.
 We show all \SFRDz variations in Figure~\ref{fig: SFR(z)}. \\
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}
+\centering
+\script{SFR_z.py}
+\includegraphics[width=0.47\textwidth]{figures/SFR_redshift.pdf}
+\includegraphics[width=0.47\textwidth]{figures/SFR_tlookback.pdf}
+\caption{Comparison of several overall star-formation rate densities, \SFRDz,  with redshift (left panel) and with lookback time (right panel).
+The solid orange and dashed red lines respectively show the star formation data from TNG100 and our corresponding fit adopting eq.
+\ref{eq: sfr1} (fiducial model).
+The dotted gray and solid blue lines are variations of eq.
+\ref{eq: sfr1} used to approximate the lower and upper edge of possible star-formation histories.
+The dotted gray line shows the model from \cite{Madau+2017}, while the solid blue line mimics the behaviour of the powerlaw-fit to the \texttt{SB: B18/C17} variations with a non-evolving low-mass end of the galaxy stellar mass function from \cite{Chruslinska+2021}.
+\label{fig: SFR(z)}}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 Two more features are visible in at the high mass end for almost all \SFRDzZ; a knee at $\Mbheen\approx35\Msun$ and another bump at $\Mbheen\approx45\Msun$.
-Although the locations of these features are constant, the features themself can disappear for variations that suppress the rate of high mass BHs (e.g., dashed lines in the top panels of Fig.
+Although the locations of these features are constant, the features themselves can disappear for variations that suppress the rate of high mass BHs (e.g., dashed lines in the top panels of Fig.
 \ref{fig: stable mass dists}).
@@
 715063).
+This research was supported in part by the National Science Foundation under Grant No. NSF PHY-1748958. %KITP acknowledgement
+%as follows: This research was supported in part by the National Science Foundation under Grant No. NSF PHY-1748958.
 \end{acknowledgments}
@@
 \includegraphics[width=0.75\textwidth]{figures/High_Low_metalFractionSFMass.pdf}
-\caption{Percentage of stellar mass formed at low metallicity ($Z < 0.1 \rm{Z_{\odot}}$) , versus high metallicity ($Z>\rm{Z_{\odot}}$) for all star formation below a certain threshold redshift: $z<0.5$ (left), $z < 3.0$ (middle) and $z<10$ (right).
-Data from observation-based variations are shown with semi-transparent thick crosses,  \citep[][]{Chruslinska2019_obs} and semi-transparent thick plus signs \citep[][]{Chruslinska+2021}, the low- and high-metallicity extremes are indicated with opague symbols.
+\caption{Percentage of stellar mass formed at low metallicity ($Z < 0.1 \rm{Z_{\odot}}$) , versus high metallicity ($Z>\rm{Z_{\odot}}$) for all star formation below a certain threshold redshift: $z<0.5$ (top), $z < 3.0$ (middle) and $z<10$ (bottom).
+Data from observation-based variations are shown with semi-transparent thick crosses,  \citep[][]{Chruslinska2019_obs} and semi-transparent thick plus signs \citep[][]{Chruslinska+2021}, the low- and high-metallicity extremes are indicated with opaque symbols.
 For data from cosmological simulations, we follow \cite{Pakmor+2022} and show Illustris \citep[][squares]{Vogelsberger+2014}, Simba \citep[][diamonds]{Dave+2019}, EAGLE \citep[][triangles]{Schaye+2015}, TNG50 and TNG100 \citep[][filled and open circles respectively]{FirstResTNG_Springel2018}.

### 2023-01-25 src/tex/ms.tex
annotated on the difference in rates and COMPAS availability

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\todo{Make sure to address the difference in rate between this paper and \citep{vanson2022_lowMbh}!}
 A myriad of astrophysical phenomena depend critically on the rate of star formation throughout the cosmic history of the Universe.
@@
 metallicity studies of previously unexplored regimes \citep[e.g.,][]{Sanders+2022}. We hope that this form will facilitate the flexibility needed to keep up with observations. 
+\edit1{The model described in this work is incorporated in the publicly available `Cosmic Integration' suite of the \COMPAS code.\footnote{\url{https://github.com/TeamCOMPAS/COMPAS/tree/dev/utils/CosmicIntegration}}
+}
 
@@
 
-We use the publicly available rapid binary population synthesis simulations presented in van Son et al (in prep).\footnote{Available for download at \url{https://sandbox.zenodo.org/record/1101303},  see also the Software and Data section in the acknowledgements}
+We use the publicly available rapid binary population synthesis simulations presented in \cite{vanson2022_lowMbh}.\footnote{Available for download at \url{https://sandbox.zenodo.org/record/1101303},  see also the Software and Data section in the acknowledgements}
 These simulations were run using version v02.26.03 of the open source \COMPAS suite \citep{COMPAS_method}\footnote{\url{https://github.com/TeamCOMPAS/COMPAS}}.
 \COMPAS is based on algorithms that model the evolution of massive binary stars following \citet{Hurley+2000, Hurley+2002} using detailed evolutionary models by \citet{Pols+1998}.
-We refer the reader to the methods section of \cite{vanson+2022} for a detailed description of our adopted physics parameters and assumptions.
+\edit1{In particular, we use the simulations behind Figure 1 from \cite{vanson2022_lowMbh}, and we refer the reader to their methods section for a detailed description of the adopted physics parameters and assumptions.}\footnote{ \edit1{ We note that the rate in \cite{vanson2022_lowMbh} is slightly higher than the fiducial rate presented in Figure \ref{fig: stable mass dists} in this work.
+This difference is caused by the use of rounded parameter values of \SFRDzZ in \cite{vanson2022_lowMbh}.} } % In particular the value of $\mu_z$ has a significant effect on the inferred rate for the stable channel.}
 %

### 2023-01-25 src/scripts/SFR_z.py
increased label fonts

@@ -77,7 +77,7 @@ if __name__ == "__main__":
                  tmin=0.0, tmax = 13.7):
         ########################################################
         # Start plotting
-        fig, ax = plt.subplots(figsize=(12,10))
+        fig, ax = plt.subplots(figsize=(10,8))
 
         if x_redshift:
             x1  = redshift_list
@@ -191,10 +191,11 @@ if __name__ == "__main__":
             ax.set_xlabel(r'$\mathrm{redshift}$', fontsize = 30)
 
             # Find loockback location for each of our redshifts
-            redshift_tick_list = [0, 0.5, 2, 3, 6, 10, 12]#[0, 0.5, 1.0, 1.5, 2, 3, 6, 10, 12]
+            # redshift_tick_list = [0, 0.5, 2, 3, 6, 10, 12]#[0, 0.5, 1.0, 1.5, 2, 3, 6, 10, 12]
+            redshift_tick_list = [0, 2, 6, 10, 12]#[0, 0.5, 1.0, 1.5, 2, 3, 6, 10, 12]
             # And annotate the tick labels :)
             ax2.set_xticks([z for z in redshift_tick_list])
-            ax2.set_xticklabels(['${:.1f}$'.format(cosmo.lookback_time(z).value) for z in redshift_tick_list])
+            ax2.set_xticklabels(['${:.1f}$'.format(cosmo.lookback_time(z).value) for z in redshift_tick_list], fontsize = 24)
             ax2.set_xlabel(r'$\mathrm{Lookback \ time \ [Gyr]}$', fontsize = 30)
 
         else:
@@ -208,7 +209,7 @@ if __name__ == "__main__":
 
             # And annotate the tick labels :)
             ax2.set_xticks([cosmo.lookback_time(z).value for z in redshift_tick_list])
-            ax2.set_xticklabels(['${:g}$'.format(z) for z in redshift_tick_list])
+            ax2.set_xticklabels(['${:g}$'.format(z) for z in redshift_tick_list], fontsize = 24)
             ax2.set_xlabel(r'$\mathrm{redshift}$', fontsize = 30)
 
 
@@ -220,7 +221,8 @@ if __name__ == "__main__":
         logy = True
         if logy:
             plt.yscale('log')
[…]

### 2023-01-27 src/tex/ms.tex
added appendix figure with residuals

@@
 
-Our best fitting parameters are listed in Table \ref{tab: fit params}.
-With these fit parameters, $\chi^2(z_j)$ is smaller than $2\cdot 10^{-4}$ at any given redshift.
+Our best fitting parameters are listed in Table \ref{tab: fit params}. With these fit parameters, $\chi^2(z_j)$ is smaller than $2\cdot 10^{-4}$ at any given redshift. 
+\edit1{To evaluate our fit, we show the residuals in Appendix \ref{app: residuals}. }
 We will refer to the \SFRDzZ with the parameters listed in Table \ref{tab: fit params} as our fiducial model.
 
-\begin{deluxetable*}{cll | cl}
+\begin{deluxetable*}{clr | cl}
 \label{tab: fit params}
@@
 \startdata
-$\mu_0$    & mean metallicity at $z=0$    & $0.025  \pm 0.001$ &  $a$ &  $0.02 \pm 0.05$ \\% \, \Msun\yr^{-1}\Mpc^{-3}$\\
-$\mu_z$    & $z$-dependence of the mean   & $-0.048 \pm 0.001$ &  $b$ &  $1.48 \pm 0.01$\\
-$\alpha$   & shape (skewness)             & $-1.767 \pm 0.05 $ &  $c$ &  $4.45 \pm 0.01$\\
-$\omega_0$ & scale at $z=0$               & $1.125  \pm 0.005$ &  $d$ &  $5.90 \pm 0.02$\\
-$\omega_z$ & $z$-dependence of the scale  & $0.048  \pm 0.0001$ &   \\
+$\mu_0$    & mean metallicity at $z=0$    & $0.025  \pm 0.036$ &  $a$ &  $0.02 \pm 0.072$ \\% \, \Msun\yr^{-1}\Mpc^{-3}$\\
+$\mu_z$    & $z$-dependence of the mean   & $-0.048 \pm 0.006$ &  $b$ &  $1.48 \pm 0.002$\\
+$\alpha$   & shape (skewness)             & $-1.778 \pm 0.002$ &  $c$ &  $4.44 \pm 0.001$\\
+$\omega_0$ & scale at $z=0$               & $1.122  \pm 0.001$ &  $d$ &  $5.90 \pm 0.002$\\
+$\omega_z$ & $z$-dependence of the scale  & $0.049  \pm 0.009$ &   \\
 \enddata
@@
 By integrating over cosmic history, we obtain the local merger rates of BBH systems, which allow us to construct the distribution of source properties at every redshift.
-We use the cosmic integration scheme that is part of the publicly available \COMPAS suite.
-The details of this framework are described in \cite{Neijssel+2019}, but also in \cite{vanson+2022}, where more similar settings to this work are used.
+We use the cosmic integration scheme that is part of the publicly available \COMPAS suite, \edit1{which includes the \SFRDzZ model described in this work.} The details of this framework are described in \cite{Neijssel+2019}, but also in \cite{vanson+2022}, where more similar settings to this work are used.
 
@@
 $\mu_z$          &   0.0   & $-0.048$ &   -0.5 \\
-$\alpha$         &   -6.0   & $-1.767$ &  0.0  \\
+$\alpha$         &   -6.0   & $-1.778$ &  0.0  \\
 $\omega_0$       &   0.7   & $1.125$  &  2.0  \\
@@
 ($a$,$b$ ... &  ($0.01$, $2.60$   & ($0.02$, $1.48$ &  ($0.03$, $2.6$ \\
-... $c$,$d$) &  $3.20$, $6.20$)   & $4.45$, $5.90$) &   $3.3$, $5.9$) \\
-% \parbox{1.75cm}{($a$,$b$, \hspace{0.7cm} $c$,$d$)} &  \parbox{1.75cm}{($0.01$, $2.60$, $3.20$, $6.20$)}   & \parbox{1.75cm}{($0.02$, $1.48$, $4.45$, $5.90$)} &  \parbox{1.75cm}{($0.03$, $2.6$, $3.3$, $5.9$)} \\
+... $c$,$d$) &  $3.20$, $6.20$)   & $4.44$, $5.90$) &   $3.3$, $5.9$) \\
 \enddata
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{\edit1{Evaluating our fit; the squared residuals \label{app: residuals} } }
+
+\begin{figure}[h]
+\centering
+\script{Fit_model_to_sfrdzZ.py}
+\includegraphics[width=0.75\textwidth]{figures/log_squared_res.pdf}
+\caption{$\log$ of the squared residuals, which appear in equation \ref{eq: cost function} to optimise our fit. \label{fig: residuals}
+  }
+\end{figure}
+
+\edit1{In Figure \ref{fig: residuals} we show the $\log$ of the squared residuals.
+The residuals are the content of the sum in equation \ref{eq: chisquare}, which is used in the cost function, equation \ref{eq: cost function}, to optimise our fit.
+We see that the maximum residuals appear just below the peak of star formation.
+We note that we chose to minimise the squared residuals (which is similar to minimising the mean squared error) in favour of e.g.
+minimising the relative error, to prevent overfitting regions of very low star-formation rate.
+}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Determining reasonable variations of the \SFRDzZ \label{app: reasonable var}}
@@
 
+\clearpage
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2023-01-27 src/scripts/Fit_model_to_sfrdzZ.py

@@ -211,3 +211,44 @@ if __name__ == "__main__":
                    header = "mu0, muz, omega0, omegaz, alpha0,sf_a, sf_b, sf_c, sf_d", delimiter=',', fmt="%s")
 
 
+    #########################################
+    # Visualize the fit
+    # plotting the squared residuals because that is what is used to optimize
+    ############################
+    ##PLOT setttings
+    from matplotlib import rc
+    import matplotlib
+    from matplotlib import ticker, cm
+    rc('font',**{'family':'sans-serif','sans-serif':['Helvetica']})
+    plt.rc('font', family='serif')
+    matplotlib.rcParams['mathtext.fontset'] = 'stix'
+    matplotlib.rcParams['font.family'] = 'STIXGeneral'
+
+    Zsun = 0.014 # Solar metallicity
+
+    ########################
+    fig, ax = plt.subplots(figsize = (11,6))
+
+    X,Y = np.meshgrid(redshift_new,  np.log10(metals_new/Zsun))
+
+    levs = np.linspace(-10, -3, num=8)
+    cs = plt.contourf(X, Y, np.log10(res_squared.T), 
+                      levs, cmap ="bone",extend ='min')
+    #                   locator = ticker.LogLocator(),
+    #                   levs, norm=mpl.colors.LogNorm(),
+
+    cbar = plt.colorbar(cs)
+    cbar.ax.set_ylabel('$\log$ squared residuals', fontsize = 30)
+    cbar.ax.tick_params(labelsize=20)
+
+    ######
+    # Plot values
+    ax.set_xlabel('Redshifts', fontsize = 30)
+    ax.set_ylabel('$\mathrm{Metallicities}, \ \log_{10}(Z/Z_{\odot})$', fontsize = 30)
+    ax.tick_params(axis='both', which='major', labelsize=22)
+    ax.tick_params(axis='both', which='minor', labelsize=22)
+    plt.ylim(-3,1.5)
+
+    plt.savefig(paths.figures / 'log_squared_res.pdf',  bbox_inches='tight')
+    # plt.show()
+    

### 2023-01-27 src/scripts/Fit_model_to_sfrdzZ.py
minor change text values

@@ -163,7 +163,7 @@ if __name__ == "__main__":
         chi_square = res_squared/np.sum(model, axis = 1)[:,np.newaxis]
         
         # Return sum Chi_squared and the max squared residual
-        return np.sum(chi_square), np.amax(res_squared)
+        return np.sum(chi_square), res_squared
 
      
     # Run your chi square calculations
@@ -173,7 +173,7 @@ if __name__ == "__main__":
     ## Function wrapper to minimize the Chi_square
     #################################################################
     def test_chi(x0 = [-0.09, 0.026, 1.9, 0.1, -3.3, 0.01, 2.6, 3.2, 6.2] ):
-        chi_square, max_res_square = calc_chi_square(metals_new, Redshifts = redshift_new, simulation_SFRD = SFRDnew.T, 
+        chi_square, res_squared = calc_chi_square(metals_new, Redshifts = redshift_new, simulation_SFRD = SFRDnew.T, 
                                            muz  =x0[0], mu_0  =x0[1],sigma0  =x0[2], sigmaz =x0[3], alpha  =x0[4],
                                            sf_a =x0[5], sf_b=x0[6], sf_c=x0[7], sf_d=x0[8])
         return chi_square
@@ -183,14 +183,8 @@ if __name__ == "__main__":
     #        # mu_z        # mu_0     # omega_0 #omega_z  #alpha       #sf_a       #sf_b       #sf_c       #sf_d
     bounds = ((-1., 0), (0.001, 0.1), (0.01, 5), (0, 1.), (-10, 0), (None,None),(None,None),(None,None),(None,None))
     # FIT
-    res = minimize(test_chi, x0= x0, method = 'BFGS',#'nelder-mead',# L-BFGS-B
+    res = minimize(test_chi, x0= x0, method = 'BFGS',# other options include: 'nelder-mead', L-BFGS-B
                    options = {'gtol': 0.05})#{'maxiter': 5000})
-
-    # res = opt.basinhopping(test_chi, x0= x0, minimizer_kwargs={'method':'BFGS'})
-    # The covariance matrix can be approximated by the inverse Hessian matrix (assuming the errors have a Gaussian distribution)
-    cov_matrix    = res['hess_inv']#.todense() #res['lowest_optimization_result']['hess_inv']
-    # the standard error is the sqrt of the diagonal elements
[…]

### 2023-01-28 src/scripts/init_values.py
updated Zenodo entry

@@ -18,8 +18,8 @@ def init():
     data_dir   = str(paths.data) +'/'    #str(paths.data)[0:-8] + 'data/'
     script_dir = str(paths.scripts) +'/' #str(paths.scripts)[0:-11] + 'scripts/'
 
-    COMPASfilename  = 'CompactCOMPAS_Output_wWeights.h5'#'COMPAS_Output_wWeights.h5'#'small_COMPAS_Output_wWeights.h5'#
-    rate_file_name  = 'CompactRate_info.h5'#'Rate_info.h5'#'small_Rate_info.h5'#'Rate_info.h5'
+    COMPASfilename  = 'COMPAS_Output_wWeights.h5'#'small_COMPAS_Output_wWeights.h5'
+    rate_file_name  = 'Rate_info.h5'#'small_Rate_info.h5'
     user_email      = "aac.van.son@gmail.com"
 
 

### 2023-01-28 src/tex/ms.tex
minor change text values
minor rephrasing in text

@@
 $\mu_0$    & mean metallicity at $z=0$    & $0.025  \pm 0.036$ &  $a$ &  $0.02 \pm 0.072$ \\% \, \Msun\yr^{-1}\Mpc^{-3}$\\
-$\mu_z$    & $z$-dependence of the mean   & $-0.048 \pm 0.006$ &  $b$ &  $1.48 \pm 0.002$\\
+$\mu_z$    & $z$-dependence of the mean   & $-0.049 \pm 0.006$ &  $b$ &  $1.48 \pm 0.002$\\
 $\alpha$   & shape (skewness)             & $-1.778 \pm 0.002$ &  $c$ &  $4.44 \pm 0.001$\\
@@
 $\mu_0$          &   0.007   & $0.025$  &  0.035  \\
-$\mu_z$          &   0.0   & $-0.048$ &   -0.5 \\
+$\mu_z$          &   0.0   & $-0.049$ &   -0.5 \\
 $\alpha$         &   -6.0   & $-1.778$ &  0.0  \\
@@
 
-For the cosmic metallicity density distribution, we vary every parameter that determines the shape of \dpdZ independently (left two columns of Table \ref{tab: fit params}), while keeping all other parameters fixed at their fiducial value.
+For the cosmic metallicity density distribution, we vary every parameter that determines the shape of \dpdZ independently (\edit1{three left-most columns of Table \ref{tab: fit params}, and top of Table \ref{tab: fit variations} }), while keeping all other parameters fixed at their fiducial value.
 For each variation, we inspect the fraction of stellar mass that is formed at low-metallicity ($Z<0.1 Z_{\odot}$) versus the fraction of stellar mass that is formed at high-metallicity ($Z> Z_{\odot}$), for all star formation that occurred below a certain threshold redshift.
@@
 
-Lastly, we consider two variations of the overall star-formation rate density, \SFRDz, where we keep the metallicity distribution \dpdZ fixed, but vary all four \SFRDz parameters at once (right two columns of Table \ref{tab: fit params}).
+We also consider two variations of the overall star-formation rate density, \SFRDz, where we keep the metallicity distribution \dpdZ fixed, but vary all four \SFRDz parameters at once (right two columns of Table \ref{tab: fit params} \edit1{, and bottom of Table \ref{tab: fit variations} }).
 We use Figure 11 from \cite{Chruslinska+2021} to determine approximate upper and lower bounds to the overall star-formation rate density.

### 2023-01-30 src/scripts/Plot_Mass_distributions.py
usetex back to True

@@ -53,7 +53,7 @@ matplotlib.rcParams['mathtext.fontset'] = 'stix'
 matplotlib.rcParams['font.family'] = 'STIXGeneral'
 rc('font',**{'family':'sans-serif','sans-serif':['Helvetica']})
 plt.rc('font', family='serif')
-rc('text', usetex=False)
+rc('text', usetex=True)
 fsize, SMALL_SIZE, MEDIUM_SIZE, BIGGER_SIZE = 30,25,25,30
 for obj in ['axes','xtick','ytick']:
 	plt.rc(obj, labelsize=MEDIUM_SIZE)          # controls default text sizes

### 2023-01-30 src/scripts/Plot_CEMass_distributions.py
disabling usetex again and added latex font to matplotlibrc

@@ -47,7 +47,7 @@ import matplotlib
 matplotlib.rcParams['mathtext.fontset'] = 'stix'
 matplotlib.rcParams['font.family'] = 'STIXGeneral'
 rc('font',**{'family':'sans-serif','sans-serif':['Helvetica']})
-rc('text', usetex=True)
+rc('text', usetex=False)
 fsize, SMALL_SIZE, MEDIUM_SIZE, BIGGER_SIZE = 30,25,25,30
 for obj in ['axes','xtick','ytick']:
     plt.rc(obj, labelsize=MEDIUM_SIZE)          # controls default text sizes
@@ -89,9 +89,6 @@ if __name__ == "__main__":
                            labels = [r'$\mathrm{Narrow: \ }  (\omega_0 = 0.70) \  \mathcal{R}_{0.2} = \ $',
                                      r'$\mathrm{Fiducial: \ } (\omega_0 = 1.13) \ \mathcal{R}_{0.2}= \ $', 
                                      r'$\mathrm{Wide: \ } (\omega_0 = 2.00) \  \mathcal{R}_{0.2} = \ $'],
-                           # labels = [r'$\mathrm{Narrow: \ }  (\omega_0 = 0.70) \  \mathcal{R}_{0.2} = \ $',
-                           #           r'$\mathrm{Fiducial: \ } (\omega_0 = 1.13) \ \mathcal{R}_{0.2}= \ $', 
-                           #           r'$\mathrm{Wide: \ } \phantom{xx} (\omega_0 = 2.00) \  \mathcal{R}_{0.2} = \ $'],
                           multipanel = True, subplot = subplot1)
 
     # 'Rates_mu00.025_muz-0.049_alpha-3.5_sigma01.129_sigmaz0.048_a0.017_b1.487_c4.442_d5.886
@@ -111,9 +108,6 @@ if __name__ == "__main__":
                            labels = [r'$\mathrm{Flat \ width: \ } (\omega_z = 0.00) \ \mathcal{R}_{0.2} = \ $',
                                      r'$\mathrm{Fiducial: \ } (\omega_z = 0.05) \ \mathcal{R}_{0.2}= \ $', 
                                      r'$\mathrm{Steep \ width: \ } (\omega_z = 0.10) \ \mathcal{R}_{0.2} = \ $'],
-                           # labels = [r'$\mathrm{Flat \ width: \ } \phantom{i} (\omega_z = 0.00) \ \mathcal{R}_{0.2} = \ $',
[…]

### 2023-01-30 src/scripts/Plot_Mass_distributions.py

@@ -53,7 +53,7 @@ matplotlib.rcParams['mathtext.fontset'] = 'stix'
 matplotlib.rcParams['font.family'] = 'STIXGeneral'
 rc('font',**{'family':'sans-serif','sans-serif':['Helvetica']})
 plt.rc('font', family='serif')
-rc('text', usetex=True)
+rc('text', usetex=False)
 fsize, SMALL_SIZE, MEDIUM_SIZE, BIGGER_SIZE = 30,25,25,30
 for obj in ['axes','xtick','ytick']:
 	plt.rc(obj, labelsize=MEDIUM_SIZE)          # controls default text sizes

### 2023-01-30 src/scripts/Plot_StableMass_distributions.py

@@ -46,7 +46,7 @@ import matplotlib
 matplotlib.rcParams['mathtext.fontset'] = 'stix'
 matplotlib.rcParams['font.family'] = 'STIXGeneral'
 rc('font',**{'family':'sans-serif','sans-serif':['Helvetica']})
-rc('text', usetex=True)
+rc('text', usetex=False)
 fsize, SMALL_SIZE, MEDIUM_SIZE, BIGGER_SIZE = 30,25,25,30
 for obj in ['axes','xtick','ytick']:
     plt.rc(obj, labelsize=MEDIUM_SIZE)          # controls default text sizes
@@ -89,13 +89,7 @@ if __name__ == "__main__":
                            labels = [r'$\mathrm{Narrow: \ }  (\omega_0 = 0.70) \  \mathcal{R}_{0.2} = \ $',
                                      r'$\mathrm{Fiducial: \ } (\omega_0 = 1.13) \ \mathcal{R}_{0.2}= \ $', 
                                      r'$\mathrm{Wide: \ } (\omega_0 = 2.00) \  \mathcal{R}_{0.2} = \ $'],
-                           # labels = [r'$\mathrm{Narrow: \ }  (\omega_0 = 0.70) \  \mathcal{R}_{0.2} = \ $',
-                           #           r'$\mathrm{Fiducial: \ } (\omega_0 = 1.13) \ \mathcal{R}_{0.2}= \ $', 
-                           #           r'$\mathrm{Wide: \ } \phantom{xx} (\omega_0 = 2.00) \  \mathcal{R}_{0.2} = \ $'],
                           multipanel = True, subplot = subplot1)
-
-    # 'Rates_mu00.025_muz-0.049_alpha-3.5_sigma01.129_sigmaz0.048_a0.017_b1.487_c4.442_d5.886
-    # Rates_mu00.025_muz-0.049_alpha-1.79_sigma01.129_sigmaz0.048_a0.017_b1.487_c4.442_d5.886
 
     ####################################################
     # Redshift evolution of the width
@@ -111,9 +105,6 @@ if __name__ == "__main__":
                            labels = [r'$\mathrm{Flat \ width: \ } (\omega_z = 0.00) \ \mathcal{R}_{0.2} = \ $',
                                      r'$\mathrm{Fiducial: \ } (\omega_z = 0.05) \ \mathcal{R}_{0.2}= \ $', 
[…]

### 2023-02-06 src/tex/article.tex
usetex back to True
added minor suggestions from coauthors

--- 2023-01-28 src/tex/ms.tex
@@
 \edit1{\texttt{Chr21\_lowZ} is characterised by a star formation–galaxy mass relation that is flat at high galaxy masses (reducing the star formation rate for the highest-mass galaxies), a galaxy stellar mass function that evolves with redshift (predicting an increasing number density of low-mass galaxies),
-and a galaxy mass-metallicity relation following \cite{PettiniPagel2004}. 
+and a local galaxy mass-metallicity relation as in \cite{PettiniPagel2004}. 
 This model further approximates the contribution of starburst galaxies following \cite{Bisigello+2018} and \cite{Caputi+2017}. 
-Including starbursts shift the peak of \SFRDzZ to lower metallicities and broadens the low metallicity part of the distribution.
+Assuming that starburst galaxies follow the empirical fundamental metallicity relation (leading to anti-correlation between the SFR and metallicity), their inclusion tends to shift the peak of \SFRDzZ to
+lower metallicities and broadens the low-metallicity part of the distribution.
 }
@@
 %
-\edit1{On the other hand, \texttt{Chr21\_highZ} assumes the star formation–galaxy mass relation does not flatten towards higher galaxy masses, a galaxy stellar mass function that is constant over redshift, and a galaxy mass-metallicity relation following \cite{KobulnickyKewley2004}.
+\edit1{On the other hand, \texttt{Chr21\_highZ} assumes the star formation–galaxy mass relation does not flatten towards higher galaxy masses, a galaxy stellar mass function where the slope for the low-mass end is constant over redshift, and a local galaxy mass-metallicity relation following \cite{KobulnickyKewley2004}.
 Lastly, this model adopts the starburst prescription from \cite{Boco+2021}, which produces results that are similar to models without starburst galaxies.

### 2023-02-06 src/tex/article.tex
removed surplus tex data and updated zenodo link in article.tex

@@
 
-We use the publicly available rapid binary population synthesis simulations presented in \cite{vanson2022_lowMbh}.\footnote{Available for download at \url{https://sandbox.zenodo.org/record/1101303},  see also the Software and Data section in the acknowledgements}
+We use the publicly available rapid binary population synthesis simulations presented in \cite{vanson2022_lowMbh}.\footnote{Available for download at \url{https://zenodo.org/record/7612755},  see also the Software and Data section in the acknowledgements}
 These simulations were run using version v02.26.03 of the open source \COMPAS suite \citep{COMPAS_method}\footnote{\url{https://github.com/TeamCOMPAS/COMPAS}}.
@@
 All code associated to reproduce the data and plots in this paper is publicly available at \url{https://github.com/LiekeVanSon/SFRD_fit}.
-The data used in this work is available on Zenodo under an open-source Creative Commons Attribution license at \dataset[10.5072/zenodo.1101303]{https://sandbox.zenodo.org/record/1101303}.
-% \dataset[doi:10.5281/zenodo.5544170]{https://doi.org/10.5281/zenodo.5544170}.
+The data used in this work is available on Zenodo under an open-source Creative Commons Attribution license at \dataset[10.5281/zenodo.7612755]{https://zenodo.org/record/7612755}.
 All observationally constrained models of the \SFRDzZ from \cite{Chruslinska+2021} can be found online at: \url{https://ftp.science.ru.nl/astro/mchruslinska/Chruslinska_et_al_2021/}.

### 2023-02-21 src/tex/article.tex
added extra plot following referee report

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-We assume that the metallicity-dependent cosmic star formation history can be separated into two independent functions 
-(as was assumed in e.g., \citealt{LangerNorman2006}, but cf. \citealt{chruslinska2022_review} for a discussion on the validity on this assumption).
+% We assume that the metallicity-dependent cosmic star formation history can be separated into two independent functions  (as was assumed in e.g., \citealt{LangerNorman2006}, but cf.
+\citealt{chruslinska2022_review} for a discussion on the validity on this assumption).
+\edit2{We write the metallicity-dependent cosmic star formation history as}
 
@@
 \boxed{
-        \SFRDzZ = \SFRDz \times \dPdZ.
+        \SFRDzZ = \SFRDz \times \dPdZ
         }
 \end{equation}
+\edit2{(similar to e.g., \citealt{LangerNorman2006}).}
 The first term is the star formation rate density, \SFRDz, that is the amount of mass formed in stars per unit time and per unit comoving volume at each redshift, $z$.
@@
 \script{Fit_model_to_sfrdzZ.py}
-\includegraphics[width=0.75\textwidth]{figures/log_squared_res.pdf}
-\caption{$\log$ of the squared residuals, which appear in equation \ref{eq: cost function} to optimise our fit. \label{fig: residuals}
+\includegraphics[width=0.49\textwidth]{figures/log_res.pdf}
+\includegraphics[width=0.49\textwidth]{figures/log_relative_err.pdf}
+\caption{Left: $\log$ of the residuals, which appear in equation \ref{eq: cost function} to optimise our fit.
+Right: $\log$ of the relative error between the TNG100 data and our best fitting model.
+We show the minimum and maximum metallicity used in \COMPAS simulations with dashed lines in each plot.
+\label{fig: residuals}
  }
@@
 
-\edit1{In Figure \ref{fig: residuals} we show the $\log$ of the squared residuals.
+\edit1{In Figure \ref{fig: residuals} we show the $\log$ of the residuals.
 The residuals are the content of the sum in equation \ref{eq: chisquare}, which is used in the cost function, equation \ref{eq: cost function}, to optimise our fit.

### 2023-02-21 src/scripts/Fit_model_to_sfrdzZ.py

@@ -151,7 +151,6 @@ if __name__ == "__main__":
                         Z_SFRD.skew_metallicity_distribution(Redshifts,mu_z = muz , mu_0 = mu_0 ,
                                                       omega_0= sigma0 , omega_z=sigmaz , alpha = alpha , 
                                                       metals=fit_metals)
-        
         ######################################
         data           = simulation_SFRD                # Model comes in dP/dlogZ, so should your sim-data !
         model          = sfr[:,np.newaxis] * dPdlogZ 
@@ -162,8 +161,8 @@ if __name__ == "__main__":
         # reduces contribution from high sfr redshifts & increases the weight where sfr is low
         chi_square = res_squared/np.sum(model, axis = 1)[:,np.newaxis]
         
-        # Return sum Chi_squared and the max squared residual
-        return np.sum(chi_square), res_squared
+        # Return sum Chi_squared 
+        return np.sum(chi_square), data, model
 
      
     # Run your chi square calculations
@@ -173,7 +172,7 @@ if __name__ == "__main__":
     ## Function wrapper to minimize the Chi_square
     #################################################################
     def test_chi(x0 = [-0.09, 0.026, 1.9, 0.1, -3.3, 0.01, 2.6, 3.2, 6.2] ):
-        chi_square, res_squared = calc_chi_square(metals_new, Redshifts = redshift_new, simulation_SFRD = SFRDnew.T, 
+        chi_square, data, model = calc_chi_square(metals_new, Redshifts = redshift_new, simulation_SFRD = SFRDnew.T, 
                                            muz  =x0[0], mu_0  =x0[1],sigma0  =x0[2], sigmaz =x0[3], alpha  =x0[4],
                                            sf_a =x0[5], sf_b=x0[6], sf_c=x0[7], sf_d=x0[8])
         return chi_square
@@ -194,14 +193,15 @@ if __name__ == "__main__":
     print('mu0 =%s, muz =%s, sigma_0 =%s, sigma_z =%s, alpha=%s'% (mu0_best, muz_best, sigma0_best, sigmaz_best, alpha_best) )
[…]

### 2023-02-22 src/tex/article.tex
expanded appendix A

@@
 \includegraphics[width=0.49\textwidth]{figures/log_relative_err.pdf}
-\caption{Left: $\log$ of the residuals, which appear in equation \ref{eq: cost function} to optimise our fit.
-Right: $\log$ of the relative error between the TNG100 data and our best fitting model.
+\caption{$\log$ of the residuals (left), and $\log$ of the relative error (right) between the TNG100 data and our best-fitting model.
 We show the minimum and maximum metallicity used in \COMPAS simulations with dashed lines in each plot.
@@
 
-\edit1{In Figure \ref{fig: residuals} we show the $\log$ of the residuals.
-The residuals are the content of the sum in equation \ref{eq: chisquare}, which is used in the cost function, equation \ref{eq: cost function}, to optimise our fit.
-We see that the maximum residuals appear just below the peak of star formation.
-We note that we chose to minimise the squared residuals (which is similar to minimising the mean squared error) in favour of e.g.
-minimising the relative error, to prevent overfitting regions of very low star-formation rate.
-}
+\edit1{In the left panel of Figure \ref{fig: residuals}, we show the $\log$ of the absolute residuals.
+The \textit{square} of the residuals is used in the cost function, equation \ref{eq: cost function}, to optimise our fit.
+We observe that the maximum residuals appear near the peak of star formation at high metallicities.
+%
+The log of the relative errors (defined as $\frac{\lvert \mathcal{S}{\rm sim} - \mathcal{S}{\rm fit} \rvert}{\mathcal{S}_{\rm fit}}$), is shown in the right-hand panel of Figure \ref{fig: residuals}.
+The relative errors generally exhibit an opposite trend with respect to the residuals.
+The relative errors are largest in regions of very low-metallicity star formation at low redshift.
+This occurs due to the very low star-formation rate in this regime (of the order $10^{-8}\Msun \yr^{-1}\Mpc^{-3}$ for the TNG simulations and $10^{-11}\Msun \yr^{-1}\Mpc^{-3}$ in our model fit).
+%
+Another regime where the relative error becomes large is at very high metallicities (about 10 times $Z_{\odot}$).
+In this regime, the TNG data is very sparse and contains regions where the rate abruptly drops to zero.
+To avoid sharp features in the data, we use interpolated TNG data to produce the fit.
+%
+We note that we chose to minimise the squared residuals (which is similar to minimising the mean squared error) in favour of minimising, for example, the relative error, to prevent overfitting such regions of very low star-formation rate.
+For the illustration purposes in this work, we are most interested in closely fitting the \SFRDzZ between the minimum ($10^{-4}$) and maximum ($0.03$) metallicities that can be simulated with \COMPAS (or more generally, with population synthesis simulations).
+For applications that focus on extremely low ($<0.01 Z_{\odot}$) or extremely high ($\sim 10\times Z_{\odot}$) metallicity star formation, a different cost function would be more appropriate.}
 

### 2023-02-22 src/scripts/Fit_model_to_sfrdzZ.py

@@ -263,7 +263,6 @@ if __name__ == "__main__":
     plt.ylim(-3,1.5)
 
     plt.savefig(paths.figures / 'log_res.pdf',  bbox_inches='tight')
-    plt.show()
 
     ############################
     # log of the relative error
@@ -303,7 +302,6 @@ if __name__ == "__main__":
     plt.ylim(-3,1.5)
 
     plt.savefig(paths.figures / 'log_relative_err.pdf',  bbox_inches='tight')
-    plt.show()
 
 
 

### 2023-02-22 src/tex/article.tex
cleaned up edit commands and some comments

@@
 metallicity studies of previously unexplored regimes \citep[e.g.,][]{Sanders+2022}. We hope that this form will facilitate the flexibility needed to keep up with observations. 
-\edit1{The model described in this work is incorporated in the publicly available `Cosmic Integration' suite of the \COMPAS code.\footnote{\url{https://github.com/TeamCOMPAS/COMPAS/tree/dev/utils/CosmicIntegration}}
-}
+The model described in this work is incorporated in the publicly available `Cosmic Integration' suite of the \COMPAS code.\footnote{\url{https://github.com/TeamCOMPAS/COMPAS/tree/dev/utils/CosmicIntegration}}
 
@@
 For the probability distribution of metallicities we draw inspiration from the approach by e.g., \cite{Neijssel+2019} who used a log-normal distribution for their phenomenological model.
-\edit1{Unfortunately, a simple log-normal distribution cannot capture the asymmetry that we see in the cosmological simulations}, which show an extended tail in  $\log_{10} Z$ towards low metallicity, combined with a very limited tail towards higher metallicity.
+Unfortunately, a simple log-normal distribution cannot capture the asymmetry that we see in the cosmological simulations, which show an extended tail in  $\log_{10} Z$ towards low metallicity, combined with a very limited tail towards higher metallicity.
 To capture this behaviour we adopt a skewed-log-normal distribution instead.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Although here, we only fit our model to the TNG100 simulation, our prescription can be easily be used to fit other simulated or observational data of the metallicity-dependent cosmic star formation history\footnote{\edit1{We provide a Jupyter notebook to facilitate this fit here: \url{https://github.com/LiekeVanSon/SFRD_fit/blob/main/src/scripts/Notebooks/Fit_model_to_sfrdzZ.ipynb} } }.
+Although here, we only fit our model to the TNG100 simulation, our prescription can be easily be used to fit other simulated or observational data of the metallicity-dependent cosmic star formation history\footnote{We provide a Jupyter notebook to facilitate this fit here: \url{https://github.com/LiekeVanSon/SFRD_fit/blob/main/src/scripts/Notebooks/Fit_model_to_sfrdzZ.ipynb} } .
 
@@
 Our best fitting parameters are listed in Table \ref{tab: fit params}. With these fit parameters, $\chi^2(z_j)$ is smaller than $2\cdot 10^{-4}$ at any given redshift. 
-\edit1{To evaluate our fit, we show the residuals in Appendix \ref{app: residuals}. }
+To evaluate our fit, we show the residuals in Appendix \ref{app: residuals}. 
 We will refer to the \SFRDzZ with the parameters listed in Table \ref{tab: fit params} as our fiducial model.
@@
 \COMPAS is based on algorithms that model the evolution of massive binary stars following \citet{Hurley+2000, Hurley+2002} using detailed evolutionary models by \citet{Pols+1998}.
-\edit1{In particular, we use the simulations behind Figure 1 from \cite{vanson2022_lowMbh}, and we refer the reader to their methods section for a detailed description of the adopted physics parameters and assumptions.}\footnote{ \edit1{ We note that the rate in \cite{vanson2022_lowMbh} is slightly higher than the fiducial rate presented in Figure \ref{fig: stable mass dists} in this work.
-This difference is caused by the use of rounded parameter values of \SFRDzZ in \cite{vanson2022_lowMbh}.} } % In particular the value of $\mu_z$ has a significant effect on the inferred rate for the stable channel.}
+In particular, we use the simulations behind Figure 1 from \cite{vanson2022_lowMbh}, and we refer the reader to their methods section for a detailed description of the adopted physics parameters and assumptions.
+\footnote{ We note that the rate in \cite{vanson2022_lowMbh} is slightly higher than the fiducial rate presented in Figure \ref{fig: stable mass dists} in this work.
+This difference is caused by the use of rounded parameter values of \SFRDzZ in \cite{vanson2022_lowMbh}.}  % In particular the value of $\mu_z$ has a significant effect on the inferred rate for the stable channel.}
 %
@@
 By integrating over cosmic history, we obtain the local merger rates of BBH systems, which allow us to construct the distribution of source properties at every redshift.
-We use the cosmic integration scheme that is part of the publicly available \COMPAS suite, \edit1{which includes the \SFRDzZ model described in this work.} The details of this framework are described in \cite{Neijssel+2019}, but also in \cite{vanson+2022}, where more similar settings to this work are used.
+We use the cosmic integration scheme that is part of the publicly available \COMPAS suite, which includes the \SFRDzZ model described in this work.
+The details of this framework are described in \cite{Neijssel+2019}, but also in \cite{vanson+2022}, where more similar settings to this work are used.
 
@@
 To determine the range that is reasonably allowed by observations, we compare our variations to the observation-based \SFRDzZ models described in \cite{Chruslinska+2021}.
-\edit1{An overview of the explored variations is shown in Table \ref{tab: fit variations}. Below we explain how we arrive at these values.  }
+An overview of the explored variations is shown in Table \ref{tab: fit variations}. Below we explain how we arrive at these values.
 
@@
 \tablewidth{0.5\textwidth} 
-\tablecaption{\edit1{Variations on \SFRDzZ. 
+\tablecaption{Variations on \SFRDzZ. 
 For every variation, we either swap the value of an individual \dpdZ parameter, or exchange the set of four \SFRDz parameters, and replace them by the the min/max values listed here.
 All other parameters are kept fixed at their fiducial value.
-}}
+}
 \tablehead{\colhead{} & \colhead{min} & \colhead{fiducial} & \colhead{max} } 
@@
 
-For the cosmic metallicity density distribution, we vary every parameter that determines the shape of \dpdZ independently (\edit1{three left-most columns of Table \ref{tab: fit params}, and top of Table \ref{tab: fit variations} }), while keeping all other parameters fixed at their fiducial value.
+For the cosmic metallicity density distribution, we vary every parameter that determines the shape of \dpdZ independently (three left-most columns of Table \ref{tab: fit params}, and top of Table \ref{tab: fit variations} ), while keeping all other parameters fixed at their fiducial value.
 For each variation, we inspect the fraction of stellar mass that is formed at low-metallicity ($Z<0.1 Z_{\odot}$) versus the fraction of stellar mass that is formed at high-metallicity ($Z> Z_{\odot}$), for all star formation that occurred below a certain threshold redshift.
@@
 We have chosen our variations such that they span a reasonable range of cosmic metallicity density distributions as allowed by observation-based and cosmological simulations-based models.
-We use the models \texttt{214-f14SB-BiC\_FMR270\_FOH\_z\_dM.dat}, and \texttt{302-f14SB-Boco\_FMR270\_FOH\_z\_dM.dat} from \cite{Chruslinska+2021}\footnote{These models \edit1{ including a detailed description of their contents } are publicly available at \url{https://ftp.science.ru.nl/astro/mchruslinska/Chruslinska_et_al_2021/} } as a representation of a very low and high metallicity star formation realisation respectively.
-These models are the low and high metallicity extreme under their fiducial SFR–metallicity correlation,
-%
-\edit1{and so we will refer to them as \texttt{Chr21\_lowZ} and \texttt{Chr21\_highZ} respectively from hereon.
+We use the models \texttt{214-f14SB-BiC\_FMR270\_FOH\_z\_dM.dat}, and \texttt{302-f14SB-Boco\_FMR270\_FOH\_z\_dM.dat} from \cite{Chruslinska+2021}\footnote{These models including a detailed description of their contents  are publicly available at \url{https://ftp.science.ru.nl/astro/mchruslinska/Chruslinska_et_al_2021/} } as a representation of a very low and high metallicity star formation realisation respectively.
+These models are the low and high metallicity extreme under their fiducial SFR–metallicity correlation, and so we will refer to them as \texttt{Chr21\_lowZ} and \texttt{Chr21\_highZ} respectively from hereon.
 The difference between these models lies in the assumptions in the underlying empirical galaxy relations.
 In general, low-mass galaxies contribute to low-metallicity star formation and shift the peak of \SFRDzZ to lower metallicities.
-}
-% lowZ model: 2: sharp flattening (high mass part of the SFMR), 1: alpha\_fix(z) (low mass end of the GSMF), 4: PP04 (MZR at $z\approx0$) -- 
-% Starburst galaxies are treated as in BiC : the properties of starbursts are based on the studies of Bisigello+18 and Caputi+17 -- 
-% nabla\_FMR0 = 0.27 dex, describing the strength of the SFR-metallicity correlation in the high SFR, low mass regime. }
 %
-\edit1{\texttt{Chr21\_lowZ} is characterised by a star formation–galaxy mass relation that is flat at high galaxy masses (reducing the star formation rate for the highest-mass galaxies), a galaxy stellar mass function that evolves with redshift (predicting an increasing number density of low-mass galaxies),
+\texttt{Chr21\_lowZ} is characterised by a star formation–galaxy mass relation that is flat at high galaxy masses (reducing the star formation rate for the highest-mass galaxies), a galaxy stellar mass function that evolves with redshift (predicting an increasing number density of low-mass galaxies),
 and a local galaxy mass-metallicity relation as in \cite{PettiniPagel2004}. 
@@
 lower metallicities and broadens the low-metallicity part of the distribution.
-}
-% highZ model: 3: no flattening (high mass part of the SFMR), 0: alpha\_fix = -1.45 (low mass end of the GSMF), 2: KK04a (MZR at $z\approx0$) --  
-% Starburst galaxies are treated as in  Boco : the properties of starbursts are based on the studies of Sargent+12/Bethermin+12, as used in Boco+21. -- 
-% nabla\_FMR0 = 0.27 dex, describing the strength of the SFR-metallicity correlation in the high SFR, low mass regime.}
+
 %
-\edit1{On the other hand, \texttt{Chr21\_highZ} assumes the star formation–galaxy mass relation does not flatten towards higher galaxy masses, a galaxy stellar mass function where the slope for the low-mass end is constant over redshift, and a local galaxy mass-metallicity relation following \cite{KobulnickyKewley2004}.
+On the other hand, \texttt{Chr21\_highZ} assumes the star formation–galaxy mass relation does not flatten towards higher galaxy masses, a galaxy stellar mass function where the slope for the low-mass end is constant over redshift, and a local galaxy mass-metallicity relation following \cite{KobulnickyKewley2004}.
 Lastly, this model adopts the starburst prescription from \cite{Boco+2021}, which produces results that are similar to models without starburst galaxies.
-}
-
 %
@@
 For every variation of our model, we inspect both the full \SFRDzZ and slices at redshifts $z = 0, 0.5, 3.0$ and $6$ by eye.
-At each slice we compare our model variation to \edit1{\texttt{Chr21\_lowZ} and \texttt{Chr21\_highZ}}, and ensure that none of our variations significantly exceeds these extremes in \SFRDzZ.
+At each slice we compare our model variation to \texttt{Chr21\_lowZ} and \texttt{Chr21\_highZ}, and ensure that none of our variations significantly exceeds these extremes in \SFRDzZ.
 This also serves as a sanity check for the overall star-formation rate density.
 
-We also consider two variations of the overall star-formation rate density, \SFRDz, where we keep the metallicity distribution \dpdZ fixed, but vary all four \SFRDz parameters at once (right two columns of Table \ref{tab: fit params} \edit1{, and bottom of Table \ref{tab: fit variations} }).
+We also consider two variations of the overall star-formation rate density, \SFRDz, where we keep the metallicity distribution \dpdZ fixed, but vary all four \SFRDz parameters at once (right two columns of Table \ref{tab: fit params}, and bottom of Table \ref{tab: fit variations}).
 We use Figure 11 from \cite{Chruslinska+2021} to determine approximate upper and lower bounds to the overall star-formation rate density.
 We choose \cite{Madau+2017} as an approximation of the lower limit.
-For the upper limit, we use the upper edge of 
-\edit1{ models that adopt starbursts following \cite{Bisigello+2018} and \cite{Caputi+2017} (\texttt{SB: B18/C17}), combined}
-with a non-evolving low-mass end of the galaxy stellar mass function \citep[shown as a thick brown line in Fig. 11 of ][and described in their table B1]{Chruslinska+2021}.
+For the upper limit, we use the upper edge of models that adopt starbursts following \cite{Bisigello+2018} and \cite{Caputi+2017} (\texttt{SB: B18/C17}), combined with a non-evolving low-mass end of the galaxy stellar mass function \citep[shown as a thick brown line in Fig.
+11 of ][and described in their table B1]{Chruslinska+2021}.
 % for the \texttt{SB: B18/C17} model variations (i.e.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{\edit1{Evaluating our fit; the squared residuals \label{app: residuals} } }
+\section{Evaluating our fit; the squared residuals \label{app: residuals} }
 
@@
 
-\edit1{In the left panel of Figure \ref{fig: residuals}, we show the $\log$ of the absolute residuals.
+\edit2{In the left panel of Figure \ref{fig: residuals}, we show the $\log$ of the absolute residuals.
 The \textit{square} of the residuals is used in the cost function, equation \ref{eq: cost function}, to optimise our fit.

### 2023-02-27 src/tex/article.tex
removed line numbers

@@
 % Define document class
-\documentclass[linenumbers,twocolumn]{aastex631}
+\documentclass[twocolumn]{aastex631}
 \usepackage{showyourwork}
@@
 Our best fitting parameters are listed in Table \ref{tab: fit params}. With these fit parameters, $\chi^2(z_j)$ is smaller than $2\cdot 10^{-4}$ at any given redshift. 
-To evaluate our fit, we show the residuals in Appendix \ref{app: residuals}. 
+To evaluate our fit, we show \edit2{the absolute residuals and relative errors} in Appendix \ref{app: residuals}. 
 We will refer to the \SFRDzZ with the parameters listed in Table \ref{tab: fit params} as our fiducial model.
@@
 Another regime where the relative error becomes large is at very high metallicities (about 10 times $Z_{\odot}$).
-In this regime, the TNG data is very sparse and contains regions where the rate abruptly drops to zero.
+This is because in this regime, the TNG data is very sparse and contains regions where the rate abruptly drops to zero.
 To avoid sharp features in the data, we use interpolated TNG data to produce the fit.
@@
 We note that we chose to minimise the squared residuals (which is similar to minimising the mean squared error) in favour of minimising, for example, the relative error, to prevent overfitting such regions of very low star-formation rate.
-For the illustration purposes in this work, we are most interested in closely fitting the \SFRDzZ between the minimum ($10^{-4}$) and maximum ($0.03$) metallicities that can be simulated with \COMPAS (or more generally, with population synthesis simulations).
+For the illustration purposes in this work, we are most interested in closely fitting the \SFRDzZ between the minimum ($10^{-4}$) and maximum ($0.03$) metallicities that can be simulated with \COMPAS.
 For applications that focus on extremely low ($<0.01 Z_{\odot}$) or extremely high ($\sim 10\times Z_{\odot}$) metallicity star formation, a different cost function would be more appropriate.}

### 2023-02-27 src/tex/article.tex
removed \edits

@@
 \citealt{chruslinska2022_review} for a discussion on the validity on this assumption).
-\edit2{We write the metallicity-dependent cosmic star formation history as}
+We write the metallicity-dependent cosmic star formation history as
 
@@
 \end{equation}
-\edit2{(similar to e.g., \citealt{LangerNorman2006}).}
+(similar to e.g., \citealt{LangerNorman2006}).
 The first term is the star formation rate density, \SFRDz, that is the amount of mass formed in stars per unit time and per unit comoving volume at each redshift, $z$.
@@
 Our best fitting parameters are listed in Table \ref{tab: fit params}. With these fit parameters, $\chi^2(z_j)$ is smaller than $2\cdot 10^{-4}$ at any given redshift. 
-To evaluate our fit, we show \edit2{the absolute residuals and relative errors} in Appendix \ref{app: residuals}. 
+To evaluate our fit, we show the absolute residuals and relative errors in Appendix \ref{app: residuals}. 
 We will refer to the \SFRDzZ with the parameters listed in Table \ref{tab: fit params} as our fiducial model.
@@
 
-\edit2{In the left panel of Figure \ref{fig: residuals}, we show the $\log$ of the absolute residuals.
+In the left panel of Figure \ref{fig: residuals}, we show the $\log$ of the absolute residuals.
 The \textit{square} of the residuals is used in the cost function, equation \ref{eq: cost function}, to optimise our fit.
@@
 For the illustration purposes in this work, we are most interested in closely fitting the \SFRDzZ between the minimum ($10^{-4}$) and maximum ($0.03$) metallicities that can be simulated with \COMPAS.
-For applications that focus on extremely low ($<0.01 Z_{\odot}$) or extremely high ($\sim 10\times Z_{\odot}$) metallicity star formation, a different cost function would be more appropriate.}
+For applications that focus on extremely low ($<0.01 Z_{\odot}$) or extremely high ($\sim 10\times Z_{\odot}$) metallicity star formation, a different cost function would be more appropriate.
 
